### 2016-12-06 submission/Schloss_PrePrints_mBio_2017.Rmd
Get paper to render for the first time

---
title: "**Pre-prints**"
bibliography: reference.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: mbio.csl
fontsize: 11pt
geometry: margin=1.0in
---

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
library(dplyr, warn.conflicts=FALSE)
library(tidyr)
library(knitr)

opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

inline_hook <- function(x){
	print(x)
	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=2, nsmall=2, scientific=FALSE))
		}

	} else {
    	paste(x)      
	}
}
knitr::knit_hooks$set(inline=inline_hook)

```

\begin{center}
\vspace{25mm}
Patrick D. Schloss${^\dagger}$

\vspace{30mm}

$\dagger$ To whom correspondence should be addressed: pschloss@umich.edu

Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
\end{center}

\newpage
\linenumbers

## Abstract

\newpage

## Introduction

### 2016-12-06 submission/Schloss_PrePrints_mBio_2017.Rmd
Outline paper

@@
 
+## Importance
+
 \newpage
@@
 ## Introduction
+* Better represents the scientific method
+* ASM Policies towards Pre-prints
+	* Bring 'em on
+	* Citable
+	* Direct submission
+	* mSphereDirect
+
+## Critiques
+* Half-baked science
+	* Sure. What's your point
+	* Post-publication peer review
+* Will get scooped
+	* No, PP establish priority
+
+## Pre-print host landscape
+* Review different sites
+* Licensing
+* Cost
+* Opportunity for comments
+
+## Pre-prints in microbiology
+* Rate of use among PP describing microbiology research over time
+* Number of revisions
+* Number of downloads
+* Number of PP published
+
+## Anecdotes
+* MinIon methods
+* PacBio paper
+* Tardigrade microbiome
+* NYC subway microbiome
+
+\newpage
+
+## References

### 2017-01-04 code/aggregate_biorxiv_altmetric_data.R
If file not found, it has no score

@@ -12,8 +12,8 @@ aggregate_alt_data <- function(alt_file){
 		altmetric <- alt_json$score
 		altmetric_pct <- alt_json$context$all$pct
 	} else {
-		altmetric <- NA
-		altmetric_pct <- NA
+		altmetric <- 0
+		altmetric_pct <- 0
 	}
 
 	list(article_id=article_id, altmetric=altmetric, altmetric_pct=altmetric_pct)

### 2017-01-04 code/aggregate_asm_altmetric_data.R
Aggregate ASM journals' altmetric data

@@ -1,0 +1,34 @@
+library(rjson)
+library(dplyr)
+options(stringsAsFactors=FALSE)
+
+aggregate_alt_data <- function(alt_file){
+	# print(alt_file)
+
+	article_id <- gsub("data/asm_altmetric/(.*).json", "\\1", alt_file)
+
+	json_file <- readLines(alt_file, warn=F)
+
+	if(json_file != "Not Found"){
+		alt_json <- fromJSON(json_file)
+		altmetric <- alt_json$score
+		altmetric_pct <- alt_json$context$all$pct
+		altmetric_pct <- ifelse(is.null(altmetric_pct), NA, altmetric_pct)
+	} else {
+		altmetric <- 0
+		altmetric_pct <- 0
+	}
+
+	list(article_id=article_id, altmetric=altmetric, altmetric_pct=altmetric_pct)
+}
+
+altmetrics_files <- list.files(path="data/asm_altmetric", pattern="*.json", full.names=T)
+alt_listed <- lapply(altmetrics_files, aggregate_alt_data)
+alt_df <- do.call(rbind.data.frame, alt_listed)
+
+date <-read.table(file="data/asm_doi_urls.tsv", header=F, stringsAsFactors=F)
+date$V1 <- gsub("http://dx.doi.org/10.1128/(.*)", "data/asm_altmetric/\\1.json", date$V1)
+stopifnot(altmetrics_files == date$V1)
+alt_df[,"date"] <- date$V2
+
+write.table(alt_df, "data/asm_altmetric/altmetric_summary.tsv", sep='\t', quote=F, row.names=F)

### 2017-01-05 submission/Schloss_PrePrints_mBio_2017.Rmd
Fill in background information in manuscript

--- 2016-12-06 submission/Schloss_PrePrints_mBio_2017.Rmd
@@
 ---
-title: "**Pre-prints**"
+title: "**Preprinting Microbiology**"
 bibliography: reference.bib
@@
 
+library(rjson)
+biorxiv <- fromJSON(readLines('data/processed/biorxiv_data_summary.json'))
+
 ```
@@
 
+## Importance
+
 \newpage
 
-## Introduction
+Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to engage their peers and non-scientists.
+Preprints have emerged as a formal venue for microbiologists to disseminate their research.
+A preprint is an unpublished manuscript that is made publicly available without going through an official peer-review process.
+Rather, an author can post their manuscript to a preprint server for others to read, share, and make comments.
+Preprints were initially adopted among physicists in the 1960s as a method of sharing interesting research amongst colleagues.
+Eventually, this community evolved into what is now the arXiv (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University.
+Among physicists and mathematicians, posting a preprint to arXiv has become the standard publication strategy followed by submission to a peer-reviewed journal.
+Within those communities researchers have been recognized with international awards for work that has only been posted to arXiv without formal review.
+Although arXiv has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
+Among the proponents of arXiv, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception.
+As adoption of preprints as a component of the scientific method has broadened among biologists, we sought to explore the specific use and concerns of preprints amongst microbiologists.
+
+***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in pursuing preprints as a stage in disseminating their research was whether it constituted prior publication.
+The broad consensus at this point is that preprints do not constitute prior publication.
+To briefly summarize journals of interest to many microbiologists, journals published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the Proceedings of the National Academy of Science, Science, and Nature have a permissive stance towards prior posting of preprints prior to submission.
+Although journals published by Cell do not forbid authors from posting preprints prior to submission, they ask authors to consult an editor prior to posting and do not allow authors to post revised preprints that contain revisions that respond to editorial input.
+Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work.
+Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated.
+
+***Landscape of preprint servers.*** Two preprint servers have sought to parallel the success of arXiv.
+In 2013, the bioRxiv (pronounced "bio-archive") was launched through Cold Spring Harbor Laboratory as a service to complement arXiv; PeerJ Preprints was initiated at the same time.
+Both options have similar features: preprint posting is free; each preprint receives a a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically posted in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
+There are several important differences between the two options.
+First, PeerJ as a for-profit organization and bioRxiv is a non-profit organization.
+This can be meaningful to authors since some journals, including the ASM Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations.
+Second, preprints at PeerJ Preprints are posted under the Creative Commons Attribution License (CC-BY) and bioRxiv preprints can be posted under one of four CC-BY licenses or with no permission for reuse.
+This can be relevant for authors hoping to submit their work a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g.
+*Proceedings of the National Academy of Sciences*).
+A cosmetic, but important difference between the two is the layout and feel of the two websites.
+Compared to the bioRxiv site, the PeerJ Preprint site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints.
+With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on bioRxiv.
+It is only possible to transfer a PeerJ Preprint for submission to PeerJ.
+In many ways, preprint servers have taken on the feel of a journal.
+As adoption of this approach to disseminating research expands, it is likely that the features of these sites will continue to improve.
+It is also likely that interfaces from third-parties will improve.
+For example, although Google Scholar includes preprints hosted at bioRxiv and PeerJ Preprints in their search results, PubMed does not.
+There is hope that the National Institutes of Health (NIH) will renew their interest in including preprints in PubMed search results.
+
+***Preprints and peer-review.*** The traditional peer-review editorial process was adapted to the technologies and trends that have evolved over the past 100 years.
+The formal peer-review system that most journals currently use was not developed until the end of the 1800s with the advent of typewriters and carbon paper (doi:10.1016/S0167-7799(02)01985-6).
+Editorial decisions were typically made by a single person or a committee (i.e.
+the editorial board) who had an expertise that covered the scope of the journal.
+As people's science became more specialized new journals would form providing a source of  validation to the new specialty.
+The growth in science in the mid 1900s resulted in a shift from difficulties finding sufficient numbers of manuscript to publish to having too many manuscripts submitted.
+It has been argued that the widespread adoption of peer review was due to the increased specialization and to deal with the large number of manuscript submissions (JAMA 1990;263:1323-1329).
+Peer-review did not achieve widespread use at many journals, including the Journal of Bacteriology, until the 1940 and 1950s.
+Given the rapid advances in communication technology and even greater specialization, it is worth pondering whether the current scientific publishing system and peer review system, in particular, needs to continue to adapt with our science.
+
+Communicating research has traditionally be done within research group meetings, departmental seminars, conferences, and as publications.
+Along this continuum, there is the assumption that the quality of the science has been improved because it has been vetted by more experts in the field.
+The public dissemination of one's research is a critical component of the scientific method.
+By describing their research, scientists subject their work to formal and informal peer review.
+Their research is scrutinized, praised, and probed to identify questions that help seed the next iteration of the scientific method.
+A common critique of these more modern approaches to publishing has been an inability to assess the quality of the science without the validation of peer-review.
+Attached to assertions of the validity of the research has become assertions of the impact and robustness of the research.
+These are all quality assessments that many acknowledge are difficult to assess by the traditional peer-review process.
+This has led to some to call for peer reviewers to place a reduced emphasis on the impact or significance of the work as pioneered by the journal PLOS ONE.
+It has also led to the call for replacing or complementing pre-publication peer review with post-publication peer review using PubMed Commons, PubPeer, journal-based discussion forums, and other mechanisms.
+Alas if scientists are going to depend on post-publication peer review or informal methods of peer-review, they must be willing to provide constructive feedback on the work of others.
+
+***Preprints have the potential to change how science is measured.*** Preprints are often viewed as existing in a state of scientific limbo.
+They represent a formal communication, but are not "published".
+As the use of preprints grows and our perceptions of preprints matures, there are a number of issues that will need to be addressed.
+First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the original researcher will lose their ability to claim primacy or their ability to publish the work in a journal.
+Considering the preprint is a citable work with a DOI, it would, in fact, be the original researcher that scooped the second.
+A growing number of scientific societies and journals, including ASM view preprints as citable and as a legitimate claim to primacy.
+Some worry that with such protection a researcher can make a claim without valid data to back it up.
+This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data.
+A second area of concern is whether a preprint can be used to support a grant proposal.
+Given the length limitations of many funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data.
+Some fear that the use of preprints will allow some to circumvent page limits by posting a half-baked manuscript.
+We would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
+A third concern is what role preprints should have in assessing a scientist's productivity.
+Clearly use of publication metrics is a contentious topic without considering the place of preprints.
+Regardless, given the propensity for researchers to list manuscripts as being "in preparation" on an application or curriculum vitae, listing them instead as preprints that can be reviewed by a committee could be seen as a significant way to enhance an application.
+In fact, several funding agencies are starting to encourage fellowship applicants to include preprints in their materials and others are requiring researchers to post preprints for all of their work.
+It is clear that the adoption of preprints will challenge how scientists interact and evaluate each other's work; however, it appears that there is great potential to empower researchers by controlling when a citable piece of work is made public.
+
+***The use of preprints from an author's perspective.*** Posting research as a preprint gives an author great control over when their work is made public.
+Under the traditional peer-review model, an author may need to submit and revise their work multiple times over a long period.
+In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process.
+A first example illustrate the utility of preprints for improving access to research and the quality of its reporting.
+In 2014, the Schloss laboratory posted a preprint to PeerJ Preprints describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform.
+At the same time, we submitted for review at PeerJ.
+While it was under review, we received feedback from someone that read the preprint as well as from Pacific Biosciences that the impact of the results could be limited because of the sequencing chemistry.
+Instead of resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to PeerJ that incorporated the original reviews as well as the feedback we received from Pacific Biosciences and the independent scientist.
+In general, the Schloss laboratory has simultaneously posted our manuscripts as preprints and submitted them to a journal.
+As a second example, this manuscript was posted to bioRxiv as a preprint on XXXXXXX XX, 2017.
+We then solicited feedback on the manuscript using social media.
+Two weeks later, we incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
+During those two weeks the abstract was read XXXX times and the PDF was accessed XXXX times.
+This process engaged XXXX commenters on bioRxiv, XXXX people on Twitter, XXXX on Facebook, and XXXX via email.
+We received useful feedback from XXX people.
+Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had we foregone the posting of a preprint.
+Although there are concerns regarding the quality of the science posted to a preprint server, we contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.
+
+## Preprints in microbiology
+* Rate of use among PP describing microbiology research over time
+* Number of revisions
+* Number of downloads
+* Number of PP published
+
+## Microbiology anecdotes
+* MinIon methods
+* PacBio paper
+* Tardigrade microbiome
+* NYC subway microbiome
+
+## Specific challenges for microbiology
+* Dual use
+* Protection of human subjects
+* Conflicts of interest
+
+## Perspective
+* Support priority in literature
+* Support citation
+* Direct submission
+* preprint scouts
+* mSphereDirect / F1000Prime
+* Licensing
+* What's in it for ASM Journals and Readers?
+
+\newpage
+
+## References

### 2017-01-06 submission/Schloss_PrePrints_mBio_2017.Rmd

@@
 
+## Background
+
 Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to engage their peers and non-scientists.
@@
 Preprints were initially adopted among physicists in the 1960s as a method of sharing interesting research amongst colleagues.
-Eventually, this community evolved into what is now the arXiv (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University.
-Among physicists and mathematicians, posting a preprint to arXiv has become the standard publication strategy followed by submission to a peer-reviewed journal.
-Within those communities researchers have been recognized with international awards for work that has only been posted to arXiv without formal review.
-Although arXiv has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
+Eventually, this community evolved into what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University.
+Among physicists and mathematicians, posting a preprint to *arXiv* has become the standard publication strategy followed by submission to a peer-reviewed journal.
+Within those communities researchers have been recognized with international awards for work that has only been posted to *arXiv* without formal review.
+Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
 Among the proponents of arXiv, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception.
@@
 ***Landscape of preprint servers.*** Two preprint servers have sought to parallel the success of arXiv.
-In 2013, the bioRxiv (pronounced "bio-archive") was launched through Cold Spring Harbor Laboratory as a service to complement arXiv; PeerJ Preprints was initiated at the same time.
+In 2013, the *bioRxiv* (pronounced "bio-archive") was launched through Cold Spring Harbor Laboratory as a service to complement arXiv; *PeerJ Preprints* was initiated at the same time.
 Both options have similar features: preprint posting is free; each preprint receives a a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically posted in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
 There are several important differences between the two options.
-First, PeerJ as a for-profit organization and bioRxiv is a non-profit organization.
+First, PeerJ as a for-profit organization and *bioRxiv* is a non-profit organization.
 This can be meaningful to authors since some journals, including the ASM Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations.
-Second, preprints at PeerJ Preprints are posted under the Creative Commons Attribution License (CC-BY) and bioRxiv preprints can be posted under one of four CC-BY licenses or with no permission for reuse.
+Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse.
 This can be relevant for authors hoping to submit their work a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g.
@@
 A cosmetic, but important difference between the two is the layout and feel of the two websites.
-Compared to the bioRxiv site, the PeerJ Preprint site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints.
+Compared to the *bioRxiv* site, the PeerJ Preprint site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints.
 With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on bioRxiv.
@@
 It is also likely that interfaces from third-parties will improve.
-For example, although Google Scholar includes preprints hosted at bioRxiv and PeerJ Preprints in their search results, PubMed does not.
+For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed does not.
 There is hope that the National Institutes of Health (NIH) will renew their interest in including preprints in PubMed search results.
@@
 A first example illustrate the utility of preprints for improving access to research and the quality of its reporting.
-In 2014, the Schloss laboratory posted a preprint to PeerJ Preprints describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform.
+In 2014, the Schloss laboratory posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform.
 At the same time, we submitted for review at PeerJ.
@@
 Instead of resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to PeerJ that incorporated the original reviews as well as the feedback we received from Pacific Biosciences and the independent scientist.
-In general, the Schloss laboratory has simultaneously posted our manuscripts as preprints and submitted them to a journal.
-As a second example, this manuscript was posted to bioRxiv as a preprint on XXXXXXX XX, 2017.
+In general, our research group has simultaneously posted our manuscripts as preprints and submitted them to a journal.
+As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **XXXXXXX XX, 2017**.
 We then solicited feedback on the manuscript using social media.
 Two weeks later, we incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
-During those two weeks the abstract was read XXXX times and the PDF was accessed XXXX times.
-This process engaged XXXX commenters on bioRxiv, XXXX people on Twitter, XXXX on Facebook, and XXXX via email.
-We received useful feedback from XXX people.
+During that time, the abstract was read **XXXX** times and the PDF was accessed **XXXX** times.
+This process engaged **XXXX** commenters on bioRxiv, **XXXX** people on Twitter, **XXXX** on Facebook, and **XXXX** via email.
+We received useful feedback from **XXX** people.
 Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had we foregone the posting of a preprint.
@@
 ## Preprints in microbiology
-* Rate of use among PP describing microbiology research over time
-* Number of revisions
-* Number of downloads
-* Number of PP published
 
-## Microbiology anecdotes
+***Preprint metrics in microbiology.*** To analyze the use of preprints, we copied the bioRxiv website on December 31, 2016.
+We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r length(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*.
+Among the `r length(biorxiv)` preprints on bioRxiv, **XXXX** were assigned by the authors into the Microbiology category.
+When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified **XXXX** additional manuscripts.
+These microbiology-affiliated preprints were primarily assigned to the **XXXX (N=XX)**, **XXXX (N=XX)**, or **XXXX (N=XX)** categories.
+One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint.
+For example, this manuscript could be assigned to either the Microbiology or Scientific Communication and Education categories.
+
+Questions:
+* How many preprints are being submitted each month - microbiology category and microbiology-ish
+* What fraction of PPs are now published that were deposited before January 1, 2016?
+* How many times is each preprint revised (perhaps looking at those that have been published)
+* How do PP altmetrics compare to ASM altmetrics over the same time span?
+* Where do microbiology/microbiology-affiliated preprints come from?
+* How many microbiology/microbiology-affiliated preprints do people submit?
+
+* Distribution of downloads
+* Distribution of abstract hits
+
+* Would love to calculate a JIF of preprints with and without those that have not yet been published.
+
+***Microbiology anecdotes.***
 * MinIon methods
@@
 
-## Specific challenges for microbiology
+***Specific challenges for microbiology.***
 * Dual use
@@
 * What's in it for ASM Journals and Readers?
+* Kills the splash for a paper when it's actually published - author wins, journal loses
 

### 2017-01-06 code/aggregate_biorxiv_data_sources.R
Convert from JSON to tsv

@@ -58,7 +58,8 @@ collect_data <- function(base_file){
 										html_text() %>%
 										gsub("[\t\n]", "", .) %>%
 										gsub ("^\\d*", "", .) %>%
-										gsub ("^\\s*", "", .)
+										gsub ("^\\s*", "", .) %>%
+										.[[1]]
 
 		#n_versions
 		n_versions <- info_page %>%
@@ -72,7 +73,8 @@ collect_data <- function(base_file){
 			date_first_deposited <- info_page %>%
 																html_nodes(".hw-version-previous-link") %>%
 																html_text() %>%
-																gsub("Previous version \\((.*) - .*\\)\\.", "\\1", .)
+																gsub("Previous version \\((.*) - .*\\)\\.", "\\1", .) %>%
+																.[[1]]
 		}
 
 		#journal_published
@@ -158,7 +160,7 @@ collect_data <- function(base_file){
 
 	} else {
 		doi <- doi
-		authors <- NA
+		# authors <- NA
 		first_author <- NA
 		corr_author <- NA
 		corr_author_email <- NA
@@ -168,6 +170,7 @@ collect_data <- function(base_file){
 		journal_published <- NA
 		category <- NA
 		is_microbiology <- NA
+		license <- NA
 		abstract_downloads <- NA
 		pdf_downloads <- NA
 		n_comments <- NA
@@ -177,7 +180,7 @@ collect_data <- function(base_file){
 
 	list(
 		doi=doi,
-		authors=authors,
+		# authors=authors,
 		first_author=first_author,
 		corr_author=corr_author,
 		corr_author_email=corr_author_email,
@@ -187,6 +190,7 @@ collect_data <- function(base_file){
 		journal_published=journal_published,
 		category=category,
 		is_microbiology=is_microbiology,
+		license <- license,
 		abstract_downloads=abstract_downloads,
 		pdf_downloads=pdf_downloads,
 		n_comments=n_comments,
@@ -197,7 +201,7 @@ collect_data <- function(base_file){
 }
 
 base_files <- list.files(path='data/biorxiv', pattern="^\\d{6}$", full.names=T)
-results <- lapply(base_files, collect_data)
+results_list <- lapply(base_files, collect_data)
+results <- do.call(rbind.data.frame, results_list)
 
-results_json <- toJSON(results)
-write(results_json, "data/processed/biorxiv_data_summary.json")
+write.table(results, "data/processed/biorxiv_data_summary.tsv", quote=F, sep='\t')

### 2017-01-06 code/aggregate_biorxiv_data_sources.R
Fix NA bug in getting affiliation

@@ -1,7 +1,6 @@
 library(httr)
 library(rvest)
 library(dplyr)
-library(rjson)
 
 disqus_count <- read.table(file="data/biorxiv_disqus/comment_count.tsv", header=T, stringsAsFactors=F,
 												colClasses=c("character", "numeric"))
@@ -58,8 +57,13 @@ collect_data <- function(base_file){
 										html_text() %>%
 										gsub("[\t\n]", "", .) %>%
 										gsub ("^\\d*", "", .) %>%
-										gsub ("^\\s*", "", .) %>%
-										.[[1]]
+										gsub ("^\\s*", "", .)
+		if(length(affiliation) != 0){
+			affiliation <- affiliation[1]
+		} else {
+			affiliation <- NA
+		}
+
 
 		#n_versions
 		n_versions <- info_page %>%
@@ -67,7 +71,11 @@ collect_data <- function(base_file){
 												length() + 1
 
 		#date_first_deposited
-		date_first_deposited <- info_page %>% html_nodes(".publication-history") %>% html_text() %>% .[[2]] %>% gsub("Posted (.*)\\.", "\\1", .)
+		date_first_deposited <- info_page %>%
+											html_nodes(".publication-history") %>%
+											html_text() %>%
+											.[[2]] %>%
+											gsub("Posted (.*)\\.", "\\1", .)
 
 		if(n_versions > 1){
 			date_first_deposited <- info_page %>%

### 2017-01-06 code/aggregate_biorxiv_data_sources.R
Trying to find bug

@@ -2,8 +2,8 @@ library(httr)
 library(rvest)
 library(dplyr)
 
-disqus_count <- read.table(file="data/biorxiv_disqus/comment_count.tsv", header=T, stringsAsFactors=F,
-												colClasses=c("character", "numeric"))
+disqus_count <- read.table(file="data/biorxiv_disqus/comment_count.tsv", header=T,
+												stringsAsFactors=F, colClasses=c("character", "numeric"))
 
 altmetric_score <- read.table(file="data/biorxiv_altmetric/altmetric_summary.tsv", header=T,
 												stringsAsFactors=F, colClasses=c("character", "numeric", "numeric"))

### 2017-01-06 submission/Schloss_PrePrints_mBio_2017.Rmd
Rough in analysis section

@@
 knitr::knit_hooks$set(inline=inline_hook)
-
-library(rjson)
-biorxiv <- fromJSON(readLines('data/processed/biorxiv_data_summary.json'))
 
@@
 
+```{r analysis}
+library(dplyr)
+
+biorxiv <- read.table(file = 'data/processed/biorxiv_data_summary.tsv')
+
+```
 ## Preprints in microbiology
 
-***Preprint metrics in microbiology.*** To analyze the use of preprints, we copied the bioRxiv website on December 31, 2016.
+***Metrics for microbiology preprints.*** To analyze the use of preprints, we copied the bioRxiv website on December 31, 2016.
 We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r length(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*.
 Among the `r length(biorxiv)` preprints on bioRxiv, **XXXX** were assigned by the authors into the Microbiology category.
-When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified **XXXX** additional manuscripts.
+When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified **XXXX** additional manuscripts (**Figure 1**).
 These microbiology-affiliated preprints were primarily assigned to the **XXXX (N=XX)**, **XXXX (N=XX)**, or **XXXX (N=XX)** categories.
@@
 For example, this manuscript could be assigned to either the Microbiology or Scientific Communication and Education categories.
+Reflecting the still relatively novelty of preprints, **XX** (**XX**%) corresponding authors who submitted a microbiology-affiliated manuscript (N=**XXX** total) have posted a single preprint and **XX**% have submitted more than 3.
+Corresponding authors that have posted microbiology-affiliated preprints are primarily affiliated with institutions in the United States (**XX**%), **XXXXX XXXXXX** (**XX**%),  and **XXXXX XXXXXX** (**XX**%).
 
-Questions:
-* How many preprints are being submitted each month - microbiology category and microbiology-ish
-* What fraction of PPs are now published that were deposited before January 1, 2016?
-* How many times is each preprint revised (perhaps looking at those that have been published)
-* How do PP altmetrics compare to ASM altmetrics over the same time span?
-* Where do microbiology/microbiology-affiliated preprints come from?
-* How many microbiology/microbiology-affiliated preprints do people submit?
+As stated above, preprints offer researchers the opportunity to improve the quality of their work by adding a more formal and public step to the scientific process.
+Among the microbiology-affiliated manuscripts, only **XX** (**XX**%) had been commented on at least once and only **XX** (**XX**%) more than three times using the *bioRxiv*-hosted commenting feature.
+Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
+Regardless, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as they post a median of **XX** versions of each preprints (IQR: **XX-XX**).
+Among the preprints posted prior to January 1, 2016, **XXX**% of the Microbiology category preprints, **XX**% of the microbiology-affiliated preprints, and **XX**% of all preprints have been published.
+Considering that these "acceptance rates" are relatively high compared to most peer-reviewed journals (e.g.
+25% at ASM Journals), these results would appear to dispel the critique that preprints represent overly preliminary research.
 
-* Distribution of downloads
-* Distribution of abstract hits
-
-* Would love to calculate a JIF of preprints with and without those that have not yet been published.
+Measuring the impact and significance of scientific research is notoriously difficult.
+Using several metrics, we sought to quantify the effect that preprints have had on the scholarly work of others.
+Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was **XXX** (IQR: **XX-XX**) and **XXX** (IQR: **XX-XX**), respectively.
+These values represent two aspects of posting a preprint.
+First, they reflect the number of times people were able to access science before it was published.
+Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall.
+To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint.
+This score measures the number of times a preprint or paper is mentioned in social media, mainstream media, peer reviews, and policy documents.
+Microbiology-affiliated preprints have had a median Altmetric Attention Score of **XXX** (IQR: **XX-XX**) and those of all preprints hosted at *bioRxiv* have had a median score of **XXX** (IQR: **XX-XX**).
+For comparison, the median Altmetric Attention Score for ASM journal articles for articles posted since November 2013 was **XXX** (IQR: **XX-XX**).
+A more traditional and controversial metric of impact has been the number of citations an article receives.
+We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints.
+To allow for a comparison to traditional journals, we considered the citations for preprints posted in 2014 and 2015 as aggregated by Web of Science.
+Among the preprints that were published, the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**) and if unpublished preprints were included the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**).
+These values are comparable to many popular microbiology journals.
+*Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community*
 
@@
 * MinIon methods
-* PacBio paper
 * Tardigrade microbiome
@@
 
-***Specific challenges for microbiology.***
-* Dual use
-* Protection of human subjects
-* Conflicts of interest
+***Specific challenges for microbiology.*** Although preprints offer an efficient and novel venue for disseminating microbiology research, there are several considerations that the scientific community and those that oversee preprint servers must consider.
+It is critical that assurances be given that policies are in place to address these issues.
+First, a significant amount of attention has been given to the potential dual use of microbiology research for individuals seeking to engage in terrorist activities.
+Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research.
+Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results.
+Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism.
+Microbiology journals have policies in place to address these issues that should be easily implemented by preprint servers.
 
@@
 ## References
+
+## Figures
+
+**Figure 1. **
+* How many preprints are being submitted each month - microbiology category and microbiology-ish

### 2017-01-06 code/aggregate_biorxiv_data_sources.R
Correct weirdness in the category and license label

@@ -109,7 +109,8 @@ collect_data <- function(base_file){
 		category <- article_page %>%
 									html_nodes(".highwire-article-collection-term") %>%
 									html_text() %>%
-									gsub("\n", "", .)
+									gsub("\n", "", .) %>%
+									.[[1]]
 
 		#is_microbiology
 		test_is_microbiology <- function(x){
@@ -198,7 +199,7 @@ collect_data <- function(base_file){
 		journal_published=journal_published,
 		category=category,
 		is_microbiology=is_microbiology,
-		license <- license,
+		license = license,
 		abstract_downloads=abstract_downloads,
 		pdf_downloads=pdf_downloads,
 		n_comments=n_comments,
@@ -210,6 +211,6 @@ collect_data <- function(base_file){
 
 base_files <- list.files(path='data/biorxiv', pattern="^\\d{6}$", full.names=T)
 results_list <- lapply(base_files, collect_data)
-results <- do.call(rbind.data.frame, results_list)
+results <- do.call(rbind, results_list)
 
 write.table(results, "data/processed/biorxiv_data_summary.tsv", quote=F, sep='\t')

### 2017-01-06 code/aggregate_biorxiv_data_sources.R
Correct weirdness in the category and license label

@@ -211,6 +211,6 @@ collect_data <- function(base_file){
 
 base_files <- list.files(path='data/biorxiv', pattern="^\\d{6}$", full.names=T)
 results_list <- lapply(base_files, collect_data)
-results <- do.call(rbind, results_list)
+results <- do.call(rbind.data.frame, results_list)
 
 write.table(results, "data/processed/biorxiv_data_summary.tsv", quote=F, sep='\t')

### 2017-01-06 code/aggregate_biorxiv_data_sources.R
Fix problem with category-less papers

@@ -109,8 +109,12 @@ collect_data <- function(base_file){
 		category <- article_page %>%
 									html_nodes(".highwire-article-collection-term") %>%
 									html_text() %>%
-									gsub("\n", "", .) %>%
-									.[[1]]
+									gsub("\n", "", .)
+		if(length(category) == 0){
+			category <- NA
+		} else {
+			category <- category[1]
+		}
 
 		#is_microbiology
 		test_is_microbiology <- function(x){

### 2017-01-12 code/aggregate_biorxiv_data_sources.R
Remove rownames and wrap strings in quotes

@@ -217,4 +217,4 @@ base_files <- list.files(path='data/biorxiv', pattern="^\\d{6}$", full.names=T)
 results_list <- lapply(base_files, collect_data)
 results <- do.call(rbind.data.frame, results_list)
 
-write.table(results, "data/processed/biorxiv_data_summary.tsv", quote=F, sep='\t')
+write.table(results, "data/processed/biorxiv_data_summary.tsv", quote=T, row.names=F, sep='\t')

### 2017-01-12 submission/Schloss_PrePrints_mBio_2017.Rmd
Add R code to manuscript

@@
 ```{r analysis}
-library(dplyr)
+biorxiv <- read.table(file = 'data/processed/biorxiv_data_summary.tsv', header=T, sep='\t', stringsAsFactors=F)
 
-biorxiv <- read.table(file = 'data/processed/biorxiv_data_summary.tsv')
+asm <- read.table(file= 'data/asm_altmetric/altmetric_summary.tsv', header=T)
+asm$date <- gsub("(\\d\\d\\d\\d)-.*", "\\1", asm$date)
+asm_post_2013 <- asm[asm$date >= 2013,]
 
+lookup <- read.table(file= 'data/processed/country_lookup.tsv', header=T, sep='\t', quote="", stringsAsFactors=F)
+
+non_micro_micro <- biorxiv$is_microbiology & biorxiv$category!="Microbiology"
+non_micro_category_counts <- sort(table(biorxiv[non_micro_micro, "category"]), decreasing=T)
+non_micro_category_names <- names(non_micro_category_counts)
+
+micro_affiliated <- biorxiv$is_microbiology | biorxiv$category == "Microbiology"
+micro_aff_author_counts <- sort(table(biorxiv[micro_affiliated, "corr_author"]), decreasing=T)
+
+micro_aff_institutes <- levels(as.factor(biorxiv[micro_affiliated, "affiliation"]))
+micro_aff_countries_count <- sort(table(lookup[biorxiv[micro_affiliated, "affiliation"], "country"]), decreasing=T)
+micro_aff_countries_percent <- 100 * micro_aff_countries_count / sum(micro_aff_countries_count)
+micro_aff_countries_names <- names(micro_aff_countries_percent)
+
+n_micro_aff_ever_commented <- sum(biorxiv[micro_affiliated, "n_comments"] != 0, na.rm=T)
+n_micro_aff_thrice_commented <- sum(biorxiv[micro_affiliated, "n_comments"] >= 3, na.rm=T)
+
+n_micro_aff_revised <- sum(biorxiv[micro_affiliated, "n_versions"] > 1, na.rm=T)
+
+n_micro_published <- sum(!is.na(biorxiv[biorxiv$category == "Microbiology", "journal_published"]))
+n_micro_aff_published <- sum(!is.na(biorxiv[micro_affiliated, "journal_published"]))
+n_all_published <- sum(!is.na(biorxiv[, "journal_published"]))
 ```
+
 ## Preprints in microbiology
@@
 ***Metrics for microbiology preprints.*** To analyze the use of preprints, we copied the bioRxiv website on December 31, 2016.
-We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r length(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*.
-Among the `r length(biorxiv)` preprints on bioRxiv, **XXXX** were assigned by the authors into the Microbiology category.
-When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified **XXXX** additional manuscripts (**Figure 1**).
-These microbiology-affiliated preprints were primarily assigned to the **XXXX (N=XX)**, **XXXX (N=XX)**, or **XXXX (N=XX)** categories.
+We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*.
+Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category.
+When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts (**Figure 1**).
+These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r r non_micro_category_counts[3]`) categories.
 One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint.
 For example, this manuscript could be assigned to either the Microbiology or Scientific Communication and Education categories.
-Reflecting the still relatively novelty of preprints, **XX** (**XX**%) corresponding authors who submitted a microbiology-affiliated manuscript (N=**XXX** total) have posted a single preprint and **XX**% have submitted more than 3.
-Corresponding authors that have posted microbiology-affiliated preprints are primarily affiliated with institutions in the United States (**XX**%), **XXXXX XXXXXX** (**XX**%),  and **XXXXX XXXXXX** (**XX**%).
+Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r 100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r 100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts)`% have posted 3 or more preprints.
+Corresponding authors that have posted microbiology-affiliated preprints are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%).
 
 As stated above, preprints offer researchers the opportunity to improve the quality of their work by adding a more formal and public step to the scientific process.
-Among the microbiology-affiliated manuscripts, only **XX** (**XX**%) had been commented on at least once and only **XX** (**XX**%) more than three times using the *bioRxiv*-hosted commenting feature.
+Among the microbiology-affiliated manuscripts, `r n_micro_aff_ever_commented` (`r 100*n_micro_aff_ever_commented/sum(micro_affiliated, na.rm=T)`%) had been commented on at least once and only `r n_micro_aff_thrice_commented` (`r 100*n_micro_aff_thrice_commented/sum(micro_affiliated, na.rm=T)`%) more than three times using the *bioRxiv*-hosted commenting feature.
 Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
-Regardless, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as they post a median of **XX** versions of each preprints (IQR: **XX-XX**).
-Among the preprints posted prior to January 1, 2016, **XXX**% of the Microbiology category preprints, **XX**% of the microbiology-affiliated preprints, and **XX**% of all preprints have been published.
-Considering that these "acceptance rates" are relatively high compared to most peer-reviewed journals (e.g.
-25% at ASM Journals), these results would appear to dispel the critique that preprints represent overly preliminary research.
+Regardless, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints are revised at least once.
+Among the preprints posted prior to January 1, 2016, `r 100*n_micro_published/sum(biorxiv$category == "Microbiology", na.rm=T)`% of the Microbiology category preprints, `r 100*n_micro_aff_published/sum(micro_affiliated, na.rm=T)`% of the microbiology-affiliated preprints, and `r 100*n_all_published/nrow(biorxiv)`% of all preprints have been published.
+Considering that these "acceptance rates" are higher than many peer-reviewed journals (e.g.
+approximately 25% at ASM Journals), these results would appear to dispel the critique that preprints represent overly preliminary research.
 
 Measuring the impact and significance of scientific research is notoriously difficult.
-Using several metrics, we sought to quantify the effect that preprints have had on the scholarly work of others.
-Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was **XXX** (IQR: **XX-XX**) and **XXX** (IQR: **XX-XX**), respectively.
+Using several metrics, we sought to quantify the effect that microbiology-affiliated preprints have had on the scholarly work of others.
+Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively.
 These values represent two aspects of posting a preprint.
@@
 This score measures the number of times a preprint or paper is mentioned in social media, mainstream media, peer reviews, and policy documents.
-Microbiology-affiliated preprints have had a median Altmetric Attention Score of **XXX** (IQR: **XX-XX**) and those of all preprints hosted at *bioRxiv* have had a median score of **XXX** (IQR: **XX-XX**).
-For comparison, the median Altmetric Attention Score for ASM journal articles for articles posted since November 2013 was **XXX** (IQR: **XX-XX**).
+Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
+For comparison, the median Altmetric Attention Score for ASM journal articles for articles posted since November 2013 was `r median(asm_post_2013[, 'altmetric'], na.rm=T)` (IQR: `r paste(quantile(asm_post_2013[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
+Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *biorxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`.
 A more traditional and controversial metric of impact has been the number of citations an article receives.

### 2017-01-12 submission/Schloss_PrePrints_mBio_2017.Rmd
Finish updating affiliation lookup table

@@
 biorxiv <- read.table(file = 'data/processed/biorxiv_data_summary.tsv', header=T, sep='\t', stringsAsFactors=F)
+biorxiv$affiliation <- gsub(";\\s*$", "", biorxiv$affiliation)
 
@@
 micro_aff_institutes <- levels(as.factor(biorxiv[micro_affiliated, "affiliation"]))
+
 micro_aff_countries_count <- sort(table(lookup[biorxiv[micro_affiliated, "affiliation"], "country"]), decreasing=T)
@@
 Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r 100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r 100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts)`% have posted 3 or more preprints.
-Corresponding authors that have posted microbiology-affiliated preprints are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%).
+Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%).
 

### 2017-01-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Continued editing and writing

@@
 
-\begin{center}
-\vspace{25mm}
-Patrick D. Schloss${^\dagger}$
-
-\vspace{30mm}
-
-$\dagger$ To whom correspondence should be addressed: pschloss@umich.edu
-
-Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
-\end{center}
-
-\newpage
-\linenumbers
-
-## Abstract
-
-## Importance
-
-\newpage
-
-## Background
-
-Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to engage their peers and non-scientists.
-Preprints have emerged as a formal venue for microbiologists to disseminate their research.
-A preprint is an unpublished manuscript that is made publicly available without going through an official peer-review process.
-Rather, an author can post their manuscript to a preprint server for others to read, share, and make comments.
-Preprints were initially adopted among physicists in the 1960s as a method of sharing interesting research amongst colleagues.
-Eventually, this community evolved into what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University.
-Among physicists and mathematicians, posting a preprint to *arXiv* has become the standard publication strategy followed by submission to a peer-reviewed journal.
-Within those communities researchers have been recognized with international awards for work that has only been posted to *arXiv* without formal review.
-Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
-Among the proponents of arXiv, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception.
-As adoption of preprints as a component of the scientific method has broadened among biologists, we sought to explore the specific use and concerns of preprints amongst microbiologists.
-
-***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in pursuing preprints as a stage in disseminating their research was whether it constituted prior publication.
-The broad consensus at this point is that preprints do not constitute prior publication.
-To briefly summarize journals of interest to many microbiologists, journals published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the Proceedings of the National Academy of Science, Science, and Nature have a permissive stance towards prior posting of preprints prior to submission.
-Although journals published by Cell do not forbid authors from posting preprints prior to submission, they ask authors to consult an editor prior to posting and do not allow authors to post revised preprints that contain revisions that respond to editorial input.
-Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work.
-Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated.
-
-***Landscape of preprint servers.*** Two preprint servers have sought to parallel the success of arXiv.
-In 2013, the *bioRxiv* (pronounced "bio-archive") was launched through Cold Spring Harbor Laboratory as a service to complement arXiv; *PeerJ Preprints* was initiated at the same time.
-Both options have similar features: preprint posting is free; each preprint receives a a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically posted in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
-There are several important differences between the two options.
-First, PeerJ as a for-profit organization and *bioRxiv* is a non-profit organization.
-This can be meaningful to authors since some journals, including the ASM Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations.
-Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse.
-This can be relevant for authors hoping to submit their work a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g.
-*Proceedings of the National Academy of Sciences*).
-A cosmetic, but important difference between the two is the layout and feel of the two websites.
-Compared to the *bioRxiv* site, the PeerJ Preprint site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints.
-With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on bioRxiv.
-It is only possible to transfer a PeerJ Preprint for submission to PeerJ.
-In many ways, preprint servers have taken on the feel of a journal.
-As adoption of this approach to disseminating research expands, it is likely that the features of these sites will continue to improve.
-It is also likely that interfaces from third-parties will improve.
-For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed does not.
-There is hope that the National Institutes of Health (NIH) will renew their interest in including preprints in PubMed search results.
-
-***Preprints and peer-review.*** The traditional peer-review editorial process was adapted to the technologies and trends that have evolved over the past 100 years.
-The formal peer-review system that most journals currently use was not developed until the end of the 1800s with the advent of typewriters and carbon paper (doi:10.1016/S0167-7799(02)01985-6).
-Editorial decisions were typically made by a single person or a committee (i.e.
-the editorial board) who had an expertise that covered the scope of the journal.
-As people's science became more specialized new journals would form providing a source of  validation to the new specialty.
-The growth in science in the mid 1900s resulted in a shift from difficulties finding sufficient numbers of manuscript to publish to having too many manuscripts submitted.
-It has been argued that the widespread adoption of peer review was due to the increased specialization and to deal with the large number of manuscript submissions (JAMA 1990;263:1323-1329).
-Peer-review did not achieve widespread use at many journals, including the Journal of Bacteriology, until the 1940 and 1950s.
-Given the rapid advances in communication technology and even greater specialization, it is worth pondering whether the current scientific publishing system and peer review system, in particular, needs to continue to adapt with our science.
-
-Communicating research has traditionally be done within research group meetings, departmental seminars, conferences, and as publications.
-Along this continuum, there is the assumption that the quality of the science has been improved because it has been vetted by more experts in the field.
-The public dissemination of one's research is a critical component of the scientific method.
-By describing their research, scientists subject their work to formal and informal peer review.
-Their research is scrutinized, praised, and probed to identify questions that help seed the next iteration of the scientific method.
-A common critique of these more modern approaches to publishing has been an inability to assess the quality of the science without the validation of peer-review.
-Attached to assertions of the validity of the research has become assertions of the impact and robustness of the research.
-These are all quality assessments that many acknowledge are difficult to assess by the traditional peer-review process.
-This has led to some to call for peer reviewers to place a reduced emphasis on the impact or significance of the work as pioneered by the journal PLOS ONE.
-It has also led to the call for replacing or complementing pre-publication peer review with post-publication peer review using PubMed Commons, PubPeer, journal-based discussion forums, and other mechanisms.
-Alas if scientists are going to depend on post-publication peer review or informal methods of peer-review, they must be willing to provide constructive feedback on the work of others.
-
-***Preprints have the potential to change how science is measured.*** Preprints are often viewed as existing in a state of scientific limbo.
-They represent a formal communication, but are not "published".
-As the use of preprints grows and our perceptions of preprints matures, there are a number of issues that will need to be addressed.
-First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the original researcher will lose their ability to claim primacy or their ability to publish the work in a journal.
-Considering the preprint is a citable work with a DOI, it would, in fact, be the original researcher that scooped the second.
-A growing number of scientific societies and journals, including ASM view preprints as citable and as a legitimate claim to primacy.
-Some worry that with such protection a researcher can make a claim without valid data to back it up.
-This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data.
-A second area of concern is whether a preprint can be used to support a grant proposal.
-Given the length limitations of many funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data.
-Some fear that the use of preprints will allow some to circumvent page limits by posting a half-baked manuscript.
-We would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
-A third concern is what role preprints should have in assessing a scientist's productivity.
-Clearly use of publication metrics is a contentious topic without considering the place of preprints.
-Regardless, given the propensity for researchers to list manuscripts as being "in preparation" on an application or curriculum vitae, listing them instead as preprints that can be reviewed by a committee could be seen as a significant way to enhance an application.
-In fact, several funding agencies are starting to encourage fellowship applicants to include preprints in their materials and others are requiring researchers to post preprints for all of their work.
-It is clear that the adoption of preprints will challenge how scientists interact and evaluate each other's work; however, it appears that there is great potential to empower researchers by controlling when a citable piece of work is made public.
-
-***The use of preprints from an author's perspective.*** Posting research as a preprint gives an author great control over when their work is made public.
-Under the traditional peer-review model, an author may need to submit and revise their work multiple times over a long period.
-In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process.
-A first example illustrate the utility of preprints for improving access to research and the quality of its reporting.
-In 2014, the Schloss laboratory posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform.
-At the same time, we submitted for review at PeerJ.
-While it was under review, we received feedback from someone that read the preprint as well as from Pacific Biosciences that the impact of the results could be limited because of the sequencing chemistry.
-Instead of resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to PeerJ that incorporated the original reviews as well as the feedback we received from Pacific Biosciences and the independent scientist.
-In general, our research group has simultaneously posted our manuscripts as preprints and submitted them to a journal.
-As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **XXXXXXX XX, 2017**.
-We then solicited feedback on the manuscript using social media.
-Two weeks later, we incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
-During that time, the abstract was read **XXXX** times and the PDF was accessed **XXXX** times.
-This process engaged **XXXX** commenters on bioRxiv, **XXXX** people on Twitter, **XXXX** on Facebook, and **XXXX** via email.
-We received useful feedback from **XXX** people.
-Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had we foregone the posting of a preprint.
-Although there are concerns regarding the quality of the science posted to a preprint server, we contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.
-
 ```{r analysis}
@@
 asm_post_2013 <- asm[asm$date >= 2013,]
+mbio <- asm_post_2013[grepl("mbio", asm_post_2013$article_id),]
 
@@
 
-## Preprints in microbiology
+\begin{center}
+\vspace{25mm}
+Patrick D. Schloss${^\dagger}$
 
-***Metrics for microbiology preprints.*** To analyze the use of preprints, we copied the bioRxiv website on December 31, 2016.
-We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*.
-Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category.
-When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts (**Figure 1**).
-These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r r non_micro_category_counts[3]`) categories.
-One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint.
-For example, this manuscript could be assigned to either the Microbiology or Scientific Communication and Education categories.
-Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r 100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r 100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts)`% have posted 3 or more preprints.
-Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%).
+\vspace{30mm}
 
-As stated above, preprints offer researchers the opportunity to improve the quality of their work by adding a more formal and public step to the scientific process.
-Among the microbiology-affiliated manuscripts, `r n_micro_aff_ever_commented` (`r 100*n_micro_aff_ever_commented/sum(micro_affiliated, na.rm=T)`%) had been commented on at least once and only `r n_micro_aff_thrice_commented` (`r 100*n_micro_aff_thrice_commented/sum(micro_affiliated, na.rm=T)`%) more than three times using the *bioRxiv*-hosted commenting feature.
-Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
-Regardless, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints are revised at least once.
-Among the preprints posted prior to January 1, 2016, `r 100*n_micro_published/sum(biorxiv$category == "Microbiology", na.rm=T)`% of the Microbiology category preprints, `r 100*n_micro_aff_published/sum(micro_affiliated, na.rm=T)`% of the microbiology-affiliated preprints, and `r 100*n_all_published/nrow(biorxiv)`% of all preprints have been published.
-Considering that these "acceptance rates" are higher than many peer-reviewed journals (e.g.
-approximately 25% at ASM Journals), these results would appear to dispel the critique that preprints represent overly preliminary research.
+$\dagger$ To whom correspondence should be addressed: pschloss@umich.edu
 
-Measuring the impact and significance of scientific research is notoriously difficult.
-Using several metrics, we sought to quantify the effect that microbiology-affiliated preprints have had on the scholarly work of others.
-Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively.
-These values represent two aspects of posting a preprint.
-First, they reflect the number of times people were able to access science before it was published.
-Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall.
-To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint.
-This score measures the number of times a preprint or paper is mentioned in social media, mainstream media, peer reviews, and policy documents.
-Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
-For comparison, the median Altmetric Attention Score for ASM journal articles for articles posted since November 2013 was `r median(asm_post_2013[, 'altmetric'], na.rm=T)` (IQR: `r paste(quantile(asm_post_2013[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
-Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *biorxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`.
-A more traditional and controversial metric of impact has been the number of citations an article receives.
-We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints.
-To allow for a comparison to traditional journals, we considered the citations for preprints posted in 2014 and 2015 as aggregated by Web of Science.
-Among the preprints that were published, the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**) and if unpublished preprints were included the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**).
-These values are comparable to many popular microbiology journals.
-*Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community*
+Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
+\end{center}
 
-***Microbiology anecdotes.***
+\newpage
+\linenumbers
+
+## Abstract
+
+## Importance
+
+\newpage
+
+## Background
+
+Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public.
+A preprint is an unpublished manuscript that is made publicly available without going through an official peer-review process.
+Rather, an author can post their manuscript to a preprint server for others to read, share, and make comments.
+Preprints were initially adopted among physicists in the 1960s as a method of sharing interesting research amongst colleagues.
+Eventually, this community evolved into what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University.
+Among physicists and mathematicians, posting a preprint to *arXiv* has become the standard publication strategy followed by submission to a peer-reviewed journal.
+Within those communities researchers have been recognized with international awards for work that has only been posted to *arXiv* without formal review.
+Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
+Among proponents of arXiv, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception.
+Considering the broadening adoption of preprints among microbiologists, we sought to explore the specific uses and concerns of preprints amongst microbiologists.
+
+***Landscape of preprint servers.*** In 2013, two preprint servers the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints* were launched to parallel the success of *arXiv*.
+Both platforms offer similar features: preprint posting is free; each preprint receives a a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
+There are several important differences between the two options.
+First, PeerJ as a for-profit organization and *bioRxiv* is a non-profit organization, hosted through Cold Spring Harbor Laboratory.
+This difference can be meaningful to authors since some journals, including the ASM Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations.
+Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse.
+This can be relevant for authors hoping to submit their work a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g.
+*Proceedings of the National Academy of Sciences*).
+A cosmetic, but important difference between the two is the layout and feel of the two websites.
+Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints.
+With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*.
+It is only possible to transfer a *PeerJ Preprint* for submission to *PeerJ*.
+In many ways, preprint servers have taken on the feel of a journal.
+As adoption of this approach to disseminating research expands, it is likely that the features of these sites will continue to improve.
+It is also likely that interfaces from third-parties will improve.
+For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not.
+There is hope that the National Institutes of Health (NIH) will renew their interest in including preprints in PubMed search results.
+
+***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in pursuing preprints as a stage in disseminating their research was whether it constituted prior publication.
+The broad consensus at this point is that preprints do not constitute prior publication.
+The current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the Proceedings of the National Academy of Science, Science, and Nature have a permissive stance towards prior posting of preprints prior to submission.
+Although journals published by Cell do not forbid authors from posting preprints prior to submission, they ask authors to consult an editor prior to posting and do not allow authors to post revised preprints that contain revisions that respond to editorial input.
+Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work.
+Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated.
+
+***Preprints and peer-review.*** The use of preprints for citations in other scientific reports and grant proposals has been called into question because preprints upend the traditional peer-review editorial process.
+It is important to note that this process was adapted to the technologies and trends that have evolved over the past 100 years.
+The formal peer-review system that most journals currently use was not developed until the end of the 1800s with the advent of typewriters and carbon paper (doi:10.1016/S0167-7799(02)01985-6).
+Editorial decisions were typically made by a single person or a committee (i.e.
+the editorial board) who had an expertise that covered the scope of the journal.
+As people's science became more specialized new journals would form providing a source of  validation to the new specialty.
+The growth in science in the mid 1900s resulted in a shift from difficulties finding sufficient numbers of manuscript to publish to having too many manuscripts submitted.
+It has been argued that the widespread adoption of peer review was due to the increased specialization and to deal with the large number of manuscript submissions (JAMA 1990;263:1323-1329).
+Peer-review did not achieve widespread use at many journals, including the Journal of Bacteriology, until the 1940s and 1950s.
+Given the rapid advances in communication technology and even greater specialization, it is worth pondering whether the current scientific publishing system and peer-review system, in particular, need to continue to adapt with our science.
+
+Communicating research has traditionally be done within research group meetings, departmental seminars, conferences, and as publications.
+Along this continuum, there is an assumption that the quality of the science has been improved because it has been vetted by more experts in the field.
+The public dissemination of one's research is a critical component of the scientific method.
+By describing their research, scientists subject their work to formal and informal peer review.
+Their research is scrutinized, praised, and probed to identify questions that help seed the next iteration of the scientific method.
+A common critique of these more modern approaches to publishing has been an inability to assess the quality of the science without the validation of peer-review.
+Attached to assertions of the validity of the research has become assertions of the impact and robustness of the research.
+These are all quality assessments that many acknowledge are difficult to assess by the traditional peer-review process.
+This has led to some journals, most notably PLOS ONE, calling for peer reviewers to place a reduced emphasis on the perceived impact or significance of the work.
+It has also led to the call for replacing or complementing pre-publication peer review with post-publication peer review using PubMed Commons, PubPeer, journal-based discussion forums, and other mechanisms.
+Alas if scientists are going to depend on post-publication peer review or informal methods of peer-review for documents like preprints, they must be willing to provide constructive feedback on the work of others.
+
+***Preprints have the potential to change the advancement of science.*** Preprints are often viewed as existing in a state of scientific limbo.
+They represent a formal communication, but are not "published".
+As the use of preprints grows and our perceptions of preprints matures, there are a number of issues that will need to be addressed.
+First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the original researcher will lose their ability to claim primacy or their ability to publish the work in a journal.
+Considering the preprint is a citable work with a DOI, it would, in fact, be the original researcher that scooped the second.
+A growing number of scientific societies and journals, including ASM view preprints as citable and as a legitimate claim to primacy.
+Some worry that with such protection a researcher can make a claim without valid data to support their claims.
+This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data.
+A second area of concern is whether a preprint can be used to support a grant proposal.
+Given the length limitations of many funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data.
+Some fear that the use of preprints will allow some to circumvent page limits by posting preliminary manuscripts.
+We would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
+A third concern is what role preprints should have in assessing a scientist's productivity.
+Clearly use of publication metrics is a contentious topic without considering the place of preprints.
+Regardless, given the propensity for researchers to list manuscripts as being "in preparation" or "in review" on an application or curriculum vitae, listing them instead as preprints that can be reviewed by a committee could be seen as a significant way to enhance an application.
+In fact, several funding agencies are starting to encourage fellowship applicants to include preprints in their materials.
+Others are mandating that researchers post preprints for all of their work prior to submitting the work to a journal.
+It is clear that the adoption of preprints will challenge how scientists interact and evaluate each other's work.
+There is great potential to empower researchers by controlling when a citable piece of work is made public.
+
+***Microbiology anecdotes.*** The peer-review editorial process can be lengthy and adversarial.
+In contrast, preprints represent a rapid and potentially collaborative method for disseminating research.
+Three examples from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints.
+
 * MinIon methods
@@
 
-## Perspective
-* Support priority in literature
-* Support citation
-* Direct submission
-* preprint scouts
-* mSphereDirect / F1000Prime
-* Licensing
-* What's in it for ASM Journals and Readers?
-* Kills the splash for a paper when it's actually published - author wins, journal loses
+***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, we copied the *bioRxiv* on December 31, 2016.
+We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*.
+Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category.
+When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts (**Figure 1**).
+These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.
+One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint.
+For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories.
+Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r 100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r 100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts)`% have posted 3 or more preprints.
+Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%).
+
+As stated above, preprints offer researchers the opportunity to improve the quality of their work by adding a more formal and public step to the scientific process.
+Among the microbiology-affiliated manuscripts, `r n_micro_aff_ever_commented` (`r 100*n_micro_aff_ever_commented/sum(micro_affiliated, na.rm=T)`%) had been commented on at least once and only `r n_micro_aff_thrice_commented` (`r 100*n_micro_aff_thrice_commented/sum(micro_affiliated, na.rm=T)`%) more than three times using the *bioRxiv*-hosted commenting feature.
+Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
+Regardless, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints were revised at least once.
+Among the preprints posted prior to January 1, 2016, `r 100*n_micro_published/sum(biorxiv$category == "Microbiology", na.rm=T)`% of the Microbiology category preprints, `r 100*n_micro_aff_published/sum(micro_affiliated, na.rm=T)`% of the microbiology-affiliated preprints, and `r 100*n_all_published/nrow(biorxiv)`% of all preprints have been published.
+It is worth noting that not all authors submit their preprints to journals suggesting that the "acceptance rates" are actually higher.
+Regardless, considering that these acceptance rates are higher than many peer-reviewed journals (e.g.
+approximately 20% at ASM Journals), these results would appear to dispel the critique that preprints represent overly preliminary research.
+
+Measuring the impact and significance of scientific research is notoriously difficult.
+Using several metrics we sought to quantify the effect that microbiology-affiliated preprints have had on the work of others.
+Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively.
+These values represent two aspects of posting a preprint.
+First, they reflect the number of times people were able to access science before it was published.
+Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall.
+To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint.
+This score measures the number of times a preprint or paper is mentioned in social media, mainstream media, peer reviews, and policy documents.
+Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
+For comparison, the median Altmetric Attention Score for articles published in *mBio* published since November 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
+Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *biorxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`.
+A more traditional and controversial metric of impact has been the number of citations an article receives.
+We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints.
+To allow for a comparison to traditional journals, we considered the citations for preprints posted in 2014 and 2015 as aggregated by Web of Science.
+Among the preprints that were published, the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**) and if unpublished preprints were included the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**).
+These values are comparable to many popular microbiology journals.
+*Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community*
+
+***Preprints from an author's perspective.*** Posting research as a preprint gives an author great control over when their work is made public.
+Under the traditional peer-review model, an author may need to submit and revise their work multiple times over a long period.
+In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process.
+A first example illustrate the utility of preprints for improving access to research and the quality of its reporting.
+In 2014, the Schloss laboratory posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform.
+At the same time, we submitted the manuscript for review at PeerJ.
+While the manuscript was under review, we received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry.
+Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to PeerJ that incorporated the original reviews as well as the feedback we received from Pacific Biosciences and the academic scientist.
+In other cases, our research group has simultaneously posted our manuscripts as preprints and submitted them to a journal.
+As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **XXXXXXX XX, 2017**.
+We then solicited feedback on the manuscript using social media.
+Two weeks later, we incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
+During that time, the abstract was read **XXXX** times and the PDF was accessed **XXXX** times.
+This process engaged **XXXX** commenters on *bioRxiv*, **XXXX** people on Twitter, **XXXX** on Facebook, and **XXXX** via email.
+We received useful feedback from **XXX** people.
+Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had we foregone the posting of a preprint.
+Although there are concerns regarding the quality of the science posted to a preprint server, we contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.
+
+***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals have in disseminating research if there is broad adoption of preprints.
+One perspective is that although authors value immediate accessibility to their work, they also value the editorial support from professional societies and other organizations.
+Furthermore, the professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals.
+An alternative perspective is that preprints will eventually replace traditional journals.
+Certainly, this is a radical perspective, but it does serve to motivate publishers to address what they can offer preprint authors.
+By adopting preprint-friendly policies, journals can create an attractive environment for authors.
+As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals.
+**F1000 Prime encourages its members to comment on preprints on the F1000 website**.
+A new venture from *mSphere*, mSphereDirect, actively encourages authors to post their manuscripts as preprints as part of the author-driven editorial process.
+In addition to integrating preprints into the traditional editorial process, several professional societies that publish journals have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature.
+These are policies that empower authors and make specific journals more attractive.
+Other practices have great potential to improve the reputation of journals.
+As measured above, preprints are able to garner attention on par with papers published in highly selective microbiology journals.
+Thus, it is in a journal's best interest to recruit these preprints to their journals.
+Several journals including **XXXXXX** and **XXXXXX** have publicly stated that they scout preprints for this purpose.
+Preprints can also be viewed as a lost opportunity to journals.
+A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal.
+Going forward, it will be interesting to see whether publishers are able to develop innovative approaches so that they can benefit by incorporating preprints into their process or if their influence is reduced by the widespread adoption of preprints.
+
+An increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method of disseminating their research prior to peer review.
+A number of critical concerns remain about how widespread their adoption will be, how they will be treated by traditional journals, and whether peer-review will adapt to new scientific trends and technologies.
+Regardless, preprints should offer a great opportunity for both scientists and journals to publish high quality science.
+
+## Acknowledgements
+
+This work was supported in part by funding from the National Institutes of Health (**XXXXXXXXXXX** and **XXXXXXXXXXX**).
+We appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases.
+The data, code, and an executable R-markdown version of this manuscript are available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.
+
+\newpage
+
+## Figures
+
+**Figure 1.**
+* How many preprints are being submitted each month - microbiology category and microbiology-ish
 
@@
 ## References
-
-## Figures
-
-**Figure 1. **
-* How many preprints are being submitted each month - microbiology category and microbiology-ish

### 2017-01-27 submission/Schloss_PrePrints_mBio_2017.Rmd
Add anecdotes

@@
 knitr::knit_hooks$set(inline=inline_hook)
-
 ```
@@
 Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
-Among proponents of arXiv, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception.
+Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception.
 Considering the broadening adoption of preprints among microbiologists, we sought to explore the specific uses and concerns of preprints amongst microbiologists.
@@
 ***Landscape of preprint servers.*** In 2013, two preprint servers the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints* were launched to parallel the success of *arXiv*.
-Both platforms offer similar features: preprint posting is free; each preprint receives a a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
+Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
 There are several important differences between the two options.
@@
 The broad consensus at this point is that preprints do not constitute prior publication.
-The current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the Proceedings of the National Academy of Science, Science, and Nature have a permissive stance towards prior posting of preprints prior to submission.
-Although journals published by Cell do not forbid authors from posting preprints prior to submission, they ask authors to consult an editor prior to posting and do not allow authors to post revised preprints that contain revisions that respond to editorial input.
+The current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, and *Nature* have a permissive stance towards prior posting of preprints prior to submission.
+Although journals published by *Cell* do not forbid authors from posting preprints prior to submission, they ask authors to consult an editor prior to posting and do not allow authors to post revised preprints that contain revisions that respond to editorial input.
 Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work.
@@
 These are all quality assessments that many acknowledge are difficult to assess by the traditional peer-review process.
-This has led to some journals, most notably PLOS ONE, calling for peer reviewers to place a reduced emphasis on the perceived impact or significance of the work.
+This has led to some journals, most notably *PLOS ONE*, calling for peer reviewers to place a reduced emphasis on the perceived impact or significance of the work.
 It has also led to the call for replacing or complementing pre-publication peer review with post-publication peer review using PubMed Commons, PubPeer, journal-based discussion forums, and other mechanisms.
@@
 Others are mandating that researchers post preprints for all of their work prior to submitting the work to a journal.
+Beyond these concerns, preprints are also causing some to change their publication goals.
+Some authors are explicitly stating that a preprint will not be submitted to a journal.
+Although these authors may be a minority of all those who post preprints, such an approach may be attractive to those that want to have a mechanism for people to cite a report of a brief research communication, a critique of another publication, or negative results.
 It is clear that the adoption of preprints will challenge how scientists interact and evaluate each other's work.
@@
 In contrast, preprints represent a rapid and potentially collaborative method for disseminating research.
-Three examples from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints.
+Several from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints.
+First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies.
+Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; the number of Zika virus-related publications is now over 1,700.
+During this time, more than 110 Zika virus-related preprints have been posted at *bioRxiv*.
+Any manuscript that was published likely went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus.
+However, those that posted their work as a preprint were able to instantly disseminate their methods and results.
 
 * MinIon methods
-* Tardigrade microbiome
-* NYC subway microbiome
+
+Second, preprints have proven useful for rapidly correcting the scientific literature.
+On February 9, 2015, Cell Systems posted a study by Afshinnekoo et al.
+online.
+The study collected and analyzed metagenomic sequence data from the New York City subway system and reported finding *Yersinia pestis* and *Bacillus anthracis*.
+Because of the focus on these two bioterrorism agents, this study generated a considerable amount of press attention.
+On April 25, 2015, Petit et al.
+posted a preprint to Zenodo demonstrating that there was no evidence for *B.
+anthracis* in the dataset.
+On July 29, 2015, a critique was published by Cell Systems along with a response from the original authors offering a correction to their manuscript.
+
+Original Online: 9 February 2015
+http://www.sciencedirect.com/science/article/pii/S2405471215000022
+
+Uh, no online: 29 July 2015
+http://www.sciencedirect.com/science/article/pii/S2405471215000162
+
+COrrection:  29 July 2015
+http://www.sciencedirect.com/science/article/pii/S2405471215000150
+
+Read preprint: April 25, 2015
+https://zenodo.org/record/17158#.WIprNbGZOiI
+
+A second anecdote surrounds the publishing of a draft tardigrade genome in *PNAS*.
+On November 23, 2015 a study of Boothby et al.
+was first published online.
+The authors posited that 17.5% of its genes came from bacteria, archaea, fungi, plants, and viruses.
+Another group had been analyzing sequence data from a parallel tardigrade genome sequencing project and did not observe the same result.
+By December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants; this analysis would eventually be posted online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016.
+Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016.
+
+Bremm PNAS: May 12, 2016. http://www.pnas.org/content/113/22/E3054.full
+Arakawa PNAS: May 31, 2016. http://www.pnas.org/content/113/22/E3057.full
+Delmont PeerJ: February 2, 2016. https://peerj.com/preprints/1695/
+
+These anecdotes underscore the value of having a rapid posting cycle to correcting errors in the scientific literature and that results posted to preprint servers were able to correct the record within weeks of the initial publication while the traditional path took six months in both cases.
+A final notable case where preprints have accelerated the correction of the scientific record was a preprint posted by Bik et al.
+reporting numerous cases of image manipulation in peer reviewed studies.
+Their preprint was posted on April 20, 2016 and published in *mBio* on June 7, 2016.
+Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the Arsenic life paper would have been different had they initially been posted as preprints.
 
@@
 Among the preprints posted prior to January 1, 2016, `r 100*n_micro_published/sum(biorxiv$category == "Microbiology", na.rm=T)`% of the Microbiology category preprints, `r 100*n_micro_aff_published/sum(micro_affiliated, na.rm=T)`% of the microbiology-affiliated preprints, and `r 100*n_all_published/nrow(biorxiv)`% of all preprints have been published.
-It is worth noting that not all authors submit their preprints to journals suggesting that the "acceptance rates" are actually higher.
+As noted above, not all authors submit their preprints to journals.
+This would indicate that the "acceptance rates" are actually higher.
 Regardless, considering that these acceptance rates are higher than many peer-reviewed journals (e.g.
-approximately 20% at ASM Journals), these results would appear to dispel the critique that preprints represent overly preliminary research.
+approximately 20% at ASM Journals), these results dispel the critique that preprints represent overly preliminary research.
 
@@
 To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint.
-This score measures the number of times a preprint or paper is mentioned in social media, mainstream media, peer reviews, and policy documents.
+The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, mainstream media, peer reviews, and policy documents.
+A higher score indicates that a preprint received more attention.
 Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).

### 2017-01-30 submission/Schloss_PrePrints_mBio_2017.Rmd
Light editing

@@
 During this time, more than 110 Zika virus-related preprints have been posted at *bioRxiv*.
-Any manuscript that was published likely went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus.
-However, those that posted their work as a preprint were able to instantly disseminate their methods and results.
+Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus.
+In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly.
 

### 2017-01-30 code/wos_amr/lookup_ids.py
Modify to include batch number so we can sort

@@ -110,13 +110,15 @@ def main():
     # Write the results to a csv file.
     with open(outfile, 'wb') as of:
         writer = csv.writer(of)
-        writer.writerow(('id', 'ut', 'doi', 'pmid', 'times cited', 'source'))
+        writer.writerow(('batch', 'id', 'ut', 'doi', 'pmid', 'times cited', 'source'))
+        counter = 0
         for grp in found:
+            counter = counter + 1
             for k, item in grp.items():
                 ut = item.get('ut')
                 if ut is not None:
                     ut = "WOS:" + ut
-                writer.writerow([k, ut, item.get('doi', ""), item.get('pmid', ""), item.get('timesCited', '0'),
+                writer.writerow([counter, k, ut, item.get('doi', ""), item.get('pmid', ""), item.get('timesCited', '0'),
                                  item.get('sourceURL', 'N/A')])
 
 if __name__ == "__main__":

### 2017-01-31 code/wos_amr/client.py
Replace versions of wos-amr

@@ -1,52 +1,0 @@
-"""
-Basic Python client for AMR.
-http://ipscience-help.thomsonreuters.com/LAMRService/WebServicesOverviewGroup/overview.html
-"""
-
-from itertools import izip_longest
-import os
-import xml.etree.ElementTree as ET
-import urllib2
-
-try:
-    USER = os.environ['WOS_USER']
-    PASSWORD = os.environ['WOS_PASSWORD']
-except KeyError:
-    raise Exception("Unable to read WOS_USER and WOS_PASSWORD environment variables.")
-
-AMR_URL = "https://ws.isiknowledge.com/cps/xrpc"
-BATCH_SIZE = 50
-
-
-def grouper(iterable, n, fillvalue=None):
-    """
-    Group iterable into n sized chunks.
-    See: http://stackoverflow.com/a/312644/758157
-    """
-    args = [iter(iterable)] * n
-    return izip_longest(*args, fillvalue=fillvalue)
-
-
-def read(raw):
-    ns = {'isi': 'http://www.isinet.com/xrpc41'}
-    raw = ET.fromstring(raw)
-    out = {}
-    for cite in raw.findall('isi:fn/isi:map/isi:map', ns):
-        cite_key = cite.attrib['name']
-        meta = {}
-        for val in cite.findall('isi:map/isi:val', ns):
-            meta[val.attrib['name']] = val.text
-        out[cite_key] = meta
-    return out
-
-
-def get(request_xml):
-    req = urllib2.Request(AMR_URL, request_xml)
-    req.add_header('Content Type', 'application/xml')
-    response = urllib2.urlopen(req)
-    text = response.read()
-    # parse into xml
-    xml = read(text)
-    return xml
-
-

### 2017-01-31 code/wos_amr/lookup_ids.py

@@ -1,125 +1,0 @@
-"""
-Expects an incoming CSV file with local ID, PMID, or DOI headers and wil post to
-AMR in batches of 50.
-
-E.g.
-
-UT
-01234
-02394
-039039
-
-PMID
-2093030
-2405903
-95930303
-
-Run as:
-
-$ python batch_lookup.py sample_file.csv outputfile.csv
-
-"""
-
-import csv
-import sys
-import xml.etree.ElementTree as ET
-
-import client
-
-
-# Template for fetching ids and timesCited from AMR
-id_request_template = u"""<?xml version="1.0" encoding="UTF-8" ?>
-<request xmlns="http://www.isinet.com/xrpc41" src="app.id=InternalVIVODemo">
-  <fn name="LinksAMR.retrieve">
-    <list>
-      <!-- authentication -->
-      <map>
-        <val name="username">{user}</val>
-        <val name="password">{password}</val>
-      </map>
-      <!-- what to to return -->
-       <map>
-         <list name="WOS">
-           <val>sourceURL</val>
-           <val>ut</val>
-           <val>doi</val>
-           <val>pmid</val>
-           <val>timesCited</val>
-         </list>
-       </map>
-       <!-- LOOKUP DATA -->
-       {items}
-    </list>
-  </fn>
-</request>
-"""
-
-
-def prep_request(items, local_id="id"):
-    """
-    Process the incoming items into an AMR request.
-
-    <map name="cite_1">
-        <val name="{id_type}">{value}</val>
-    </map>
-    """
-    map_items = ET.Element("map")
-    for idx, pub in enumerate(items):
-        if pub is None:
-            continue
-        local_id_value = pub.get(local_id) or pub.get(local_id.upper())
-        if local_id_value is None:
-            local_id_value = str(idx)
-        this_item = ET.Element("map", name=local_id_value)
-        for k, v in pub.items():
-            if v is None:
-                continue
-            de = ET.Element("val", name=k.lower())
-            de.text = v.strip()
-            this_item.append(de)
-        map_items.append(this_item)
-
-    request_items = ET.tostring(map_items)
-    xml = id_request_template.format(user=client.USER, password=client.PASSWORD, items=request_items)
-    return xml
-
-
-def main():
-    try:
-        infile = sys.argv[1]
-        outfile = sys.argv[2]
-    except IndexError:
-        raise Exception("An input and outpfile file is required.")
-    found = []
-    to_check = []
-    with open(infile) as inf:
[…]

### 2017-02-01 code/get_asm_pub_date.R
Generate citation count files

@@ -1,0 +1,12 @@
+library(dplyr)
+
+dates <- read.table(file="data/asm_doi_urls.tsv")
+dates$V1 <- toupper(gsub("http://dx.doi.org/", "", dates$V1))
+
+cites <- read.csv(file="data/wos_counts/asm_wos.temp")
+cites$doi <- toupper(cites$doi)
+
+combined <- inner_join(dates, cites, by=c("V1" = "doi"))[,c("V1", "V2", "times.cited")]
+colnames(combined) <- c("doi", "date", "times.cited")
+
+write.table(combined, file="data/wos_counts/asm_wos.csv", sep=',', row.names=F)

### 2017-02-01 code/get_biorxiv_pub_date.R

@@ -1,6 +1,6 @@
 library(rentrez)
 
-wos <- read.csv(file="data/wos_counts/biorxiv_wos.csv", na.string="N/A")
+wos <- read.csv(file="data/wos_counts/biorxiv_wos.temp", na.string="N/A")
 wos <- wos[!is.na(wos$pmid),]
 
 get_pubdate <- function(id){
@@ -13,9 +13,9 @@ month <- gsub("^20\\d\\d\\s?(...).*", "\\1", dates)
 month <- gsub("20..", "", month)
 month[month == ""] <- "Jan"
 
-month_convert <- c(Jan = 1,  Feb = 2,  Mar = 3,  Apr = 4,
-									 May = 5,  Jun = 6,  Jul = 7,  Aug = 8,
-									 Sep = 9,  Oct = 10, Nov = 11, Dec = 12)
+month_convert <- c(Jan = "01", Feb = "02", Mar = "03", Apr = "04",
+									 May = "05", Jun = "06", Jul = "07", Aug = "08",
+									 Sep = "09", Oct = "10", Nov = "11", Dec = "12")
 
 month_number <- unname(month_convert[month])
 year_month <- paste(year, month_number, sep='-')

### 2017-02-01 code/wos-amr/lookup_ids.py
Add my changes to wos-amr code

@@ -1,0 +1,125 @@
+"""
+Expects an incoming CSV file with local ID, PMID, or DOI headers and wil post to
+AMR in batches of 50.
+
+E.g.
+
+UT
+01234
+02394
+039039
+
+PMID
+2093030
+2405903
+95930303
+
+Run as:
+
+$ python batch_lookup.py sample_file.csv outputfile.csv
+
+"""
+
+import csv
+import sys
+import xml.etree.ElementTree as ET
+
+import client
+
+
+# Template for fetching ids and timesCited from AMR
+id_request_template = u"""<?xml version="1.0" encoding="UTF-8" ?>
+<request xmlns="http://www.isinet.com/xrpc41" src="app.id=InternalVIVODemo">
+  <fn name="LinksAMR.retrieve">
+    <list>
+      <!-- authentication -->
+      <map>
+        <val name="username">{user}</val>
+        <val name="password">{password}</val>
+      </map>
+      <!-- what to to return -->
+       <map>
+         <list name="WOS">
+           <val>sourceURL</val>
+           <val>ut</val>
+           <val>doi</val>
+           <val>pmid</val>
+           <val>timesCited</val>
+         </list>
+       </map>
+       <!-- LOOKUP DATA -->
+       {items}
+    </list>
+  </fn>
+</request>
+"""
+
+
+def prep_request(items, local_id="id"):
+    """
+    Process the incoming items into an AMR request.
+
+    <map name="cite_1">
+        <val name="{id_type}">{value}</val>
+    </map>
+    """
+    map_items = ET.Element("map")
+    for idx, pub in enumerate(items):
+        if pub is None:
+            continue
+        local_id_value = pub.get(local_id) or pub.get(local_id.upper())
+        if local_id_value is None:
+            local_id_value = str(idx)
+        this_item = ET.Element("map", name=local_id_value)
+        for k, v in pub.items():
+            if v is None:
+                continue
+            de = ET.Element("val", name=k.lower())
+            de.text = v.strip()
+            this_item.append(de)
+        map_items.append(this_item)
+
+    request_items = ET.tostring(map_items)
+    xml = id_request_template.format(user=client.USER, password=client.PASSWORD, items=request_items)
+    return xml
+
+
+def main():
+    try:
+        infile = sys.argv[1]
+        outfile = sys.argv[2]
+    except IndexError:
+        raise Exception("An input and outpfile file is required.")
+    found = []
+    to_check = []
+    with open(infile) as inf:
[…]

### 2017-02-01 submission/Schloss_PrePrints_mBio_2017.Rmd
Add citation data

@@
 biorxiv$affiliation <- gsub(";\\s*$", "", biorxiv$affiliation)
+biorxiv$journal_published_doi <- tolower(gsub("http://dx.doi.org/", "", biorxiv$journal_published_doi))
 
@@
 n_all_published <- sum(!is.na(biorxiv[, "journal_published"]))
+
+biorxiv_cited <- read.csv("data/wos_counts/biorxiv_wos.csv", stringsAsFactors=F)
+biorxiv_cited$doi <- tolower(biorxiv_cited$doi)
+biorxiv_cited <- inner_join(biorxiv_cited, biorxiv, by=c("doi"="journal_published_doi"))
+biorxiv_cited_affiliated <- biorxiv_cited[biorxiv_cited$is_microbiology | biorxiv_cited$category == "Microbiology",]
+cites_2015 <- grep("2015", biorxiv_cited_affiliated$year_month)
+biorxiv_cited_affiliated_2015 <-  biorxiv_cited_affiliated[cites_2015, "times.cited"]
+
+asm_cited <- read.csv("data/wos_counts/asm_wos.csv", stringsAsFactors=F)
+mbio_cited <- asm_cited[grepl("MBIO", asm_cited$doi),]
+mbio_2015 <- grep("201[45]", mbio_cited$date)
+mbio_cited_2015 <- mbio_cited[mbio_2015, "times.cited"]
 ```
@@
 We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints.
-To allow for a comparison to traditional journals, we considered the citations for preprints posted in 2014 and 2015 as aggregated by Web of Science.
-Among the preprints that were published, the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**) and if unpublished preprints were included the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**).
-These values are comparable to many popular microbiology journals.
-*Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community*
+To allow for a comparison to traditional journals, we considered the citations for preprints posted in 2015 as aggregated by Web of Science.
+Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`).
+For comparison, for the papers published in *mBio* in 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`).
+Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community
 

### 2017-02-06 submission/Schloss_PrePrints_mBio_2017.Rmd
Editing

@@
 
-## Background
-
-Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public.
+***Background.*** Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public.
 A preprint is an unpublished manuscript that is made publicly available without going through an official peer-review process.
-Rather, an author can post their manuscript to a preprint server for others to read, share, and make comments.
+An author can post their manuscript to a preprint server for others to read, share, and make comments.
 Preprints were initially adopted among physicists in the 1960s as a method of sharing interesting research amongst colleagues.
@@
 There are several important differences between the two options.
-First, PeerJ as a for-profit organization and *bioRxiv* is a non-profit organization, hosted through Cold Spring Harbor Laboratory.
+First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory.
 This difference can be meaningful to authors since some journals, including the ASM Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations.
@@
 
-***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in pursuing preprints as a stage in disseminating their research was whether it constituted prior publication.
+***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in posting their work as preprints as a stage in disseminating their research was whether it constituted prior publication.
 The broad consensus at this point is that preprints do not constitute prior publication.
@@
 the editorial board) who had an expertise that covered the scope of the journal.
-As people's science became more specialized new journals would form providing a source of  validation to the new specialty.
+As people's science became more specialized, new journals would form to support and provide a source of validation to the new specialty.
 The growth in science in the mid 1900s resulted in a shift from difficulties finding sufficient numbers of manuscript to publish to having too many manuscripts submitted.
-It has been argued that the widespread adoption of peer review was due to the increased specialization and to deal with the large number of manuscript submissions (JAMA 1990;263:1323-1329).
-Peer-review did not achieve widespread use at many journals, including the Journal of Bacteriology, until the 1940s and 1950s.
+It has been argued that the widespread adoption of decentralized peer-review was due to the increased specialization and to deal with the large number of manuscript submissions (JAMA 1990;263:1323-1329).
+Peer-review did not achieve widespread use at many journals, including the *Journal of Bacteriology*, until the 1940s and 1950s.
 Given the rapid advances in communication technology and even greater specialization, it is worth pondering whether the current scientific publishing system and peer-review system, in particular, need to continue to adapt with our science.
 
-Communicating research has traditionally be done within research group meetings, departmental seminars, conferences, and as publications.
+Communicating research has traditionally been done within research group meetings, departmental seminars, conferences, and as publications.
 Along this continuum, there is an assumption that the quality of the science has been improved because it has been vetted by more experts in the field.
@@
 Their research is scrutinized, praised, and probed to identify questions that help seed the next iteration of the scientific method.
-A common critique of these more modern approaches to publishing has been an inability to assess the quality of the science without the validation of peer-review.
+A common critique of more modern approaches to publishing has been an inability to assess the quality of the science without the validation of peer-review.
 Attached to assertions of the validity of the research has become assertions of the impact and robustness of the research.
 These are all quality assessments that many acknowledge are difficult to assess by the traditional peer-review process.
-This has led to some journals, most notably *PLOS ONE*, calling for peer reviewers to place a reduced emphasis on the perceived impact or significance of the work.
-It has also led to the call for replacing or complementing pre-publication peer review with post-publication peer review using PubMed Commons, PubPeer, journal-based discussion forums, and other mechanisms.
-Alas if scientists are going to depend on post-publication peer review or informal methods of peer-review for documents like preprints, they must be willing to provide constructive feedback on the work of others.
+This has led to some journals, most notably *PLOS ONE*, calling for referees to place a reduced emphasis on the perceived impact or significance of the work.
+It has also led to the call for replacing or complementing pre-publication peer-review with post-publication peer-review using PubMed Commons, PubPeer, journal-based discussion forums, and other mechanisms.
+Alas if scientists are going to depend on post-publication peer-review or informal methods of peer-review for documents like preprints, they must be willing to provide constructive feedback on the work of others.
 
 ***Preprints have the potential to change the advancement of science.*** Preprints are often viewed as existing in a state of scientific limbo.
-They represent a formal communication, but are not "published".
+As noted above, they represent a formal communication, but are not officially published.
 As the use of preprints grows and our perceptions of preprints matures, there are a number of issues that will need to be addressed.
 First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the original researcher will lose their ability to claim primacy or their ability to publish the work in a journal.
-Considering the preprint is a citable work with a DOI, it would, in fact, be the original researcher that scooped the second.
+Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second.
 A growing number of scientific societies and journals, including ASM view preprints as citable and as a legitimate claim to primacy.
@@
 Some authors are explicitly stating that a preprint will not be submitted to a journal.
-Although these authors may be a minority of all those who post preprints, such an approach may be attractive to those that want to have a mechanism for people to cite a report of a brief research communication, a critique of another publication, or negative results.
+Although these authors may be a minority of those who post preprints, such an approach may be attractive to those that want to have a mechanism for people to cite a report of a brief research communication, a critique of another publication, or negative results.
 It is clear that the adoption of preprints will challenge how scientists interact and evaluate each other's work.
@@
 In contrast, preprints represent a rapid and potentially collaborative method for disseminating research.
-Several from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints.
+Several anecdotes from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints.
 First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies.
@@
 In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly.
-
-* MinIon methods
-
+Over the last several years rapid advances in DNA sequencing technologies have fundamentally changed how microbial science is performed.
+One notable technology, the MinIon sequencing platform from Oxford Nanopore has received considerable attention from researchers who post new methods and results to preprint servers.
+For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.
 Second, preprints have proven useful for rapidly correcting the scientific literature.
@@
 On July 29, 2015, a critique was published by Cell Systems along with a response from the original authors offering a correction to their manuscript.
-
-Original Online: 9 February 2015
-http://www.sciencedirect.com/science/article/pii/S2405471215000022
-
-Uh, no online: 29 July 2015
-http://www.sciencedirect.com/science/article/pii/S2405471215000162
-
-COrrection:  29 July 2015
-http://www.sciencedirect.com/science/article/pii/S2405471215000150
-
-Read preprint: April 25, 2015
-https://zenodo.org/record/17158#.WIprNbGZOiI
-
 A second anecdote surrounds the publishing of a draft tardigrade genome in *PNAS*.
@@
 Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016.
-
-Bremm PNAS: May 12, 2016. http://www.pnas.org/content/113/22/E3054.full
-Arakawa PNAS: May 31, 2016. http://www.pnas.org/content/113/22/E3057.full
-Delmont PeerJ: February 2, 2016. https://peerj.com/preprints/1695/
-
 These anecdotes underscore the value of having a rapid posting cycle to correcting errors in the scientific literature and that results posted to preprint servers were able to correct the record within weeks of the initial publication while the traditional path took six months in both cases.
@@
 Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the Arsenic life paper would have been different had they initially been posted as preprints.
+
+Original Online: 9 February 2015 http://www.sciencedirect.com/science/article/pii/S2405471215000022
+Uh, no online: 29 July 2015 http://www.sciencedirect.com/science/article/pii/S2405471215000162
+Correction:  29 July 2015 http://www.sciencedirect.com/science/article/pii/S2405471215000150
+Read preprint: April 25, 2015 https://zenodo.org/record/17158#.WIprNbGZOiI
+
+Bremm PNAS: May 12, 2016. http://www.pnas.org/content/113/22/E3054.full
+Arakawa PNAS: May 31, 2016. http://www.pnas.org/content/113/22/E3057.full
+Delmont PeerJ: February 2, 2016. https://peerj.com/preprints/1695/
 
@@
 
-***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, we copied the *bioRxiv* on December 31, 2016.
+***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, we downloaded the *bioRxiv* on December 31, 2016.
 We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*.
 Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category.
-When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts (**Figure 1**).
-These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.
 One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint.
 For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories.
+To counter this limitation, we developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, or *pathogen*.
+We identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that we considered microbiology-affiliated.
+These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.
+As the total number of preprints has grown exponentially since the creation of *biorxiv*, submission of microbiology-affiliated preprints has largely followed this growth (**Figure 1A**).
+
+Although preprints are still relatively new, the collection of microbiology-affiliated preprints indicates widespread experimentation with the format and considerable geographic diversity.
 Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r 100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r 100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts)`% have posted 3 or more preprints.
 Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%).
+As the preprint format matures, it will be interesting to see whether the fraction of authors that post multiple preprints increases and whether the geographic diversity amongst those authors is maintained.
 
@@
 Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall.
-To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint.
+To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint (**Figure 1B**).
 The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, mainstream media, peer reviews, and policy documents.
@@
 We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints.
-To allow for a comparison to traditional journals, we considered the citations for preprints posted in 2015 as aggregated by Web of Science.
+To allow for a comparison to traditional journals, we considered the citations for preprints posted in 2015 as aggregated by Web of Science (**Figure 1C**).
 Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`).
@@
 ***Preprints from an author's perspective.*** Posting research as a preprint gives an author great control over when their work is made public.
-Under the traditional peer-review model, an author may need to submit and revise their work multiple times over a long period.
+Under the traditional peer-review model, an author may need to submit and revise their work multiple times to several journals over a long period before it is finally published.
 In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process.
@@
 In 2014, the Schloss laboratory posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform.
-At the same time, we submitted the manuscript for review at PeerJ.
+At the same time, they submitted the manuscript for review at *PeerJ*.
 While the manuscript was under review, we received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry.
-Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to PeerJ that incorporated the original reviews as well as the feedback we received from Pacific Biosciences and the academic scientist.
+Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from Pacific Biosciences and the academic scientist.
 In other cases, our research group has simultaneously posted our manuscripts as preprints and submitted them to a journal.
@@
 As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals.
-**F1000 Prime encourages its members to comment on preprints on the F1000 website**.
 A new venture from *mSphere*, mSphereDirect, actively encourages authors to post their manuscripts as preprints as part of the author-driven editorial process.
@@
 
-An increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method of disseminating their research prior to peer review.
+***Conclusions.*** An increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method of disseminating their research prior to peer review.
 A number of critical concerns remain about how widespread their adoption will be, how they will be treated by traditional journals, and whether peer-review will adapt to new scientific trends and technologies.
@@
 
-This work was supported in part by funding from the National Institutes of Health (**XXXXXXXXXXX** and **XXXXXXXXXXX**).
+This work was supported in part by funding to PDS from the National Institutes of Health (P30DK034933).
 We appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases.
@@
 
-**Figure 1.**
-* How many preprints are being submitted each month - microbiology category and microbiology-ish
+**Figure 1.
+Summary of microbiology-affiliated preprints since the creation of** ***biorxiv.*** The total number of preprints posted for each quarter ending December 31, 2016 has largely tracked the overall submission of preprints to *biorxiv* (A).
+The Altmetric attention scores of preprints posted to *biorxiv* are similar to those published in *mBio* since November 2013 indicating preprints engender a similar level of attention (B).
+The number of times preprints that were published in 2015 have been cited is similar to the number of citations for papers published in *mBio* in 2015 indicates that published preprints are of high quality (C).
 

### 2017-02-07 code/build_figure1.R
Build full figure 1

@@ -1,6 +1,8 @@
 library(ggplot2)
 library(dplyr)
 library(tidyr)
+library(cowplot)
+library(sportcolors)
 
 get_quarter <- function(date){
 
@@ -20,9 +22,19 @@ get_quarter <- function(date){
 	return(quarter)
 }
 
-data <- read.table(file="data/processed/biorxiv_data_summary.tsv", header=T, stringsAsFactors=F)
+my_theme <- theme_classic() +
+							theme(legend.title = element_blank(),
+										legend.background = element_blank(),
+										legend.text = element_text(size=6),
+										legend.key.size = unit(0.5, "lines"),
+										axis.title = element_text(size=8),
+										axis.text = element_text(size=6)
+							)
 
-counts <- data %>% filter(!is.na(date_first_deposited)) %>%
+biorxiv <- read.table(file="data/processed/biorxiv_data_summary.tsv", header=T, stringsAsFactors=F)
+biorxiv$journal_published_doi <- tolower(gsub("http://dx.doi.org/", "", biorxiv$journal_published_doi))
+
+counts <- biorxiv %>% filter(!is.na(date_first_deposited)) %>%
 									mutate(year_quarter = paste(gsub(".*, ", "", date_first_deposited),
 				 																			sapply(date_first_deposited, get_quarter))) %>%
 									group_by(year_quarter) %>%
@@ -31,18 +43,115 @@ counts <- data %>% filter(!is.na(date_first_deposited)) %>%
 
 tidied <- gather(counts, key=dataset, value=n_pp, all_n_pp, micro_n_pp)
 
-ggplot(tidied, aes(x=rep(1:nrow(all_data),2), y=n_pp, group=dataset, col=dataset)) +
+time_course <- ggplot(tidied,
+											aes(x=rep(1:length(unique(tidied$year_quarter)),2),
+													y=n_pp,
+													group=dataset,
+													col=dataset)
+										) +
 			geom_rect(aes(xmin=-Inf, xmax=1.5, ymin=-Inf, ymax=Inf), fill="#CCCCCC", color="#CCCCCC") +
 			geom_rect(aes(xmin=5.5, xmax=9.5, ymin=-Inf, ymax=Inf), fill="#CCCCCC", color="#CCCCCC") +
-			geom_line(size=1.5, lineend="round") +
-			labs(x="Year", y="Number of Preprints Posted per Quarter") +
+			geom_line(lineend="round") +
+			labs(x="Year", y="Number of Preprints\nPosted per Quarter") +
[…]

### 2017-02-07 submission/Schloss_PrePrints_mBio_2017.Rmd
Use citation counts from 2014 and 2015

@@
 biorxiv_cited_affiliated <- biorxiv_cited[biorxiv_cited$is_microbiology | biorxiv_cited$category == "Microbiology",]
-cites_2015 <- grep("2015", biorxiv_cited_affiliated$year_month)
+cites_2015 <- grep("201[45]", biorxiv_cited_affiliated$year_month)
 biorxiv_cited_affiliated_2015 <-  biorxiv_cited_affiliated[cites_2015, "times.cited"]
@@
 We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints.
-To allow for a comparison to traditional journals, we considered the citations for preprints posted in 2015 as aggregated by Web of Science (**Figure 1C**).
+To allow for a comparison to traditional journals, we considered the citations for preprints published in 2014 and 2015 as aggregated by Web of Science (**Figure 1C**).
 Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`).
-For comparison, for the papers published in *mBio* in 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`).
+For comparison, for the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`).
 Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community
@@
 The Altmetric attention scores of preprints posted to *biorxiv* are similar to those published in *mBio* since November 2013 indicating preprints engender a similar level of attention (B).
-The number of times preprints that were published in 2015 have been cited is similar to the number of citations for papers published in *mBio* in 2015 indicates that published preprints are of high quality (C).
+The number of times preprints that were published in 2014 and 2015 have been cited is similar to the number of citations for papers published in *mBio* in 2014 and 2015 indicates that published preprints are frequently cited (C).
+Regions with common background shading in A are from the same year.
+The vertical lines in B and C indicate the median Altmetric impact score and the median number of citations.
 

### 2017-02-07 code/build_figure1.R

@@ -108,8 +108,8 @@ altmetric_plot <- source_altmetric %>% #filter(source == "biorxiv") %>%
 biorxiv_cited <- read.csv("data/wos_counts/biorxiv_wos.csv", stringsAsFactors=F)
 biorxiv_cited$doi <- tolower(biorxiv_cited$doi)
 biorxiv_cited <- inner_join(biorxiv_cited, biorxiv, by=c("doi"="journal_published_doi"))
-biorxiv_cited_affiliated <- biorxiv_cited[micro_affiliated,]
-cites_2015 <- grep("2015", biorxiv_cited_affiliated$year_month)
+biorxiv_cited_affiliated <- biorxiv_cited[biorxiv_cited$is_microbiology | biorxiv_cited$category == "Microbiology",]
+cites_2015 <- grep("201[45]", biorxiv_cited_affiliated$year_month)
 biorxiv_cited_affiliated_2015 <-  biorxiv_cited_affiliated[cites_2015, "times.cited"]
 
 asm_cited <- read.csv("data/wos_counts/asm_wos.csv", stringsAsFactors=F)
@@ -142,7 +142,7 @@ citation_plot <- source_citations %>%
 											scale_x_continuous(expand = c(0.02, 0), limits=c(0,80)) +
 											scale_fill_manual(breaks=names(j), labels=plot_labels, values=paste0("#", team_colors("Chicago Cubs")), name=NULL)+
 											scale_color_manual(breaks=names(j), labels=plot_labels, values=paste0("#", team_colors("Chicago Cubs")), name=NULL)+
-											labs(x="Number of Citations", y="Number of Papers\nPublished in 2015") +
+											labs(x="Number of Citations", y="Number of Papers\nPublished in 2014/2015") +
  											my_theme +
  											theme(legend.position = c(0.8,0.9))
 

### 2017-02-07 code/build_figure1.R
Fix margins around y-axis labels

@@ -149,9 +149,15 @@ citation_plot <- source_citations %>%
 ################################################################################################
 
 ggdraw() +
-	draw_plot(time_course, x=0,y=0.66,width=1,height=0.30) +
-	draw_plot(altmetric_plot, x=0,y=0.33,1,0.30) +
-	draw_plot(citation_plot, x=0,y=0.0,1,0.30) +
+	draw_plot(time_course +
+				theme(axis.title.y = element_text(margin = margin(r=1))),
+				x=0,y=0.66,width=1,height=0.33) +
+	draw_plot(altmetric_plot +
+				theme(axis.title.y = element_text(margin = margin(r=5))),
+				x=0,y=0.33,1,0.33) +
+	draw_plot(citation_plot +
+				theme(axis.title.y = element_text(margin = margin(r=7))),
+				x=0,y=0.0,1,0.33) +
 	draw_plot_label(c("A", "B", "C"), x=c(0,0,0), y=c(1.00,0.66,0.33), size=12) +
 	ggsave('figures/figure1.tiff', width=8.4, height=14, units="cm") +
 	ggsave('figures/figure1.png', width=8.4, height=14, units="cm")

### 2017-02-07 code/build_figure1.R
Remove x-axis ticks from figure 1A

@@ -59,7 +59,7 @@ time_course <- ggplot(tidied,
 													labels=c("All preprints", "Microbiology-affiliated"),
 													values=c("#002c5a", "#ffcb0b"), name=NULL)+
 			my_theme +
-			theme(legend.position = c(0.23,0.92))
+			theme(legend.position = c(0.23,0.92), axis.ticks.x=element_blank())
 
 
 ################################################################################################

### 2017-02-07 submission/Schloss_PrePrints_mBio_2017.Rmd
Add references

@@
 \vspace{25mm}
-Patrick D. Schloss${^\dagger}$
+Patrick D. Schloss${^\dagger}$${^{,1}}$
+
+Stefano Bertuzzi${^2}$
+
+Lynn W. Enquist${^3}$
 
@@
 
-Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
+$1$ Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
+$2$ American Society for Microbiology, Washington, DC
+$3$ Princeton Neuroscience Institute, Princeton University, Princeton, NJ
+
+Format: Perspective or Commentary
+Number of words: ~4500 plus references, figures, and abstract
+
 \end{center}
@@
 
-## Importance
-
 \newpage
@@
 ***Background.*** Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public.
-A preprint is an unpublished manuscript that is made publicly available without going through an official peer-review process.
+A preprint is an unpublished manuscript that is made publicly available without going through an official peer-review process [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016].
 An author can post their manuscript to a preprint server for others to read, share, and make comments.
-Preprints were initially adopted among physicists in the 1960s as a method of sharing interesting research amongst colleagues.
-Eventually, this community evolved into what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University.
+Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues [@Nature1966].
+Eventually, this community evolved into what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011].
 Among physicists and mathematicians, posting a preprint to *arXiv* has become the standard publication strategy followed by submission to a peer-reviewed journal.
-Within those communities researchers have been recognized with international awards for work that has only been posted to *arXiv* without formal review.
 Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
-Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception.
+Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012].
 Considering the broadening adoption of preprints among microbiologists, we sought to explore the specific uses and concerns of preprints amongst microbiologists.
 
-***Landscape of preprint servers.*** In 2013, two preprint servers the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints* were launched to parallel the success of *arXiv*.
+***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched to parallel the success of *arXiv* [@Callaway2013].
 Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
@@
 The broad consensus at this point is that preprints do not constitute prior publication.
-The current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, and *Nature* have a permissive stance towards prior posting of preprints prior to submission.
-Although journals published by *Cell* do not forbid authors from posting preprints prior to submission, they ask authors to consult an editor prior to posting and do not allow authors to post revised preprints that contain revisions that respond to editorial input.
+This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, and *Nature*, which have a permissive stance towards prior posting of preprints prior to submission.
+Although journals published by Cell Press do not forbid authors from posting preprints prior to submission, they ask authors to consult an editor prior to posting and do not allow authors to post revised preprints that contain revisions that respond to editorial input.
 Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work.
-Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated.
+Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated [@PreprintPolicy; @Sherpa].
 
-***Preprints and peer-review.*** The use of preprints for citations in other scientific reports and grant proposals has been called into question because preprints upend the traditional peer-review editorial process.
+***Preprints and peer-review.*** The use of preprints for citations in other scientific reports and grant proposals has been called into question because preprints upend the traditional peer-review editorial process [@Drubin2016].
 It is important to note that this process was adapted to the technologies and trends that have evolved over the past 100 years.
-The formal peer-review system that most journals currently use was not developed until the end of the 1800s with the advent of typewriters and carbon paper (doi:10.1016/S0167-7799(02)01985-6).
+The formal peer-review system that most journals currently use was not developed until the end of the 1800s with the advent of typewriters and carbon paper [@Spier2002].
 Editorial decisions were typically made by a single person or a committee (i.e.
@@
 The growth in science in the mid 1900s resulted in a shift from difficulties finding sufficient numbers of manuscript to publish to having too many manuscripts submitted.
-It has been argued that the widespread adoption of decentralized peer-review was due to the increased specialization and to deal with the large number of manuscript submissions (JAMA 1990;263:1323-1329).
+It has been argued that the widespread adoption of decentralized peer-review was due to the increased specialization and to deal with the large number of manuscript submissions [@Burnham1990].
 Peer-review did not achieve widespread use at many journals, including the *Journal of Bacteriology*, until the 1940s and 1950s.
@@
 This has led to some journals, most notably *PLOS ONE*, calling for referees to place a reduced emphasis on the perceived impact or significance of the work.
-It has also led to the call for replacing or complementing pre-publication peer-review with post-publication peer-review using PubMed Commons, PubPeer, journal-based discussion forums, and other mechanisms.
+It has also led to the call for replacing or complementing pre-publication peer-review with post-publication peer-review using PubMed Commons, PubPeer, journal-based discussion forums, F1000Research, and other mechanisms.
 Alas if scientists are going to depend on post-publication peer-review or informal methods of peer-review for documents like preprints, they must be willing to provide constructive feedback on the work of others.
@@
 As noted above, they represent a formal communication, but are not officially published.
-As the use of preprints grows and our perceptions of preprints matures, there are a number of issues that will need to be addressed.
+As the use of preprints grows and scientists' perceptions of preprints matures, there are a number of issues that will need to be addressed.
 First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the original researcher will lose their ability to claim primacy or their ability to publish the work in a journal.
 Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second.
-A growing number of scientific societies and journals, including ASM view preprints as citable and as a legitimate claim to primacy.
-Some worry that with such protection a researcher can make a claim without valid data to support their claims.
+A growing number of scientific societies and journals, including ASM view preprints as citable and as a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016].
+Some scientists worry that with such protection a researcher can make a claim without valid data to support their claims [@Berg2016].
 This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data.
 A second area of concern is whether a preprint can be used to support a grant proposal.
-Given the length limitations of many funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data.
-Some fear that the use of preprints will allow some to circumvent page limits by posting preliminary manuscripts.
+Given the length limitations placed on grant proposals by funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data.
+Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts.
 We would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
 A third concern is what role preprints should have in assessing a scientist's productivity.
-Clearly use of publication metrics is a contentious topic without considering the place of preprints.
-Regardless, given the propensity for researchers to list manuscripts as being "in preparation" or "in review" on an application or curriculum vitae, listing them instead as preprints that can be reviewed by a committee could be seen as a significant way to enhance an application.
-In fact, several funding agencies are starting to encourage fellowship applicants to include preprints in their materials.
-Others are mandating that researchers post preprints for all of their work prior to submitting the work to a journal.
+Clearly use of publication metrics as an indicator of a scientist's productivity and impact is a contentious topic without even discussing the role of preprints.
+Regardless, given the propensity for researchers to list manuscripts as being "in preparation" or "in review" on an application or curriculum vitae, listing them instead as preprints that can be reviewed by a committee would significantly enhance an application and a reviewer's ability to judge the application.
+In fact, several funding agencies including the Wellcome Trust and the UK Medical Research Council encouraging fellowship applicants to include preprints in their materials; meanwhile, the NIH is in the process of soliciting input from the scientific community on their role in grant applications.
+Others are mandating that researchers post preprints for all of their work prior to submitting the work to a journal [@Dolgin2016].
 Beyond these concerns, preprints are also causing some to change their publication goals.
-Some authors are explicitly stating that a preprint will not be submitted to a journal.
+Some authors are explicitly stating that a preprint will not be submitted to a journal [@SinghChawla2017].
 Although these authors may be a minority of those who post preprints, such an approach may be attractive to those that want to have a mechanism for people to cite a report of a brief research communication, a critique of another publication, or negative results.
@@
 First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies.
-Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; the number of Zika virus-related publications is now over 1,700.
-During this time, more than 110 Zika virus-related preprints have been posted at *bioRxiv*.
+Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of January 2017 the number of Zika virus-related publications was over 1,700.
+During the recent outbreak, more than 110 Zika virus-related preprints have been posted at *bioRxiv*.
 Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus.
@@
 Over the last several years rapid advances in DNA sequencing technologies have fundamentally changed how microbial science is performed.
-One notable technology, the MinIon sequencing platform from Oxford Nanopore has received considerable attention from researchers who post new methods and results to preprint servers.
+One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 90 preprints describing new MinIon-based methods and results to preprint servers.
 For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.
@@
 On February 9, 2015, Cell Systems posted a study by Afshinnekoo et al.
-online.
+online [@Afshinnekoo2015a].
 The study collected and analyzed metagenomic sequence data from the New York City subway system and reported finding *Yersinia pestis* and *Bacillus anthracis*.
@@
 posted a preprint to Zenodo demonstrating that there was no evidence for *B.
-anthracis* in the dataset.
-On July 29, 2015, a critique was published by Cell Systems along with a response from the original authors offering a correction to their manuscript.
+anthracis* in the dataset [@Petit2015].
+On July 29, 2015, a critique was published by Cell Systems along with a response from the original authors offering a correction to their manuscript [@Ackelsberg2015; @Afshinnekoo2015b].
 A second anecdote surrounds the publishing of a draft tardigrade genome in *PNAS*.
 On November 23, 2015 a study of Boothby et al.
-was first published online.
+[@Boothby2015] was first published online.
 The authors posited that 17.5% of its genes came from bacteria, archaea, fungi, plants, and viruses.
 Another group had been analyzing sequence data from a parallel tardigrade genome sequencing project and did not observe the same result.
-By December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants; this analysis would eventually be posted online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016.
-Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016.
+By December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants [@Koutsovoulos2016a]; this analysis would eventually be published online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016 [@Boothby2016; @Koutsovoulos2016b].
+Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016 [@Bemm2016; @Arakawa2016; @Delmont2016].
 These anecdotes underscore the value of having a rapid posting cycle to correcting errors in the scientific literature and that results posted to preprint servers were able to correct the record within weeks of the initial publication while the traditional path took six months in both cases.
 A final notable case where preprints have accelerated the correction of the scientific record was a preprint posted by Bik et al.
-reporting numerous cases of image manipulation in peer reviewed studies.
-Their preprint was posted on April 20, 2016 and published in *mBio* on June 7, 2016.
-Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the Arsenic life paper would have been different had they initially been posted as preprints.
-
-Original Online: 9 February 2015 http://www.sciencedirect.com/science/article/pii/S2405471215000022
-Uh, no online: 29 July 2015 http://www.sciencedirect.com/science/article/pii/S2405471215000162
-Correction:  29 July 2015 http://www.sciencedirect.com/science/article/pii/S2405471215000150
-Read preprint: April 25, 2015 https://zenodo.org/record/17158#.WIprNbGZOiI
-
-Bremm PNAS: May 12, 2016. http://www.pnas.org/content/113/22/E3054.full
-Arakawa PNAS: May 31, 2016. http://www.pnas.org/content/113/22/E3057.full
-Delmont PeerJ: February 2, 2016. https://peerj.com/preprints/1695/
+reporting numerous cases of image manipulation in peer reviewed studies [@Bik2016a].
+Their preprint was posted on April 20, 2016 and published in *mBio* on June 7, 2016 [@Bik2016b].
+Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the infamous "Arsenic Life" paper [@WolfeSimon2010] would have been different had they initially been posted as preprints.
 
@@
 Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism.
-Microbiology journals have policies in place to address these issues that should be easily implemented by preprint servers.
+Although layering requirements on top of preprints detracts from the efficiency of the preprint format, microbiology journals have policies for these issues in place that should be easy to implement by preprint servers.
 
@@
 To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint (**Figure 1B**).
-The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, mainstream media, peer reviews, and policy documents.
+The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, mainstream media, Wikipedia, policy documents, and other sources [@Altmetric].
 A higher score indicates that a preprint received more attention.
@@
 A first example illustrate the utility of preprints for improving access to research and the quality of its reporting.
-In 2014, the Schloss laboratory posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform.
+In 2014, the Schloss laboratory posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform [@Schloss2015].
 At the same time, they submitted the manuscript for review at *PeerJ*.
 While the manuscript was under review, we received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry.
-Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from Pacific Biosciences and the academic scientist.
+Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from Pacific Biosciences and the academic scientist [@Schloss2016a; @Schloss2016b].
 In other cases, our research group has simultaneously posted our manuscripts as preprints and submitted them to a journal.
+Feedback on the preprint has been incorporated with the comments from the traditional editorial process.
 As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **XXXXXXX XX, 2017**.
@@
 A new venture from *mSphere*, mSphereDirect, actively encourages authors to post their manuscripts as preprints as part of the author-driven editorial process.
-In addition to integrating preprints into the traditional editorial process, several professional societies that publish journals have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature.
+In addition to integrating preprints into the traditional editorial process, several professional societies that publish journals have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016].
 These are policies that empower authors and make specific journals more attractive.
@@
 Thus, it is in a journal's best interest to recruit these preprints to their journals.
-Several journals including **XXXXXX** and **XXXXXX** have publicly stated that they scout preprints for this purpose.
+Several journals including *PLOS Genetics* and *Genome Biology* have publicly stated that they scout preprints for this purpose [@Vence2017; @Barsh2016].
 Preprints can also be viewed as a lost opportunity to journals.
 A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal.
-Going forward, it will be interesting to see whether publishers are able to develop innovative approaches so that they can benefit by incorporating preprints into their process or if their influence is reduced by the widespread adoption of preprints.
+Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.
 
-***Conclusions.*** An increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method of disseminating their research prior to peer review.
-A number of critical concerns remain about how widespread their adoption will be, how they will be treated by traditional journals, and whether peer-review will adapt to new scientific trends and technologies.
+***Conclusions.*** An increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method for disseminating their research prior to peer review.
+A number of critical concerns remain about how widespread their adoption will be, how they will be perceived by traditional journals and other scientists, and whether traditional peer-review will adapt to the new scientific trends and technologies.
 Regardless, preprints should offer a great opportunity for both scientists and journals to publish high quality science.
@@
 
-## Figures
+\includegraphics[width=3.5in]{../figures/figure1.png}
 

### 2017-02-07 submission/Schloss_PrePrints_mBio_2017.Rmd
Create tex file

@@
   pdf_document:
+    keep_tex: true
     includes:
@@
 
-$1$ Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
-$2$ American Society for Microbiology, Washington, DC
-$3$ Princeton Neuroscience Institute, Princeton University, Princeton, NJ
+1 Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
 
-Format: Perspective or Commentary
-Number of words: ~4500 plus references, figures, and abstract
+2 American Society for Microbiology, Washington, DC
+
+3 Princeton Neuroscience Institute, Princeton University, Princeton, NJ
+
+\vspace{10mm}
+
+\textbf{Format:} Perspective or Commentary
+
+\textbf{Number of words:} \textasciitilde4500 plus references, figures, and abstract
 
@@
 
+The field of microbiology has experience significant growth due to rapid advances in technology and the influx of scientists driven by a curiosity to understand how bacteria, archaea, microbial eukaryotes, and viruses interact with each other and their environment to sustain myriad biochemical processes that are essential for maintaining the Earth.
+With this explosion in scientific output, a significant bottleneck has been the ability to disseminate this new knowledge to peers and the public in a timely manner.
+Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck and to recruit a broader pool of reviewers prior to submitting to traditional journals.
+Although use of preprints is still limited, early indications are that preprints are as robust and impactful as peer-reviewed papers.
+As publishing moves to embrace advances in internet technology, there are many opportunities for scientists and publishers to benefit from the use of preprints.
+
 \newpage
@@
 Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues [@Nature1966].
-Eventually, this community evolved into what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011].
-Among physicists and mathematicians, posting a preprint to *arXiv* has become the standard publication strategy followed by submission to a peer-reviewed journal.
+While the biological community's commitment to preprints waned, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011].
+Among physicists and mathematicians, posting a preprint to *arXiv* followed by submission to a peer-reviewed journal has become the standard publication strategy.
 Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
 Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012].
-Considering the broadening adoption of preprints among microbiologists, we sought to explore the specific uses and concerns of preprints amongst microbiologists.
+Considering the broadening adoption of preprints among microbiologists, we sought to explore the specific uses of and concerns regarding preprints.
 
-***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched to parallel the success of *arXiv* [@Callaway2013].
+***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013].
 Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
@@
 First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory.
-This difference can be meaningful to authors since some journals, including the ASM Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations.
+This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations.
 Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse.
-This can be relevant for authors hoping to submit their work a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g.
+This can be relevant for authors hoping to submit their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g.
 *Proceedings of the National Academy of Sciences*).
-A cosmetic, but important difference between the two is the layout and feel of the two websites.
+A cosmetic, but still relevant difference between the two is the layout and feel of the two websites.
 Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints.
@@
 For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not.
-There is hope that the National Institutes of Health (NIH) will renew their interest in including preprints in PubMed search results.
+There is also hope that the National Institutes of Health (NIH) will renew their interest in including preprints in PubMed search results.
+As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, it will be important to balance the requirements placed on authors for those features with the current efficiency of the preprint format.
+
+***Specific challenges for microbiology.*** Although preprints offer an efficient and novel venue for disseminating microbiology research, there are several considerations that the scientific community and those that oversee preprint servers must consider.
+It is critical that assurances be given that policies are in place to address these issues.
+First, a significant amount of attention has been given to the potential dual use of microbiology research for individuals seeking to engage in terrorist activities.
+Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research.
+Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results.
+Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism.
+Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers.
 
@@
 ***Preprints and peer-review.*** The use of preprints for citations in other scientific reports and grant proposals has been called into question because preprints upend the traditional peer-review editorial process [@Drubin2016].
-It is important to note that this process was adapted to the technologies and trends that have evolved over the past 100 years.
+It is important to note that the peer-review process was adapted to the technologies and trends that have evolved over the past 100 years.
 The formal peer-review system that most journals currently use was not developed until the end of the 1800s with the advent of typewriters and carbon paper [@Spier2002].
@@
 the editorial board) who had an expertise that covered the scope of the journal.
-As people's science became more specialized, new journals would form to support and provide a source of validation to the new specialty.
-The growth in science in the mid 1900s resulted in a shift from difficulties finding sufficient numbers of manuscript to publish to having too many manuscripts submitted.
+As science became more specialized, new journals would form to support and provide a source of validation to the new specialty.
+The growth in science in the mid 1900s resulted in a shift from journals struggling to find sufficient numbers of manuscript to publish to having too many manuscripts submitted.
 It has been argued that the widespread adoption of decentralized peer-review was due to the increased specialization and to deal with the large number of manuscript submissions [@Burnham1990].
 Peer-review did not achieve widespread use at many journals, including the *Journal of Bacteriology*, until the 1940s and 1950s.
-Given the rapid advances in communication technology and even greater specialization, it is worth pondering whether the current scientific publishing system and peer-review system, in particular, need to continue to adapt with our science.
+Thus the "tradition" of peer-review is only 70 years old.
+Given the rapid advances in communication technology and even greater specialization within microbiology, it is worth pondering whether the current scientific publishing system and peer-review system, in particular, need to continue to adapt with our science.
 
@@
 A common critique of more modern approaches to publishing has been an inability to assess the quality of the science without the validation of peer-review.
-Attached to assertions of the validity of the research has become assertions of the impact and robustness of the research.
+Attached to assertions of the validity of the research has been assertions of the impact and robustness of the research.
 These are all quality assessments that many acknowledge are difficult to assess by the traditional peer-review process.
@@
 As the use of preprints grows and scientists' perceptions of preprints matures, there are a number of issues that will need to be addressed.
-First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the original researcher will lose their ability to claim primacy or their ability to publish the work in a journal.
+First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the preprint author will lose their ability to claim primacy or their ability to publish the work in a journal.
 Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second.
-A growing number of scientific societies and journals, including ASM view preprints as citable and as a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016].
+A growing number of scientific societies and journals, including ASM view preprints as citable and as having a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016].
 Some scientists worry that with such protection a researcher can make a claim without valid data to support their claims [@Berg2016].
@@
 In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly.
-Over the last several years rapid advances in DNA sequencing technologies have fundamentally changed how microbial science is performed.
+Over the last several years there have also been rapid advances in DNA sequencing technologies have fundamentally changed how microbial science is performed.
 One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 90 preprints describing new MinIon-based methods and results to preprint servers.
 For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.
-Second, preprints have proven useful for rapidly correcting the scientific literature.
+Preprints have proven useful for rapidly correcting the scientific literature.
 On February 9, 2015, Cell Systems posted a study by Afshinnekoo et al.
@@
 The study collected and analyzed metagenomic sequence data from the New York City subway system and reported finding *Yersinia pestis* and *Bacillus anthracis*.
-Because of the focus on these two bioterrorism agents, this study generated a considerable amount of press attention.
+Because of the focus on these two bioterrorism agents, this study generated a considerable amount of media attention.
 On April 25, 2015, Petit et al.
-posted a preprint to Zenodo demonstrating that there was no evidence for *B.
-anthracis* in the dataset [@Petit2015].
-On July 29, 2015, a critique was published by Cell Systems along with a response from the original authors offering a correction to their manuscript [@Ackelsberg2015; @Afshinnekoo2015b].
-A second anecdote surrounds the publishing of a draft tardigrade genome in *PNAS*.
-On November 23, 2015 a study of Boothby et al.
+[@Petit2015] posted a preprint to Zenodo demonstrating that there was no evidence for *B.
+anthracis* in the dataset.
+On July 29, 2015, a critique was published by *Cell Systems* along with a response from the original authors offering a correction to their manuscript [@Ackelsberg2015; @Afshinnekoo2015b].
+A second anecdote of using preprints to aid in post-publication peer-review surrounds the publishing of a draft tardigrade genome in *The Proceedings of the National Academy of Sciences*.
+On November 23, 2015 a study by Boothby et al.
 [@Boothby2015] was first published online.
@@
 Another group had been analyzing sequence data from a parallel tardigrade genome sequencing project and did not observe the same result.
-By December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants [@Koutsovoulos2016a]; this analysis would eventually be published online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016 [@Boothby2016; @Koutsovoulos2016b].
+A week later, on December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants [@Koutsovoulos2016a]; this analysis would eventually be published online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016 [@Boothby2016; @Koutsovoulos2016b].
 Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016 [@Bemm2016; @Arakawa2016; @Delmont2016].
@@
 Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the infamous "Arsenic Life" paper [@WolfeSimon2010] would have been different had they initially been posted as preprints.
-
-***Specific challenges for microbiology.*** Although preprints offer an efficient and novel venue for disseminating microbiology research, there are several considerations that the scientific community and those that oversee preprint servers must consider.
-It is critical that assurances be given that policies are in place to address these issues.
-First, a significant amount of attention has been given to the potential dual use of microbiology research for individuals seeking to engage in terrorist activities.
-Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research.
-Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results.
-Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism.
-Although layering requirements on top of preprints detracts from the efficiency of the preprint format, microbiology journals have policies for these issues in place that should be easy to implement by preprint servers.
 
@@
 In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process.
-A first example illustrate the utility of preprints for improving access to research and the quality of its reporting.
+A first example illustrates the utility of preprints for improving access to research and the quality of its reporting.
 In 2014, the Schloss laboratory posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform [@Schloss2015].
 At the same time, they submitted the manuscript for review at *PeerJ*.
-While the manuscript was under review, we received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry.
-Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from Pacific Biosciences and the academic scientist [@Schloss2016a; @Schloss2016b].
-In other cases, our research group has simultaneously posted our manuscripts as preprints and submitted them to a journal.
-Feedback on the preprint has been incorporated with the comments from the traditional editorial process.
-As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **XXXXXXX XX, 2017**.
+While the manuscript was under review, they received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry.
+Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from the academic scientist and Pacific Biosciences.
+It was eventually published by *PeerJ* [@Schloss2016a; @Schloss2016b].
+Since 2015, we have continued to post manuscripts as preprints at the same time as we have submitted manuscripts.
+Although the feedback to other manuscripts has not been as helpful as our initial experience, we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b].
+As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **February XX, 2017**.
 We then solicited feedback on the manuscript using social media.
@@
 
-***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals have in disseminating research if there is broad adoption of preprints.
+***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals will have in disseminating research if there is broad adoption of preprints.
 One perspective is that although authors value immediate accessibility to their work, they also value the editorial support from professional societies and other organizations.
@@
 As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals.
-A new venture from *mSphere*, mSphereDirect, actively encourages authors to post their manuscripts as preprints as part of the author-driven editorial process.
-In addition to integrating preprints into the traditional editorial process, several professional societies that publish journals have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016].
+A new venture from *mSphere*, mSphereDirect, actively encourages authors to post their manuscripts as preprints as part of the author-driven editorial process [@Imperiale2016].
+In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016].
 These are policies that empower authors and make specific journals more attractive.

### 2017-02-07 submission/Schloss_PrePrints_mBio_2017.tex
Create tex file

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Preprinting Microbiology},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{\textbf{Preprinting Microbiology}}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}

\usepackage[none]{hyphenat}

\usepackage{setspace}
\doublespacing
\setlength{\parskip}{1em}

\usepackage{lineno}

\usepackage{pdfpages}
\usepackage{comment}

\begin{document}
\maketitle

\begin{center}
\vspace{25mm}
Patrick D. Schloss${^\dagger}$${^{,1}}$

Stefano Bertuzzi${^2}$

Lynn W. Enquist${^3}$

\vspace{30mm}

$\dagger$ To whom correspondence should be addressed: pschloss@umich.edu

1 Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI

2 American Society for Microbiology, Washington, DC

3 Princeton Neuroscience Institute, Princeton University, Princeton, NJ

\vspace{10mm}

\textbf{Format:} Perspective or Commentary

\textbf{Number of words:} \textasciitilde4500 plus references, figures, and abstract

\end{center}

\newpage

\linenumbers

\subsection{Abstract}\label{abstract}

The field of microbiology has experience significant growth due to rapid
advances in technology and the influx of scientists driven by a
curiosity to understand how bacteria, archaea, microbial eukaryotes, and
viruses interact with each other and their environment to sustain myriad
biochemical processes that are essential for maintaining the Earth. With
this explosion in scientific output, a significant bottleneck has been
the ability to disseminate this new knowledge to peers and the public in
a timely manner. Preprints have emerged as a tool that a growing number
of microbiologists are using to overcome this bottleneck and to recruit
a broader pool of reviewers prior to submitting to traditional journals.
Although use of preprints is still limited, early indications are that
preprints are as robust and impactful as peer-reviewed papers. As
publishing moves to embrace advances in internet technology, there are
many opportunities for scientists and publishers to benefit from the use
of preprints.

\newpage

\textbf{\emph{Background.}} Many scientists, including microbiologists,
have begun to use preprints and other online venues such as social
media, blog posts, and videos as methods to garner attention for their
research and to engage the public. A preprint is an unpublished
manuscript that is made publicly available without going through an
official peer-review process (1--4). An author can post their manuscript
to a preprint server for others to read, share, and make comments.
Preprints were initially adopted among physicists and biologists in the
1960s as a method of sharing interesting research amongst colleagues
(5). While the biological community's commitment to preprints waned, the
physics community adopted what is now the \emph{arXiv} (pronounced
``archive'') preprint server that was hosted at the Los Alamos National
Laboratories from 1991 to 1999 and then at Cornell University (6). Among
physicists and mathematicians, posting a preprint to \emph{arXiv}
followed by submission to a peer-reviewed journal has become the
standard publication strategy. Although \emph{arXiv} has hosted a number
of computational biology papers, the server has not drawn widespread
attention from biologists. Among proponents of \emph{arXiv}, preprints
have aided in the development of research communication by accelerating
the release of the science and helping it to achieve a wider audience
for critique and reception (7). Considering the broadening adoption of
preprints among microbiologists, we sought to explore the specific uses
of and concerns regarding preprints.

\textbf{\emph{Landscape of preprint servers.}} In 2013, two preprint
servers, the \emph{bioRxiv} (pronounced ``bio-archive'') and \emph{PeerJ
Preprints}, were launched as preprint servers for biologists that would
parallel \emph{arXiv} (8). Both platforms offer similar features:
preprint posting is free; each preprint receives a digital object
identifier (DOI) that facilitates the ability to cite preprints in other
scholarly work; if the preprint is ever published, the preprint is
linked to the published version; the submission process for both options
is relatively simple allowing authors to upload a PDF version of their
preprint and supplemental materials; preprints are typically publicly
available in under 24 hours; they have built in venues for authors to
discuss their research with people who leave comments on the manuscript;
preprints undergo a basic screening process to remove submissions with
offensive or non-scientific content; and the sites provide article-level
metrics indicating the number of times an abstract has been accessed or
the preprint has been downloaded. There are several important
differences between the two options. First, \emph{PeerJ Prints} is a
for-profit organization and \emph{bioRxiv} is a non-profit organization
sponsored by Cold Spring Harbor Laboratory. This difference can be
meaningful to authors since some journals, including the American
Society for Microbiology (ASM) Journals, will only accept submissions
that have been posted on preprint servers hosted by non-profit
organizations. Second, preprints at \emph{PeerJ Preprints} are posted
under the Creative Commons Attribution License (CC-BY) and
\emph{bioRxiv} preprints can be posted under one of four CC-BY licenses
or with no permission for reuse. This can be relevant for authors hoping
to submit their work to a journal as journals will not consider
manuscripts posted as preprints under a CC-BY license (e.g.
\emph{Proceedings of the National Academy of Sciences}). A cosmetic, but
still relevant difference between the two is the layout and feel of the
two websites. Compared to the \emph{bioRxiv} site, the \emph{PeerJ
Preprint} site is more fluid, gives readers the ability to ``follow'' a
preprint, and provides better access to article keywords and the ability
to search preprints. With broader acceptance of preprints by traditional
journals, many journals, including all of the ASM journals, have
established mechanisms to directly submit manuscripts that are posted as
preprints on \emph{bioRxiv}. It is only possible to transfer a
\emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many ways,
preprint servers have taken on the feel of a journal. As adoption of
this approach to disseminating research expands, it is likely that the
features of these sites will continue to improve. It is also likely that
interfaces from third-parties will improve. For example, although Google
Scholar includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ
Preprints} in their search results, PubMed and Web of Science do not.
There is also hope that the National Institutes of Health (NIH) will
renew their interest in including preprints in PubMed search results. As
preprint servers begin to look and act like traditional journals by
incorporating features and interfaces, it will be important to balance
the requirements placed on authors for those features with the current
efficiency of the preprint format.

\textbf{\emph{Specific challenges for microbiology.}} Although preprints
offer an efficient and novel venue for disseminating microbiology
research, there are several considerations that the scientific community
and those that oversee preprint servers must consider. It is critical
that assurances be given that policies are in place to address these
issues. First, a significant amount of attention has been given to the
potential dual use of microbiology research for individuals seeking to
engage in terrorist activities. Second, for researchers engaging in
research that involves human subjects it is critical that assurances be
made that institutional review boards have been consulted and have
approved of the research. Third, there is significant concern regarding
researchers hiding potential conflicts of interest that could affect a
project's experimental design, analysis, and interpretation of results.
Finally, recent expansions in scientific publishing have revealed
numerous cases of plagiarism. Again, while hoping to maintain the
efficiency of the preprint format, traditional microbiology journals
have policies for these issues in place that should be easy to implement
by preprint servers.

\textbf{\emph{Acceptance of preprints by journals.}} An early
controversy encountered by researchers interested in posting their work
as preprints as a stage in disseminating their research was whether it
constituted prior publication. The broad consensus at this point is that
preprints do not constitute prior publication. This consensus is
reflected in the current policies of journals that commonly publish
microbiology research including those published by ASM, the Microbiology
Society, International Society for Microbial Ecology, PLOS, the
\emph{Proceedings of the National Academy of Science}, \emph{Science},
and \emph{Nature}, which have a permissive stance towards prior posting
of preprints prior to submission. Although journals published by Cell
Press do not forbid authors from posting preprints prior to submission,
they ask authors to consult an editor prior to posting and do not allow
authors to post revised preprints that contain revisions that respond to
editorial input. Considering the relatively fluid nature of many of
these policies and the journals' specific policies, prospective authors
should be aware of the positions taken by the journals where they may
eventually submit their work. Comprehensive lists of journals' attitudes
towards preprints are available online and are regularly updated (9,
10).

\textbf{\emph{Preprints and peer-review.}} The use of preprints for
citations in other scientific reports and grant proposals has been
called into question because preprints upend the traditional peer-review
editorial process (11). It is important to note that the peer-review
process was adapted to the technologies and trends that have evolved
over the past 100 years. The formal peer-review system that most
journals currently use was not developed until the end of the 1800s with
the advent of typewriters and carbon paper (12). Editorial decisions
were typically made by a single person or a committee (i.e.~the
editorial board) who had an expertise that covered the scope of the
journal. As science became more specialized, new journals would form to
support and provide a source of validation to the new specialty. The
growth in science in the mid 1900s resulted in a shift from journals
struggling to find sufficient numbers of manuscript to publish to having
too many manuscripts submitted. It has been argued that the widespread
adoption of decentralized peer-review was due to the increased
specialization and to deal with the large number of manuscript
submissions (13). Peer-review did not achieve widespread use at many
journals, including the \emph{Journal of Bacteriology}, until the 1940s
and 1950s. Thus the ``tradition'' of peer-review is only 70 years old.
Given the rapid advances in communication technology and even greater
specialization within microbiology, it is worth pondering whether the
current scientific publishing system and peer-review system, in
particular, need to continue to adapt with our science.

Communicating research has traditionally been done within research group
meetings, departmental seminars, conferences, and as publications. Along
this continuum, there is an assumption that the quality of the science
has been improved because it has been vetted by more experts in the
field. The public dissemination of one's research is a critical
component of the scientific method. By describing their research,
scientists subject their work to formal and informal peer review. Their
research is scrutinized, praised, and probed to identify questions that
help seed the next iteration of the scientific method. A common critique
of more modern approaches to publishing has been an inability to assess
the quality of the science without the validation of peer-review.
Attached to assertions of the validity of the research has been
assertions of the impact and robustness of the research. These are all
quality assessments that many acknowledge are difficult to assess by the
traditional peer-review process. This has led to some journals, most
notably \emph{PLOS ONE}, calling for referees to place a reduced
emphasis on the perceived impact or significance of the work. It has
also led to the call for replacing or complementing pre-publication
peer-review with post-publication peer-review using PubMed Commons,
PubPeer, journal-based discussion forums, F1000Research, and other
mechanisms. Alas if scientists are going to depend on post-publication
peer-review or informal methods of peer-review for documents like
preprints, they must be willing to provide constructive feedback on the
work of others.

\textbf{\emph{Preprints have the potential to change the advancement of
science.}} Preprints are often viewed as existing in a state of
scientific limbo. As noted above, they represent a formal communication,
but are not officially published. As the use of preprints grows and
scientists' perceptions of preprints matures, there are a number of
issues that will need to be addressed. First, a common concern is that
if a researcher posts their work as a preprint, it will be ``scooped''
by another researcher and the preprint author will lose their ability to
claim primacy or their ability to publish the work in a journal.
Considering the preprint is a citable work with a DOI, it would, in
fact, be the preprint author that scooped the second. A growing number
of scientific societies and journals, including ASM view preprints as
citable and as having a legitimate claim to primacy (1, 14--16). Some
scientists worry that with such protection a researcher can make a claim
without valid data to support their claims (3). This is possible;
however, it is also the responsibility of the scientific community to
utilize the peer-review mechanisms that are available to comment on
those preprints pointing out methodological problems or to indicate that
they are speaking beyond the data. A second area of concern is whether a
preprint can be used to support a grant proposal. Given the length
limitations placed on grant proposals by funding agencies, there is a
push to cite previous work to indicate a research team's competence in
an area or to provide preliminary data. Some fear that the use of
preprints will allow scientists to circumvent page limits by posting
preliminary manuscripts. We would hope that both consumers of preprints
and grant proposal reviewers would be able to differentiate between
someone trying to game the system and someone that is using preprints as
a mechanism to improve their science. A third concern is what role
preprints should have in assessing a scientist's productivity. Clearly
use of publication metrics as an indicator of a scientist's productivity
and impact is a contentious topic without even discussing the role of
preprints. Regardless, given the propensity for researchers to list
manuscripts as being ``in preparation'' or ``in review'' on an
application or curriculum vitae, listing them instead as preprints that
can be reviewed by a committee would significantly enhance an
application and a reviewer's ability to judge the application. In fact,
several funding agencies including the Wellcome Trust and the UK Medical
Research Council encouraging fellowship applicants to include preprints
in their materials; meanwhile, the NIH is in the process of soliciting
input from the scientific community on their role in grant applications.
Others are mandating that researchers post preprints for all of their
work prior to submitting the work to a journal (17). Beyond these
concerns, preprints are also causing some to change their publication
goals. Some authors are explicitly stating that a preprint will not be
submitted to a journal (18). Although these authors may be a minority of
those who post preprints, such an approach may be attractive to those
that want to have a mechanism for people to cite a report of a brief
research communication, a critique of another publication, or negative
results. It is clear that the adoption of preprints will challenge how
scientists interact and evaluate each other's work. There is great
potential to empower researchers by controlling when a citable piece of
work is made public.

\textbf{\emph{Microbiology anecdotes.}} The peer-review editorial
process can be lengthy and adversarial. In contrast, preprints represent
a rapid and potentially collaborative method for disseminating research.
Several anecdotes from the microbiology literature are emblematic of
benefits of the rapid release cycle that is inherent in the use of
preprints. First, preprints have proven useful for rapidly disseminating
results for disease outbreaks and new technologies. Prior to the recent
Zika virus outbreak there were approximately 50 publications that
touched on the biology and epidemiology of the virus; as of January 2017
the number of Zika virus-related publications was over 1,700. During the
recent outbreak, more than 110 Zika virus-related preprints have been
posted at \emph{bioRxiv}. Any manuscript that was published went through
several month delays in releasing information to health care workers,
the public, and scientists needing to learn new methods to study a
previously obscure virus. In contrast, those that posted their work as a
preprint were able to disseminate their methods and results instantly.
Over the last several years there have also been rapid advances in DNA
sequencing technologies have fundamentally changed how microbial science
is performed. One notable technology, the MinIon sequencing platform
from Oxford Nanopore, has received considerable attention from
researchers who have posted more than 90 preprints describing new
MinIon-based methods and results to preprint servers. For such a rapidly
developing technology, the ability to share and consume methods from
other scientists has created a feed forward effect where the technology
has likely advanced at a faster rate than it otherwise would have.
Preprints have proven useful for rapidly correcting the scientific
literature. On February 9, 2015, Cell Systems posted a study by
Afshinnekoo et al. online (19). The study collected and analyzed
metagenomic sequence data from the New York City subway system and
reported finding \emph{Yersinia pestis} and \emph{Bacillus anthracis}.
Because of the focus on these two bioterrorism agents, this study
generated a considerable amount of media attention. On April 25, 2015,
Petit et al. (20) posted a preprint to Zenodo demonstrating that there
was no evidence for \emph{B. anthracis} in the dataset. On July 29,
2015, a critique was published by \emph{Cell Systems} along with a
response from the original authors offering a correction to their
manuscript (21, 22). A second anecdote of using preprints to aid in
post-publication peer-review surrounds the publishing of a draft
tardigrade genome in \emph{The Proceedings of the National Academy of
Sciences}. On November 23, 2015 a study by Boothby et al. (23) was first
published online. The authors posited that 17.5\% of its genes came from
bacteria, archaea, fungi, plants, and viruses. Another group had been
analyzing sequence data from a parallel tardigrade genome sequencing
project and did not observe the same result. A week later, on December
1, 2015, the second group had posted a preprint comparing the two genome
sequences and demonstrating that the exciting claims of horizontal gene
transfer were really the product of contaminants (24); this analysis
would eventually be published online by the original journal on March
24, 2016 followed by a rebuttal by the original authors on May 31, 2016
(25, 26). Two other analyses of the original data were published in May
2016 and a third was posted as a preprint on February 2, 2016 (27--29).
These anecdotes underscore the value of having a rapid posting cycle to
correcting errors in the scientific literature and that results posted
to preprint servers were able to correct the record within weeks of the
initial publication while the traditional path took six months in both
cases. A final notable case where preprints have accelerated the
correction of the scientific record was a preprint posted by Bik et al.
reporting numerous cases of image manipulation in peer reviewed studies
(30). Their preprint was posted on April 20, 2016 and published in
\emph{mBio} on June 7, 2016 (31). Instead of using preprints to react to
published papers that have been through peer review, it would be
interesting to consider how the editorial process for these examples and
the infamous ``Arsenic Life'' paper (32) would have been different had
they initially been posted as preprints.

\textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
analyze the use of preprints, we downloaded the \emph{bioRxiv} on
December 31, 2016. We chose to analyze the use of \emph{bioRxiv}
preprints because these preprints are amenable for submission to ASM
journals and there were 7,434 preprints compared to the 2,650 available
at \emph{PeerJ Preprint}. Among the 7,434 preprints on bioRxiv, 329 were
assigned by the authors into the Microbiology category. One limitation
of the \emph{bioRxiv} interface is the inability to assign manuscripts
to multiple categories or to tag the content of the preprint. For
example, this manuscript could be assigned to either the Microbiology or
the Scientific Communication and Education categories. To counter this
limitation, we developed a more permissive approach that classified
preprints as being microbiology-affiliated if their title or abstract
had words containing \emph{yeast}, \emph{fung}, \emph{viral},
\emph{virus}, \emph{archaea}, \emph{bacteri}, \emph{microb},
\emph{microorganism}, or \emph{pathogen}. We identified 1,228 additional
manuscripts that we considered microbiology-affiliated. These
microbiology-affiliated preprints were primarily assigned to the
Evolutionary Biology (N=221), Genomics (N=184), or Bioinformatics
(N=182) categories. As the total number of preprints has grown
exponentially since the creation of \emph{biorxiv}, submission of
microbiology-affiliated preprints has largely followed this growth
(\textbf{Figure 1A}).

Although preprints are still relatively new, the collection of
microbiology-affiliated preprints indicates widespread experimentation
with the format and considerable geographic diversity. Reflecting the
still relatively novelty of preprints, 1,132 (86.15\%) corresponding
authors who submitted a microbiology-affiliated manuscript (N=1,314
total) have posted a single preprint and 3.58\% have posted 3 or more
preprints. Corresponding authors that have posted
microbiology-affiliated preprints are from 60 countries and are
primarily affiliated with institutions in the United States (50.80\% of
microbiology-affiliated preprints), United Kingdom (11.95\%), and
Germany (4.17\%). As the preprint format matures, it will be interesting
to see whether the fraction of authors that post multiple preprints
increases and whether the geographic diversity amongst those authors is
maintained.

As stated above, preprints offer researchers the opportunity to improve
the quality of their work by adding a more formal and public step to the
scientific process. Among the microbiology-affiliated manuscripts, 146
(9.32\%) had been commented on at least once and only 35 (2.23\%) more
than three times using the \emph{bioRxiv}-hosted commenting feature.
Although the hosted commenting is only one mechanism for peer review,
this result was somewhat disturbing since the preprint model implicitly
depends on people's willingness to offer others feedback. Regardless,
authors do appear to be incorporating feedback from colleagues or
editorial insights from journals as 404 (25.80\%) of preprints were
revised at least once. Among the preprints posted prior to January 1,
2016, 31.61\% of the Microbiology category preprints, 35.12\% of the
microbiology-affiliated preprints, and 33.79\% of all preprints have
been published. As noted above, not all authors submit their preprints
to journals. This would indicate that the ``acceptance rates'' are
actually higher. Regardless, considering that these acceptance rates are
higher than many peer-reviewed journals (e.g.~approximately 20\% at ASM
Journals), these results dispel the critique that preprints represent
overly preliminary research.

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics we sought to quantify the
effect that microbiology-affiliated preprints have had on the work of
others. Using the download statistics associated with each preprint, we
found that the median number of times an abstract or PDF had been
accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to 568),
respectively. These values represent two aspects of posting a preprint.
First, they reflect the number of times people were able to access
science before it was published. Second, they reflect the number of
times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the public, we obtained the Altmetric
Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
Attention Score measures the number of times a preprint or paper is
mentioned in social media, mainstream media, Wikipedia, policy
documents, and other sources (33). A higher score indicates that a
preprint received more attention. Microbiology-affiliated preprints have
had a median Altmetric Attention Score of 7.28 (IQR: 3.25 to 16.3495)
and those of all preprints hosted at \emph{bioRxiv} have had a median
score of 7.05 (IQR: 3 to 15.556). For comparison, the median Altmetric
Attention Score for articles published in \emph{mBio} published since
November 2013 was 4.45 (IQR: 1.25 to 13.604). Of all scholarship tracked
by Altmetric, the median Altmetric Attention Score for preprints posted
at \emph{biorxiv} ranks at the 86 percentile (IQR: 66 to 94. A more
traditional and controversial metric of impact has been the number of
citations an article receives. We obtained the number of citations for
the published versions of manuscripts that were initially posted as
preprints. To allow for a comparison to traditional journals, we
considered the citations for preprints published in 2014 and 2015 as
aggregated by Web of Science (\textbf{Figure 1C}). Among the preprints
that were published and could be found in the Web of Science database,
the median number of citations was 6.50 (IQR: 2-14; mean: 13.60). For
comparison, for the papers published in \emph{mBio} in 2014 and 2015,
the median number of citations was 5 (IQR: 2-9; mean: 6.73). Although it
is impossible to quantify the quality or impact of research with
individual metrics, it is clear that preprints and the publications that
result from them are broadly accepted by the microbiology community

\textbf{\emph{Preprints from an author's perspective.}} Posting research
as a preprint gives an author great control over when their work is made
public. Under the traditional peer-review model, an author may need to
submit and revise their work multiple times to several journals over a
long period before it is finally published. In contrast, an author can
post the preprint at the start of the process for others to consume and
comment on as it works its way through the editorial process. A first
example illustrates the utility of preprints for improving access to
research and the quality of its reporting. In 2014, the Schloss
laboratory posted a preprint to \emph{PeerJ Preprints} describing a
method of sequencing 16S rRNA gene sequences using the Pacific
Biosciences sequencing platform (34). At the same time, they submitted
the manuscript for review at \emph{PeerJ}. While the manuscript was
under review, they received feedback from an academic scientist and from
scientists at Pacific Biosciences that the impact of the results could
be enhanced by using a recently released version of the sequencing
chemistry. Instead of ignoring this feedback and resubmitting the
manuscript to address the reviews, we generated new data and submitted
an updated preprint a year later with a simultaneous submission to
\emph{PeerJ} that incorporated the original reviews as well as the
feedback we received from the academic scientist and Pacific
Biosciences. It was eventually published by \emph{PeerJ} (35, 36). Since
2015, we have continued to post manuscripts as preprints at the same
time as we have submitted manuscripts. Although the feedback to other
manuscripts has not been as helpful as our initial experience, we were
able to sidestep lengthy review processes by immediately making our
results available; in one case our preprint was available 7 months ahead
of the final published version (37, 38). As a second example, this
manuscript was posted to \emph{bioRxiv} as a preprint on
\textbf{February XX, 2017}. We then solicited feedback on the manuscript
using social media. Two weeks later, we incorporated the comments and
posted a revised preprint and submitted the manuscript to \emph{mBio}.
During that time, the abstract was read \textbf{XXXX} times and the PDF
was accessed \textbf{XXXX} times. This process engaged \textbf{XXXX}
commenters on \emph{bioRxiv}, \textbf{XXXX} people on Twitter,
\textbf{XXXX} on Facebook, and \textbf{XXXX} via email. We received
useful feedback from \textbf{XXX} people. Compared to the two or three
scientists that typically review a manuscript, this experience engaged a
much larger and more diverse community than had we foregone the posting
of a preprint. Although there are concerns regarding the quality of the
science posted to a preprint server, we contend that responsible use of
preprints as a part of the scientific process can significantly enhance
the science.

\textbf{\emph{Preprints from a publisher's perspective.}} A lingering
question is what role traditional journals will have in disseminating
research if there is broad adoption of preprints. One perspective is
that although authors value immediate accessibility to their work, they
also value the editorial support from professional societies and other
organizations. Furthermore, the professional copyediting, layout, and
publicity that these publishers offer are also unique features of
traditional journals. An alternative perspective is that preprints will
eventually replace traditional journals. Certainly, this is a radical
perspective, but it does serve to motivate publishers to address what
they can offer preprint authors. By adopting preprint-friendly policies,
journals can create an attractive environment for authors. As discussed
above, a growing number of journals have created mechanisms for authors
to directly submit preprints to their journals. A new venture from
\emph{mSphere}, mSphereDirect, actively encourages authors to post their
manuscripts as preprints as part of the author-driven editorial process
(39). In addition to integrating preprints into the traditional
editorial process, several professional societies have also explicitly
supported citation of preprints in their other publications and
recognize the priority of preprints in the literature (14--16). These
are policies that empower authors and make specific journals more
attractive. Other practices have great potential to improve the
reputation of journals. As measured above, preprints are able to garner
attention on par with papers published in highly selective microbiology
journals. Thus, it is in a journal's best interest to recruit these
preprints to their journals. Several journals including \emph{PLOS
Genetics} and \emph{Genome Biology} have publicly stated that they scout
preprints for this purpose (40, 41). Preprints can also be viewed as a
lost opportunity to journals. A preprint that garners significant
attention may be ignored when it is finally published, brining little
additional attention to the journal. Going forward, it will be
interesting to see the innovative approaches that publishers develop so
that they can benefit by incorporating preprints into their process and
whether publishers' influence is reduced by the widespread adoption of
preprints.

\textbf{\emph{Conclusions.}} An increasing number of microbiologists are
posting their unpublished work to preprint severs as an efficient method
for disseminating their research prior to peer review. A number of
critical concerns remain about how widespread their adoption will be,
how they will be perceived by traditional journals and other scientists,
and whether traditional peer-review will adapt to the new scientific
trends and technologies. Regardless, preprints should offer a great
opportunity for both scientists and journals to publish high quality
science.

\subsection{Acknowledgements}\label{acknowledgements}

This work was supported in part by funding to PDS from the National
Institutes of Health (P30DK034933). We appreciate the support of
Altmetric, Inc and Thompson Reuters who provided advanced programming
interface (API) access to their databases. The data, code, and an
executable R-markdown version of this manuscript are available at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.

\newpage

\includegraphics[width=3.5in]{../figures/figure1.png}

\textbf{Figure 1. Summary of microbiology-affiliated preprints since the
creation of} \textbf{\emph{biorxiv.}} The total number of preprints
posted for each quarter ending December 31, 2016 has largely tracked the
overall submission of preprints to \emph{biorxiv} (A). The Altmetric
attention scores of preprints posted to \emph{biorxiv} are similar to
those published in \emph{mBio} since November 2013 indicating preprints
engender a similar level of attention (B). The number of times preprints
that were published in 2014 and 2015 have been cited is similar to the
number of citations for papers published in \emph{mBio} in 2014 and 2015
indicates that published preprints are frequently cited (C). Regions
with common background shading in A are from the same year. The vertical
lines in B and C indicate the median Altmetric impact score and the
median number of citations.

\newpage

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\hypertarget{ref-Vale2015}{}
1. \textbf{Vale RD}. 2015. Accelerating scientific publication in
biology. Proceedings of the National Academy of Sciences
\textbf{112}:13439--13446.
doi:\href{https://doi.org/10.1073/pnas.1511912112}{10.1073/pnas.1511912112}.

\hypertarget{ref-DesjardinsProulx2013}{}
2. \textbf{Desjardins-Proulx P}, \textbf{White EP}, \textbf{Adamson JJ},
\textbf{Ram K}, \textbf{Poisot T}, \textbf{Gravel D}. 2013. The case for
open preprints in biology. PLoS Biology \textbf{11}:e1001563.
doi:\href{https://doi.org/10.1371/journal.pbio.1001563}{10.1371/journal.pbio.1001563}.

\hypertarget{ref-Berg2016}{}
3. \textbf{Berg JM}, \textbf{Bhalla N}, \textbf{Bourne PE},
\textbf{Chalfie M}, \textbf{Drubin DG}, \textbf{Fraser JS},
\textbf{Greider CW}, \textbf{Hendricks M}, \textbf{Jones C},
\textbf{Kiley R}, \textbf{King S}, \textbf{Kirschner MW},
\textbf{Krumholz HM}, \textbf{Lehmann R}, \textbf{Leptin M},
\textbf{Pulverer B}, \textbf{Rosenzweig B}, \textbf{Spiro JE},
\textbf{Stebbins M}, \textbf{Strasser C}, \textbf{Swaminathan S},
\textbf{Turner P}, \textbf{Vale RD}, \textbf{VijayRaghavan K},
\textbf{Wolberger C}. 2016. Preprints for the life sciences. Science
\textbf{352}:899--901.
doi:\href{https://doi.org/10.1126/science.aaf9133}{10.1126/science.aaf9133}.

\hypertarget{ref-Bhalla2016}{}
4. \textbf{Bhalla N}. 2016. Has the time come for preprints in biology?
Molecular Biology of the Cell \textbf{27}:1185--1187.
doi:\href{https://doi.org/10.1091/mbc.e16-02-0123}{10.1091/mbc.e16-02-0123}.

\hypertarget{ref-Nature1966}{}
5. 1966. Preprints galore. Nature \textbf{211}:897--898.
doi:\href{https://doi.org/10.1038/211897a0}{10.1038/211897a0}.

\hypertarget{ref-Ginsparg2011}{}
6. \textbf{Ginsparg P}. 2011. ArXiv at 20. Nature \textbf{476}:145--147.
doi:\href{https://doi.org/10.1038/476145a}{10.1038/476145a}.

\hypertarget{ref-Shuai2012}{}
7. \textbf{Shuai X}, \textbf{Pepe A}, \textbf{Bollen J}. 2012. How the
scientific community reacts to newly submitted preprints: Article
downloads, twitter mentions, and citations. PLoS ONE \textbf{7}:e47523.
doi:\href{https://doi.org/10.1371/journal.pone.0047523}{10.1371/journal.pone.0047523}.

\hypertarget{ref-Callaway2013}{}
8. \textbf{Callaway E}. 2013. Biomedical journal and publisher hope to
bring preprints to life. Nature Medicine \textbf{19}:512--512.
doi:\href{https://doi.org/10.1038/nm0513-512}{10.1038/nm0513-512}.

\hypertarget{ref-PreprintPolicy}{}
9. List of academic journals by preprint policy.
\url{https://en.wikipedia.org/wiki/List_of_academic_journals_by_preprint_policy}.

\hypertarget{ref-Sherpa}{}
10. Publisher copyright policies \& self-archiving.
\url{http://www.sherpa.ac.uk/romeo/index.php}.

\hypertarget{ref-Drubin2016}{}
11. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
articles and why MBoC quickly embraced preprints. Molecular Biology of
the Cell \textbf{27}:3181--3182.
doi:\href{https://doi.org/10.1091/mbc.e16-09-0651}{10.1091/mbc.e16-09-0651}.

\hypertarget{ref-Spier2002}{}
12. \textbf{Spier R}. 2002. The history of the peer-review process.
Trends in Biotechnology \textbf{20}:357--358.
doi:\href{https://doi.org/10.1016/s0167-7799(02)01985-6}{10.1016/s0167-7799(02)01985-6}.

\hypertarget{ref-Burnham1990}{}
13. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
JAMA: The Journal of the American Medical Association \textbf{263}:1323.
doi:\href{https://doi.org/10.1001/jama.1990.03440100023003}{10.1001/jama.1990.03440100023003}.

\hypertarget{ref-Pulverer2016}{}
14. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
\textbf{35}:2617--2619.
doi:\href{https://doi.org/10.15252/embj.201670030}{10.15252/embj.201670030}.

\hypertarget{ref-Loew2016}{}
15. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
\textbf{111}:E01--E02.
doi:\href{https://doi.org/10.1016/j.bpj.2016.06.035}{10.1016/j.bpj.2016.06.035}.

\hypertarget{ref-Vale2016}{}
16. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
the life sciences. eLife \textbf{5}.
doi:\href{https://doi.org/10.7554/elife.16931}{10.7554/elife.16931}.

\hypertarget{ref-Dolgin2016}{}
17. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
Nature.
doi:\href{https://doi.org/10.1038/nature.2016.21074}{10.1038/nature.2016.21074}.

\hypertarget{ref-SinghChawla2017}{}
18. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
Nature.
doi:\href{https://doi.org/10.1038/nature.2017.21333}{10.1038/nature.2017.21333}.

\hypertarget{ref-Afshinnekoo2015a}{}
19. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
\textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
\textbf{Maritz JM}, \textbf{Reeves D}, \textbf{Gandara J},
\textbf{Chhangawala S}, \textbf{Ahsanuddin S}, \textbf{Simmons A},
\textbf{Nessel T}, \textbf{Sundaresh B}, \textbf{Pereira E},
\textbf{Jorgensen E}, \textbf{Kolokotronis S-O}, \textbf{Kirchberger N},
\textbf{Garcia I}, \textbf{Gandara D}, \textbf{Dhanraj S},
\textbf{Nawrin T}, \textbf{Saletore Y}, \textbf{Alexander N},
\textbf{Vijay P}, \textbf{Hénaff EM}, \textbf{Zumbo P}, \textbf{Walsh
M}, \textbf{O'Mullan GD}, \textbf{Tighe S}, \textbf{Dudley JT},
\textbf{Dunaif A}, \textbf{Ennis S}, \textbf{O'Halloran E},
\textbf{Magalhaes TR}, \textbf{Boone B}, \textbf{Jones AL}, \textbf{Muth
TR}, \textbf{Paolantonio KS}, \textbf{Alter E}, \textbf{Schadt EE},
\textbf{Garbarino J}, \textbf{Prill RJ}, \textbf{Carlton JM},
\textbf{Levy S}, \textbf{Mason CE}. 2015. Geospatial resolution of human
and bacterial diversity with city-scale metagenomics. Cell Systems
\textbf{1}:72--87.
doi:\href{https://doi.org/10.1016/j.cels.2015.01.001}{10.1016/j.cels.2015.01.001}.

\hypertarget{ref-Petit2015}{}
20. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
\textbf{Read TD}. 2015. Searching for anthrax in the New York City
subway metagenome.
doi:\href{https://doi.org/10.5281/zenodo.17158}{10.5281/zenodo.17158}.

\hypertarget{ref-Ackelsberg2015}{}
21. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
\textbf{Petersen J}, \textbf{Mead P}, \textbf{Schriefer M},
\textbf{Kingry L}, \textbf{Hoffmaster A}, \textbf{Gee JE}. 2015. Lack of
evidence for plague or anthrax on the new york city subway. Cell Systems
\textbf{1}:4--5.
doi:\href{https://doi.org/10.1016/j.cels.2015.07.008}{10.1016/j.cels.2015.07.008}.

\hypertarget{ref-Afshinnekoo2015b}{}
22. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
\textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
\textbf{Maritz JM}, \textbf{Reeves D}, \textbf{Gandara J},
\textbf{Chhangawala S}, \textbf{Ahsanuddin S}, \textbf{Simmons A},
\textbf{Nessel T}, \textbf{Sundaresh B}, \textbf{Pereira E},
\textbf{Jorgensen E}, \textbf{Kolokotronis S-O}, \textbf{Kirchberger N},
\textbf{Garcia I}, \textbf{Gandara D}, \textbf{Dhanraj S},
\textbf{Nawrin T}, \textbf{Saletore Y}, \textbf{Alexander N},
\textbf{Vijay P}, \textbf{Hénaff EM}, \textbf{Zumbo P}, \textbf{Walsh
M}, \textbf{O'Mullan GD}, \textbf{Tighe S}, \textbf{Dudley JT},
\textbf{Dunaif A}, \textbf{Ennis S}, \textbf{O'Halloran E},
\textbf{Magalhaes TR}, \textbf{Boone B}, \textbf{Jones AL}, \textbf{Muth
TR}, \textbf{Paolantonio KS}, \textbf{Alter E}, \textbf{Schadt EE},
\textbf{Garbarino J}, \textbf{Prill RJ}, \textbf{Carlton JM},
\textbf{Levy S}, \textbf{Mason CE}. 2015. Modern methods for delineating
metagenomic complexity. Cell Systems \textbf{1}:6--7.
doi:\href{https://doi.org/10.1016/j.cels.2015.07.007}{10.1016/j.cels.2015.07.007}.

\hypertarget{ref-Boothby2015}{}
23. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
\textbf{Wang JR}, \textbf{Patanella KA}, \textbf{Nishimura EO},
\textbf{Tintori SC}, \textbf{Li Q}, \textbf{Jones CD}, \textbf{Yandell
M}, \textbf{Messina DN}, \textbf{Glasscock J}, \textbf{Goldstein B}.
2015. Evidence for extensive horizontal gene transfer from the draft
genome of a tardigrade. Proceedings of the National Academy of Sciences
\textbf{112}:15976--15981.
doi:\href{https://doi.org/10.1073/pnas.1510461112}{10.1073/pnas.1510461112}.

\hypertarget{ref-Koutsovoulos2016a}{}
24. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
\textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
H}, \textbf{Thomas F}, \textbf{Aboobaker A}, \textbf{Blaxter M}. 2016.
No evidence for extensive horizontal gene transfer in the genome of the
tardigrade hypsibius dujardini. bioRxiv 033464.
doi:\href{https://doi.org/10.1101/033464}{10.1101/033464}.

\hypertarget{ref-Boothby2016}{}
25. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
al. and arakawa: Identifying foreign genes in independentHypsibius
dujardinigenome assemblies. Proceedings of the National Academy of
Sciences \textbf{113}:E3058--E3061.
doi:\href{https://doi.org/10.1073/pnas.1601149113}{10.1073/pnas.1601149113}.

\hypertarget{ref-Koutsovoulos2016b}{}
26. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
\textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
H}, \textbf{Thomas F}, \textbf{Aboobaker AA}, \textbf{Blaxter M}. 2016.
No evidence for extensive horizontal gene transfer in the genome of the
tardigradeHypsibius dujardini. Proceedings of the National Academy of
Sciences \textbf{113}:5053--5058.
doi:\href{https://doi.org/10.1073/pnas.1600338113}{10.1073/pnas.1600338113}.

\hypertarget{ref-Bemm2016}{}
27. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
\textbf{Förster F}. 2016. Genome of a tardigrade: Horizontal gene
transfer or bacterial contamination? Proceedings of the National Academy
of Sciences \textbf{113}:E3054--E3056.
doi:\href{https://doi.org/10.1073/pnas.1525116113}{10.1073/pnas.1525116113}.

\hypertarget{ref-Arakawa2016}{}
28. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
transfer from the draft genome of a tardigrade. Proceedings of the
National Academy of Sciences \textbf{113}:E3057--E3057.
doi:\href{https://doi.org/10.1073/pnas.1602711113}{10.1073/pnas.1602711113}.

\hypertarget{ref-Delmont2016}{}
29. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
contamination with advanced visualization and analysis practices:
Metagenomic approaches for eukaryotic genome assemblies.
doi:\href{https://doi.org/10.7287/peerj.preprints.1695v1}{10.7287/peerj.preprints.1695v1}.

\hypertarget{ref-Bik2016a}{}
30. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
prevalence of inappropriate image duplication in biomedical research
publications. bioRxiv 049452.
doi:\href{https://doi.org/10.1101/049452}{10.1101/049452}.

\hypertarget{ref-Bik2016b}{}
31. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
prevalence of inappropriate image duplication in biomedical research
publications. mBio \textbf{7}:e00809--16.
doi:\href{https://doi.org/10.1128/mbio.00809-16}{10.1128/mbio.00809-16}.

\hypertarget{ref-WolfeSimon2010}{}
32. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
\textbf{Gordon GW}, \textbf{Hoeft SE}, \textbf{Pett-Ridge J},
\textbf{Stolz JF}, \textbf{Webb SM}, \textbf{Weber PK}, \textbf{Davies
PCW}, \textbf{Anbar AD}, \textbf{Oremland RS}. 2010. A bacterium that
can grow by using arsenic instead of phosphorus. Science
\textbf{332}:1163--1166.
doi:\href{https://doi.org/10.1126/science.1197258}{10.1126/science.1197258}.

\hypertarget{ref-Altmetric}{}
33. How is the Altmetric Attention Score calculated?
\url{https://help.altmetric.com/support/solutions/articles/6000060969-how-is-the-altmetric-attention-score-calculated-}.

\hypertarget{ref-Schloss2015}{}
34. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
\textbf{Highlander SK}. 2015. Sequencing 16S rRNA gene fragments using
the PacBio SMRT DNA sequencing system.
doi:\href{https://doi.org/10.7287/peerj.preprints.778v1}{10.7287/peerj.preprints.778v1}.

\hypertarget{ref-Schloss2016a}{}
35. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
\textbf{Westcott SL}, \textbf{Highlander SK}. 2016. Sequencing 16S rRNA
gene fragments using the PacBio SMRT DNA sequencing system.
doi:\href{https://doi.org/10.7287/peerj.preprints.778v2}{10.7287/peerj.preprints.778v2}.

\hypertarget{ref-Schloss2016b}{}
36. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
\textbf{Westcott SL}, \textbf{Highlander SK}. 2016. Sequencing 16S rRNA
gene fragments using the PacBio SMRT DNA sequencing system. PeerJ
\textbf{4}:e1869.
doi:\href{https://doi.org/10.7717/peerj.1869}{10.7717/peerj.1869}.

\hypertarget{ref-Baxter2016a}{}
37. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
\textbf{Ruffin MT}, \textbf{Schloss P}. 2016. DNA from fecal
immunochemical test can replace stool for microbiota-based colorectal
cancer screening. bioRxiv 048389.
doi:\href{https://doi.org/10.1101/048389}{10.1101/048389}.

\hypertarget{ref-Baxter2016b}{}
38. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
\textbf{Ruffin MT}, \textbf{Schloss PD}. 2016. DNA from fecal
immunochemical test can replace stool for detection of colonic lesions
using a microbiota-based model. Microbiome \textbf{4}.
doi:\href{https://doi.org/10.1186/s40168-016-0205-y}{10.1186/s40168-016-0205-y}.

\hypertarget{ref-Imperiale2016}{}
39. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
mSphereDirect: Author-initiated peer review of manuscripts. mSphere
\textbf{1}:e00307--16.
doi:\href{https://doi.org/10.1128/msphere.00307-16}{10.1128/msphere.00307-16}.

\hypertarget{ref-Vence2017}{}
40. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.

\hypertarget{ref-Barsh2016}{}
41. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
\textbf{Singh ND}, \textbf{Copenhaver GP}. 2016. Bringing PLOS genetics
editors to preprint servers. PLOS Genetics \textbf{12}:e1006448.
doi:\href{https://doi.org/10.1371/journal.pgen.1006448}{10.1371/journal.pgen.1006448}.

\end{document}

### 2017-02-07 submission/Schloss_PrePrints_mBio_2017.Rmd
Editing

@@
 		} else {
-			paste(format(x,big.mark=',', digits=2, nsmall=2, scientific=FALSE))
+			paste(format(x,big.mark=',', digits=1, nsmall=1, scientific=FALSE))
 		}
@@
 ***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, we downloaded the *bioRxiv* on December 31, 2016.
-We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*.
+We chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,650 available at *PeerJ Preprint*.
 Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category.
@@
 These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.
-As the total number of preprints has grown exponentially since the creation of *biorxiv*, submission of microbiology-affiliated preprints has largely followed this growth (**Figure 1A**).
 
+As the total number of preprints has grown exponentially since the creation of *bioRxiv*, submission of microbiology-affiliated preprints has largely followed this growth (**Figure 1A**).
 Although preprints are still relatively new, the collection of microbiology-affiliated preprints indicates widespread experimentation with the format and considerable geographic diversity.
-Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r 100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r 100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts)`% have posted 3 or more preprints.
-Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%).
+Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r round(100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts), 1)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r round(100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts), 1)`% have posted 3 or more preprints.
+Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r round(micro_aff_countries_percent[1], 1)`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r round(micro_aff_countries_percent[2], 1)`%), and `r micro_aff_countries_names[3]` (`r round(micro_aff_countries_percent[3], 1)`%).
 As the preprint format matures, it will be interesting to see whether the fraction of authors that post multiple preprints increases and whether the geographic diversity amongst those authors is maintained.
@@
 To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint (**Figure 1B**).
-The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, mainstream media, Wikipedia, policy documents, and other sources [@Altmetric].
+The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, traditional media, Wikipedia, policy documents, and other sources [@Altmetric].
 A higher score indicates that a preprint received more attention.
-Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
-For comparison, the median Altmetric Attention Score for articles published in *mBio* published since November 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
+Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`).
+For comparison, the median Altmetric Attention Score for articles published in *mBio* published since 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(round(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`).
 Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *biorxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`.

### 2017-02-07 submission/Schloss_PrePrints_mBio_2017.tex
Editing

@@
 analyze the use of preprints, we downloaded the \emph{bioRxiv} on
-December 31, 2016. We chose to analyze the use of \emph{bioRxiv}
-preprints because these preprints are amenable for submission to ASM
-journals and there were 7,434 preprints compared to the 2,650 available
-at \emph{PeerJ Preprint}. Among the 7,434 preprints on bioRxiv, 329 were
+December 31, 2016. We chose to analyze \emph{bioRxiv} preprints because
+these preprints are amenable for submission to ASM journals and there
+were 7,434 \emph{bioRxiv} preprints compared to the 2,650 available at
+\emph{PeerJ Preprint}. Among the 7,434 preprints on bioRxiv, 329 were
 assigned by the authors into the Microbiology category. One limitation
@@
 Evolutionary Biology (N=221), Genomics (N=184), or Bioinformatics
-(N=182) categories. As the total number of preprints has grown
-exponentially since the creation of \emph{biorxiv}, submission of
-microbiology-affiliated preprints has largely followed this growth
-(\textbf{Figure 1A}).
+(N=182) categories.
 
+As the total number of preprints has grown exponentially since the
+creation of \emph{bioRxiv}, submission of microbiology-affiliated
+preprints has largely followed this growth (\textbf{Figure 1A}).
 Although preprints are still relatively new, the collection of
@@
 with the format and considerable geographic diversity. Reflecting the
-still relatively novelty of preprints, 1,132 (86.15\%) corresponding
+still relatively novelty of preprints, 1,132 (86.1\%) corresponding
 authors who submitted a microbiology-affiliated manuscript (N=1,314
-total) have posted a single preprint and 3.58\% have posted 3 or more
+total) have posted a single preprint and 3.6\% have posted 3 or more
 preprints. Corresponding authors that have posted
 microbiology-affiliated preprints are from 60 countries and are
-primarily affiliated with institutions in the United States (50.80\% of
-microbiology-affiliated preprints), United Kingdom (11.95\%), and
-Germany (4.17\%). As the preprint format matures, it will be interesting
-to see whether the fraction of authors that post multiple preprints
-increases and whether the geographic diversity amongst those authors is
+primarily affiliated with institutions in the United States (50.8\% of
+microbiology-affiliated preprints), United Kingdom (11.9\%), and Germany
+(4.2\%). As the preprint format matures, it will be interesting to see
+whether the fraction of authors that post multiple preprints increases
+and whether the geographic diversity amongst those authors is
 maintained.
@@
 scientific process. Among the microbiology-affiliated manuscripts, 146
-(9.32\%) had been commented on at least once and only 35 (2.23\%) more
+(9.3\%) had been commented on at least once and only 35 (2.2\%) more
 than three times using the \emph{bioRxiv}-hosted commenting feature.
@@
 authors do appear to be incorporating feedback from colleagues or
-editorial insights from journals as 404 (25.80\%) of preprints were
+editorial insights from journals as 404 (25.8\%) of preprints were
 revised at least once. Among the preprints posted prior to January 1,
-2016, 31.61\% of the Microbiology category preprints, 35.12\% of the
-microbiology-affiliated preprints, and 33.79\% of all preprints have
-been published. As noted above, not all authors submit their preprints
-to journals. This would indicate that the ``acceptance rates'' are
-actually higher. Regardless, considering that these acceptance rates are
-higher than many peer-reviewed journals (e.g.~approximately 20\% at ASM
+2016, 31.6\% of the Microbiology category preprints, 35.1\% of the
+microbiology-affiliated preprints, and 33.8\% of all preprints have been
+published. As noted above, not all authors submit their preprints to
+journals. This would indicate that the ``acceptance rates'' are actually
+higher. Regardless, considering that these acceptance rates are higher
+than many peer-reviewed journals (e.g.~approximately 20\% at ASM
 Journals), these results dispel the critique that preprints represent
@@
 Attention Score measures the number of times a preprint or paper is
-mentioned in social media, mainstream media, Wikipedia, policy
+mentioned in social media, traditional media, Wikipedia, policy
 documents, and other sources (33). A higher score indicates that a
 preprint received more attention. Microbiology-affiliated preprints have
-had a median Altmetric Attention Score of 7.28 (IQR: 3.25 to 16.3495)
-and those of all preprints hosted at \emph{bioRxiv} have had a median
-score of 7.05 (IQR: 3 to 15.556). For comparison, the median Altmetric
-Attention Score for articles published in \emph{mBio} published since
-November 2013 was 4.45 (IQR: 1.25 to 13.604). Of all scholarship tracked
-by Altmetric, the median Altmetric Attention Score for preprints posted
-at \emph{biorxiv} ranks at the 86 percentile (IQR: 66 to 94. A more
-traditional and controversial metric of impact has been the number of
-citations an article receives. We obtained the number of citations for
-the published versions of manuscripts that were initially posted as
-preprints. To allow for a comparison to traditional journals, we
-considered the citations for preprints published in 2014 and 2015 as
-aggregated by Web of Science (\textbf{Figure 1C}). Among the preprints
-that were published and could be found in the Web of Science database,
-the median number of citations was 6.50 (IQR: 2-14; mean: 13.60). For
-comparison, for the papers published in \emph{mBio} in 2014 and 2015,
-the median number of citations was 5 (IQR: 2-9; mean: 6.73). Although it
-is impossible to quantify the quality or impact of research with
-individual metrics, it is clear that preprints and the publications that
-result from them are broadly accepted by the microbiology community
+had a median Altmetric Attention Score of 7.3 (IQR: 3.2 to 16.3) and
+those of all preprints hosted at \emph{bioRxiv} have had a median score
+of 7.0 (IQR: 3 to 15.6). For comparison, the median Altmetric Attention
+Score for articles published in \emph{mBio} published since 2013 was 4.5
+(IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
+Altmetric Attention Score for preprints posted at \emph{biorxiv} ranks
+at the 86 percentile (IQR: 66 to 94. A more traditional and
+controversial metric of impact has been the number of citations an
+article receives. We obtained the number of citations for the published
+versions of manuscripts that were initially posted as preprints. To
+allow for a comparison to traditional journals, we considered the
+citations for preprints published in 2014 and 2015 as aggregated by Web
+of Science (\textbf{Figure 1C}). Among the preprints that were published
+and could be found in the Web of Science database, the median number of
+citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, for the
+papers published in \emph{mBio} in 2014 and 2015, the median number of
+citations was 5 (IQR: 2-9; mean: 6.7). Although it is impossible to
+quantify the quality or impact of research with individual metrics, it
+is clear that preprints and the publications that result from them are
+broadly accepted by the microbiology community
 

### 2017-02-08 submission/Schloss_PrePrints_mBio_2017.Rmd
Edit and strengthen Acknowledgements section

@@
 Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck and to recruit a broader pool of reviewers prior to submitting to traditional journals.
-Although use of preprints is still limited, early indications are that preprints are as robust and impactful as peer-reviewed papers.
+Although use of preprints is still limited in the biological sciences, early indications are that preprints are as robust and impactful as peer-reviewed papers.
 As publishing moves to embrace advances in internet technology, there are many opportunities for scientists and publishers to benefit from the use of preprints.
@@
 In many ways, preprint servers have taken on the feel of a journal.
-As adoption of this approach to disseminating research expands, it is likely that the features of these sites will continue to improve.
+As adoption of this approach expands, it is likely that the features of these sites will continue to improve.
 It is also likely that interfaces from third-parties will improve.
@@
 As the use of preprints grows and scientists' perceptions of preprints matures, there are a number of issues that will need to be addressed.
+
 First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the preprint author will lose their ability to claim primacy or their ability to publish the work in a journal.
@@
 This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data.
+
 A second area of concern is whether a preprint can be used to support a grant proposal.
@@
 We would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
+
 A third concern is what role preprints should have in assessing a scientist's productivity.
@@
 Others are mandating that researchers post preprints for all of their work prior to submitting the work to a journal [@Dolgin2016].
+
 Beyond these concerns, preprints are also causing some to change their publication goals.
@@
 Several anecdotes from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints.
+
 First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies.
@@
 For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.
-Preprints have proven useful for rapidly correcting the scientific literature.
-On February 9, 2015, Cell Systems posted a study by Afshinnekoo et al.
+
+Second, preprints have proven useful for rapidly correcting the scientific literature.
+On February 9, 2015, *Cell Systems* posted a study by Afshinnekoo et al.
 online [@Afshinnekoo2015a].
@@
 Although preprints are still relatively new, the collection of microbiology-affiliated preprints indicates widespread experimentation with the format and considerable geographic diversity.
-Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r round(100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts), 1)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r round(100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts), 1)`% have posted 3 or more preprints.
+Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r round(100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts), 1)`%) corresponding authors who submitted a microbiology-affiliated preprint (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r round(100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts), 1)`% have posted 3 or more preprints.
 Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r round(micro_aff_countries_percent[1], 1)`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r round(micro_aff_countries_percent[2], 1)`%), and `r micro_aff_countries_names[3]` (`r round(micro_aff_countries_percent[3], 1)`%).
@@
 As stated above, preprints offer researchers the opportunity to improve the quality of their work by adding a more formal and public step to the scientific process.
-Among the microbiology-affiliated manuscripts, `r n_micro_aff_ever_commented` (`r 100*n_micro_aff_ever_commented/sum(micro_affiliated, na.rm=T)`%) had been commented on at least once and only `r n_micro_aff_thrice_commented` (`r 100*n_micro_aff_thrice_commented/sum(micro_affiliated, na.rm=T)`%) more than three times using the *bioRxiv*-hosted commenting feature.
+Among the microbiology-affiliated preprints, `r n_micro_aff_ever_commented` (`r 100*n_micro_aff_ever_commented/sum(micro_affiliated, na.rm=T)`%) had been commented on at least once and only `r n_micro_aff_thrice_commented` (`r 100*n_micro_aff_thrice_commented/sum(micro_affiliated, na.rm=T)`%) more than three times using the *bioRxiv*-hosted commenting feature.
 Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
@@
 We appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases.
-The data, code, and an executable R-markdown version of this manuscript are available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.
+The workflow utilized commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.`r paste(version$major, version$minor, sep='.')`).
+Within R we utilized the  cowplot (v.`r packageDescription("cowplot")$Version`), dplyr (v.`r packageDescription("dplyr")$Version`),
+ggplot2 (v.`r packageDescription("ggplot2")$Version`), httr (v.`r packageDescription("httr")$Version`), RCurl (v.`r packageDescription("RCurl")$Version`),
+rentrez (v.`r packageDescription("rentrez")$Version`), rjson (v.`r packageDescription("rjson")$Version`), rvest (v.`r packageDescription("rvest")$Version`), sportcolors (v.`r packageDescription("sportcolors")$Version`), and tidyr (v.`r packageDescription("tidyr")$Version`) packages.
+A reproducible version of this manuscript and analysis is available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.
 

### 2017-02-08 submission/Schloss_PrePrints_mBio_2017.tex
Edit and strengthen Acknowledgements section

@@
 a broader pool of reviewers prior to submitting to traditional journals.
-Although use of preprints is still limited, early indications are that
-preprints are as robust and impactful as peer-reviewed papers. As
-publishing moves to embrace advances in internet technology, there are
-many opportunities for scientists and publishers to benefit from the use
-of preprints.
+Although use of preprints is still limited in the biological sciences,
+early indications are that preprints are as robust and impactful as
+peer-reviewed papers. As publishing moves to embrace advances in
+internet technology, there are many opportunities for scientists and
+publishers to benefit from the use of preprints.
 
@@
 preprint servers have taken on the feel of a journal. As adoption of
-this approach to disseminating research expands, it is likely that the
-features of these sites will continue to improve. It is also likely that
-interfaces from third-parties will improve. For example, although Google
-Scholar includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ
-Preprints} in their search results, PubMed and Web of Science do not.
-There is also hope that the National Institutes of Health (NIH) will
-renew their interest in including preprints in PubMed search results. As
-preprint servers begin to look and act like traditional journals by
-incorporating features and interfaces, it will be important to balance
-the requirements placed on authors for those features with the current
+this approach expands, it is likely that the features of these sites
+will continue to improve. It is also likely that interfaces from
+third-parties will improve. For example, although Google Scholar
+includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ Preprints}
+in their search results, PubMed and Web of Science do not. There is also
+hope that the National Institutes of Health (NIH) will renew their
+interest in including preprints in PubMed search results. As preprint
+servers begin to look and act like traditional journals by incorporating
+features and interfaces, it will be important to balance the
+requirements placed on authors for those features with the current
 efficiency of the preprint format.
@@
 scientists' perceptions of preprints matures, there are a number of
-issues that will need to be addressed. First, a common concern is that
-if a researcher posts their work as a preprint, it will be ``scooped''
-by another researcher and the preprint author will lose their ability to
-claim primacy or their ability to publish the work in a journal.
-Considering the preprint is a citable work with a DOI, it would, in
-fact, be the preprint author that scooped the second. A growing number
-of scientific societies and journals, including ASM view preprints as
-citable and as having a legitimate claim to primacy (1, 14--16). Some
-scientists worry that with such protection a researcher can make a claim
-without valid data to support their claims (3). This is possible;
-however, it is also the responsibility of the scientific community to
-utilize the peer-review mechanisms that are available to comment on
-those preprints pointing out methodological problems or to indicate that
-they are speaking beyond the data. A second area of concern is whether a
-preprint can be used to support a grant proposal. Given the length
-limitations placed on grant proposals by funding agencies, there is a
-push to cite previous work to indicate a research team's competence in
-an area or to provide preliminary data. Some fear that the use of
-preprints will allow scientists to circumvent page limits by posting
-preliminary manuscripts. We would hope that both consumers of preprints
-and grant proposal reviewers would be able to differentiate between
-someone trying to game the system and someone that is using preprints as
-a mechanism to improve their science. A third concern is what role
-preprints should have in assessing a scientist's productivity. Clearly
-use of publication metrics as an indicator of a scientist's productivity
-and impact is a contentious topic without even discussing the role of
-preprints. Regardless, given the propensity for researchers to list
-manuscripts as being ``in preparation'' or ``in review'' on an
-application or curriculum vitae, listing them instead as preprints that
-can be reviewed by a committee would significantly enhance an
-application and a reviewer's ability to judge the application. In fact,
-several funding agencies including the Wellcome Trust and the UK Medical
-Research Council encouraging fellowship applicants to include preprints
-in their materials; meanwhile, the NIH is in the process of soliciting
-input from the scientific community on their role in grant applications.
-Others are mandating that researchers post preprints for all of their
-work prior to submitting the work to a journal (17). Beyond these
-concerns, preprints are also causing some to change their publication
-goals. Some authors are explicitly stating that a preprint will not be
-submitted to a journal (18). Although these authors may be a minority of
-those who post preprints, such an approach may be attractive to those
-that want to have a mechanism for people to cite a report of a brief
-research communication, a critique of another publication, or negative
-results. It is clear that the adoption of preprints will challenge how
-scientists interact and evaluate each other's work. There is great
-potential to empower researchers by controlling when a citable piece of
-work is made public.
+issues that will need to be addressed.
+
+First, a common concern is that if a researcher posts their work as a
+preprint, it will be ``scooped'' by another researcher and the preprint
+author will lose their ability to claim primacy or their ability to
+publish the work in a journal. Considering the preprint is a citable
+work with a DOI, it would, in fact, be the preprint author that scooped
+the second. A growing number of scientific societies and journals,
+including ASM view preprints as citable and as having a legitimate claim
+to primacy (1, 14--16). Some scientists worry that with such protection
+a researcher can make a claim without valid data to support their claims
+(3). This is possible; however, it is also the responsibility of the
+scientific community to utilize the peer-review mechanisms that are
+available to comment on those preprints pointing out methodological
+problems or to indicate that they are speaking beyond the data.
+
+A second area of concern is whether a preprint can be used to support a
+grant proposal. Given the length limitations placed on grant proposals
+by funding agencies, there is a push to cite previous work to indicate a
+research team's competence in an area or to provide preliminary data.
+Some fear that the use of preprints will allow scientists to circumvent
+page limits by posting preliminary manuscripts. We would hope that both
+consumers of preprints and grant proposal reviewers would be able to
+differentiate between someone trying to game the system and someone that
+is using preprints as a mechanism to improve their science.
+
+A third concern is what role preprints should have in assessing a
+scientist's productivity. Clearly use of publication metrics as an
+indicator of a scientist's productivity and impact is a contentious
+topic without even discussing the role of preprints. Regardless, given
+the propensity for researchers to list manuscripts as being ``in
+preparation'' or ``in review'' on an application or curriculum vitae,
+listing them instead as preprints that can be reviewed by a committee
+would significantly enhance an application and a reviewer's ability to
+judge the application. In fact, several funding agencies including the
+Wellcome Trust and the UK Medical Research Council encouraging
+fellowship applicants to include preprints in their materials;
+meanwhile, the NIH is in the process of soliciting input from the
+scientific community on their role in grant applications. Others are
+mandating that researchers post preprints for all of their work prior to
+submitting the work to a journal (17).
+
+Beyond these concerns, preprints are also causing some to change their
+publication goals. Some authors are explicitly stating that a preprint
+will not be submitted to a journal (18). Although these authors may be a
+minority of those who post preprints, such an approach may be attractive
+to those that want to have a mechanism for people to cite a report of a
+brief research communication, a critique of another publication, or
+negative results. It is clear that the adoption of preprints will
+challenge how scientists interact and evaluate each other's work. There
+is great potential to empower researchers by controlling when a citable
+piece of work is made public.
 
@@
 benefits of the rapid release cycle that is inherent in the use of
-preprints. First, preprints have proven useful for rapidly disseminating
-results for disease outbreaks and new technologies. Prior to the recent
-Zika virus outbreak there were approximately 50 publications that
-touched on the biology and epidemiology of the virus; as of January 2017
-the number of Zika virus-related publications was over 1,700. During the
-recent outbreak, more than 110 Zika virus-related preprints have been
-posted at \emph{bioRxiv}. Any manuscript that was published went through
-several month delays in releasing information to health care workers,
-the public, and scientists needing to learn new methods to study a
+preprints.
+
+First, preprints have proven useful for rapidly disseminating results
+for disease outbreaks and new technologies. Prior to the recent Zika
+virus outbreak there were approximately 50 publications that touched on
+the biology and epidemiology of the virus; as of January 2017 the number
+of Zika virus-related publications was over 1,700. During the recent
+outbreak, more than 110 Zika virus-related preprints have been posted at
+\emph{bioRxiv}. Any manuscript that was published went through several
+month delays in releasing information to health care workers, the
+public, and scientists needing to learn new methods to study a
 previously obscure virus. In contrast, those that posted their work as a
@@
 has likely advanced at a faster rate than it otherwise would have.
-Preprints have proven useful for rapidly correcting the scientific
-literature. On February 9, 2015, Cell Systems posted a study by
-Afshinnekoo et al. online (19). The study collected and analyzed
-metagenomic sequence data from the New York City subway system and
-reported finding \emph{Yersinia pestis} and \emph{Bacillus anthracis}.
-Because of the focus on these two bioterrorism agents, this study
-generated a considerable amount of media attention. On April 25, 2015,
-Petit et al. (20) posted a preprint to Zenodo demonstrating that there
-was no evidence for \emph{B. anthracis} in the dataset. On July 29,
-2015, a critique was published by \emph{Cell Systems} along with a
+
+Second, preprints have proven useful for rapidly correcting the
+scientific literature. On February 9, 2015, \emph{Cell Systems} posted a
+study by Afshinnekoo et al. online (19). The study collected and
+analyzed metagenomic sequence data from the New York City subway system
+and reported finding \emph{Yersinia pestis} and \emph{Bacillus
+anthracis}. Because of the focus on these two bioterrorism agents, this
+study generated a considerable amount of media attention. On April 25,
+2015, Petit et al. (20) posted a preprint to Zenodo demonstrating that
+there was no evidence for \emph{B. anthracis} in the dataset. On July
+29, 2015, a critique was published by \emph{Cell Systems} along with a
 response from the original authors offering a correction to their
@@
 still relatively novelty of preprints, 1,132 (86.1\%) corresponding
-authors who submitted a microbiology-affiliated manuscript (N=1,314
-total) have posted a single preprint and 3.6\% have posted 3 or more
-preprints. Corresponding authors that have posted
-microbiology-affiliated preprints are from 60 countries and are
-primarily affiliated with institutions in the United States (50.8\% of
-microbiology-affiliated preprints), United Kingdom (11.9\%), and Germany
-(4.2\%). As the preprint format matures, it will be interesting to see
-whether the fraction of authors that post multiple preprints increases
-and whether the geographic diversity amongst those authors is
-maintained.
+authors who submitted a microbiology-affiliated preprint (N=1,314 total)
+have posted a single preprint and 3.6\% have posted 3 or more preprints.
+Corresponding authors that have posted microbiology-affiliated preprints
+are from 60 countries and are primarily affiliated with institutions in
+the United States (50.8\% of microbiology-affiliated preprints), United
+Kingdom (11.9\%), and Germany (4.2\%). As the preprint format matures,
+it will be interesting to see whether the fraction of authors that post
+multiple preprints increases and whether the geographic diversity
+amongst those authors is maintained.
 
@@
 the quality of their work by adding a more formal and public step to the
-scientific process. Among the microbiology-affiliated manuscripts, 146
+scientific process. Among the microbiology-affiliated preprints, 146
 (9.3\%) had been commented on at least once and only 35 (2.2\%) more
@@
 Altmetric, Inc and Thompson Reuters who provided advanced programming
-interface (API) access to their databases. The data, code, and an
-executable R-markdown version of this manuscript are available at
+interface (API) access to their databases. The workflow utilized
+commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
+Within R we utilized the cowplot (v.0.6.3), dplyr (v.0.5.0), ggplot2
+(v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
+rjson (v.0.2.15), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and tidyr
+(v.0.6.0) packages. A reproducible version of this manuscript and
+analysis is available at
 \url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.

### 2017-02-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Incorporate Stefano's edits

@@
 
-The field of microbiology has experience significant growth due to rapid advances in technology and the influx of scientists driven by a curiosity to understand how bacteria, archaea, microbial eukaryotes, and viruses interact with each other and their environment to sustain myriad biochemical processes that are essential for maintaining the Earth.
+The field of microbiology has experienced significant growth due to transformative advances in technology and the influx of scientists driven by a curiosity to understand how bacteria, archaea, microbial eukaryotes, and viruses interact with each other and their environment to sustain myriad biochemical processes that are essential for maintaining the Earth.
 With this explosion in scientific output, a significant bottleneck has been the ability to disseminate this new knowledge to peers and the public in a timely manner.
-Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck and to recruit a broader pool of reviewers prior to submitting to traditional journals.
-Although use of preprints is still limited in the biological sciences, early indications are that preprints are as robust and impactful as peer-reviewed papers.
-As publishing moves to embrace advances in internet technology, there are many opportunities for scientists and publishers to benefit from the use of preprints.
+Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck and to recruit in an effective and transparent way a broader pool of reviewers prior to submitting to traditional journals.
+Although use of preprints is still limited in the biological sciences, early indications are that preprints are as robust tool that can complement and enhance peer-reviewed publications.
+As publishing moves to embrace advances in internet technology, there are many opportunities for preprints and peer-reviewed journals to coexist in the same ecosystem.
 
@@
 ***Background.*** Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public.
-A preprint is an unpublished manuscript that is made publicly available without going through an official peer-review process [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016].
-An author can post their manuscript to a preprint server for others to read, share, and make comments.
+A preprint is an interim research product, such as an unpublished manuscript, made publicly available before going through an official peer-review process [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016].
+Authors can post their manuscript to a preprint server for others to read, share, and comment.
 Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues [@Nature1966].
 While the biological community's commitment to preprints waned, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011].
-Among physicists and mathematicians, posting a preprint to *arXiv* followed by submission to a peer-reviewed journal has become the standard publication strategy.
+For some physicists and mathematicians, posting a preprint to *arXiv* followed by submission to a peer-reviewed journal has become a standard publication pathway.
 Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
@@
 ***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013].
-Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
+Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
 There are several important differences between the two options.
@@
 *Proceedings of the National Academy of Sciences*).
+We particularly like the *bioRxiv* licensing flexibility, which empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research resultsl however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option.
 A cosmetic, but still relevant difference between the two is the layout and feel of the two websites.
@@
 For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not.
-There is also hope that the National Institutes of Health (NIH) will renew their interest in including preprints in PubMed search results.
-As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, it will be important to balance the requirements placed on authors for those features with the current efficiency of the preprint format.
+There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.
+As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, we think that it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted.
+It is therefore essential to balance the requirements placed on authors for features associated with preprints with the current desirable efficiency of the preprint format.
 
@@
 It is critical that assurances be given that policies are in place to address these issues.
-First, a significant amount of attention has been given to the potential dual use of microbiology research for individuals seeking to engage in terrorist activities.
+First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in terrorist activities.
 Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research.
 Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results.
-Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism.
+Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism or misconduct.
 Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers.
@@
 The broad consensus at this point is that preprints do not constitute prior publication.
-This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, and *Nature*, which have a permissive stance towards prior posting of preprints prior to submission.
-Although journals published by Cell Press do not forbid authors from posting preprints prior to submission, they ask authors to consult an editor prior to posting and do not allow authors to post revised preprints that contain revisions that respond to editorial input.
+This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, *Nature* and Cell press, which each take a generally permissive stance towards prior posting of preprints prior to submission.
 Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work.
@@
 ***Preprints have the potential to change the advancement of science.*** Preprints are often viewed as existing in a state of scientific limbo.
-As noted above, they represent a formal communication, but are not officially published.
+As noted above, they represent a formal communication, but an interim one, not officially published.
 As the use of preprints grows and scientists' perceptions of preprints matures, there are a number of issues that will need to be addressed.
@@
 Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second.
+The use of preprints uncouples the communication of the discovery from the relevance of the discovery, which will come later based on peer-review, comments from other scientists at meetings or online, and eventually citations.
 A growing number of scientific societies and journals, including ASM view preprints as citable and as having a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016].
@@
 We would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
+This would be greatly facilitated if funding agencies would include preprints as evidence for research progress, but listed separately from peer-reviewed publications to help review panels in their decisions and to help author substantiate evidence they feel they need to provide.
 
@@
 Some authors are explicitly stating that a preprint will not be submitted to a journal [@SinghChawla2017].
-Although these authors may be a minority of those who post preprints, such an approach may be attractive to those that want to have a mechanism for people to cite a report of a brief research communication, a critique of another publication, or negative results.
+Although these authors may be a minority of those who post preprints, such an approach may be attractive to those who need to cite a report of a brief research communication, a critique of another publication, or negative results.
 It is clear that the adoption of preprints will challenge how scientists interact and evaluate each other's work.
@@
 [@Boothby2015] was first published online.
-The authors posited that 17.5% of its genes came from bacteria, archaea, fungi, plants, and viruses.
+The authors claimed that 17.5% of its genes came from bacteria, archaea, fungi, plants, and viruses.
 Another group had been analyzing sequence data from a parallel tardigrade genome sequencing project and did not observe the same result.
@@
 Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
-Regardless, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints were revised at least once.
+We understand that it is not in the tradition of the scientific community to comment publicly online about colleagues’ research results.
+We think this will change given the possibilities of new media, and possibly incentives for open commenting and reviewing could shift the trend.
+Importantly, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints were revised at least once.
 Among the preprints posted prior to January 1, 2016, `r 100*n_micro_published/sum(biorxiv$category == "Microbiology", na.rm=T)`% of the Microbiology category preprints, `r 100*n_micro_aff_published/sum(micro_affiliated, na.rm=T)`% of the microbiology-affiliated preprints, and `r 100*n_all_published/nrow(biorxiv)`% of all preprints have been published.
@@
 Measuring the impact and significance of scientific research is notoriously difficult.
-Using several metrics we sought to quantify the effect that microbiology-affiliated preprints have had on the work of others.
+Using several metrics we sought to quantify the effect that broadly defined microbiology-affiliated preprints have had on the work of others.
 Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively.
@@
 For comparison, the median Altmetric Attention Score for articles published in *mBio* published since 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(round(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`).
-Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *biorxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`.
+Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *bioRxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`.
 A more traditional and controversial metric of impact has been the number of citations an article receives.
@@
 For comparison, for the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`).
-Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community
+Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community.
 
@@
 ***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals will have in disseminating research if there is broad adoption of preprints.
-One perspective is that although authors value immediate accessibility to their work, they also value the editorial support from professional societies and other organizations.
-Furthermore, the professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals.
+We think that edited peer-reviewed journals offer, and will continue to offer significant added value to a publication.
+A scholarly publishing ecosystem in which preprints coexist with journals will allow authors to gain value from the immediate communication of their work associated with preprints and also benefit from the peer-reviewed, professionally edited publication that publishers can provide.
+The professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals.
 An alternative perspective is that preprints will eventually replace traditional journals.
-Certainly, this is a radical perspective, but it does serve to motivate publishers to address what they can offer preprint authors.
+Certainly, this is a radical perspective, but it does serve to motivate publishers to capture the innovation opportunities offered by preprints.
 By adopting preprint-friendly policies, journals can create an attractive environment for authors.
 As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals.
-A new venture from *mSphere*, mSphereDirect, actively encourages authors to post their manuscripts as preprints as part of the author-driven editorial process [@Imperiale2016].
+An example is offered by the ASM, which earlier this year launched a new venture from *mSphere*.
+mSphereDirect is a publication track of the journal that capitalizes on the opportunity offered to couple preprints with rigorous peer-review.
+mSphereDirect.
+actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016].
+ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles.
 In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016].
@@
 **Figure 1.
-Summary of microbiology-affiliated preprints since the creation of** ***biorxiv.*** The total number of preprints posted for each quarter ending December 31, 2016 has largely tracked the overall submission of preprints to *biorxiv* (A).
-The Altmetric attention scores of preprints posted to *biorxiv* are similar to those published in *mBio* since November 2013 indicating preprints engender a similar level of attention (B).
+Summary of microbiology-affiliated preprints since the creation of** ***bioRxiv.*** The total number of preprints posted for each quarter ending December 31, 2016 has largely tracked the overall submission of preprints to *bioRxiv* (A).
+The Altmetric attention scores of preprints posted to *bioRxiv* are similar to those published in *mBio* since November 2013 indicating preprints engender a similar level of attention (B).
 The number of times preprints that were published in 2014 and 2015 have been cited is similar to the number of citations for papers published in *mBio* in 2014 and 2015 indicates that published preprints are frequently cited (C).

### 2017-02-13 submission/Schloss_PrePrints_mBio_2017.tex
Incorporate Stefano's edits

@@
 
-The field of microbiology has experience significant growth due to rapid
-advances in technology and the influx of scientists driven by a
-curiosity to understand how bacteria, archaea, microbial eukaryotes, and
-viruses interact with each other and their environment to sustain myriad
-biochemical processes that are essential for maintaining the Earth. With
-this explosion in scientific output, a significant bottleneck has been
-the ability to disseminate this new knowledge to peers and the public in
-a timely manner. Preprints have emerged as a tool that a growing number
-of microbiologists are using to overcome this bottleneck and to recruit
-a broader pool of reviewers prior to submitting to traditional journals.
-Although use of preprints is still limited in the biological sciences,
-early indications are that preprints are as robust and impactful as
-peer-reviewed papers. As publishing moves to embrace advances in
-internet technology, there are many opportunities for scientists and
-publishers to benefit from the use of preprints.
+The field of microbiology has experienced significant growth due to
+transformative advances in technology and the influx of scientists
+driven by a curiosity to understand how bacteria, archaea, microbial
+eukaryotes, and viruses interact with each other and their environment
+to sustain myriad biochemical processes that are essential for
+maintaining the Earth. With this explosion in scientific output, a
+significant bottleneck has been the ability to disseminate this new
+knowledge to peers and the public in a timely manner. Preprints have
+emerged as a tool that a growing number of microbiologists are using to
+overcome this bottleneck and to recruit in an effective and transparent
+way a broader pool of reviewers prior to submitting to traditional
+journals. Although use of preprints is still limited in the biological
+sciences, early indications are that preprints are as robust tool that
+can complement and enhance peer-reviewed publications. As publishing
+moves to embrace advances in internet technology, there are many
+opportunities for preprints and peer-reviewed journals to coexist in the
+same ecosystem.
 
@@
 media, blog posts, and videos as methods to garner attention for their
-research and to engage the public. A preprint is an unpublished
-manuscript that is made publicly available without going through an
-official peer-review process (1--4). An author can post their manuscript
-to a preprint server for others to read, share, and make comments.
-Preprints were initially adopted among physicists and biologists in the
-1960s as a method of sharing interesting research amongst colleagues
-(5). While the biological community's commitment to preprints waned, the
-physics community adopted what is now the \emph{arXiv} (pronounced
-``archive'') preprint server that was hosted at the Los Alamos National
-Laboratories from 1991 to 1999 and then at Cornell University (6). Among
-physicists and mathematicians, posting a preprint to \emph{arXiv}
-followed by submission to a peer-reviewed journal has become the
-standard publication strategy. Although \emph{arXiv} has hosted a number
-of computational biology papers, the server has not drawn widespread
-attention from biologists. Among proponents of \emph{arXiv}, preprints
-have aided in the development of research communication by accelerating
-the release of the science and helping it to achieve a wider audience
-for critique and reception (7). Considering the broadening adoption of
-preprints among microbiologists, we sought to explore the specific uses
-of and concerns regarding preprints.
+research and to engage the public. A preprint is an interim research
+product, such as an unpublished manuscript, made publicly available
+before going through an official peer-review process (1--4). Authors can
+post their manuscript to a preprint server for others to read, share,
+and comment. Preprints were initially adopted among physicists and
+biologists in the 1960s as a method of sharing interesting research
+amongst colleagues (5). While the biological community's commitment to
+preprints waned, the physics community adopted what is now the
+\emph{arXiv} (pronounced ``archive'') preprint server that was hosted at
+the Los Alamos National Laboratories from 1991 to 1999 and then at
+Cornell University (6). For some physicists and mathematicians, posting
+a preprint to \emph{arXiv} followed by submission to a peer-reviewed
+journal has become a standard publication pathway. Although \emph{arXiv}
+has hosted a number of computational biology papers, the server has not
+drawn widespread attention from biologists. Among proponents of
+\emph{arXiv}, preprints have aided in the development of research
+communication by accelerating the release of the science and helping it
+to achieve a wider audience for critique and reception (7). Considering
+the broadening adoption of preprints among microbiologists, we sought to
+explore the specific uses of and concerns regarding preprints.
 
@@
 preprint and supplemental materials; preprints are typically publicly
-available in under 24 hours; they have built in venues for authors to
+available in about 24 hours; they have built in venues for authors to
 discuss their research with people who leave comments on the manuscript;
@@
 manuscripts posted as preprints under a CC-BY license (e.g.
-\emph{Proceedings of the National Academy of Sciences}). A cosmetic, but
-still relevant difference between the two is the layout and feel of the
-two websites. Compared to the \emph{bioRxiv} site, the \emph{PeerJ
-Preprint} site is more fluid, gives readers the ability to ``follow'' a
-preprint, and provides better access to article keywords and the ability
-to search preprints. With broader acceptance of preprints by traditional
-journals, many journals, including all of the ASM journals, have
-established mechanisms to directly submit manuscripts that are posted as
-preprints on \emph{bioRxiv}. It is only possible to transfer a
-\emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many ways,
-preprint servers have taken on the feel of a journal. As adoption of
-this approach expands, it is likely that the features of these sites
+\emph{Proceedings of the National Academy of Sciences}). We particularly
+like the \emph{bioRxiv} licensing flexibility, which empowers authors to
+choose the model that best suits them, while ensuring the rapid posting
+of their research resultsl however, it is important to provide clear
+information to authors on the legal and practical tradeoffs of each
+option. A cosmetic, but still relevant difference between the two is the
+layout and feel of the two websites. Compared to the \emph{bioRxiv}
+site, the \emph{PeerJ Preprint} site is more fluid, gives readers the
+ability to ``follow'' a preprint, and provides better access to article
+keywords and the ability to search preprints. With broader acceptance of
+preprints by traditional journals, many journals, including all of the
+ASM journals, have established mechanisms to directly submit manuscripts
+that are posted as preprints on \emph{bioRxiv}. It is only possible to
+transfer a \emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many
+ways, preprint servers have taken on the feel of a journal. As adoption
+of this approach expands, it is likely that the features of these sites
 will continue to improve. It is also likely that interfaces from
@@
 hope that the National Institutes of Health (NIH) will renew their
-interest in including preprints in PubMed search results. As preprint
-servers begin to look and act like traditional journals by incorporating
-features and interfaces, it will be important to balance the
-requirements placed on authors for those features with the current
-efficiency of the preprint format.
+interest in indexing preprints as separate research products than
+peer-reviewed publications. As preprint servers begin to look and act
+like traditional journals by incorporating features and interfaces, we
+think that it is important to value the strength of the preprint - that
+of an interim research product, nimble and quickly posted. It is
+therefore essential to balance the requirements placed on authors for
+features associated with preprints with the current desirable efficiency
+of the preprint format.
 
@@
 that assurances be given that policies are in place to address these
-issues. First, a significant amount of attention has been given to the
-potential dual use of microbiology research for individuals seeking to
+issues. First, a significant amount of attention has to be given to the
+potential dual use research of concern (DURC) since posted results in
+microbiology research could offer insights to individuals seeking to
 engage in terrorist activities. Second, for researchers engaging in
@@
 Finally, recent expansions in scientific publishing have revealed
-numerous cases of plagiarism. Again, while hoping to maintain the
-efficiency of the preprint format, traditional microbiology journals
-have policies for these issues in place that should be easy to implement
-by preprint servers.
+numerous cases of plagiarism or misconduct. Again, while hoping to
+maintain the efficiency of the preprint format, traditional microbiology
+journals have policies for these issues in place that should be easy to
+implement by preprint servers.
 
@@
 \emph{Proceedings of the National Academy of Science}, \emph{Science},
-and \emph{Nature}, which have a permissive stance towards prior posting
-of preprints prior to submission. Although journals published by Cell
-Press do not forbid authors from posting preprints prior to submission,
-they ask authors to consult an editor prior to posting and do not allow
-authors to post revised preprints that contain revisions that respond to
-editorial input. Considering the relatively fluid nature of many of
-these policies and the journals' specific policies, prospective authors
-should be aware of the positions taken by the journals where they may
-eventually submit their work. Comprehensive lists of journals' attitudes
-towards preprints are available online and are regularly updated (9,
-10).
+\emph{Nature} and Cell press, which each take a generally permissive
+stance towards prior posting of preprints prior to submission.
+Considering the relatively fluid nature of many of these policies and
+the journals' specific policies, prospective authors should be aware of
+the positions taken by the journals where they may eventually submit
+their work. Comprehensive lists of journals' attitudes towards preprints
+are available online and are regularly updated (9, 10).
 
@@
 scientific limbo. As noted above, they represent a formal communication,
-but are not officially published. As the use of preprints grows and
-scientists' perceptions of preprints matures, there are a number of
-issues that will need to be addressed.
+but an interim one, not officially published. As the use of preprints
+grows and scientists' perceptions of preprints matures, there are a
+number of issues that will need to be addressed.
 
@@
 work with a DOI, it would, in fact, be the preprint author that scooped
-the second. A growing number of scientific societies and journals,
-including ASM view preprints as citable and as having a legitimate claim
-to primacy (1, 14--16). Some scientists worry that with such protection
-a researcher can make a claim without valid data to support their claims
-(3). This is possible; however, it is also the responsibility of the
-scientific community to utilize the peer-review mechanisms that are
-available to comment on those preprints pointing out methodological
-problems or to indicate that they are speaking beyond the data.
+the second. The use of preprints uncouples the communication of the
+discovery from the relevance of the discovery, which will come later
+based on peer-review, comments from other scientists at meetings or
+online, and eventually citations. A growing number of scientific
+societies and journals, including ASM view preprints as citable and as
+having a legitimate claim to primacy (1, 14--16). Some scientists worry
+that with such protection a researcher can make a claim without valid
+data to support their claims (3). This is possible; however, it is also
+the responsibility of the scientific community to utilize the
+peer-review mechanisms that are available to comment on those preprints
+pointing out methodological problems or to indicate that they are
+speaking beyond the data.
 
@@
 differentiate between someone trying to game the system and someone that
-is using preprints as a mechanism to improve their science.
+is using preprints as a mechanism to improve their science. This would
+be greatly facilitated if funding agencies would include preprints as
+evidence for research progress, but listed separately from peer-reviewed
+publications to help review panels in their decisions and to help author
+substantiate evidence they feel they need to provide.
 
@@
 minority of those who post preprints, such an approach may be attractive
-to those that want to have a mechanism for people to cite a report of a
-brief research communication, a critique of another publication, or
-negative results. It is clear that the adoption of preprints will
-challenge how scientists interact and evaluate each other's work. There
-is great potential to empower researchers by controlling when a citable
-piece of work is made public.
+to those who need to cite a report of a brief research communication, a
+critique of another publication, or negative results. It is clear that
+the adoption of preprints will challenge how scientists interact and
+evaluate each other's work. There is great potential to empower
+researchers by controlling when a citable piece of work is made public.
 
@@
 Sciences}. On November 23, 2015 a study by Boothby et al. (23) was first
-published online. The authors posited that 17.5\% of its genes came from
+published online. The authors claimed that 17.5\% of its genes came from
 bacteria, archaea, fungi, plants, and viruses. Another group had been
@@
 this result was somewhat disturbing since the preprint model implicitly
-depends on people's willingness to offer others feedback. Regardless,
+depends on people's willingness to offer others feedback. We understand
+that it is not in the tradition of the scientific community to comment
+publicly online about colleagues' research results. We think this will
+change given the possibilities of new media, and possibly incentives for
+open commenting and reviewing could shift the trend. Importantly,
 authors do appear to be incorporating feedback from colleagues or
@@
 notoriously difficult. Using several metrics we sought to quantify the
-effect that microbiology-affiliated preprints have had on the work of
-others. Using the download statistics associated with each preprint, we
-found that the median number of times an abstract or PDF had been
-accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to 568),
-respectively. These values represent two aspects of posting a preprint.
-First, they reflect the number of times people were able to access
-science before it was published. Second, they reflect the number of
-times people were able to access a version of a manuscript that is
+effect that broadly defined microbiology-affiliated preprints have had
+on the work of others. Using the download statistics associated with
+each preprint, we found that the median number of times an abstract or
+PDF had been accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to
+568), respectively. These values represent two aspects of posting a
+preprint. First, they reflect the number of times people were able to
+access science before it was published. Second, they reflect the number
+of times people were able to access a version of a manuscript that is
 published behind a paywall. To obtain a measure of a preprint's ability
@@
 (IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
-Altmetric Attention Score for preprints posted at \emph{biorxiv} ranks
+Altmetric Attention Score for preprints posted at \emph{bioRxiv} ranks
 at the 86 percentile (IQR: 66 to 94. A more traditional and
@@
 is clear that preprints and the publications that result from them are
-broadly accepted by the microbiology community
+broadly accepted by the microbiology community.
 
@@
 question is what role traditional journals will have in disseminating
-research if there is broad adoption of preprints. One perspective is
-that although authors value immediate accessibility to their work, they
-also value the editorial support from professional societies and other
-organizations. Furthermore, the professional copyediting, layout, and
+research if there is broad adoption of preprints. We think that edited
+peer-reviewed journals offer, and will continue to offer significant
+added value to a publication. A scholarly publishing ecosystem in which
+preprints coexist with journals will allow authors to gain value from
+the immediate communication of their work associated with preprints and
+also benefit from the peer-reviewed, professionally edited publication
+that publishers can provide. The professional copyediting, layout, and
 publicity that these publishers offer are also unique features of
@@
 eventually replace traditional journals. Certainly, this is a radical
-perspective, but it does serve to motivate publishers to address what
-they can offer preprint authors. By adopting preprint-friendly policies,
-journals can create an attractive environment for authors. As discussed
-above, a growing number of journals have created mechanisms for authors
-to directly submit preprints to their journals. A new venture from
-\emph{mSphere}, mSphereDirect, actively encourages authors to post their
-manuscripts as preprints as part of the author-driven editorial process
-(39). In addition to integrating preprints into the traditional
-editorial process, several professional societies have also explicitly
-supported citation of preprints in their other publications and
-recognize the priority of preprints in the literature (14--16). These
-are policies that empower authors and make specific journals more
+perspective, but it does serve to motivate publishers to capture the
+innovation opportunities offered by preprints. By adopting
+preprint-friendly policies, journals can create an attractive
+environment for authors. As discussed above, a growing number of
+journals have created mechanisms for authors to directly submit
+preprints to their journals. An example is offered by the ASM, which
+earlier this year launched a new venture from \emph{mSphere}.
+mSphereDirect is a publication track of the journal that capitalizes on
+the opportunity offered to couple preprints with rigorous peer-review.
+mSphereDirect. actively encourages authors to post their manuscripts as
+preprints as part of an author-driven editorial process where an
+editorial decision is rendered within five days and publication in
+\emph{mSphere} within a month (39). ASM is developing a new platform,
+MicroNow, which will help coalesce specific communities within the
+microbial sciences, further enhancing the use of preprints as well as
+published articles. In addition to integrating preprints into the
+traditional editorial process, several professional societies have also
+explicitly supported citation of preprints in their other publications
+and recognize the priority of preprints in the literature (14--16).
+These are policies that empower authors and make specific journals more
 attractive. Other practices have great potential to improve the
@@
 \textbf{Figure 1. Summary of microbiology-affiliated preprints since the
-creation of} \textbf{\emph{biorxiv.}} The total number of preprints
+creation of} \textbf{\emph{bioRxiv.}} The total number of preprints
 posted for each quarter ending December 31, 2016 has largely tracked the
-overall submission of preprints to \emph{biorxiv} (A). The Altmetric
-attention scores of preprints posted to \emph{biorxiv} are similar to
+overall submission of preprints to \emph{bioRxiv} (A). The Altmetric
+attention scores of preprints posted to \emph{bioRxiv} are similar to
 those published in \emph{mBio} since November 2013 indicating preprints

### 2017-02-18 submission/Schloss_PrePrints_mBio_2017.Rmd
Editing

@@
 \vspace{25mm}
-Patrick D. Schloss${^\dagger}$${^{,1}}$
-
-Stefano Bertuzzi${^2}$
-
-Lynn W. Enquist${^3}$
+Patrick D. Schloss${^\dagger}$
 
@@
 
-$\dagger$ To whom correspondence should be addressed: pschloss@umich.edu
-
-1 Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
-
-2 American Society for Microbiology, Washington, DC
-
-3 Princeton Neuroscience Institute, Princeton University, Princeton, NJ
+$\dagger$ To whom correspondence should be addressed: pschloss@umich.edu; Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
 
@@
 Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck and to recruit in an effective and transparent way a broader pool of reviewers prior to submitting to traditional journals.
-Although use of preprints is still limited in the biological sciences, early indications are that preprints are as robust tool that can complement and enhance peer-reviewed publications.
+Although use of preprints is still limited in the biological sciences, early indications are that preprints are a robust tool that can complement and enhance peer-reviewed publications.
 As publishing moves to embrace advances in internet technology, there are many opportunities for preprints and peer-reviewed journals to coexist in the same ecosystem.
@@
 Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012].
-Considering the broadening adoption of preprints among microbiologists, we sought to explore the specific uses of and concerns regarding preprints.
+Considering the broadening adoption of preprints among microbiologists, I sought to explore the specific uses of and concerns regarding preprints.
 
@@
 *Proceedings of the National Academy of Sciences*).
-We particularly like the *bioRxiv* licensing flexibility, which empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research resultsl however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option.
+The flexibility of the *bioRxiv* licensing empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research results however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option.
 A cosmetic, but still relevant difference between the two is the layout and feel of the two websites.
@@
 There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.
-As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, we think that it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted.
+As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted.
 It is therefore essential to balance the requirements placed on authors for features associated with preprints with the current desirable efficiency of the preprint format.
@@
 Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts.
-We would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
+I would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
 This would be greatly facilitated if funding agencies would include preprints as evidence for research progress, but listed separately from peer-reviewed publications to help review panels in their decisions and to help author substantiate evidence they feel they need to provide.
@@
 
-***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, we downloaded the *bioRxiv* on December 31, 2016.
-We chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,650 available at *PeerJ Preprint*.
+***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, I downloaded the *bioRxiv* on December 31, 2016.
+I chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,650 available at *PeerJ Preprint*.
 Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category.
@@
 For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories.
-To counter this limitation, we developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, or *pathogen*.
-We identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that we considered microbiology-affiliated.
+To counter this limitation, I developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, or *pathogen*.
+I identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that I considered microbiology-affiliated.
 These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.
@@
 Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
-We understand that it is not in the tradition of the scientific community to comment publicly online about colleagues’ research results.
-We think this will change given the possibilities of new media, and possibly incentives for open commenting and reviewing could shift the trend.
+Although it is not in the tradition of the scientific community to comment publicly online about colleagues’ research results, I am optimistic that this will change given the possibilities of new media, and possibly incentives for open commenting and reviewing could shift the trend.
 Importantly, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints were revised at least once.
@@
 Measuring the impact and significance of scientific research is notoriously difficult.
-Using several metrics we sought to quantify the effect that broadly defined microbiology-affiliated preprints have had on the work of others.
-Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively.
+Using several metrics I sought to quantify the effect that broadly defined microbiology-affiliated preprints have had on the work of others.
+Using the download statistics associated with each preprint, I found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively.
 These values represent two aspects of posting a preprint.
@@
 Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall.
-To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint (**Figure 1B**).
+To obtain a measure of a preprint's ability to garner attention and engage the public, I obtained the Altmetric Attention Score for each preprint (**Figure 1B**).
 The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, traditional media, Wikipedia, policy documents, and other sources [@Altmetric].
@@
 A more traditional and controversial metric of impact has been the number of citations an article receives.
-We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints.
-To allow for a comparison to traditional journals, we considered the citations for preprints published in 2014 and 2015 as aggregated by Web of Science (**Figure 1C**).
+I obtained the number of citations for the published versions of manuscripts that were initially posted as preprints.
+To allow for a comparison to traditional journals, I considered the citations for preprints published in 2014 and 2015 as aggregated by Web of Science (**Figure 1C**).
 Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`).
@@
 A first example illustrates the utility of preprints for improving access to research and the quality of its reporting.
-In 2014, the Schloss laboratory posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform [@Schloss2015].
+In 2014, my research group posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform [@Schloss2015].
 At the same time, they submitted the manuscript for review at *PeerJ*.
@@
 As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **February XX, 2017**.
-We then solicited feedback on the manuscript using social media.
-Two weeks later, we incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
+I then solicited feedback on the manuscript using social media.
+Two weeks later, I incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
 During that time, the abstract was read **XXXX** times and the PDF was accessed **XXXX** times.
 This process engaged **XXXX** commenters on *bioRxiv*, **XXXX** people on Twitter, **XXXX** on Facebook, and **XXXX** via email.
-We received useful feedback from **XXX** people.
-Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had we foregone the posting of a preprint.
-Although there are concerns regarding the quality of the science posted to a preprint server, we contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.
+I received useful feedback from **XXX** people.
+Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had I foregone the posting of a preprint.
+Although there are concerns regarding the quality of the science posted to a preprint server, I contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.
 
 ***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals will have in disseminating research if there is broad adoption of preprints.
-We think that edited peer-reviewed journals offer, and will continue to offer significant added value to a publication.
+Edited peer-reviewed journals offer and will continue to offer significant added value to a publication.
 A scholarly publishing ecosystem in which preprints coexist with journals will allow authors to gain value from the immediate communication of their work associated with preprints and also benefit from the peer-reviewed, professionally edited publication that publishers can provide.
@@
 actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016].
-ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles.
+ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication).
 In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016].
@@
 
+I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful comments on earlier versions of this manuscript.
 This work was supported in part by funding to PDS from the National Institutes of Health (P30DK034933).
-We appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases.
+I appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases.
 The workflow utilized commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.`r paste(version$major, version$minor, sep='.')`).
-Within R we utilized the  cowplot (v.`r packageDescription("cowplot")$Version`), dplyr (v.`r packageDescription("dplyr")$Version`),
+Within R I utilized the cowplot (v.`r packageDescription("cowplot")$Version`), dplyr (v.`r packageDescription("dplyr")$Version`),
 ggplot2 (v.`r packageDescription("ggplot2")$Version`), httr (v.`r packageDescription("httr")$Version`), RCurl (v.`r packageDescription("RCurl")$Version`),

### 2017-02-18 code/build_figure1.R

@@ -159,5 +159,5 @@ ggdraw() +
 				theme(axis.title.y = element_text(margin = margin(r=7))),
 				x=0,y=0.0,1,0.33) +
 	draw_plot_label(c("A", "B", "C"), x=c(0,0,0), y=c(1.00,0.66,0.33), size=12) +
-	ggsave('figures/figure1.tiff', width=8.4, height=14, units="cm") +
+	ggsave('figures/figure1.eps', width=8.4, height=14, units="cm") +
 	ggsave('figures/figure1.png', width=8.4, height=14, units="cm")

### 2017-02-18 submission/Schloss_PrePrints_mBio_2017.tex
Render with eps file instead of tiff

@@
     \usepackage{mathspec}
+    \usepackage{xltxtra,xunicode}
   \else
@@
   \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
   \newcommand{\euro}{€}
@@
 \usepackage[margin=1.0in]{geometry}
-\usepackage{hyperref}
-\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
-\hypersetup{unicode=true,
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
             pdftitle={Preprinting Microbiology},
-            pdfborder={0 0 0},
-            breaklinks=true}
+            colorlinks=true,
+            citecolor=blue,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
 \urlstyle{same}  % don't use monospace font for urls
@@
 journals. Although use of preprints is still limited in the biological
-sciences, early indications are that preprints are as robust tool that
+sciences, early indications are that preprints are a robust tool that
 can complement and enhance peer-reviewed publications. As publishing
@@
 to achieve a wider audience for critique and reception (7). Considering
-the broadening adoption of preprints among microbiologists, we sought to
+the broadening adoption of preprints among microbiologists, I sought to
 explore the specific uses of and concerns regarding preprints.
@@
 manuscripts posted as preprints under a CC-BY license (e.g.
-\emph{Proceedings of the National Academy of Sciences}). We particularly
-like the \emph{bioRxiv} licensing flexibility, which empowers authors to
-choose the model that best suits them, while ensuring the rapid posting
-of their research resultsl however, it is important to provide clear
-information to authors on the legal and practical tradeoffs of each
-option. A cosmetic, but still relevant difference between the two is the
-layout and feel of the two websites. Compared to the \emph{bioRxiv}
-site, the \emph{PeerJ Preprint} site is more fluid, gives readers the
-ability to ``follow'' a preprint, and provides better access to article
-keywords and the ability to search preprints. With broader acceptance of
-preprints by traditional journals, many journals, including all of the
-ASM journals, have established mechanisms to directly submit manuscripts
-that are posted as preprints on \emph{bioRxiv}. It is only possible to
-transfer a \emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many
-ways, preprint servers have taken on the feel of a journal. As adoption
-of this approach expands, it is likely that the features of these sites
+\emph{Proceedings of the National Academy of Sciences}). The flexibility
+of the \emph{bioRxiv} licensing empowers authors to choose the model
+that best suits them, while ensuring the rapid posting of their research
+results however, it is important to provide clear information to authors
+on the legal and practical tradeoffs of each option. A cosmetic, but
+still relevant difference between the two is the layout and feel of the
+two websites. Compared to the \emph{bioRxiv} site, the \emph{PeerJ
+Preprint} site is more fluid, gives readers the ability to ``follow'' a
+preprint, and provides better access to article keywords and the ability
+to search preprints. With broader acceptance of preprints by traditional
+journals, many journals, including all of the ASM journals, have
+established mechanisms to directly submit manuscripts that are posted as
+preprints on \emph{bioRxiv}. It is only possible to transfer a
+\emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many ways,
+preprint servers have taken on the feel of a journal. As adoption of
+this approach expands, it is likely that the features of these sites
 will continue to improve. It is also likely that interfaces from
@@
 peer-reviewed publications. As preprint servers begin to look and act
-like traditional journals by incorporating features and interfaces, we
-think that it is important to value the strength of the preprint - that
-of an interim research product, nimble and quickly posted. It is
-therefore essential to balance the requirements placed on authors for
-features associated with preprints with the current desirable efficiency
-of the preprint format.
+like traditional journals by incorporating features and interfaces, it
+is important to value the strength of the preprint - that of an interim
+research product, nimble and quickly posted. It is therefore essential
+to balance the requirements placed on authors for features associated
+with preprints with the current desirable efficiency of the preprint
+format.
 
@@
 Some fear that the use of preprints will allow scientists to circumvent
-page limits by posting preliminary manuscripts. We would hope that both
+page limits by posting preliminary manuscripts. I would hope that both
 consumers of preprints and grant proposal reviewers would be able to
@@
 \textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
-analyze the use of preprints, we downloaded the \emph{bioRxiv} on
-December 31, 2016. We chose to analyze \emph{bioRxiv} preprints because
+analyze the use of preprints, I downloaded the \emph{bioRxiv} on
+December 31, 2016. I chose to analyze \emph{bioRxiv} preprints because
 these preprints are amenable for submission to ASM journals and there
@@
 the Scientific Communication and Education categories. To counter this
-limitation, we developed a more permissive approach that classified
+limitation, I developed a more permissive approach that classified
 preprints as being microbiology-affiliated if their title or abstract
@@
 \emph{virus}, \emph{archaea}, \emph{bacteri}, \emph{microb},
-\emph{microorganism}, or \emph{pathogen}. We identified 1,228 additional
-manuscripts that we considered microbiology-affiliated. These
+\emph{microorganism}, or \emph{pathogen}. I identified 1,228 additional
+manuscripts that I considered microbiology-affiliated. These
 microbiology-affiliated preprints were primarily assigned to the
@@
 this result was somewhat disturbing since the preprint model implicitly
-depends on people's willingness to offer others feedback. We understand
-that it is not in the tradition of the scientific community to comment
-publicly online about colleagues' research results. We think this will
-change given the possibilities of new media, and possibly incentives for
-open commenting and reviewing could shift the trend. Importantly,
-authors do appear to be incorporating feedback from colleagues or
-editorial insights from journals as 404 (25.8\%) of preprints were
-revised at least once. Among the preprints posted prior to January 1,
-2016, 31.6\% of the Microbiology category preprints, 35.1\% of the
-microbiology-affiliated preprints, and 33.8\% of all preprints have been
-published. As noted above, not all authors submit their preprints to
-journals. This would indicate that the ``acceptance rates'' are actually
-higher. Regardless, considering that these acceptance rates are higher
-than many peer-reviewed journals (e.g.~approximately 20\% at ASM
-Journals), these results dispel the critique that preprints represent
-overly preliminary research.
+depends on people's willingness to offer others feedback. Although it is
+not in the tradition of the scientific community to comment publicly
+online about colleagues' research results, I am optimistic that this
+will change given the possibilities of new media, and possibly
+incentives for open commenting and reviewing could shift the trend.
+Importantly, authors do appear to be incorporating feedback from
+colleagues or editorial insights from journals as 404 (25.8\%) of
+preprints were revised at least once. Among the preprints posted prior
+to January 1, 2016, 31.6\% of the Microbiology category preprints,
+35.1\% of the microbiology-affiliated preprints, and 33.8\% of all
+preprints have been published. As noted above, not all authors submit
+their preprints to journals. This would indicate that the ``acceptance
+rates'' are actually higher. Regardless, considering that these
+acceptance rates are higher than many peer-reviewed journals
+(e.g.~approximately 20\% at ASM Journals), these results dispel the
+critique that preprints represent overly preliminary research.
 
 Measuring the impact and significance of scientific research is
-notoriously difficult. Using several metrics we sought to quantify the
+notoriously difficult. Using several metrics I sought to quantify the
 effect that broadly defined microbiology-affiliated preprints have had
 on the work of others. Using the download statistics associated with
-each preprint, we found that the median number of times an abstract or
+each preprint, I found that the median number of times an abstract or
 PDF had been accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to
@@
 published behind a paywall. To obtain a measure of a preprint's ability
-to garner attention and engage the public, we obtained the Altmetric
+to garner attention and engage the public, I obtained the Altmetric
 Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
@@
 controversial metric of impact has been the number of citations an
-article receives. We obtained the number of citations for the published
+article receives. I obtained the number of citations for the published
 versions of manuscripts that were initially posted as preprints. To
-allow for a comparison to traditional journals, we considered the
+allow for a comparison to traditional journals, I considered the
 citations for preprints published in 2014 and 2015 as aggregated by Web
@@
 example illustrates the utility of preprints for improving access to
-research and the quality of its reporting. In 2014, the Schloss
-laboratory posted a preprint to \emph{PeerJ Preprints} describing a
-method of sequencing 16S rRNA gene sequences using the Pacific
-Biosciences sequencing platform (34). At the same time, they submitted
-the manuscript for review at \emph{PeerJ}. While the manuscript was
-under review, they received feedback from an academic scientist and from
+research and the quality of its reporting. In 2014, my research group
+posted a preprint to \emph{PeerJ Preprints} describing a method of
+sequencing 16S rRNA gene sequences using the Pacific Biosciences
+sequencing platform (34). At the same time, they submitted the
+manuscript for review at \emph{PeerJ}. While the manuscript was under
+review, they received feedback from an academic scientist and from
 scientists at Pacific Biosciences that the impact of the results could
@@
 manuscript was posted to \emph{bioRxiv} as a preprint on
-\textbf{February XX, 2017}. We then solicited feedback on the manuscript
-using social media. Two weeks later, we incorporated the comments and
+\textbf{February XX, 2017}. I then solicited feedback on the manuscript
+using social media. Two weeks later, I incorporated the comments and
 posted a revised preprint and submitted the manuscript to \emph{mBio}.
@@
 commenters on \emph{bioRxiv}, \textbf{XXXX} people on Twitter,
-\textbf{XXXX} on Facebook, and \textbf{XXXX} via email. We received
+\textbf{XXXX} on Facebook, and \textbf{XXXX} via email. I received
 useful feedback from \textbf{XXX} people. Compared to the two or three
 scientists that typically review a manuscript, this experience engaged a
-much larger and more diverse community than had we foregone the posting
+much larger and more diverse community than had I foregone the posting
 of a preprint. Although there are concerns regarding the quality of the
-science posted to a preprint server, we contend that responsible use of
+science posted to a preprint server, I contend that responsible use of
 preprints as a part of the scientific process can significantly enhance
@@
 question is what role traditional journals will have in disseminating
-research if there is broad adoption of preprints. We think that edited
-peer-reviewed journals offer, and will continue to offer significant
-added value to a publication. A scholarly publishing ecosystem in which
-preprints coexist with journals will allow authors to gain value from
-the immediate communication of their work associated with preprints and
-also benefit from the peer-reviewed, professionally edited publication
-that publishers can provide. The professional copyediting, layout, and
+research if there is broad adoption of preprints. Edited peer-reviewed
+journals offer and will continue to offer significant added value to a
+publication. A scholarly publishing ecosystem in which preprints coexist
+with journals will allow authors to gain value from the immediate
+communication of their work associated with preprints and also benefit
+from the peer-reviewed, professionally edited publication that
+publishers can provide. The professional copyediting, layout, and
 publicity that these publishers offer are also unique features of
@@
 microbial sciences, further enhancing the use of preprints as well as
-published articles. In addition to integrating preprints into the
-traditional editorial process, several professional societies have also
-explicitly supported citation of preprints in their other publications
-and recognize the priority of preprints in the literature (14--16).
-These are policies that empower authors and make specific journals more
-attractive. Other practices have great potential to improve the
-reputation of journals. As measured above, preprints are able to garner
-attention on par with papers published in highly selective microbiology
-journals. Thus, it is in a journal's best interest to recruit these
-preprints to their journals. Several journals including \emph{PLOS
-Genetics} and \emph{Genome Biology} have publicly stated that they scout
-preprints for this purpose (40, 41). Preprints can also be viewed as a
-lost opportunity to journals. A preprint that garners significant
-attention may be ignored when it is finally published, brining little
-additional attention to the journal. Going forward, it will be
-interesting to see the innovative approaches that publishers develop so
-that they can benefit by incorporating preprints into their process and
-whether publishers' influence is reduced by the widespread adoption of
+published articles (Stefano Bertuzzi, personal communication). In
+addition to integrating preprints into the traditional editorial
+process, several professional societies have also explicitly supported
+citation of preprints in their other publications and recognize the
+priority of preprints in the literature (14--16). These are policies
+that empower authors and make specific journals more attractive. Other
+practices have great potential to improve the reputation of journals. As
+measured above, preprints are able to garner attention on par with
+papers published in highly selective microbiology journals. Thus, it is
+in a journal's best interest to recruit these preprints to their
+journals. Several journals including \emph{PLOS Genetics} and
+\emph{Genome Biology} have publicly stated that they scout preprints for
+this purpose (40, 41). Preprints can also be viewed as a lost
+opportunity to journals. A preprint that garners significant attention
+may be ignored when it is finally published, brining little additional
+attention to the journal. Going forward, it will be interesting to see
+the innovative approaches that publishers develop so that they can
+benefit by incorporating preprints into their process and whether
+publishers' influence is reduced by the widespread adoption of
 preprints.
@@
 
-This work was supported in part by funding to PDS from the National
-Institutes of Health (P30DK034933). We appreciate the support of
-Altmetric, Inc and Thompson Reuters who provided advanced programming
-interface (API) access to their databases. The workflow utilized
-commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
-Within R we utilized the cowplot (v.0.6.3), dplyr (v.0.5.0), ggplot2
-(v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
-rjson (v.0.2.15), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and tidyr
-(v.0.6.0) packages. A reproducible version of this manuscript and
-analysis is available at
+I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful
+comments on earlier versions of this manuscript. This work was supported
+in part by funding to PDS from the National Institutes of Health
+(P30DK034933). I appreciate the support of Altmetric, Inc and Thompson
+Reuters who provided advanced programming interface (API) access to
+their databases. The workflow utilized commands in GNU make (v.3.81),
+GNU bash (v.4.1.2), and R (v.3.3.2). Within R I utilized the cowplot
+(v.0.6.9990), dplyr (v.0.5.0), ggplot2 (v.2.1.0.9001), httr (v.1.2.1),
+RCurl (v.1.95-4.8), rentrez (v.1.0.4), rjson (v.0.2.15), rvest
+(v.0.3.2), sportcolors (v.0.0.1), and tidyr (v.0.6.0) packages. A
+reproducible version of this manuscript and analysis is available at
 \url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.
@@
 
+\hyperdef{}{references}{\label{references}}
 \subsection*{References}\label{references}
@@
 
-\hypertarget{refs}{}
-\hypertarget{ref-Vale2015}{}
+\hyperdef{}{ref-Vale2015}{\label{ref-Vale2015}}
 1. \textbf{Vale RD}. 2015. Accelerating scientific publication in
@@
 \textbf{112}:13439--13446.
-doi:\href{https://doi.org/10.1073/pnas.1511912112}{10.1073/pnas.1511912112}.
+doi:\url{http://doi.org/10.1073/pnas.1511912112}.
 
-\hypertarget{ref-DesjardinsProulx2013}{}
+\hyperdef{}{ref-DesjardinsProulx2013}{\label{ref-DesjardinsProulx2013}}
 2. \textbf{Desjardins-Proulx P}, \textbf{White EP}, \textbf{Adamson JJ},
@@
 open preprints in biology. PLoS Biology \textbf{11}:e1001563.
-doi:\href{https://doi.org/10.1371/journal.pbio.1001563}{10.1371/journal.pbio.1001563}.
+doi:\url{http://doi.org/10.1371/journal.pbio.1001563}.
 
-\hypertarget{ref-Berg2016}{}
+\hyperdef{}{ref-Berg2016}{\label{ref-Berg2016}}
 3. \textbf{Berg JM}, \textbf{Bhalla N}, \textbf{Bourne PE},
@@
 \textbf{Wolberger C}. 2016. Preprints for the life sciences. Science
-\textbf{352}:899--901.
-doi:\href{https://doi.org/10.1126/science.aaf9133}{10.1126/science.aaf9133}.
+\textbf{352}:899--901. doi:\url{http://doi.org/10.1126/science.aaf9133}.
 
-\hypertarget{ref-Bhalla2016}{}
+\hyperdef{}{ref-Bhalla2016}{\label{ref-Bhalla2016}}
 4. \textbf{Bhalla N}. 2016. Has the time come for preprints in biology?
 Molecular Biology of the Cell \textbf{27}:1185--1187.
-doi:\href{https://doi.org/10.1091/mbc.e16-02-0123}{10.1091/mbc.e16-02-0123}.
+doi:\url{http://doi.org/10.1091/mbc.e16-02-0123}.
 
-\hypertarget{ref-Nature1966}{}
+\hyperdef{}{ref-Nature1966}{\label{ref-Nature1966}}
 5. 1966. Preprints galore. Nature \textbf{211}:897--898.
-doi:\href{https://doi.org/10.1038/211897a0}{10.1038/211897a0}.
+doi:\url{http://doi.org/10.1038/211897a0}.
 
-\hypertarget{ref-Ginsparg2011}{}
+\hyperdef{}{ref-Ginsparg2011}{\label{ref-Ginsparg2011}}
 6. \textbf{Ginsparg P}. 2011. ArXiv at 20. Nature \textbf{476}:145--147.
-doi:\href{https://doi.org/10.1038/476145a}{10.1038/476145a}.
+doi:\url{http://doi.org/10.1038/476145a}.
 
-\hypertarget{ref-Shuai2012}{}
+\hyperdef{}{ref-Shuai2012}{\label{ref-Shuai2012}}
 7. \textbf{Shuai X}, \textbf{Pepe A}, \textbf{Bollen J}. 2012. How the
@@
 downloads, twitter mentions, and citations. PLoS ONE \textbf{7}:e47523.
-doi:\href{https://doi.org/10.1371/journal.pone.0047523}{10.1371/journal.pone.0047523}.
+doi:\url{http://doi.org/10.1371/journal.pone.0047523}.
 
-\hypertarget{ref-Callaway2013}{}
+\hyperdef{}{ref-Callaway2013}{\label{ref-Callaway2013}}
 8. \textbf{Callaway E}. 2013. Biomedical journal and publisher hope to
 bring preprints to life. Nature Medicine \textbf{19}:512--512.
-doi:\href{https://doi.org/10.1038/nm0513-512}{10.1038/nm0513-512}.
+doi:\url{http://doi.org/10.1038/nm0513-512}.
 
-\hypertarget{ref-PreprintPolicy}{}
+\hyperdef{}{ref-PreprintPolicy}{\label{ref-PreprintPolicy}}
 9. List of academic journals by preprint policy.
@@
 
-\hypertarget{ref-Sherpa}{}
+\hyperdef{}{ref-Sherpa}{\label{ref-Sherpa}}
 10. Publisher copyright policies \& self-archiving.
@@
 
-\hypertarget{ref-Drubin2016}{}
+\hyperdef{}{ref-Drubin2016}{\label{ref-Drubin2016}}
 11. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
@@
 the Cell \textbf{27}:3181--3182.
-doi:\href{https://doi.org/10.1091/mbc.e16-09-0651}{10.1091/mbc.e16-09-0651}.
+doi:\url{http://doi.org/10.1091/mbc.e16-09-0651}.
 
-\hypertarget{ref-Spier2002}{}
+\hyperdef{}{ref-Spier2002}{\label{ref-Spier2002}}
 12. \textbf{Spier R}. 2002. The history of the peer-review process.
 Trends in Biotechnology \textbf{20}:357--358.
-doi:\href{https://doi.org/10.1016/s0167-7799(02)01985-6}{10.1016/s0167-7799(02)01985-6}.
+doi:\url{http://doi.org/10.1016/s0167-7799(02)01985-6}.
 
-\hypertarget{ref-Burnham1990}{}
+\hyperdef{}{ref-Burnham1990}{\label{ref-Burnham1990}}
 13. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
 JAMA: The Journal of the American Medical Association \textbf{263}:1323.
-doi:\href{https://doi.org/10.1001/jama.1990.03440100023003}{10.1001/jama.1990.03440100023003}.
+doi:\url{http://doi.org/10.1001/jama.1990.03440100023003}.
 
-\hypertarget{ref-Pulverer2016}{}
+\hyperdef{}{ref-Pulverer2016}{\label{ref-Pulverer2016}}
 14. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
 \textbf{35}:2617--2619.
-doi:\href{https://doi.org/10.15252/embj.201670030}{10.15252/embj.201670030}.
+doi:\url{http://doi.org/10.15252/embj.201670030}.
 
-\hypertarget{ref-Loew2016}{}
+\hyperdef{}{ref-Loew2016}{\label{ref-Loew2016}}
 15. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
 \textbf{111}:E01--E02.
-doi:\href{https://doi.org/10.1016/j.bpj.2016.06.035}{10.1016/j.bpj.2016.06.035}.
+doi:\url{http://doi.org/10.1016/j.bpj.2016.06.035}.
 
-\hypertarget{ref-Vale2016}{}
+\hyperdef{}{ref-Vale2016}{\label{ref-Vale2016}}
 16. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
 the life sciences. eLife \textbf{5}.
-doi:\href{https://doi.org/10.7554/elife.16931}{10.7554/elife.16931}.
+doi:\url{http://doi.org/10.7554/elife.16931}.
 
-\hypertarget{ref-Dolgin2016}{}
+\hyperdef{}{ref-Dolgin2016}{\label{ref-Dolgin2016}}
 17. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
-Nature.
-doi:\href{https://doi.org/10.1038/nature.2016.21074}{10.1038/nature.2016.21074}.
+Nature. doi:\url{http://doi.org/10.1038/nature.2016.21074}.
 
-\hypertarget{ref-SinghChawla2017}{}
+\hyperdef{}{ref-SinghChawla2017}{\label{ref-SinghChawla2017}}
 18. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
-Nature.
-doi:\href{https://doi.org/10.1038/nature.2017.21333}{10.1038/nature.2017.21333}.
+Nature. doi:\url{http://doi.org/10.1038/nature.2017.21333}.
 
-\hypertarget{ref-Afshinnekoo2015a}{}
+\hyperdef{}{ref-Afshinnekoo2015a}{\label{ref-Afshinnekoo2015a}}
 19. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
@@
 and bacterial diversity with city-scale metagenomics. Cell Systems
-\textbf{1}:72--87.
-doi:\href{https://doi.org/10.1016/j.cels.2015.01.001}{10.1016/j.cels.2015.01.001}.
+\textbf{1}:72--87. doi:\url{http://doi.org/10.1016/j.cels.2015.01.001}.
 
-\hypertarget{ref-Petit2015}{}
+\hyperdef{}{ref-Petit2015}{\label{ref-Petit2015}}
 20. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
 \textbf{Read TD}. 2015. Searching for anthrax in the New York City
-subway metagenome.
-doi:\href{https://doi.org/10.5281/zenodo.17158}{10.5281/zenodo.17158}.
+subway metagenome. doi:\url{http://doi.org/10.5281/zenodo.17158}.
 
-\hypertarget{ref-Ackelsberg2015}{}
+\hyperdef{}{ref-Ackelsberg2015}{\label{ref-Ackelsberg2015}}
 21. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
@@
 evidence for plague or anthrax on the new york city subway. Cell Systems
-\textbf{1}:4--5.
-doi:\href{https://doi.org/10.1016/j.cels.2015.07.008}{10.1016/j.cels.2015.07.008}.
+\textbf{1}:4--5. doi:\url{http://doi.org/10.1016/j.cels.2015.07.008}.
 
-\hypertarget{ref-Afshinnekoo2015b}{}
+\hyperdef{}{ref-Afshinnekoo2015b}{\label{ref-Afshinnekoo2015b}}
 22. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
@@
 metagenomic complexity. Cell Systems \textbf{1}:6--7.
-doi:\href{https://doi.org/10.1016/j.cels.2015.07.007}{10.1016/j.cels.2015.07.007}.
+doi:\url{http://doi.org/10.1016/j.cels.2015.07.007}.
 
-\hypertarget{ref-Boothby2015}{}
+\hyperdef{}{ref-Boothby2015}{\label{ref-Boothby2015}}
 23. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
@@
 \textbf{112}:15976--15981.
-doi:\href{https://doi.org/10.1073/pnas.1510461112}{10.1073/pnas.1510461112}.
+doi:\url{http://doi.org/10.1073/pnas.1510461112}.
 
-\hypertarget{ref-Koutsovoulos2016a}{}
+\hyperdef{}{ref-Koutsovoulos2016a}{\label{ref-Koutsovoulos2016a}}
 24. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
@@
 tardigrade hypsibius dujardini. bioRxiv 033464.
-doi:\href{https://doi.org/10.1101/033464}{10.1101/033464}.
+doi:\url{http://doi.org/10.1101/033464}.
 
-\hypertarget{ref-Boothby2016}{}
+\hyperdef{}{ref-Boothby2016}{\label{ref-Boothby2016}}
 25. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
@@
 Sciences \textbf{113}:E3058--E3061.
-doi:\href{https://doi.org/10.1073/pnas.1601149113}{10.1073/pnas.1601149113}.
+doi:\url{http://doi.org/10.1073/pnas.1601149113}.
 
-\hypertarget{ref-Koutsovoulos2016b}{}
+\hyperdef{}{ref-Koutsovoulos2016b}{\label{ref-Koutsovoulos2016b}}
 26. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
@@
 Sciences \textbf{113}:5053--5058.
-doi:\href{https://doi.org/10.1073/pnas.1600338113}{10.1073/pnas.1600338113}.
+doi:\url{http://doi.org/10.1073/pnas.1600338113}.
 
-\hypertarget{ref-Bemm2016}{}
+\hyperdef{}{ref-Bemm2016}{\label{ref-Bemm2016}}
 27. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
@@
 of Sciences \textbf{113}:E3054--E3056.
-doi:\href{https://doi.org/10.1073/pnas.1525116113}{10.1073/pnas.1525116113}.
+doi:\url{http://doi.org/10.1073/pnas.1525116113}.
 
-\hypertarget{ref-Arakawa2016}{}
+\hyperdef{}{ref-Arakawa2016}{\label{ref-Arakawa2016}}
 28. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
@@
 National Academy of Sciences \textbf{113}:E3057--E3057.
-doi:\href{https://doi.org/10.1073/pnas.1602711113}{10.1073/pnas.1602711113}.
+doi:\url{http://doi.org/10.1073/pnas.1602711113}.
 
-\hypertarget{ref-Delmont2016}{}
+\hyperdef{}{ref-Delmont2016}{\label{ref-Delmont2016}}
 29. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
@@
 Metagenomic approaches for eukaryotic genome assemblies.
-doi:\href{https://doi.org/10.7287/peerj.preprints.1695v1}{10.7287/peerj.preprints.1695v1}.
+doi:\url{http://doi.org/10.7287/peerj.preprints.1695v1}.
 
-\hypertarget{ref-Bik2016a}{}
+\hyperdef{}{ref-Bik2016a}{\label{ref-Bik2016a}}
 30. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
 prevalence of inappropriate image duplication in biomedical research
-publications. bioRxiv 049452.
-doi:\href{https://doi.org/10.1101/049452}{10.1101/049452}.
+publications. bioRxiv 049452. doi:\url{http://doi.org/10.1101/049452}.
 
-\hypertarget{ref-Bik2016b}{}
+\hyperdef{}{ref-Bik2016b}{\label{ref-Bik2016b}}
 31. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
@@
 publications. mBio \textbf{7}:e00809--16.
-doi:\href{https://doi.org/10.1128/mbio.00809-16}{10.1128/mbio.00809-16}.
+doi:\url{http://doi.org/10.1128/mbio.00809-16}.
 
-\hypertarget{ref-WolfeSimon2010}{}
+\hyperdef{}{ref-WolfeSimon2010}{\label{ref-WolfeSimon2010}}
 32. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
@@
 \textbf{332}:1163--1166.
-doi:\href{https://doi.org/10.1126/science.1197258}{10.1126/science.1197258}.
+doi:\url{http://doi.org/10.1126/science.1197258}.
 
-\hypertarget{ref-Altmetric}{}
+\hyperdef{}{ref-Altmetric}{\label{ref-Altmetric}}
 33. How is the Altmetric Attention Score calculated?
@@
 
-\hypertarget{ref-Schloss2015}{}
+\hyperdef{}{ref-Schloss2015}{\label{ref-Schloss2015}}
 34. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
@@
 the PacBio SMRT DNA sequencing system.
-doi:\href{https://doi.org/10.7287/peerj.preprints.778v1}{10.7287/peerj.preprints.778v1}.
+doi:\url{http://doi.org/10.7287/peerj.preprints.778v1}.
 
-\hypertarget{ref-Schloss2016a}{}
+\hyperdef{}{ref-Schloss2016a}{\label{ref-Schloss2016a}}
 35. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
@@
 gene fragments using the PacBio SMRT DNA sequencing system.
-doi:\href{https://doi.org/10.7287/peerj.preprints.778v2}{10.7287/peerj.preprints.778v2}.
+doi:\url{http://doi.org/10.7287/peerj.preprints.778v2}.
 
-\hypertarget{ref-Schloss2016b}{}
+\hyperdef{}{ref-Schloss2016b}{\label{ref-Schloss2016b}}
 36. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
@@
 gene fragments using the PacBio SMRT DNA sequencing system. PeerJ
-\textbf{4}:e1869.
-doi:\href{https://doi.org/10.7717/peerj.1869}{10.7717/peerj.1869}.
+\textbf{4}:e1869. doi:\url{http://doi.org/10.7717/peerj.1869}.
 
-\hypertarget{ref-Baxter2016a}{}
+\hyperdef{}{ref-Baxter2016a}{\label{ref-Baxter2016a}}
 37. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
@@
 cancer screening. bioRxiv 048389.
-doi:\href{https://doi.org/10.1101/048389}{10.1101/048389}.
+doi:\url{http://doi.org/10.1101/048389}.
 
-\hypertarget{ref-Baxter2016b}{}
+\hyperdef{}{ref-Baxter2016b}{\label{ref-Baxter2016b}}
 38. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
@@
 using a microbiota-based model. Microbiome \textbf{4}.
-doi:\href{https://doi.org/10.1186/s40168-016-0205-y}{10.1186/s40168-016-0205-y}.
+doi:\url{http://doi.org/10.1186/s40168-016-0205-y}.
 
-\hypertarget{ref-Imperiale2016}{}
+\hyperdef{}{ref-Imperiale2016}{\label{ref-Imperiale2016}}
 39. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
@@
 \textbf{1}:e00307--16.
-doi:\href{https://doi.org/10.1128/msphere.00307-16}{10.1128/msphere.00307-16}.
+doi:\url{http://doi.org/10.1128/msphere.00307-16}.
 
-\hypertarget{ref-Vence2017}{}
+\hyperdef{}{ref-Vence2017}{\label{ref-Vence2017}}
 40. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.
 
-\hypertarget{ref-Barsh2016}{}
+\hyperdef{}{ref-Barsh2016}{\label{ref-Barsh2016}}
 41. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
@@
 editors to preprint servers. PLOS Genetics \textbf{12}:e1006448.
-doi:\href{https://doi.org/10.1371/journal.pgen.1006448}{10.1371/journal.pgen.1006448}.
+doi:\url{http://doi.org/10.1371/journal.pgen.1006448}.
 

### 2017-02-18 code/build_figure1.R

@@ -98,8 +98,8 @@ altmetric_plot <- source_altmetric %>% #filter(source == "biorxiv") %>%
 											scale_y_continuous(expand = c(0.02, 0), limits=c(0,200)) +
 											scale_x_continuous(expand = c(0.02, 0), limits=c(0,100)) +
 											labs(x="Altmetric Impact Score", y="Number of\nPapers or Preprints") +
-											scale_fill_manual(breaks=names(j), labels=plot_labels, values=paste0("#", team_colors("Chicago Cubs")), name=NULL)+
-											scale_color_manual(breaks=names(j), labels=plot_labels, values=paste0("#", team_colors("Chicago Cubs")), name=NULL)+
+											scale_fill_manual(breaks=names(j), labels=plot_labels, values=team_colors("Chicago Cubs"), name=NULL)+
+											scale_color_manual(breaks=names(j), labels=plot_labels, values=team_colors("Chicago Cubs"), name=NULL)+
 											my_theme +
 											theme(legend.position = c(0.8,0.9))
 
@@ -140,8 +140,8 @@ citation_plot <- source_citations %>%
 											geom_vline(data=median_cites, aes(xintercept=median, color=source), size=0.5, show.legend=FALSE, alpha=0.5) +
 											scale_y_continuous(expand = c(0.02, 0), limits=c(0,100)) +
 											scale_x_continuous(expand = c(0.02, 0), limits=c(0,80)) +
-											scale_fill_manual(breaks=names(j), labels=plot_labels, values=paste0("#", team_colors("Chicago Cubs")), name=NULL)+
-											scale_color_manual(breaks=names(j), labels=plot_labels, values=paste0("#", team_colors("Chicago Cubs")), name=NULL)+
+											scale_fill_manual(breaks=names(j), labels=plot_labels, values=team_colors("Chicago Cubs"), name=NULL)+
+											scale_color_manual(breaks=names(j), labels=plot_labels, values=team_colors("Chicago Cubs"), name=NULL)+
 											labs(x="Number of Citations", y="Number of Papers\nPublished in 2014/2015") +
  											my_theme +
  											theme(legend.position = c(0.8,0.9))

### 2017-02-18 code/build_figure1.R
Change eps to pdf format

@@ -159,5 +159,5 @@ ggdraw() +
 				theme(axis.title.y = element_text(margin = margin(r=7))),
 				x=0,y=0.0,1,0.33) +
 	draw_plot_label(c("A", "B", "C"), x=c(0,0,0), y=c(1.00,0.66,0.33), size=12) +
-	ggsave('figures/figure1.eps', width=8.4, height=14, units="cm") +
+	ggsave('figures/figure1.pdf', width=8.4, height=14, units="cm") +
 	ggsave('figures/figure1.png', width=8.4, height=14, units="cm")

### 2017-02-21 submission/Schloss_PrePrints_mBio_2017.Rmd
Add reference to JID and updated ICMJE statement

@@
 
-***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in posting their work as preprints as a stage in disseminating their research was whether it constituted prior publication.
-The broad consensus at this point is that preprints do not constitute prior publication.
-This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, *Nature* and Cell press, which each take a generally permissive stance towards prior posting of preprints prior to submission.
+***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in posting their work as preprints as a stage in disseminating their research was whether it constituted prior publication [@Angell1991].
+The broad consensus of the International Committee of Medical Journal Editors and numerous journals is that preprints do not constitute prior publication [@ICMJE].
+This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, *Nature*, *Journal of Infectious Diseases*, and Cell press, which each take a generally permissive stance towards prior posting of preprints prior to submission.
 Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work.

### 2017-02-21 submission/Schloss_PrePrints_mBio_2017.tex
Final rendering prior to submitting preprint

@@
 as preprints as a stage in disseminating their research was whether it
-constituted prior publication. The broad consensus at this point is that
-preprints do not constitute prior publication. This consensus is
-reflected in the current policies of journals that commonly publish
-microbiology research including those published by ASM, the Microbiology
-Society, International Society for Microbial Ecology, PLOS, the
-\emph{Proceedings of the National Academy of Science}, \emph{Science},
-\emph{Nature} and Cell press, which each take a generally permissive
-stance towards prior posting of preprints prior to submission.
-Considering the relatively fluid nature of many of these policies and
-the journals' specific policies, prospective authors should be aware of
-the positions taken by the journals where they may eventually submit
-their work. Comprehensive lists of journals' attitudes towards preprints
-are available online and are regularly updated (9, 10).
+constituted prior publication (9). The broad consensus of the
+International Committee of Medical Journal Editors and numerous journals
+is that preprints do not constitute prior publication (10). This
+consensus is reflected in the current policies of journals that commonly
+publish microbiology research including those published by ASM, the
+Microbiology Society, International Society for Microbial Ecology, PLOS,
+the \emph{Proceedings of the National Academy of Science},
+\emph{Science}, \emph{Nature}, \emph{Journal of Infectious Diseases},
+and Cell press, which each take a generally permissive stance towards
+prior posting of preprints prior to submission. Considering the
+relatively fluid nature of many of these policies and the journals'
+specific policies, prospective authors should be aware of the positions
+taken by the journals where they may eventually submit their work.
+Comprehensive lists of journals' attitudes towards preprints are
+available online and are regularly updated (11, 12).
 
@@
 called into question because preprints upend the traditional peer-review
-editorial process (11). It is important to note that the peer-review
+editorial process (13). It is important to note that the peer-review
 process was adapted to the technologies and trends that have evolved
@@
 journals currently use was not developed until the end of the 1800s with
-the advent of typewriters and carbon paper (12). Editorial decisions
+the advent of typewriters and carbon paper (14). Editorial decisions
 were typically made by a single person or a committee (i.e.~the
@@
 specialization and to deal with the large number of manuscript
-submissions (13). Peer-review did not achieve widespread use at many
+submissions (15). Peer-review did not achieve widespread use at many
 journals, including the \emph{Journal of Bacteriology}, until the 1940s
@@
 societies and journals, including ASM view preprints as citable and as
-having a legitimate claim to primacy (1, 14--16). Some scientists worry
+having a legitimate claim to primacy (1, 16--18). Some scientists worry
 that with such protection a researcher can make a claim without valid
@@
 mandating that researchers post preprints for all of their work prior to
-submitting the work to a journal (17).
+submitting the work to a journal (19).
 
@@
 publication goals. Some authors are explicitly stating that a preprint
-will not be submitted to a journal (18). Although these authors may be a
+will not be submitted to a journal (20). Although these authors may be a
 minority of those who post preprints, such an approach may be attractive
@@
 scientific literature. On February 9, 2015, \emph{Cell Systems} posted a
-study by Afshinnekoo et al. online (19). The study collected and
+study by Afshinnekoo et al. online (21). The study collected and
 analyzed metagenomic sequence data from the New York City subway system
@@
 study generated a considerable amount of media attention. On April 25,
-2015, Petit et al. (20) posted a preprint to Zenodo demonstrating that
+2015, Petit et al. (22) posted a preprint to Zenodo demonstrating that
 there was no evidence for \emph{B. anthracis} in the dataset. On July
@@
 response from the original authors offering a correction to their
-manuscript (21, 22). A second anecdote of using preprints to aid in
+manuscript (23, 24). A second anecdote of using preprints to aid in
 post-publication peer-review surrounds the publishing of a draft
 tardigrade genome in \emph{The Proceedings of the National Academy of
-Sciences}. On November 23, 2015 a study by Boothby et al. (23) was first
+Sciences}. On November 23, 2015 a study by Boothby et al. (25) was first
 published online. The authors claimed that 17.5\% of its genes came from
@@
 sequences and demonstrating that the exciting claims of horizontal gene
-transfer were really the product of contaminants (24); this analysis
+transfer were really the product of contaminants (26); this analysis
 would eventually be published online by the original journal on March
 24, 2016 followed by a rebuttal by the original authors on May 31, 2016
-(25, 26). Two other analyses of the original data were published in May
-2016 and a third was posted as a preprint on February 2, 2016 (27--29).
+(27, 28). Two other analyses of the original data were published in May
+2016 and a third was posted as a preprint on February 2, 2016 (29--31).
 These anecdotes underscore the value of having a rapid posting cycle to
@@
 reporting numerous cases of image manipulation in peer reviewed studies
-(30). Their preprint was posted on April 20, 2016 and published in
-\emph{mBio} on June 7, 2016 (31). Instead of using preprints to react to
+(32). Their preprint was posted on April 20, 2016 and published in
+\emph{mBio} on June 7, 2016 (33). Instead of using preprints to react to
 published papers that have been through peer review, it would be
 interesting to consider how the editorial process for these examples and
-the infamous ``Arsenic Life'' paper (32) would have been different had
+the infamous ``Arsenic Life'' paper (34) would have been different had
 they initially been posted as preprints.
@@
 mentioned in social media, traditional media, Wikipedia, policy
-documents, and other sources (33). A higher score indicates that a
+documents, and other sources (35). A higher score indicates that a
 preprint received more attention. Microbiology-affiliated preprints have
@@
 sequencing 16S rRNA gene sequences using the Pacific Biosciences
-sequencing platform (34). At the same time, they submitted the
+sequencing platform (36). At the same time, they submitted the
 manuscript for review at \emph{PeerJ}. While the manuscript was under
@@
 feedback we received from the academic scientist and Pacific
-Biosciences. It was eventually published by \emph{PeerJ} (35, 36). Since
+Biosciences. It was eventually published by \emph{PeerJ} (37, 38). Since
 2015, we have continued to post manuscripts as preprints at the same
@@
 results available; in one case our preprint was available 7 months ahead
-of the final published version (37, 38). As a second example, this
+of the final published version (39, 40). As a second example, this
 manuscript was posted to \emph{bioRxiv} as a preprint on
-\textbf{February XX, 2017}. I then solicited feedback on the manuscript
+\textbf{February 22, 2017}. I then solicited feedback on the manuscript
 using social media. Two weeks later, I incorporated the comments and
@@
 editorial decision is rendered within five days and publication in
-\emph{mSphere} within a month (39). ASM is developing a new platform,
+\emph{mSphere} within a month (41). ASM is developing a new platform,
 MicroNow, which will help coalesce specific communities within the
@@
 citation of preprints in their other publications and recognize the
-priority of preprints in the literature (14--16). These are policies
+priority of preprints in the literature (16--18). These are policies
 that empower authors and make specific journals more attractive. Other
@@
 \emph{Genome Biology} have publicly stated that they scout preprints for
-this purpose (40, 41). Preprints can also be viewed as a lost
+this purpose (42, 43). Preprints can also be viewed as a lost
 opportunity to journals. A preprint that garners significant attention
@@
 
+\hyperdef{}{ref-Angell1991}{\label{ref-Angell1991}}
+9. \textbf{Angell M}, \textbf{Kassirer JP}. 1991. The ingelfinger rule
+revisited. New England Journal of Medicine \textbf{325}:1371--1373.
+doi:\url{http://doi.org/10.1056/nejm199111073251910}.
+
+\hyperdef{}{ref-ICMJE}{\label{ref-ICMJE}}
+10. Recommendations for the conduct, reporting, editing, and publication
+of scholarly work in medical journals.
+\url{http://www.icmje.org/news-and-editorials/icmje-recommendations_annotated_dec16.pdf}.
+
 \hyperdef{}{ref-PreprintPolicy}{\label{ref-PreprintPolicy}}
-9. List of academic journals by preprint policy.
+11. List of academic journals by preprint policy.
 \url{https://en.wikipedia.org/wiki/List_of_academic_journals_by_preprint_policy}.
@@
 \hyperdef{}{ref-Sherpa}{\label{ref-Sherpa}}
-10. Publisher copyright policies \& self-archiving.
+12. Publisher copyright policies \& self-archiving.
 \url{http://www.sherpa.ac.uk/romeo/index.php}.
@@
 \hyperdef{}{ref-Drubin2016}{\label{ref-Drubin2016}}
-11. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
+13. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
 articles and why MBoC quickly embraced preprints. Molecular Biology of
@@
 \hyperdef{}{ref-Spier2002}{\label{ref-Spier2002}}
-12. \textbf{Spier R}. 2002. The history of the peer-review process.
+14. \textbf{Spier R}. 2002. The history of the peer-review process.
 Trends in Biotechnology \textbf{20}:357--358.
@@
 \hyperdef{}{ref-Burnham1990}{\label{ref-Burnham1990}}
-13. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
+15. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
 JAMA: The Journal of the American Medical Association \textbf{263}:1323.
@@
 \hyperdef{}{ref-Pulverer2016}{\label{ref-Pulverer2016}}
-14. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
+16. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
 \textbf{35}:2617--2619.
@@
 \hyperdef{}{ref-Loew2016}{\label{ref-Loew2016}}
-15. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
+17. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
 \textbf{111}:E01--E02.
@@
 \hyperdef{}{ref-Vale2016}{\label{ref-Vale2016}}
-16. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
+18. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
 the life sciences. eLife \textbf{5}.
@@
 \hyperdef{}{ref-Dolgin2016}{\label{ref-Dolgin2016}}
-17. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
+19. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
 Nature. doi:\url{http://doi.org/10.1038/nature.2016.21074}.
@@
 \hyperdef{}{ref-SinghChawla2017}{\label{ref-SinghChawla2017}}
-18. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
+20. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
 Nature. doi:\url{http://doi.org/10.1038/nature.2017.21333}.
@@
 \hyperdef{}{ref-Afshinnekoo2015a}{\label{ref-Afshinnekoo2015a}}
-19. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
+21. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
 \textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
@@
 \hyperdef{}{ref-Petit2015}{\label{ref-Petit2015}}
-20. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
+22. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
 \textbf{Read TD}. 2015. Searching for anthrax in the New York City
@@
 \hyperdef{}{ref-Ackelsberg2015}{\label{ref-Ackelsberg2015}}
-21. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
+23. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
 \textbf{Petersen J}, \textbf{Mead P}, \textbf{Schriefer M},
@@
 \hyperdef{}{ref-Afshinnekoo2015b}{\label{ref-Afshinnekoo2015b}}
-22. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
+24. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
 \textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
@@
 \hyperdef{}{ref-Boothby2015}{\label{ref-Boothby2015}}
-23. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
+25. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
 \textbf{Wang JR}, \textbf{Patanella KA}, \textbf{Nishimura EO},
@@
 \hyperdef{}{ref-Koutsovoulos2016a}{\label{ref-Koutsovoulos2016a}}
-24. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
+26. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
 \textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
@@
 \hyperdef{}{ref-Boothby2016}{\label{ref-Boothby2016}}
-25. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
+27. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
 al. and arakawa: Identifying foreign genes in independentHypsibius
@@
 \hyperdef{}{ref-Koutsovoulos2016b}{\label{ref-Koutsovoulos2016b}}
-26. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
+28. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
 \textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
@@
 \hyperdef{}{ref-Bemm2016}{\label{ref-Bemm2016}}
-27. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
+29. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
 \textbf{Förster F}. 2016. Genome of a tardigrade: Horizontal gene
@@
 \hyperdef{}{ref-Arakawa2016}{\label{ref-Arakawa2016}}
-28. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
+30. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
 transfer from the draft genome of a tardigrade. Proceedings of the
@@
 \hyperdef{}{ref-Delmont2016}{\label{ref-Delmont2016}}
-29. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
+31. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
 contamination with advanced visualization and analysis practices:
@@
 \hyperdef{}{ref-Bik2016a}{\label{ref-Bik2016a}}
-30. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
+32. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
 prevalence of inappropriate image duplication in biomedical research
@@
 \hyperdef{}{ref-Bik2016b}{\label{ref-Bik2016b}}
-31. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
+33. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
 prevalence of inappropriate image duplication in biomedical research
@@
 \hyperdef{}{ref-WolfeSimon2010}{\label{ref-WolfeSimon2010}}
-32. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
+34. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
 \textbf{Gordon GW}, \textbf{Hoeft SE}, \textbf{Pett-Ridge J},
@@
 \hyperdef{}{ref-Altmetric}{\label{ref-Altmetric}}
-33. How is the Altmetric Attention Score calculated?
+35. How is the Altmetric Attention Score calculated?
 \url{https://help.altmetric.com/support/solutions/articles/6000060969-how-is-the-altmetric-attention-score-calculated-}.
@@
 \hyperdef{}{ref-Schloss2015}{\label{ref-Schloss2015}}
-34. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
+36. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
 \textbf{Highlander SK}. 2015. Sequencing 16S rRNA gene fragments using
@@
 \hyperdef{}{ref-Schloss2016a}{\label{ref-Schloss2016a}}
-35. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
+37. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
 \textbf{Westcott SL}, \textbf{Highlander SK}. 2016. Sequencing 16S rRNA
@@
 \hyperdef{}{ref-Schloss2016b}{\label{ref-Schloss2016b}}
-36. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
+38. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
 \textbf{Westcott SL}, \textbf{Highlander SK}. 2016. Sequencing 16S rRNA
@@
 \hyperdef{}{ref-Baxter2016a}{\label{ref-Baxter2016a}}
-37. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
+39. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
 \textbf{Ruffin MT}, \textbf{Schloss P}. 2016. DNA from fecal
@@
 \hyperdef{}{ref-Baxter2016b}{\label{ref-Baxter2016b}}
-38. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
+40. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
 \textbf{Ruffin MT}, \textbf{Schloss PD}. 2016. DNA from fecal
@@
 \hyperdef{}{ref-Imperiale2016}{\label{ref-Imperiale2016}}
-39. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
+41. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
 mSphereDirect: Author-initiated peer review of manuscripts. mSphere
@@
 \hyperdef{}{ref-Vence2017}{\label{ref-Vence2017}}
-40. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.
+42. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.
 
 \hyperdef{}{ref-Barsh2016}{\label{ref-Barsh2016}}
-41. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
+43. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
 \textbf{Singh ND}, \textbf{Copenhaver GP}. 2016. Bringing PLOS genetics

### 2017-02-23 submission/Schloss_PrePrints_mBio_2017.Rmd
Update deposition date
minor typos, PrePubMed, ScienceOpen

@@
 While the biological community's commitment to preprints waned, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011].
-For some physicists and mathematicians, posting a preprint to *arXiv* followed by submission to a peer-reviewed journal has become a standard publication pathway.
+For some physicists and mathematicians, posting a preprint to *arXiv* optionally followed by submission to a peer-reviewed journal has become a standard publication pathway.
 Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
@@
 For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not.
+For this reason an independent PrePubMed indexing and search engine was developed (<http://www.prepubmed.org/>).
+Additionally, the for-profit publishing network ScienceOpen (<https://www.scienceopen.com/>) indexes *arXiv* preprints and opens up a discussion channel, which is not available on the *arXiv* website.
 There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.
@@
 In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly.
-Over the last several years there have also been rapid advances in DNA sequencing technologies have fundamentally changed how microbial science is performed.
+Over the last several years there have also been rapid advances in DNA sequencing technologies that have fundamentally changed how microbial science is performed.
 One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 90 preprints describing new MinIon-based methods and results to preprint servers.
@@
 For comparison, the median Altmetric Attention Score for articles published in *mBio* published since 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(round(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`).
-Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *bioRxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`.
+Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *bioRxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
 A more traditional and controversial metric of impact has been the number of citations an article receives.
@@
 Although the feedback to other manuscripts has not been as helpful as our initial experience, we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b].
-As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **February XX, 2017**.
+As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **February 22, 2017**.
 I then solicited feedback on the manuscript using social media.
@@
 mSphereDirect is a publication track of the journal that capitalizes on the opportunity offered to couple preprints with rigorous peer-review.
-mSphereDirect.
-actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016].
+mSphereDirect actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016].
 ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication).

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Address confusion in Issue #25
Made it more clear that the section refers to the current manuscript. I
also populated the numbers as of March 13, 2017. Closes #25.

--- 2017-02-21 submission/Schloss_PrePrints_mBio_2017.Rmd
@@
 Although the feedback to other manuscripts has not been as helpful as our initial experience, we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b].
-As a second example, this manuscript was posted to *bioRxiv*  as a preprint on **February XX, 2017**.
+As a second example, a preprint of the current manuscript was posted to *bioRxiv* on February 22, 2017.
 I then solicited feedback on the manuscript using social media.
-Two weeks later, I incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
-During that time, the abstract was read **XXXX** times and the PDF was accessed **XXXX** times.
-This process engaged **XXXX** commenters on *bioRxiv*, **XXXX** people on Twitter, **XXXX** on Facebook, and **XXXX** via email.
-I received useful feedback from **XXX** people.
+On March **13**, 2017 I incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
+During that time, the abstract was accessed **189** times and the PDF was accessed **107** times.
+This process engaged **3** commenters on *bioRxiv*, **61** people on Twitter, **2** people on the manuscript's GitHub repository, **1** person on a blog, and **2** via email.
 Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had I foregone the posting of a preprint.
+Furthermore, the preprint version of this manuscript had an Attention Score of **44**, which placed it in the top **5%** of all research scored by Altmetric.
 Although there are concerns regarding the quality of the science posted to a preprint server, I contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.
@@
 A scholarly publishing ecosystem in which preprints coexist with journals will allow authors to gain value from the immediate communication of their work associated with preprints and also benefit from the peer-reviewed, professionally edited publication that publishers can provide.
+
 The professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals.

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Clarify tweeting data

@@
 During that time, the abstract was accessed **189** times and the PDF was accessed **107** times.
-This process engaged **3** commenters on *bioRxiv*, **61** people on Twitter, **2** people on the manuscript's GitHub repository, **1** person on a blog, and **2** via email.
+This process engaged **3** commenters on *bioRxiv*, **61** people either tweeted or re-tweeted the preprint on Twitter, **2** people on the manuscript's GitHub repository, **1** person on a blog, and **2** via email.
 Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had I foregone the posting of a preprint.

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Address feedback in pull request
Added text about PrePubMed and the ASAPBio RFA
Closes #11

@@
 For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not.
+A relatively new example of what this might look like is PrePubMed (http://www.prepubmed.org/), which seeks to index preprints from numerous sources.
+A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org).
 There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Add sentence about possible COI of Bik paper
Closes #7

@@
 A final notable case where preprints have accelerated the correction of the scientific record was a preprint posted by Bik et al.
-reporting numerous cases of image manipulation in peer reviewed studies [@Bik2016a].
-Their preprint was posted on April 20, 2016 and published in *mBio* on June 7, 2016 [@Bik2016b].
+[@Bik2016a] reporting numerous cases of image manipulation in peer reviewed studies.
+This was a case where a journal may have been reluctant to publish the findings because it could have put the journal in a bad light.
+Posting the manuscript as a preprint removed potential conflicts of interests from journals that could have hindered its ability to be published.
+After the preprint was posted on April 20, 2016 it was published in *mBio* on June 7, 2016 [@Bik2016b].
 Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the infamous "Arsenic Life" paper [@WolfeSimon2010] would have been different had they initially been posted as preprints.

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Clarified language about transfer
Clarified language regarding submission between PeerJ Preprints and
PeerJ. Closes #6
Added comment to the end of Specific challenges
Closes #5

@@
 With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*.
-It is only possible to transfer a *PeerJ Preprint* for submission to *PeerJ*.
+The only direct submission mechanism for manuscripts submitted at *PeerJ Preprint* is to the *PeerJ* journal.
 In many ways, preprint servers have taken on the feel of a journal.
@@
 Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers.
+It is possible that if preprint usage continues to expand, many of these problems may also grow as has been seen in the expansion of the publishing industry.
 

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Add paragraph on fractured preprint landscape
Broke up the Preprint Landscape section to describe the opportunity for
other interim research products including blog posts, videos, protocols,
etc. This also made for an easier connection to discuss the need for
indexing services to bridge the fracturing preprint landscape.

Closes #3
Closes #21

@@
 As adoption of this approach expands, it is likely that the features of these sites will continue to improve.
-It is also likely that interfaces from third-parties will improve.
+It is also worth noting that numerous other opportunities exist for other forms of interim research products (e.g.
+blog posts, videos, protocols, etc.) to obtain DOIs that make the work citable.
+As these possibilities increase, the landscape is likely to become fractured.
+
+One solution to the fracturing of the preprint landscape would be indexing sites that allow a user to easily search for content across the preprint landscape.
+Several examples of these efforts already exist and it likely that these interfaces and their ability to span the landscape will improve.
 For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not.
@@
 There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.
-As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted.
+As preprint servers and other content providers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted.
 It is therefore essential to balance the requirements placed on authors for features associated with preprints with the current desirable efficiency of the preprint format.

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Acknowledge those that provided feedback on the preprint

@@
 
-I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful comments on earlier versions of this manuscript.
+I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful comments on earlier versions of this manuscript and to the numerous individuals who provided feedback on the preprint version of the manuscript.
 This work was supported in part by funding to PDS from the National Institutes of Health (P30DK034933).

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Add evolving analysis Zika preprint
Not only can preprints be updated with multiple versions, but
some people are using them to slowly roll out late breaking
data collection and analyses in the hope of reducing the friction
of studying a novel area. Closes #9

@@
 In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly.
+Another interesting use of preprints to disseminate new information about Zika virus has been the posting of a preprint describing the Zika virus outbreak in the US Virgin Islands that will be continually updated as new data and analyses are performed [@Black2017].
 Over the last several years there have also been rapid advances in DNA sequencing technologies that have fundamentally changed how microbial science is performed.
@@
 I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful comments on earlier versions of this manuscript and to the numerous individuals who provided feedback on the preprint version of the manuscript.
-This work was supported in part by funding to PDS from the National Institutes of Health (P30DK034933).
+This work was supported in part by funding from the National Institutes of Health (P30DK034933).
 I appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases.

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Correct typo, Close #8

@@
 Although preprints are still relatively new, the collection of microbiology-affiliated preprints indicates widespread experimentation with the format and considerable geographic diversity.
-Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r round(100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts), 1)`%) corresponding authors who submitted a microbiology-affiliated preprint (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r round(100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts), 1)`% have posted 3 or more preprints.
+Reflecting the relative novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r round(100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts), 1)`%) corresponding authors who submitted a microbiology-affiliated preprint (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r round(100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts), 1)`% have posted 3 or more preprints.
 Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r round(micro_aff_countries_percent[1], 1)`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r round(micro_aff_countries_percent[2], 1)`%), and `r micro_aff_countries_names[3]` (`r round(micro_aff_countries_percent[3], 1)`%).

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Add text re public comments speeding peer review
Close #24
Provide a citation to the first microbiology PP
Closes #18

@@
 mSphereDirect actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016].
+As the mSphereDirect mechanism evolves and is perhaps adopted by other journals, it will be interesting to see whether public feedback will be used to futher streamline the editorial process.
 ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication).
@@
 
-***Conclusions.*** An increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method for disseminating their research prior to peer review.
+***Conclusions.*** Since the first microbiology-affiliated preprint was posted on bioRxiv in November 2013 [@Hockett2013], an increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method for disseminating their research prior to peer review.
 A number of critical concerns remain about how widespread their adoption will be, how they will be perceived by traditional journals and other scientists, and whether traditional peer-review will adapt to the new scientific trends and technologies.

### 2017-03-14 submission/Schloss_PrePrints_mBio_2017.Rmd
Add comment about preprint preventing scooping
Address testing of journal policies
Add sentence to paragraph discussing scooping and results that are too
preliminary to indicate that there is a tension that may test journals'
policies and how they will litigate whether to publish work that was
previously published as a preprint. Close #1

@@
 Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second.
+Furthermore, a preprint could prevent getting scooped since a preprint would indicate to others in the field that the work had already been done, which would prevent wasted time and effort.
 The use of preprints uncouples the communication of the discovery from the relevance of the discovery, which will come later based on peer-review, comments from other scientists at meetings or online, and eventually citations.
@@
 This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data.
+As preprints gain broader adoption, the tension between establishing primacy and the completeness of the preprint may test the policies of preprint-friendly journals.
 

### 2017-03-14 submission/Schloss_PrePrints_mBio_2017.Rmd
Editing text

@@
 
-\textbf{Format:} Perspective or Commentary
+\textbf{Format:} Perspective
 
@@
 
-The field of microbiology has experienced significant growth due to transformative advances in technology and the influx of scientists driven by a curiosity to understand how bacteria, archaea, microbial eukaryotes, and viruses interact with each other and their environment to sustain myriad biochemical processes that are essential for maintaining the Earth.
+The field of microbiology has experienced significant growth due to transformative advances in technology and the influx of scientists driven by a curiosity to understand how microbes interact with each other and their environment to sustain myriad biochemical processes that are essential for maintaining the Earth.
 With this explosion in scientific output, a significant bottleneck has been the ability to disseminate this new knowledge to peers and the public in a timely manner.
-Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck and to recruit in an effective and transparent way a broader pool of reviewers prior to submitting to traditional journals.
+Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck.
+Furthermore, posting preprints can help to transparently recruit a more diverse pool of reviewers prior to submitting to a traditional journal.
 Although use of preprints is still limited in the biological sciences, early indications are that preprints are a robust tool that can complement and enhance peer-reviewed publications.
@@
 ***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013].
-Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
+Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built-in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
 There are several important differences between the two options.
@@
 *Proceedings of the National Academy of Sciences*).
-The flexibility of the *bioRxiv* licensing empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research results however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option.
+The flexibility of the *bioRxiv* licensing empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research results; however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option.
 A cosmetic, but still relevant difference between the two is the layout and feel of the two websites.
@@
 blog posts, videos, protocols, etc.) to obtain DOIs that make the work citable.
-As these possibilities increase, the landscape is likely to become fractured.
+As these possibilities increase, the preprint landscape risks becoming fractured.
 
@@
 Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers.
-It is possible that if preprint usage continues to expand, many of these problems may also grow as has been seen in the expansion of the publishing industry.
+It is possible that if preprint usage continues to expand, many of these problems may also grow as has been experienced in the expansion of the traditional publishing industry.
 
@@
 The broad consensus of the International Committee of Medical Journal Editors and numerous journals is that preprints do not constitute prior publication [@ICMJE].
-This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, *Nature*, *Journal of Infectious Diseases*, and Cell press, which each take a generally permissive stance towards prior posting of preprints prior to submission.
+This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, *Nature*, *Journal of Infectious Diseases*, and Cell press.
+Each take a generally permissive stance towards posting of preprints prior to submission.
 Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work.
@@
 
-***Preprints and peer-review.*** The use of preprints for citations in other scientific reports and grant proposals has been called into question because preprints upend the traditional peer-review editorial process [@Drubin2016].
+***Preprints and peer-review.*** The use of preprints for citations in other scientific reports and grant proposals has recently been called into question [@Drubin2016].
 It is important to note that the peer-review process was adapted to the technologies and trends that have evolved over the past 100 years.
@@
 Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts.
-I would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
+One would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
 This would be greatly facilitated if funding agencies would include preprints as evidence for research progress, but listed separately from peer-reviewed publications to help review panels in their decisions and to help author substantiate evidence they feel they need to provide.
@@
 First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies.
-Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of January 2017 the number of Zika virus-related publications was over 1,700.
-During the recent outbreak, more than 110 Zika virus-related preprints have been posted at *bioRxiv*.
+Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of March 2017 the number of Zika virus-related publications was over 2,000.
+During the recent outbreak, more than 130 Zika virus-related preprints have been posted at *bioRxiv*.
 Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus.
@@
 Over the last several years there have also been rapid advances in DNA sequencing technologies that have fundamentally changed how microbial science is performed.
-One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 90 preprints describing new MinIon-based methods and results to preprint servers.
+One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 100 preprints describing new MinIon-based methods and results to preprint servers.
 For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.
@@
 Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`).
-For comparison, for the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`).
+For comparison, among the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`).
 Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community.
@@
 In 2014, my research group posted a preprint to *PeerJ Preprints* describing a method of sequencing 16S rRNA gene sequences using the Pacific Biosciences sequencing platform [@Schloss2015].
-At the same time, they submitted the manuscript for review at *PeerJ*.
-While the manuscript was under review, they received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry.
+At the same time, we submitted the manuscript for review at *PeerJ*.
+While the manuscript was under review, we received feedback from an academic scientist and from scientists at Pacific Biosciences that the impact of the results could be enhanced by using a recently released version of the sequencing chemistry.
 Instead of ignoring this feedback and resubmitting the manuscript to address the reviews, we generated new data and submitted an updated preprint a year later with a simultaneous submission to *PeerJ* that incorporated the original reviews as well as the feedback we received from the academic scientist and Pacific Biosciences.
@@
 Since 2015, we have continued to post manuscripts as preprints at the same time as we have submitted manuscripts.
-Although the feedback to other manuscripts has not been as helpful as our initial experience, we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b].
-As a second example, a preprint of the current manuscript was posted to *bioRxiv* on February 22, 2017.
+Although the feedback to other manuscripts has not always been as helpful as our initial experience, in each case we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b].
+As another example, I posted a preprint of the current manuscript to *bioRxiv* on February 22, 2017.
 I then solicited feedback on the manuscript using social media.
-On March **13**, 2017 I incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
-During that time, the abstract was accessed **189** times and the PDF was accessed **107** times.
-This process engaged **3** commenters on *bioRxiv*, **61** people either tweeted or re-tweeted the preprint on Twitter, **2** people on the manuscript's GitHub repository, **1** person on a blog, and **2** via email.
+On March 14, 2017 I incorporated the comments and posted a revised preprint and submitted the manuscript to *mBio*.
+During that time, the abstract was accessed 189 times and the PDF was accessed 107 times.
+This process engaged 3 commenters on *bioRxiv*, 61 people either tweeted or re-tweeted the preprint on Twitter, 2 people on the manuscript's GitHub repository, 1 person on a blog, and 2 via email.
 Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had I foregone the posting of a preprint.
-Furthermore, the preprint version of this manuscript had an Attention Score of **44**, which placed it in the top **5%** of all research scored by Altmetric.
+Furthermore, the preprint version of this manuscript had an Attention Score of 44, which placed it in the top 5% of all research scored by Altmetric.
 Although there are concerns regarding the quality of the science posted to a preprint server, I contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.
@@
 mSphereDirect actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016].
-As the mSphereDirect mechanism evolves and is perhaps adopted by other journals, it will be interesting to see whether public feedback will be used to futher streamline the editorial process.
+As the mSphereDirect mechanism evolves and is perhaps adopted by other journals, it will be interesting to see whether public feedback on preprints will be used to further streamline the editorial process.
 ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles (Stefano Bertuzzi, personal communication).
@@
 A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal.
-Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.
+Going forward, there will likely be many innovative approaches that publishers develop to benefit from incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.
 

### 2017-03-14 submission/Schloss_PrePrints_mBio_2017.tex
Editing text

@@
     \usepackage{mathspec}
-    \usepackage{xltxtra,xunicode}
   \else
@@
   \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
@@
 \usepackage[margin=1.0in]{geometry}
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
-\fi
-\hypersetup{breaklinks=true,
-            bookmarks=true,
-            pdfauthor={},
+\usepackage{hyperref}
+\hypersetup{unicode=true,
             pdftitle={Preprinting Microbiology},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=magenta,
-            pdfborder={0 0 0}}
+            pdfborder={0 0 0},
+            breaklinks=true}
 \urlstyle{same}  % don't use monospace font for urls
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
 \setlength{\parindent}{0pt}
 \setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 \setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
@@
   \predate{}\postdate{}
-
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
 
@@
 transformative advances in technology and the influx of scientists
-driven by a curiosity to understand how bacteria, archaea, microbial
-eukaryotes, and viruses interact with each other and their environment
-to sustain myriad biochemical processes that are essential for
-maintaining the Earth. With this explosion in scientific output, a
-significant bottleneck has been the ability to disseminate this new
-knowledge to peers and the public in a timely manner. Preprints have
-emerged as a tool that a growing number of microbiologists are using to
-overcome this bottleneck and to recruit in an effective and transparent
-way a broader pool of reviewers prior to submitting to traditional
-journals. Although use of preprints is still limited in the biological
-sciences, early indications are that preprints are a robust tool that
-can complement and enhance peer-reviewed publications. As publishing
-moves to embrace advances in internet technology, there are many
-opportunities for preprints and peer-reviewed journals to coexist in the
-same ecosystem.
+driven by a curiosity to understand how microbes interact with each
+other and their environment to sustain myriad biochemical processes that
+are essential for maintaining the Earth. With this explosion in
+scientific output, a significant bottleneck has been the ability to
+disseminate this new knowledge to peers and the public in a timely
+manner. Preprints have emerged as a tool that a growing number of
+microbiologists are using to overcome this bottleneck. Furthermore,
+posting preprints can help to transparently recruit a more diverse pool
+of reviewers prior to submitting to a traditional journal. Although use
+of preprints is still limited in the biological sciences, early
+indications are that preprints are a robust tool that can complement and
+enhance peer-reviewed publications. As publishing moves to embrace
+advances in internet technology, there are many opportunities for
+preprints and peer-reviewed journals to coexist in the same ecosystem.
 
@@
 Cornell University (6). For some physicists and mathematicians, posting
-a preprint to \emph{arXiv} followed by submission to a peer-reviewed
-journal has become a standard publication pathway. Although \emph{arXiv}
-has hosted a number of computational biology papers, the server has not
-drawn widespread attention from biologists. Among proponents of
-\emph{arXiv}, preprints have aided in the development of research
-communication by accelerating the release of the science and helping it
-to achieve a wider audience for critique and reception (7). Considering
-the broadening adoption of preprints among microbiologists, I sought to
-explore the specific uses of and concerns regarding preprints.
+a preprint to \emph{arXiv} optionally followed by submission to a
+peer-reviewed journal has become a standard publication pathway.
+Although \emph{arXiv} has hosted a number of computational biology
+papers, the server has not drawn widespread attention from biologists.
+Among proponents of \emph{arXiv}, preprints have aided in the
+development of research communication by accelerating the release of the
+science and helping it to achieve a wider audience for critique and
+reception (7). Considering the broadening adoption of preprints among
+microbiologists, I sought to explore the specific uses of and concerns
+regarding preprints.
 
@@
 preprint and supplemental materials; preprints are typically publicly
-available in about 24 hours; they have built in venues for authors to
+available in about 24 hours; they have built-in venues for authors to
 discuss their research with people who leave comments on the manuscript;
@@
 that best suits them, while ensuring the rapid posting of their research
-results however, it is important to provide clear information to authors
-on the legal and practical tradeoffs of each option. A cosmetic, but
-still relevant difference between the two is the layout and feel of the
-two websites. Compared to the \emph{bioRxiv} site, the \emph{PeerJ
+results; however, it is important to provide clear information to
+authors on the legal and practical tradeoffs of each option. A cosmetic,
+but still relevant difference between the two is the layout and feel of
+the two websites. Compared to the \emph{bioRxiv} site, the \emph{PeerJ
 Preprint} site is more fluid, gives readers the ability to ``follow'' a
@@
 established mechanisms to directly submit manuscripts that are posted as
-preprints on \emph{bioRxiv}. It is only possible to transfer a
-\emph{PeerJ Preprint} for submission to \emph{PeerJ}. In many ways,
-preprint servers have taken on the feel of a journal. As adoption of
-this approach expands, it is likely that the features of these sites
-will continue to improve. It is also likely that interfaces from
-third-parties will improve. For example, although Google Scholar
-includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ Preprints}
-in their search results, PubMed and Web of Science do not. There is also
-hope that the National Institutes of Health (NIH) will renew their
-interest in indexing preprints as separate research products than
-peer-reviewed publications. As preprint servers begin to look and act
-like traditional journals by incorporating features and interfaces, it
-is important to value the strength of the preprint - that of an interim
-research product, nimble and quickly posted. It is therefore essential
-to balance the requirements placed on authors for features associated
-with preprints with the current desirable efficiency of the preprint
-format.
+preprints on \emph{bioRxiv}. The only direct submission mechanism for
+manuscripts submitted at \emph{PeerJ Preprint} is to the \emph{PeerJ}
+journal. In many ways, preprint servers have taken on the feel of a
+journal. As adoption of this approach expands, it is likely that the
+features of these sites will continue to improve. It is also worth
+noting that numerous other opportunities exist for other forms of
+interim research products (e.g.~blog posts, videos, protocols, etc.) to
+obtain DOIs that make the work citable. As these possibilities increase,
+the preprint landscape risks becoming fractured.
+
+One solution to the fracturing of the preprint landscape would be
+indexing sites that allow a user to easily search for content across the
+preprint landscape. Several examples of these efforts already exist and
+it likely that these interfaces and their ability to span the landscape
+will improve. For example, although Google Scholar includes preprints
+hosted at \emph{bioRxiv} and \emph{PeerJ Preprints} in their search
+results, PubMed and Web of Science do not. A relatively new example of
+what this might look like is PrePubMed
+(\url{http://www.prepubmed.org/}), which seeks to index preprints from
+numerous sources. A more organized effort is being initiated with
+funding through ASAPbio to create a ``Central Service'' that would
+aggregate preprints in the life sciences (\url{http://asapbio.org}).
+There is also hope that the National Institutes of Health (NIH) will
+renew their interest in indexing preprints as separate research products
+than peer-reviewed publications. As preprint servers and other content
+providers begin to look and act like traditional journals by
+incorporating features and interfaces, it is important to value the
+strength of the preprint - that of an interim research product, nimble
+and quickly posted. It is therefore essential to balance the
+requirements placed on authors for features associated with preprints
+with the current desirable efficiency of the preprint format.
 
@@
 journals have policies for these issues in place that should be easy to
-implement by preprint servers.
+implement by preprint servers. It is possible that if preprint usage
+continues to expand, many of these problems may also grow as has been
+experienced in the expansion of the traditional publishing industry.
 
@@
 \emph{Science}, \emph{Nature}, \emph{Journal of Infectious Diseases},
-and Cell press, which each take a generally permissive stance towards
-prior posting of preprints prior to submission. Considering the
-relatively fluid nature of many of these policies and the journals'
-specific policies, prospective authors should be aware of the positions
-taken by the journals where they may eventually submit their work.
-Comprehensive lists of journals' attitudes towards preprints are
-available online and are regularly updated (11, 12).
+and Cell press. Each take a generally permissive stance towards posting
+of preprints prior to submission. Considering the relatively fluid
+nature of many of these policies and the journals' specific policies,
+prospective authors should be aware of the positions taken by the
+journals where they may eventually submit their work. Comprehensive
+lists of journals' attitudes towards preprints are available online and
+are regularly updated (11, 12).
 
 \textbf{\emph{Preprints and peer-review.}} The use of preprints for
-citations in other scientific reports and grant proposals has been
-called into question because preprints upend the traditional peer-review
-editorial process (13). It is important to note that the peer-review
-process was adapted to the technologies and trends that have evolved
-over the past 100 years. The formal peer-review system that most
+citations in other scientific reports and grant proposals has recently
+been called into question (13). It is important to note that the
+peer-review process was adapted to the technologies and trends that have
+evolved over the past 100 years. The formal peer-review system that most
 journals currently use was not developed until the end of the 1800s with
@@
 work with a DOI, it would, in fact, be the preprint author that scooped
-the second. The use of preprints uncouples the communication of the
-discovery from the relevance of the discovery, which will come later
-based on peer-review, comments from other scientists at meetings or
-online, and eventually citations. A growing number of scientific
-societies and journals, including ASM view preprints as citable and as
-having a legitimate claim to primacy (1, 16--18). Some scientists worry
-that with such protection a researcher can make a claim without valid
-data to support their claims (3). This is possible; however, it is also
-the responsibility of the scientific community to utilize the
-peer-review mechanisms that are available to comment on those preprints
-pointing out methodological problems or to indicate that they are
-speaking beyond the data.
+the second. Furthermore, a preprint could prevent getting scooped since
+a preprint would indicate to others in the field that the work had
+already been done, which would prevent wasted time and effort. The use
+of preprints uncouples the communication of the discovery from the
+relevance of the discovery, which will come later based on peer-review,
+comments from other scientists at meetings or online, and eventually
+citations. A growing number of scientific societies and journals,
+including ASM view preprints as citable and as having a legitimate claim
+to primacy (1, 16--18). Some scientists worry that with such protection
+a researcher can make a claim without valid data to support their claims
+(3). This is possible; however, it is also the responsibility of the
+scientific community to utilize the peer-review mechanisms that are
+available to comment on those preprints pointing out methodological
+problems or to indicate that they are speaking beyond the data. As
+preprints gain broader adoption, the tension between establishing
+primacy and the completeness of the preprint may test the policies of
+preprint-friendly journals.
 
@@
 Some fear that the use of preprints will allow scientists to circumvent
-page limits by posting preliminary manuscripts. I would hope that both
+page limits by posting preliminary manuscripts. One would hope that both
 consumers of preprints and grant proposal reviewers would be able to
@@
 virus outbreak there were approximately 50 publications that touched on
-the biology and epidemiology of the virus; as of January 2017 the number
-of Zika virus-related publications was over 1,700. During the recent
-outbreak, more than 110 Zika virus-related preprints have been posted at
+the biology and epidemiology of the virus; as of March 2017 the number
+of Zika virus-related publications was over 2,000. During the recent
+outbreak, more than 130 Zika virus-related preprints have been posted at
 \emph{bioRxiv}. Any manuscript that was published went through several
@@
 preprint were able to disseminate their methods and results instantly.
-Over the last several years there have also been rapid advances in DNA
-sequencing technologies have fundamentally changed how microbial science
-is performed. One notable technology, the MinIon sequencing platform
-from Oxford Nanopore, has received considerable attention from
-researchers who have posted more than 90 preprints describing new
-MinIon-based methods and results to preprint servers. For such a rapidly
-developing technology, the ability to share and consume methods from
-other scientists has created a feed forward effect where the technology
-has likely advanced at a faster rate than it otherwise would have.
+Another interesting use of preprints to disseminate new information
+about Zika virus has been the posting of a preprint describing the Zika
+virus outbreak in the US Virgin Islands that will be continually updated
+as new data and analyses are performed (21). Over the last several years
+there have also been rapid advances in DNA sequencing technologies that
+have fundamentally changed how microbial science is performed. One
+notable technology, the MinIon sequencing platform from Oxford Nanopore,
+has received considerable attention from researchers who have posted
+more than 100 preprints describing new MinIon-based methods and results
+to preprint servers. For such a rapidly developing technology, the
+ability to share and consume methods from other scientists has created a
+feed forward effect where the technology has likely advanced at a faster
+rate than it otherwise would have.
 
@@
 scientific literature. On February 9, 2015, \emph{Cell Systems} posted a
-study by Afshinnekoo et al. online (21). The study collected and
+study by Afshinnekoo et al. online (22). The study collected and
 analyzed metagenomic sequence data from the New York City subway system
@@
 study generated a considerable amount of media attention. On April 25,
-2015, Petit et al. (22) posted a preprint to Zenodo demonstrating that
+2015, Petit et al. (23) posted a preprint to Zenodo demonstrating that
 there was no evidence for \emph{B. anthracis} in the dataset. On July
@@
 response from the original authors offering a correction to their
-manuscript (23, 24). A second anecdote of using preprints to aid in
+manuscript (24, 25). A second anecdote of using preprints to aid in
 post-publication peer-review surrounds the publishing of a draft
 tardigrade genome in \emph{The Proceedings of the National Academy of
-Sciences}. On November 23, 2015 a study by Boothby et al. (25) was first
+Sciences}. On November 23, 2015 a study by Boothby et al. (26) was first
 published online. The authors claimed that 17.5\% of its genes came from
@@
 sequences and demonstrating that the exciting claims of horizontal gene
-transfer were really the product of contaminants (26); this analysis
+transfer were really the product of contaminants (27); this analysis
 would eventually be published online by the original journal on March
 24, 2016 followed by a rebuttal by the original authors on May 31, 2016
-(27, 28). Two other analyses of the original data were published in May
-2016 and a third was posted as a preprint on February 2, 2016 (29--31).
+(28, 29). Two other analyses of the original data were published in May
+2016 and a third was posted as a preprint on February 2, 2016 (30--32).
 These anecdotes underscore the value of having a rapid posting cycle to
@@
 correction of the scientific record was a preprint posted by Bik et al.
-reporting numerous cases of image manipulation in peer reviewed studies
-(32). Their preprint was posted on April 20, 2016 and published in
-\emph{mBio} on June 7, 2016 (33). Instead of using preprints to react to
-published papers that have been through peer review, it would be
-interesting to consider how the editorial process for these examples and
-the infamous ``Arsenic Life'' paper (34) would have been different had
-they initially been posted as preprints.
+(33) reporting numerous cases of image manipulation in peer reviewed
+studies. This was a case where a journal may have been reluctant to
+publish the findings because it could have put the journal in a bad
+light. Posting the manuscript as a preprint removed potential conflicts
+of interests from journals that could have hindered its ability to be
+published. After the preprint was posted on April 20, 2016 it was
+published in \emph{mBio} on June 7, 2016 (34). Instead of using
+preprints to react to published papers that have been through peer
+review, it would be interesting to consider how the editorial process
+for these examples and the infamous ``Arsenic Life'' paper (35) would
+have been different had they initially been posted as preprints.
 
@@
 with the format and considerable geographic diversity. Reflecting the
-still relatively novelty of preprints, 1,132 (86.1\%) corresponding
-authors who submitted a microbiology-affiliated preprint (N=1,314 total)
-have posted a single preprint and 3.6\% have posted 3 or more preprints.
+relative novelty of preprints, 1,132 (86.1\%) corresponding authors who
+submitted a microbiology-affiliated preprint (N=1,314 total) have posted
+a single preprint and 3.6\% have posted 3 or more preprints.
 Corresponding authors that have posted microbiology-affiliated preprints
@@
 mentioned in social media, traditional media, Wikipedia, policy
-documents, and other sources (35). A higher score indicates that a
+documents, and other sources (36). A higher score indicates that a
 preprint received more attention. Microbiology-affiliated preprints have
@@
 Altmetric Attention Score for preprints posted at \emph{bioRxiv} ranks
-at the 86 percentile (IQR: 66 to 94. A more traditional and
+at the 86 percentile (IQR: 66 to 94). A more traditional and
 controversial metric of impact has been the number of citations an
@@
 and could be found in the Web of Science database, the median number of
-citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, for the
+citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, among the
 papers published in \emph{mBio} in 2014 and 2015, the median number of
@@
 sequencing 16S rRNA gene sequences using the Pacific Biosciences
-sequencing platform (36). At the same time, they submitted the
-manuscript for review at \emph{PeerJ}. While the manuscript was under
-review, they received feedback from an academic scientist and from
-scientists at Pacific Biosciences that the impact of the results could
-be enhanced by using a recently released version of the sequencing
-chemistry. Instead of ignoring this feedback and resubmitting the
-manuscript to address the reviews, we generated new data and submitted
-an updated preprint a year later with a simultaneous submission to
-\emph{PeerJ} that incorporated the original reviews as well as the
-feedback we received from the academic scientist and Pacific
-Biosciences. It was eventually published by \emph{PeerJ} (37, 38). Since
-2015, we have continued to post manuscripts as preprints at the same
-time as we have submitted manuscripts. Although the feedback to other
-manuscripts has not been as helpful as our initial experience, we were
-able to sidestep lengthy review processes by immediately making our
-results available; in one case our preprint was available 7 months ahead
-of the final published version (39, 40). As a second example, this
-manuscript was posted to \emph{bioRxiv} as a preprint on
-\textbf{February 22, 2017}. I then solicited feedback on the manuscript
-using social media. Two weeks later, I incorporated the comments and
-posted a revised preprint and submitted the manuscript to \emph{mBio}.
-During that time, the abstract was read \textbf{XXXX} times and the PDF
-was accessed \textbf{XXXX} times. This process engaged \textbf{XXXX}
-commenters on \emph{bioRxiv}, \textbf{XXXX} people on Twitter,
-\textbf{XXXX} on Facebook, and \textbf{XXXX} via email. I received
-useful feedback from \textbf{XXX} people. Compared to the two or three
-scientists that typically review a manuscript, this experience engaged a
-much larger and more diverse community than had I foregone the posting
-of a preprint. Although there are concerns regarding the quality of the
-science posted to a preprint server, I contend that responsible use of
-preprints as a part of the scientific process can significantly enhance
-the science.
+sequencing platform (37). At the same time, we submitted the manuscript
+for review at \emph{PeerJ}. While the manuscript was under review, we
+received feedback from an academic scientist and from scientists at
+Pacific Biosciences that the impact of the results could be enhanced by
+using a recently released version of the sequencing chemistry. Instead
+of ignoring this feedback and resubmitting the manuscript to address the
+reviews, we generated new data and submitted an updated preprint a year
+later with a simultaneous submission to \emph{PeerJ} that incorporated
+the original reviews as well as the feedback we received from the
+academic scientist and Pacific Biosciences. It was eventually published
+by \emph{PeerJ} (38, 39). Since 2015, we have continued to post
+manuscripts as preprints at the same time as we have submitted
+manuscripts. Although the feedback to other manuscripts has not always
+been as helpful as our initial experience, in each case we were able to
+sidestep lengthy review processes by immediately making our results
+available; in one case our preprint was available 7 months ahead of the
+final published version (40, 41). As another example, I posted a
+preprint of the current manuscript to \emph{bioRxiv} on February 22,
+2017. I then solicited feedback on the manuscript using social media. On
+March 14, 2017 I incorporated the comments and posted a revised preprint
+and submitted the manuscript to \emph{mBio}. During that time, the
+abstract was accessed 189 times and the PDF was accessed 107 times. This
+process engaged 3 commenters on \emph{bioRxiv}, 61 people either tweeted
+or re-tweeted the preprint on Twitter, 2 people on the manuscript's
+GitHub repository, 1 person on a blog, and 2 via email. Compared to the
+two or three scientists that typically review a manuscript, this
+experience engaged a much larger and more diverse community than had I
+foregone the posting of a preprint. Furthermore, the preprint version of
+this manuscript had an Attention Score of 44, which placed it in the top
+5\% of all research scored by Altmetric. Although there are concerns
+regarding the quality of the science posted to a preprint server, I
+contend that responsible use of preprints as a part of the scientific
+process can significantly enhance the science.
 
@@
 from the peer-reviewed, professionally edited publication that
-publishers can provide. The professional copyediting, layout, and
-publicity that these publishers offer are also unique features of
-traditional journals. An alternative perspective is that preprints will
-eventually replace traditional journals. Certainly, this is a radical
-perspective, but it does serve to motivate publishers to capture the
-innovation opportunities offered by preprints. By adopting
-preprint-friendly policies, journals can create an attractive
-environment for authors. As discussed above, a growing number of
-journals have created mechanisms for authors to directly submit
-preprints to their journals. An example is offered by the ASM, which
-earlier this year launched a new venture from \emph{mSphere}.
-mSphereDirect is a publication track of the journal that capitalizes on
-the opportunity offered to couple preprints with rigorous peer-review.
-mSphereDirect. actively encourages authors to post their manuscripts as
-preprints as part of an author-driven editorial process where an
-editorial decision is rendered within five days and publication in
-\emph{mSphere} within a month (41). ASM is developing a new platform,
-MicroNow, which will help coalesce specific communities within the
-microbial sciences, further enhancing the use of preprints as well as
-published articles (Stefano Bertuzzi, personal communication). In
+publishers can provide.
+
+The professional copyediting, layout, and publicity that these
+publishers offer are also unique features of traditional journals. An
+alternative perspective is that preprints will eventually replace
+traditional journals. Certainly, this is a radical perspective, but it
+does serve to motivate publishers to capture the innovation
+opportunities offered by preprints. By adopting preprint-friendly
+policies, journals can create an attractive environment for authors. As
+discussed above, a growing number of journals have created mechanisms
+for authors to directly submit preprints to their journals. An example
+is offered by the ASM, which earlier this year launched a new venture
+from \emph{mSphere}. mSphereDirect is a publication track of the journal
+that capitalizes on the opportunity offered to couple preprints with
+rigorous peer-review. mSphereDirect actively encourages authors to post
+their manuscripts as preprints as part of an author-driven editorial
+process where an editorial decision is rendered within five days and
+publication in \emph{mSphere} within a month (42). As the mSphereDirect
+mechanism evolves and is perhaps adopted by other journals, it will be
+interesting to see whether public feedback on preprints will be used to
+further streamline the editorial process. ASM is developing a new
+platform, MicroNow, which will help coalesce specific communities within
+the microbial sciences, further enhancing the use of preprints as well
+as published articles (Stefano Bertuzzi, personal communication). In
 addition to integrating preprints into the traditional editorial
@@
 \emph{Genome Biology} have publicly stated that they scout preprints for
-this purpose (42, 43). Preprints can also be viewed as a lost
+this purpose (43, 44). Preprints can also be viewed as a lost
 opportunity to journals. A preprint that garners significant attention
 may be ignored when it is finally published, brining little additional
-attention to the journal. Going forward, it will be interesting to see
-the innovative approaches that publishers develop so that they can
-benefit by incorporating preprints into their process and whether
-publishers' influence is reduced by the widespread adoption of
-preprints.
+attention to the journal. Going forward, there will likely be many
+innovative approaches that publishers develop to benefit from
+incorporating preprints into their process and whether publishers'
+influence is reduced by the widespread adoption of preprints.
 
-\textbf{\emph{Conclusions.}} An increasing number of microbiologists are
-posting their unpublished work to preprint severs as an efficient method
-for disseminating their research prior to peer review. A number of
-critical concerns remain about how widespread their adoption will be,
-how they will be perceived by traditional journals and other scientists,
-and whether traditional peer-review will adapt to the new scientific
-trends and technologies. Regardless, preprints should offer a great
-opportunity for both scientists and journals to publish high quality
-science.
+\textbf{\emph{Conclusions.}} Since the first microbiology-affiliated
+preprint was posted on bioRxiv in November 2013 (45), an increasing
+number of microbiologists are posting their unpublished work to preprint
+severs as an efficient method for disseminating their research prior to
+peer review. A number of critical concerns remain about how widespread
+their adoption will be, how they will be perceived by traditional
+journals and other scientists, and whether traditional peer-review will
+adapt to the new scientific trends and technologies. Regardless,
+preprints should offer a great opportunity for both scientists and
+journals to publish high quality science.
 
@@
 I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful
-comments on earlier versions of this manuscript. This work was supported
-in part by funding to PDS from the National Institutes of Health
-(P30DK034933). I appreciate the support of Altmetric, Inc and Thompson
-Reuters who provided advanced programming interface (API) access to
-their databases. The workflow utilized commands in GNU make (v.3.81),
-GNU bash (v.4.1.2), and R (v.3.3.2). Within R I utilized the cowplot
-(v.0.6.9990), dplyr (v.0.5.0), ggplot2 (v.2.1.0.9001), httr (v.1.2.1),
-RCurl (v.1.95-4.8), rentrez (v.1.0.4), rjson (v.0.2.15), rvest
-(v.0.3.2), sportcolors (v.0.0.1), and tidyr (v.0.6.0) packages. A
-reproducible version of this manuscript and analysis is available at
+comments on earlier versions of this manuscript and to the numerous
+individuals who provided feedback on the preprint version of the
+manuscript. This work was supported in part by funding from the National
+Institutes of Health (P30DK034933). I appreciate the support of
+Altmetric, Inc and Thompson Reuters who provided advanced programming
+interface (API) access to their databases. The workflow utilized
+commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
+Within R I utilized the cowplot (v.0.6.3), dplyr (v.0.5.0), ggplot2
+(v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
+rjson (v.0.2.15), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and tidyr
+(v.0.6.0) packages. A reproducible version of this manuscript and
+analysis is available at
 \url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.
@@
 
-\hyperdef{}{references}{\label{references}}
 \subsection*{References}\label{references}
@@
 
-\hyperdef{}{ref-Vale2015}{\label{ref-Vale2015}}
+\hypertarget{refs}{}
+\hypertarget{ref-Vale2015}{}
 1. \textbf{Vale RD}. 2015. Accelerating scientific publication in
@@
 \textbf{112}:13439--13446.
-doi:\url{http://doi.org/10.1073/pnas.1511912112}.
+doi:\href{https://doi.org/10.1073/pnas.1511912112}{10.1073/pnas.1511912112}.
 
-\hyperdef{}{ref-DesjardinsProulx2013}{\label{ref-DesjardinsProulx2013}}
+\hypertarget{ref-DesjardinsProulx2013}{}
 2. \textbf{Desjardins-Proulx P}, \textbf{White EP}, \textbf{Adamson JJ},
@@
 open preprints in biology. PLoS Biology \textbf{11}:e1001563.
-doi:\url{http://doi.org/10.1371/journal.pbio.1001563}.
+doi:\href{https://doi.org/10.1371/journal.pbio.1001563}{10.1371/journal.pbio.1001563}.
 
-\hyperdef{}{ref-Berg2016}{\label{ref-Berg2016}}
+\hypertarget{ref-Berg2016}{}
 3. \textbf{Berg JM}, \textbf{Bhalla N}, \textbf{Bourne PE},
@@
 \textbf{Wolberger C}. 2016. Preprints for the life sciences. Science
-\textbf{352}:899--901. doi:\url{http://doi.org/10.1126/science.aaf9133}.
+\textbf{352}:899--901.
+doi:\href{https://doi.org/10.1126/science.aaf9133}{10.1126/science.aaf9133}.
 
-\hyperdef{}{ref-Bhalla2016}{\label{ref-Bhalla2016}}
+\hypertarget{ref-Bhalla2016}{}
 4. \textbf{Bhalla N}. 2016. Has the time come for preprints in biology?
 Molecular Biology of the Cell \textbf{27}:1185--1187.
-doi:\url{http://doi.org/10.1091/mbc.e16-02-0123}.
+doi:\href{https://doi.org/10.1091/mbc.e16-02-0123}{10.1091/mbc.e16-02-0123}.
 
-\hyperdef{}{ref-Nature1966}{\label{ref-Nature1966}}
+\hypertarget{ref-Nature1966}{}
 5. 1966. Preprints galore. Nature \textbf{211}:897--898.
-doi:\url{http://doi.org/10.1038/211897a0}.
+doi:\href{https://doi.org/10.1038/211897a0}{10.1038/211897a0}.
 
-\hyperdef{}{ref-Ginsparg2011}{\label{ref-Ginsparg2011}}
+\hypertarget{ref-Ginsparg2011}{}
 6. \textbf{Ginsparg P}. 2011. ArXiv at 20. Nature \textbf{476}:145--147.
-doi:\url{http://doi.org/10.1038/476145a}.
+doi:\href{https://doi.org/10.1038/476145a}{10.1038/476145a}.
 
-\hyperdef{}{ref-Shuai2012}{\label{ref-Shuai2012}}
+\hypertarget{ref-Shuai2012}{}
 7. \textbf{Shuai X}, \textbf{Pepe A}, \textbf{Bollen J}. 2012. How the
@@
 downloads, twitter mentions, and citations. PLoS ONE \textbf{7}:e47523.
-doi:\url{http://doi.org/10.1371/journal.pone.0047523}.
+doi:\href{https://doi.org/10.1371/journal.pone.0047523}{10.1371/journal.pone.0047523}.
 
-\hyperdef{}{ref-Callaway2013}{\label{ref-Callaway2013}}
+\hypertarget{ref-Callaway2013}{}
 8. \textbf{Callaway E}. 2013. Biomedical journal and publisher hope to
 bring preprints to life. Nature Medicine \textbf{19}:512--512.
-doi:\url{http://doi.org/10.1038/nm0513-512}.
+doi:\href{https://doi.org/10.1038/nm0513-512}{10.1038/nm0513-512}.
 
-\hyperdef{}{ref-Angell1991}{\label{ref-Angell1991}}
+\hypertarget{ref-Angell1991}{}
 9. \textbf{Angell M}, \textbf{Kassirer JP}. 1991. The ingelfinger rule
 revisited. New England Journal of Medicine \textbf{325}:1371--1373.
-doi:\url{http://doi.org/10.1056/nejm199111073251910}.
+doi:\href{https://doi.org/10.1056/nejm199111073251910}{10.1056/nejm199111073251910}.
 
-\hyperdef{}{ref-ICMJE}{\label{ref-ICMJE}}
+\hypertarget{ref-ICMJE}{}
 10. Recommendations for the conduct, reporting, editing, and publication
@@
 
-\hyperdef{}{ref-PreprintPolicy}{\label{ref-PreprintPolicy}}
+\hypertarget{ref-PreprintPolicy}{}
 11. List of academic journals by preprint policy.
@@
 
-\hyperdef{}{ref-Sherpa}{\label{ref-Sherpa}}
+\hypertarget{ref-Sherpa}{}
 12. Publisher copyright policies \& self-archiving.
@@
 
-\hyperdef{}{ref-Drubin2016}{\label{ref-Drubin2016}}
+\hypertarget{ref-Drubin2016}{}
 13. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
@@
 the Cell \textbf{27}:3181--3182.
-doi:\url{http://doi.org/10.1091/mbc.e16-09-0651}.
+doi:\href{https://doi.org/10.1091/mbc.e16-09-0651}{10.1091/mbc.e16-09-0651}.
 
-\hyperdef{}{ref-Spier2002}{\label{ref-Spier2002}}
+\hypertarget{ref-Spier2002}{}
 14. \textbf{Spier R}. 2002. The history of the peer-review process.
 Trends in Biotechnology \textbf{20}:357--358.
-doi:\url{http://doi.org/10.1016/s0167-7799(02)01985-6}.
+doi:\href{https://doi.org/10.1016/s0167-7799(02)01985-6}{10.1016/s0167-7799(02)01985-6}.
 
-\hyperdef{}{ref-Burnham1990}{\label{ref-Burnham1990}}
+\hypertarget{ref-Burnham1990}{}
 15. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
 JAMA: The Journal of the American Medical Association \textbf{263}:1323.
-doi:\url{http://doi.org/10.1001/jama.1990.03440100023003}.
+doi:\href{https://doi.org/10.1001/jama.1990.03440100023003}{10.1001/jama.1990.03440100023003}.
 
-\hyperdef{}{ref-Pulverer2016}{\label{ref-Pulverer2016}}
+\hypertarget{ref-Pulverer2016}{}
 16. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
 \textbf{35}:2617--2619.
-doi:\url{http://doi.org/10.15252/embj.201670030}.
+doi:\href{https://doi.org/10.15252/embj.201670030}{10.15252/embj.201670030}.
 
-\hyperdef{}{ref-Loew2016}{\label{ref-Loew2016}}
+\hypertarget{ref-Loew2016}{}
 17. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
 \textbf{111}:E01--E02.
-doi:\url{http://doi.org/10.1016/j.bpj.2016.06.035}.
+doi:\href{https://doi.org/10.1016/j.bpj.2016.06.035}{10.1016/j.bpj.2016.06.035}.
 
-\hyperdef{}{ref-Vale2016}{\label{ref-Vale2016}}
+\hypertarget{ref-Vale2016}{}
 18. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
 the life sciences. eLife \textbf{5}.
-doi:\url{http://doi.org/10.7554/elife.16931}.
+doi:\href{https://doi.org/10.7554/elife.16931}{10.7554/elife.16931}.
 
-\hyperdef{}{ref-Dolgin2016}{\label{ref-Dolgin2016}}
+\hypertarget{ref-Dolgin2016}{}
 19. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
-Nature. doi:\url{http://doi.org/10.1038/nature.2016.21074}.
+Nature.
+doi:\href{https://doi.org/10.1038/nature.2016.21074}{10.1038/nature.2016.21074}.
 
-\hyperdef{}{ref-SinghChawla2017}{\label{ref-SinghChawla2017}}
+\hypertarget{ref-SinghChawla2017}{}
 20. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
-Nature. doi:\url{http://doi.org/10.1038/nature.2017.21333}.
+Nature.
+doi:\href{https://doi.org/10.1038/nature.2017.21333}{10.1038/nature.2017.21333}.
 
-\hyperdef{}{ref-Afshinnekoo2015a}{\label{ref-Afshinnekoo2015a}}
-21. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
+\hypertarget{ref-Black2017}{}
+21. \textbf{Black A}, \textbf{Potter B}, \textbf{Dudas G},
+\textbf{Feldstein L}, \textbf{Grubaugh ND}, \textbf{Andersen KG},
+\textbf{Ellis BR}, \textbf{Ellis EM}, \textbf{Bedford T}. 2017. Genetic
+characterization of the zika virus epidemic in the us virgin islands.
+bioRxiv 113100.
+
+\hypertarget{ref-Afshinnekoo2015a}{}
+22. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
 \textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
@@
 and bacterial diversity with city-scale metagenomics. Cell Systems
-\textbf{1}:72--87. doi:\url{http://doi.org/10.1016/j.cels.2015.01.001}.
+\textbf{1}:72--87.
+doi:\href{https://doi.org/10.1016/j.cels.2015.01.001}{10.1016/j.cels.2015.01.001}.
 
-\hyperdef{}{ref-Petit2015}{\label{ref-Petit2015}}
-22. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
+\hypertarget{ref-Petit2015}{}
+23. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
 \textbf{Read TD}. 2015. Searching for anthrax in the New York City
-subway metagenome. doi:\url{http://doi.org/10.5281/zenodo.17158}.
+subway metagenome.
+doi:\href{https://doi.org/10.5281/zenodo.17158}{10.5281/zenodo.17158}.
 
-\hyperdef{}{ref-Ackelsberg2015}{\label{ref-Ackelsberg2015}}
-23. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
+\hypertarget{ref-Ackelsberg2015}{}
+24. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
 \textbf{Petersen J}, \textbf{Mead P}, \textbf{Schriefer M},
@@
 evidence for plague or anthrax on the new york city subway. Cell Systems
-\textbf{1}:4--5. doi:\url{http://doi.org/10.1016/j.cels.2015.07.008}.
+\textbf{1}:4--5.
+doi:\href{https://doi.org/10.1016/j.cels.2015.07.008}{10.1016/j.cels.2015.07.008}.
 
-\hyperdef{}{ref-Afshinnekoo2015b}{\label{ref-Afshinnekoo2015b}}
-24. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
+\hypertarget{ref-Afshinnekoo2015b}{}
+25. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
 \textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
@@
 metagenomic complexity. Cell Systems \textbf{1}:6--7.
-doi:\url{http://doi.org/10.1016/j.cels.2015.07.007}.
+doi:\href{https://doi.org/10.1016/j.cels.2015.07.007}{10.1016/j.cels.2015.07.007}.
 
-\hyperdef{}{ref-Boothby2015}{\label{ref-Boothby2015}}
-25. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
+\hypertarget{ref-Boothby2015}{}
+26. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
 \textbf{Wang JR}, \textbf{Patanella KA}, \textbf{Nishimura EO},
@@
 \textbf{112}:15976--15981.
-doi:\url{http://doi.org/10.1073/pnas.1510461112}.
+doi:\href{https://doi.org/10.1073/pnas.1510461112}{10.1073/pnas.1510461112}.
 
-\hyperdef{}{ref-Koutsovoulos2016a}{\label{ref-Koutsovoulos2016a}}
-26. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
+\hypertarget{ref-Koutsovoulos2016a}{}
+27. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
 \textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
@@
 tardigrade hypsibius dujardini. bioRxiv 033464.
-doi:\url{http://doi.org/10.1101/033464}.
+doi:\href{https://doi.org/10.1101/033464}{10.1101/033464}.
 
-\hyperdef{}{ref-Boothby2016}{\label{ref-Boothby2016}}
-27. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
+\hypertarget{ref-Boothby2016}{}
+28. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
 al. and arakawa: Identifying foreign genes in independentHypsibius
@@
 Sciences \textbf{113}:E3058--E3061.
-doi:\url{http://doi.org/10.1073/pnas.1601149113}.
+doi:\href{https://doi.org/10.1073/pnas.1601149113}{10.1073/pnas.1601149113}.
 
-\hyperdef{}{ref-Koutsovoulos2016b}{\label{ref-Koutsovoulos2016b}}
-28. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
+\hypertarget{ref-Koutsovoulos2016b}{}
+29. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
 \textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
@@
 Sciences \textbf{113}:5053--5058.
-doi:\url{http://doi.org/10.1073/pnas.1600338113}.
+doi:\href{https://doi.org/10.1073/pnas.1600338113}{10.1073/pnas.1600338113}.
 
-\hyperdef{}{ref-Bemm2016}{\label{ref-Bemm2016}}
-29. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
+\hypertarget{ref-Bemm2016}{}
+30. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
 \textbf{Förster F}. 2016. Genome of a tardigrade: Horizontal gene
@@
 of Sciences \textbf{113}:E3054--E3056.
-doi:\url{http://doi.org/10.1073/pnas.1525116113}.
+doi:\href{https://doi.org/10.1073/pnas.1525116113}{10.1073/pnas.1525116113}.
 
-\hyperdef{}{ref-Arakawa2016}{\label{ref-Arakawa2016}}
-30. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
+\hypertarget{ref-Arakawa2016}{}
+31. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
 transfer from the draft genome of a tardigrade. Proceedings of the
 National Academy of Sciences \textbf{113}:E3057--E3057.
-doi:\url{http://doi.org/10.1073/pnas.1602711113}.
+doi:\href{https://doi.org/10.1073/pnas.1602711113}{10.1073/pnas.1602711113}.
 
-\hyperdef{}{ref-Delmont2016}{\label{ref-Delmont2016}}
-31. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
+\hypertarget{ref-Delmont2016}{}
+32. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
 contamination with advanced visualization and analysis practices:
 Metagenomic approaches for eukaryotic genome assemblies.
-doi:\url{http://doi.org/10.7287/peerj.preprints.1695v1}.
+doi:\href{https://doi.org/10.7287/peerj.preprints.1695v1}{10.7287/peerj.preprints.1695v1}.
 
-\hyperdef{}{ref-Bik2016a}{\label{ref-Bik2016a}}
-32. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
-prevalence of inappropriate image duplication in biomedical research
-publications. bioRxiv 049452. doi:\url{http://doi.org/10.1101/049452}.
-
-\hyperdef{}{ref-Bik2016b}{\label{ref-Bik2016b}}
+\hypertarget{ref-Bik2016a}{}
 33. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
 prevalence of inappropriate image duplication in biomedical research
+publications. bioRxiv 049452.
+doi:\href{https://doi.org/10.1101/049452}{10.1101/049452}.
+
+\hypertarget{ref-Bik2016b}{}
+34. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
+prevalence of inappropriate image duplication in biomedical research
 publications. mBio \textbf{7}:e00809--16.
-doi:\url{http://doi.org/10.1128/mbio.00809-16}.
+doi:\href{https://doi.org/10.1128/mbio.00809-16}{10.1128/mbio.00809-16}.
 
-\hyperdef{}{ref-WolfeSimon2010}{\label{ref-WolfeSimon2010}}
-34. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
+\hypertarget{ref-WolfeSimon2010}{}
+35. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
 \textbf{Gordon GW}, \textbf{Hoeft SE}, \textbf{Pett-Ridge J},
@@
 \textbf{332}:1163--1166.
-doi:\url{http://doi.org/10.1126/science.1197258}.
+doi:\href{https://doi.org/10.1126/science.1197258}{10.1126/science.1197258}.
 
-\hyperdef{}{ref-Altmetric}{\label{ref-Altmetric}}
-35. How is the Altmetric Attention Score calculated?
+\hypertarget{ref-Altmetric}{}
+36. How is the Altmetric Attention Score calculated?
 \url{https://help.altmetric.com/support/solutions/articles/6000060969-how-is-the-altmetric-attention-score-calculated-}.
 
-\hyperdef{}{ref-Schloss2015}{\label{ref-Schloss2015}}
-36. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
+\hypertarget{ref-Schloss2015}{}
+37. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
 \textbf{Highlander SK}. 2015. Sequencing 16S rRNA gene fragments using
 the PacBio SMRT DNA sequencing system.
-doi:\url{http://doi.org/10.7287/peerj.preprints.778v1}.
+doi:\href{https://doi.org/10.7287/peerj.preprints.778v1}{10.7287/peerj.preprints.778v1}.
 
-\hyperdef{}{ref-Schloss2016a}{\label{ref-Schloss2016a}}
-37. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
+\hypertarget{ref-Schloss2016a}{}
+38. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
 \textbf{Westcott SL}, \textbf{Highlander SK}. 2016. Sequencing 16S rRNA
 gene fragments using the PacBio SMRT DNA sequencing system.
-doi:\url{http://doi.org/10.7287/peerj.preprints.778v2}.
+doi:\href{https://doi.org/10.7287/peerj.preprints.778v2}{10.7287/peerj.preprints.778v2}.
 
-\hyperdef{}{ref-Schloss2016b}{\label{ref-Schloss2016b}}
-38. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
+\hypertarget{ref-Schloss2016b}{}
+39. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
 \textbf{Westcott SL}, \textbf{Highlander SK}. 2016. Sequencing 16S rRNA
 gene fragments using the PacBio SMRT DNA sequencing system. PeerJ
-\textbf{4}:e1869. doi:\url{http://doi.org/10.7717/peerj.1869}.
+\textbf{4}:e1869.
+doi:\href{https://doi.org/10.7717/peerj.1869}{10.7717/peerj.1869}.
 
-\hyperdef{}{ref-Baxter2016a}{\label{ref-Baxter2016a}}
-39. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
+\hypertarget{ref-Baxter2016a}{}
+40. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
 \textbf{Ruffin MT}, \textbf{Schloss P}. 2016. DNA from fecal
@@
 cancer screening. bioRxiv 048389.
-doi:\url{http://doi.org/10.1101/048389}.
+doi:\href{https://doi.org/10.1101/048389}{10.1101/048389}.
 
-\hyperdef{}{ref-Baxter2016b}{\label{ref-Baxter2016b}}
-40. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
+\hypertarget{ref-Baxter2016b}{}
+41. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
 \textbf{Ruffin MT}, \textbf{Schloss PD}. 2016. DNA from fecal
@@
 using a microbiota-based model. Microbiome \textbf{4}.
-doi:\url{http://doi.org/10.1186/s40168-016-0205-y}.
+doi:\href{https://doi.org/10.1186/s40168-016-0205-y}{10.1186/s40168-016-0205-y}.
 
-\hyperdef{}{ref-Imperiale2016}{\label{ref-Imperiale2016}}
-41. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
+\hypertarget{ref-Imperiale2016}{}
+42. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
 mSphereDirect: Author-initiated peer review of manuscripts. mSphere
 \textbf{1}:e00307--16.
-doi:\url{http://doi.org/10.1128/msphere.00307-16}.
+doi:\href{https://doi.org/10.1128/msphere.00307-16}{10.1128/msphere.00307-16}.
 
-\hyperdef{}{ref-Vence2017}{\label{ref-Vence2017}}
-42. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.
+\hypertarget{ref-Vence2017}{}
+43. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.
 
-\hyperdef{}{ref-Barsh2016}{\label{ref-Barsh2016}}
-43. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
+\hypertarget{ref-Barsh2016}{}
+44. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
 \textbf{Singh ND}, \textbf{Copenhaver GP}. 2016. Bringing PLOS genetics
 editors to preprint servers. PLOS Genetics \textbf{12}:e1006448.
-doi:\url{http://doi.org/10.1371/journal.pgen.1006448}.
+doi:\href{https://doi.org/10.1371/journal.pgen.1006448}{10.1371/journal.pgen.1006448}.
+
+\hypertarget{ref-Hockett2013}{}
+45. \textbf{Hockett KL}, \textbf{Nishimura MT}, \textbf{Karlsrud E},
+\textbf{Dougherty K}, \textbf{Baltrus DA}. 2013. Interactions between
+genome architecture and virulence genes in pseudomonas syringae, strain
+cc1557 as a model. bioRxiv 000869.
 

### 2017-03-14 submission/Schloss_PrePrints_mBio_2017.tex
Render prior to submission

@@
   \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
 \fi
@@
 \usepackage[margin=1.0in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
             pdftitle={Preprinting Microbiology},
-            pdfborder={0 0 0},
-            breaklinks=true}
+            colorlinks=true,
+            citecolor=blue,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
 \urlstyle{same}  % don't use monospace font for urls
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
 \setlength{\parindent}{0pt}
 \setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 \setcounter{secnumdepth}{0}
+
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+%%% Change title format to be more compact
+\usepackage{titling}
+
+% Create subtitle command for use in maketitle
+\newcommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
+
+\setlength{\droptitle}{-2em}
+  \title{\textbf{Preprinting Microbiology}}
+  \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
+  \author{}
+  \preauthor{}\postauthor{}
+  \date{}
+  \predate{}\postdate{}
+
 % Redefines (sub)paragraphs to behave more like sections
@@
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-  \title{\textbf{Preprinting Microbiology}}
-  \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-  \author{}
-  \preauthor{}\postauthor{}
-  \date{}
-  \predate{}\postdate{}
-
 \usepackage{helvet} % Helvetica font
@@
 
-\textbf{Number of words:} \textasciitilde4500 plus references, figures, and abstract
+\textbf{Number of words:} \textasciitilde5400 plus references, figures, and abstract
 
@@
 commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
-Within R I utilized the cowplot (v.0.6.3), dplyr (v.0.5.0), ggplot2
-(v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
-rjson (v.0.2.15), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and tidyr
+Within R I utilized the cowplot (v.0.6.9990), dplyr (v.0.5.0), ggplot2
+(v.2.1.0.9001), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
+rjson (v.0.2.15), rvest (v.0.3.2), sportcolors (v.0.0.1), and tidyr
 (v.0.6.0) packages. A reproducible version of this manuscript and
@@
 \newpage
-
-\includegraphics[width=3.5in]{../figures/figure1.png}
 
@@
 \textbf{112}:13439--13446.
-doi:\href{https://doi.org/10.1073/pnas.1511912112}{10.1073/pnas.1511912112}.
-
-\hypertarget{ref-DesjardinsProulx2013}{}
+doi:\url{http://doi.org/10.1073/pnas.1511912112}.
+
+\hyperdef{}{ref-DesjardinsProulx2013}{\label{ref-DesjardinsProulx2013}}
 2. \textbf{Desjardins-Proulx P}, \textbf{White EP}, \textbf{Adamson JJ},
@@
 open preprints in biology. PLoS Biology \textbf{11}:e1001563.
-doi:\href{https://doi.org/10.1371/journal.pbio.1001563}{10.1371/journal.pbio.1001563}.
-
-\hypertarget{ref-Berg2016}{}
+doi:\url{http://doi.org/10.1371/journal.pbio.1001563}.
+
+\hyperdef{}{ref-Berg2016}{\label{ref-Berg2016}}
 3. \textbf{Berg JM}, \textbf{Bhalla N}, \textbf{Bourne PE},
@@
 \textbf{Wolberger C}. 2016. Preprints for the life sciences. Science
-\textbf{352}:899--901.
-doi:\href{https://doi.org/10.1126/science.aaf9133}{10.1126/science.aaf9133}.
-
-\hypertarget{ref-Bhalla2016}{}
+\textbf{352}:899--901. doi:\url{http://doi.org/10.1126/science.aaf9133}.
+
+\hyperdef{}{ref-Bhalla2016}{\label{ref-Bhalla2016}}
 4. \textbf{Bhalla N}. 2016. Has the time come for preprints in biology?
 Molecular Biology of the Cell \textbf{27}:1185--1187.
-doi:\href{https://doi.org/10.1091/mbc.e16-02-0123}{10.1091/mbc.e16-02-0123}.
-
-\hypertarget{ref-Nature1966}{}
+doi:\url{http://doi.org/10.1091/mbc.e16-02-0123}.
+
+\hyperdef{}{ref-Nature1966}{\label{ref-Nature1966}}
 5. 1966. Preprints galore. Nature \textbf{211}:897--898.
-doi:\href{https://doi.org/10.1038/211897a0}{10.1038/211897a0}.
-
-\hypertarget{ref-Ginsparg2011}{}
+doi:\url{http://doi.org/10.1038/211897a0}.
+
+\hyperdef{}{ref-Ginsparg2011}{\label{ref-Ginsparg2011}}
 6. \textbf{Ginsparg P}. 2011. ArXiv at 20. Nature \textbf{476}:145--147.
-doi:\href{https://doi.org/10.1038/476145a}{10.1038/476145a}.
-
-\hypertarget{ref-Shuai2012}{}
+doi:\url{http://doi.org/10.1038/476145a}.
+
+\hyperdef{}{ref-Shuai2012}{\label{ref-Shuai2012}}
 7. \textbf{Shuai X}, \textbf{Pepe A}, \textbf{Bollen J}. 2012. How the
@@
 downloads, twitter mentions, and citations. PLoS ONE \textbf{7}:e47523.
-doi:\href{https://doi.org/10.1371/journal.pone.0047523}{10.1371/journal.pone.0047523}.
-
-\hypertarget{ref-Callaway2013}{}
+doi:\url{http://doi.org/10.1371/journal.pone.0047523}.
+
+\hyperdef{}{ref-Callaway2013}{\label{ref-Callaway2013}}
 8. \textbf{Callaway E}. 2013. Biomedical journal and publisher hope to
 bring preprints to life. Nature Medicine \textbf{19}:512--512.
-doi:\href{https://doi.org/10.1038/nm0513-512}{10.1038/nm0513-512}.
-
-\hypertarget{ref-Angell1991}{}
+doi:\url{http://doi.org/10.1038/nm0513-512}.
+
+\hyperdef{}{ref-Angell1991}{\label{ref-Angell1991}}
 9. \textbf{Angell M}, \textbf{Kassirer JP}. 1991. The ingelfinger rule
 revisited. New England Journal of Medicine \textbf{325}:1371--1373.
-doi:\href{https://doi.org/10.1056/nejm199111073251910}{10.1056/nejm199111073251910}.
-
-\hypertarget{ref-ICMJE}{}
+doi:\url{http://doi.org/10.1056/nejm199111073251910}.
+
+\hyperdef{}{ref-ICMJE}{\label{ref-ICMJE}}
 10. Recommendations for the conduct, reporting, editing, and publication
@@
 
-\hypertarget{ref-PreprintPolicy}{}
+\hyperdef{}{ref-PreprintPolicy}{\label{ref-PreprintPolicy}}
 11. List of academic journals by preprint policy.
@@
 
-\hypertarget{ref-Sherpa}{}
+\hyperdef{}{ref-Sherpa}{\label{ref-Sherpa}}
 12. Publisher copyright policies \& self-archiving.
@@
 
-\hypertarget{ref-Drubin2016}{}
+\hyperdef{}{ref-Drubin2016}{\label{ref-Drubin2016}}
 13. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
@@
 the Cell \textbf{27}:3181--3182.
-doi:\href{https://doi.org/10.1091/mbc.e16-09-0651}{10.1091/mbc.e16-09-0651}.
-
-\hypertarget{ref-Spier2002}{}
+doi:\url{http://doi.org/10.1091/mbc.e16-09-0651}.
+
+\hyperdef{}{ref-Spier2002}{\label{ref-Spier2002}}
 14. \textbf{Spier R}. 2002. The history of the peer-review process.
 Trends in Biotechnology \textbf{20}:357--358.
-doi:\href{https://doi.org/10.1016/s0167-7799(02)01985-6}{10.1016/s0167-7799(02)01985-6}.
-
-\hypertarget{ref-Burnham1990}{}
+doi:\url{http://doi.org/10.1016/s0167-7799(02)01985-6}.
+
+\hyperdef{}{ref-Burnham1990}{\label{ref-Burnham1990}}
 15. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
 JAMA: The Journal of the American Medical Association \textbf{263}:1323.
-doi:\href{https://doi.org/10.1001/jama.1990.03440100023003}{10.1001/jama.1990.03440100023003}.
-
-\hypertarget{ref-Pulverer2016}{}
+doi:\url{http://doi.org/10.1001/jama.1990.03440100023003}.
+
+\hyperdef{}{ref-Pulverer2016}{\label{ref-Pulverer2016}}
 16. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
 \textbf{35}:2617--2619.
-doi:\href{https://doi.org/10.15252/embj.201670030}{10.15252/embj.201670030}.
-
-\hypertarget{ref-Loew2016}{}
+doi:\url{http://doi.org/10.15252/embj.201670030}.
+
+\hyperdef{}{ref-Loew2016}{\label{ref-Loew2016}}
 17. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
 \textbf{111}:E01--E02.
-doi:\href{https://doi.org/10.1016/j.bpj.2016.06.035}{10.1016/j.bpj.2016.06.035}.
-
-\hypertarget{ref-Vale2016}{}
+doi:\url{http://doi.org/10.1016/j.bpj.2016.06.035}.
+
+\hyperdef{}{ref-Vale2016}{\label{ref-Vale2016}}
 18. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
 the life sciences. eLife \textbf{5}.
-doi:\href{https://doi.org/10.7554/elife.16931}{10.7554/elife.16931}.
-
-\hypertarget{ref-Dolgin2016}{}
+doi:\url{http://doi.org/10.7554/elife.16931}.
+
+\hyperdef{}{ref-Dolgin2016}{\label{ref-Dolgin2016}}
 19. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
-Nature.
-doi:\href{https://doi.org/10.1038/nature.2016.21074}{10.1038/nature.2016.21074}.
-
-\hypertarget{ref-SinghChawla2017}{}
+Nature. doi:\url{http://doi.org/10.1038/nature.2016.21074}.
+
+\hyperdef{}{ref-SinghChawla2017}{\label{ref-SinghChawla2017}}
 20. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
-Nature.
-doi:\href{https://doi.org/10.1038/nature.2017.21333}{10.1038/nature.2017.21333}.
-
-\hypertarget{ref-Black2017}{}
+Nature. doi:\url{http://doi.org/10.1038/nature.2017.21333}.
+
+\hyperdef{}{ref-Black2017}{\label{ref-Black2017}}
 21. \textbf{Black A}, \textbf{Potter B}, \textbf{Dudas G},
@@
 \textbf{Ellis BR}, \textbf{Ellis EM}, \textbf{Bedford T}. 2017. Genetic
-characterization of the zika virus epidemic in the us virgin islands.
+characterization of the zika virus epidemic in the uS virgin islands.
 bioRxiv 113100.
 
-\hypertarget{ref-Afshinnekoo2015a}{}
+\hyperdef{}{ref-Afshinnekoo2015a}{\label{ref-Afshinnekoo2015a}}
 22. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
@@
 and bacterial diversity with city-scale metagenomics. Cell Systems
-\textbf{1}:72--87.
-doi:\href{https://doi.org/10.1016/j.cels.2015.01.001}{10.1016/j.cels.2015.01.001}.
-
-\hypertarget{ref-Petit2015}{}
+\textbf{1}:72--87. doi:\url{http://doi.org/10.1016/j.cels.2015.01.001}.
+
+\hyperdef{}{ref-Petit2015}{\label{ref-Petit2015}}
 23. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
 \textbf{Read TD}. 2015. Searching for anthrax in the New York City
-subway metagenome.
-doi:\href{https://doi.org/10.5281/zenodo.17158}{10.5281/zenodo.17158}.
-
-\hypertarget{ref-Ackelsberg2015}{}
+subway metagenome. doi:\url{http://doi.org/10.5281/zenodo.17158}.
+
+\hyperdef{}{ref-Ackelsberg2015}{\label{ref-Ackelsberg2015}}
 24. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
@@
 evidence for plague or anthrax on the new york city subway. Cell Systems
-\textbf{1}:4--5.
-doi:\href{https://doi.org/10.1016/j.cels.2015.07.008}{10.1016/j.cels.2015.07.008}.
-
-\hypertarget{ref-Afshinnekoo2015b}{}
+\textbf{1}:4--5. doi:\url{http://doi.org/10.1016/j.cels.2015.07.008}.
+
+\hyperdef{}{ref-Afshinnekoo2015b}{\label{ref-Afshinnekoo2015b}}
 25. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
@@
 metagenomic complexity. Cell Systems \textbf{1}:6--7.
-doi:\href{https://doi.org/10.1016/j.cels.2015.07.007}{10.1016/j.cels.2015.07.007}.
-
-\hypertarget{ref-Boothby2015}{}
+doi:\url{http://doi.org/10.1016/j.cels.2015.07.007}.
+
+\hyperdef{}{ref-Boothby2015}{\label{ref-Boothby2015}}
 26. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
@@
 \textbf{112}:15976--15981.
-doi:\href{https://doi.org/10.1073/pnas.1510461112}{10.1073/pnas.1510461112}.
-
-\hypertarget{ref-Koutsovoulos2016a}{}
+doi:\url{http://doi.org/10.1073/pnas.1510461112}.
+
+\hyperdef{}{ref-Koutsovoulos2016a}{\label{ref-Koutsovoulos2016a}}
 27. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
@@
 tardigrade hypsibius dujardini. bioRxiv 033464.
-doi:\href{https://doi.org/10.1101/033464}{10.1101/033464}.
-
-\hypertarget{ref-Boothby2016}{}
+doi:\url{http://doi.org/10.1101/033464}.
+
+\hyperdef{}{ref-Boothby2016}{\label{ref-Boothby2016}}
 28. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
@@
 Sciences \textbf{113}:E3058--E3061.
-doi:\href{https://doi.org/10.1073/pnas.1601149113}{10.1073/pnas.1601149113}.
-
-\hypertarget{ref-Koutsovoulos2016b}{}
+doi:\url{http://doi.org/10.1073/pnas.1601149113}.
+
+\hyperdef{}{ref-Koutsovoulos2016b}{\label{ref-Koutsovoulos2016b}}
 29. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
@@
 Sciences \textbf{113}:5053--5058.
-doi:\href{https://doi.org/10.1073/pnas.1600338113}{10.1073/pnas.1600338113}.
-
-\hypertarget{ref-Bemm2016}{}
+doi:\url{http://doi.org/10.1073/pnas.1600338113}.
+
+\hyperdef{}{ref-Bemm2016}{\label{ref-Bemm2016}}
 30. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
@@
 of Sciences \textbf{113}:E3054--E3056.
-doi:\href{https://doi.org/10.1073/pnas.1525116113}{10.1073/pnas.1525116113}.
-
-\hypertarget{ref-Arakawa2016}{}
+doi:\url{http://doi.org/10.1073/pnas.1525116113}.
+
+\hyperdef{}{ref-Arakawa2016}{\label{ref-Arakawa2016}}
 31. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
@@
 National Academy of Sciences \textbf{113}:E3057--E3057.
-doi:\href{https://doi.org/10.1073/pnas.1602711113}{10.1073/pnas.1602711113}.
-
-\hypertarget{ref-Delmont2016}{}
+doi:\url{http://doi.org/10.1073/pnas.1602711113}.
+
+\hyperdef{}{ref-Delmont2016}{\label{ref-Delmont2016}}
 32. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
@@
 Metagenomic approaches for eukaryotic genome assemblies.
-doi:\href{https://doi.org/10.7287/peerj.preprints.1695v1}{10.7287/peerj.preprints.1695v1}.
-
-\hypertarget{ref-Bik2016a}{}
+doi:\url{http://doi.org/10.7287/peerj.preprints.1695v1}.
+
+\hyperdef{}{ref-Bik2016a}{\label{ref-Bik2016a}}
 33. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
 prevalence of inappropriate image duplication in biomedical research
-publications. bioRxiv 049452.
-doi:\href{https://doi.org/10.1101/049452}{10.1101/049452}.
-
-\hypertarget{ref-Bik2016b}{}
+publications. bioRxiv 049452. doi:\url{http://doi.org/10.1101/049452}.
+
+\hyperdef{}{ref-Bik2016b}{\label{ref-Bik2016b}}
 34. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
@@
 publications. mBio \textbf{7}:e00809--16.
-doi:\href{https://doi.org/10.1128/mbio.00809-16}{10.1128/mbio.00809-16}.
-
-\hypertarget{ref-WolfeSimon2010}{}
+doi:\url{http://doi.org/10.1128/mbio.00809-16}.
+
+\hyperdef{}{ref-WolfeSimon2010}{\label{ref-WolfeSimon2010}}
 35. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
@@
 \textbf{332}:1163--1166.
-doi:\href{https://doi.org/10.1126/science.1197258}{10.1126/science.1197258}.
-
-\hypertarget{ref-Altmetric}{}
+doi:\url{http://doi.org/10.1126/science.1197258}.
+
+\hyperdef{}{ref-Altmetric}{\label{ref-Altmetric}}
 36. How is the Altmetric Attention Score calculated?
@@
 
-\hypertarget{ref-Schloss2015}{}
+\hyperdef{}{ref-Schloss2015}{\label{ref-Schloss2015}}
 37. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
@@
 the PacBio SMRT DNA sequencing system.
-doi:\href{https://doi.org/10.7287/peerj.preprints.778v1}{10.7287/peerj.preprints.778v1}.
-
-\hypertarget{ref-Schloss2016a}{}
+doi:\url{http://doi.org/10.7287/peerj.preprints.778v1}.
+
+\hyperdef{}{ref-Schloss2016a}{\label{ref-Schloss2016a}}
 38. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
@@
 gene fragments using the PacBio SMRT DNA sequencing system.
-doi:\href{https://doi.org/10.7287/peerj.preprints.778v2}{10.7287/peerj.preprints.778v2}.
-
-\hypertarget{ref-Schloss2016b}{}
+doi:\url{http://doi.org/10.7287/peerj.preprints.778v2}.
+
+\hyperdef{}{ref-Schloss2016b}{\label{ref-Schloss2016b}}
 39. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
@@
 gene fragments using the PacBio SMRT DNA sequencing system. PeerJ
-\textbf{4}:e1869.
-doi:\href{https://doi.org/10.7717/peerj.1869}{10.7717/peerj.1869}.
-
-\hypertarget{ref-Baxter2016a}{}
+\textbf{4}:e1869. doi:\url{http://doi.org/10.7717/peerj.1869}.
+
+\hyperdef{}{ref-Baxter2016a}{\label{ref-Baxter2016a}}
 40. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
@@
 cancer screening. bioRxiv 048389.
-doi:\href{https://doi.org/10.1101/048389}{10.1101/048389}.
-
-\hypertarget{ref-Baxter2016b}{}
+doi:\url{http://doi.org/10.1101/048389}.
+
+\hyperdef{}{ref-Baxter2016b}{\label{ref-Baxter2016b}}
 41. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
@@
 using a microbiota-based model. Microbiome \textbf{4}.
-doi:\href{https://doi.org/10.1186/s40168-016-0205-y}{10.1186/s40168-016-0205-y}.
-
-\hypertarget{ref-Imperiale2016}{}
+doi:\url{http://doi.org/10.1186/s40168-016-0205-y}.
+
+\hyperdef{}{ref-Imperiale2016}{\label{ref-Imperiale2016}}
 42. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
@@
 \textbf{1}:e00307--16.
-doi:\href{https://doi.org/10.1128/msphere.00307-16}{10.1128/msphere.00307-16}.
-
-\hypertarget{ref-Vence2017}{}
+doi:\url{http://doi.org/10.1128/msphere.00307-16}.
+
+\hyperdef{}{ref-Vence2017}{\label{ref-Vence2017}}
 43. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.
 
-\hypertarget{ref-Barsh2016}{}
+\hyperdef{}{ref-Barsh2016}{\label{ref-Barsh2016}}
 44. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
@@
 editors to preprint servers. PLOS Genetics \textbf{12}:e1006448.
-doi:\href{https://doi.org/10.1371/journal.pgen.1006448}{10.1371/journal.pgen.1006448}.
-
-\hypertarget{ref-Hockett2013}{}
+doi:\url{http://doi.org/10.1371/journal.pgen.1006448}.
+
+\hyperdef{}{ref-Hockett2013}{\label{ref-Hockett2013}}
 45. \textbf{Hockett KL}, \textbf{Nishimura MT}, \textbf{Karlsrud E},
@@
 genome architecture and virulence genes in pseudomonas syringae, strain
-cc1557 as a model. bioRxiv 000869.
+cC1557 as a model. bioRxiv 000869.
 

### 2017-04-17 code/get_biorxiv_doi_numbers.R
Fix problems reading JSON at crossref

@@ -1,32 +1,36 @@
 #https://github.com/CrossRef/rest-api-doc/blob/master/rest_api.md
 
-library(rjson)
+library(RJSONIO)
 library(RCurl)
 
 urls <- character()
 cursor <- "*"
-n_articles <- 1000
 
-while(n_articles == 1000){
-	search <- "http://api.crossref.org/prefixes/10.1101/works?rows=1000&filter=from-pub-date:2013-11&cursor="
+n_articles <- 1000
+counter <- n_articles
+
+while(counter == n_articles){
+	search <- paste0("http://api.crossref.org/prefixes/10.1101/works?rows=", n_articles, "&filter=from-pub-date:2013-11&cursor=")
 
 	search_cursor <- paste0(search, cursor)
 
+	page <- getURL(search_cursor)
+	json <- fromJSON(page, unexpected.escape="keep")
 
-	page <- fromJSON(getURL(search_cursor), unexpected.escape="keep")
+	if(json$status == "ok"){
+		cursor <- json$message["next-cursor"]
 
-	if(page$status == "ok"){
-	cursor <- page$message["next-cursor"]
+		articles <- json$message[["items"]]
+		counter <- length(articles)
 
-	articles <- page$message[["items"]]
-	n_articles <- length(articles)
+		urls <- c(urls, unlist(sapply(articles, '[[', 'URL')))
 
-	urls <- c(urls, unlist(sapply(articles, '[[', 'URL')))
-	print(length(urls))
+		print(length(urls))
 
 	} else {
-		n_articles <- 0;
+		counter <- 0;
 	}
+	Sys.sleep(0.5)
 }
 
 biorxiv_urls <- urls[grepl("10.1101\\/\\d{6}", urls)]

### 2017-04-17 submission/Schloss_PrePrints_mBio_2017.Rmd
Remove figure; update word count
Change rjson to RJSONIO

@@
 
-The field of microbiology has experienced significant growth due to transformative advances in technology and the influx of scientists driven by a curiosity to understand how microbes interact with each other and their environment to sustain myriad biochemical processes that are essential for maintaining the Earth.
-With this explosion in scientific output, a significant bottleneck has been the ability to disseminate this new knowledge to peers and the public in a timely manner.
+The field of microbiology has experienced significant growth due to transformative advances in technology and the influx of scientists driven by a curiosity to understand how microbes sustain myriad biochemical processes that maintain the Earth.
+With this explosion in scientific output, a significant bottleneck has been the ability to rapidly disseminate new knowledge to peers and the public.
 Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck.
@@
 ggplot2 (v.`r packageDescription("ggplot2")$Version`), httr (v.`r packageDescription("httr")$Version`), RCurl (v.`r packageDescription("RCurl")$Version`),
-rentrez (v.`r packageDescription("rentrez")$Version`), rjson (v.`r packageDescription("rjson")$Version`), rvest (v.`r packageDescription("rvest")$Version`), sportcolors (v.`r packageDescription("sportcolors")$Version`), and tidyr (v.`r packageDescription("tidyr")$Version`) packages.
+rentrez (v.`r packageDescription("rentrez")$Version`), RJSONIO (v.`r packageDescription("RJSONIO")$Version`), rvest (v.`r packageDescription("rvest")$Version`), sportcolors (v.`r packageDescription("sportcolors")$Version`), and tidyr (v.`r packageDescription("tidyr")$Version`) packages.
 A reproducible version of this manuscript and analysis is available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.

### 2017-04-17 code/aggregate_biorxiv_altmetric_data.R

@@ -1,4 +1,4 @@
-library(rjson)
+library(RJSONIO)
 
 aggregate_alt_data <- function(alt_file){
 	print(alt_file)

### 2017-04-17 code/get_asm_doi_numbers.R

@@ -1,6 +1,6 @@
 #https://github.com/CrossRef/rest-api-doc/blob/master/rest_api.md
 
-library(rjson)
+library(RJSONIO)
 library(RCurl)
 
 urls <- character()

### 2017-04-17 submission/Schloss_PrePrints_mBio_2017.tex

@@
 (v.2.1.0.9001), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
-rjson (v.0.2.15), rvest (v.0.3.2), sportcolors (v.0.0.1), and tidyr
+RJSONIO (v.0.2.15), rvest (v.0.3.2), sportcolors (v.0.0.1), and tidyr
 (v.0.6.0) packages. A reproducible version of this manuscript and

### 2017-04-17 code/aggregate_biorxiv_disqus_data.R
Change file to content

@@ -13,7 +13,7 @@ parse_response <- function(x){
 }
 
 summarize_json <- function(x){
-	json_data <- fromJSON(file=x)$response
+	json_data <- fromJSON(content=x)$response
 	t(sapply(json_data, parse_response))
 }
 

### 2017-04-17 code/aggregate_biorxiv_altmetric_data.R
Update code to use RJSONIO

@@ -10,7 +10,7 @@ aggregate_alt_data <- function(alt_file){
 	if(json_file != "Not Found"){
 		alt_json <- fromJSON(json_file)
 		altmetric <- alt_json$score
-		altmetric_pct <- alt_json$context$all$pct
+		altmetric_pct <- alt_json$context$all["pct"]
 	} else {
 		altmetric <- 0
 		altmetric_pct <- 0

### 2017-04-17 code/get_biorxiv_doi_numbers.R

@@ -1,6 +1,6 @@
 #https://github.com/CrossRef/rest-api-doc/blob/master/rest_api.md
 
-library(RJSONIOIO)
+library(RJSONIO)
 library(RCurl)
 
 urls <- character()

### 2017-04-17 submission/Schloss_PrePrints_mBio_2017.Rmd
Add protist as a microbiology-related search term

@@
 For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories.
-To counter this limitation, I developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, or *pathogen*.
+To counter this limitation, I developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, *pathogen*, or *protist*.
 I identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that I considered microbiology-affiliated.

### 2017-04-17 code/aggregate_asm_altmetric_data.R
Fix problem with altmetric API change

@@ -12,7 +12,7 @@ aggregate_alt_data <- function(alt_file){
 	if(json_file != "Not Found"){
 		alt_json <- fromJSON(json_file)
 		altmetric <- alt_json$score
-		altmetric_pct <- alt_json$context$all$pct
+		altmetric_pct <- alt_json$context$all["pct"]
 		altmetric_pct <- ifelse(is.null(altmetric_pct), NA, altmetric_pct)
 	} else {
 		altmetric <- 0

### 2017-04-17 code/aggregate_biorxiv_data_sources.R
Add new error catch

@@ -23,7 +23,7 @@ collect_data <- function(base_file){
 	#doi
 	doi <- gsub("data/biorxiv/", "10.1101/", base_file)
 
-	if(!grepl("This paper is still processing|DOI Not Found", article_page)){
+	if(!grepl("This paper is still processing|DOI Not Found|TypeError", article_page)){
 
 		metric_page <- read_html(metric_file)
 		info_page <- read_html(info_file)

### 2017-04-18 code/aggregate_biorxiv_data_sources.R
Handle cases where abstracts have been viewed but not the pdf

@@ -23,7 +23,7 @@ collect_data <- function(base_file){
 	#doi
 	doi <- gsub("data/biorxiv/", "10.1101/", base_file)
 
-	if(!grepl("This paper is still processing|DOI Not Found|TypeError", article_page)){
+	if(!grepl("This paper is still processing|DOI Not Found", article_page)){
 
 		metric_page <- read_html(metric_file)
 		info_page <- read_html(info_file)
@@ -151,7 +151,12 @@ collect_data <- function(base_file){
 												.[[1]]
 
 			abstract_downloads <- sum(metric_table[,"Abstract"])
-			pdf_downloads <- sum(metric_table[,"PDF"])
+
+			if("PDF" %in% names(metric_table)){
+				pdf_downloads <- sum(metric_table[,"PDF"])
+			} else {
+				pdf_downloads <- 0
+			}
 		}
 
 

### 2017-04-18 code/aggregate_asm_altmetric_data.R
Use left_join to merge data frames

@@ -27,8 +27,10 @@ alt_listed <- lapply(altmetrics_files, aggregate_alt_data)
 alt_df <- do.call(rbind.data.frame, alt_listed)
 
 date <-read.table(file="data/asm_doi_urls.tsv", header=F, stringsAsFactors=F)
-date$V1 <- gsub("http://dx.doi.org/10.1128/(.*)", "data/asm_altmetric/\\1.json", date$V1)
-stopifnot(altmetrics_files == date$V1)
-alt_df[,"date"] <- date$V2
+colnames(date) <- c("article_id", "date")
+date$article_id <- gsub("http://dx.doi.org/10.1128/(.*)", "\\1", date$article_id)
 
-write.table(alt_df, "data/asm_altmetric/altmetric_summary.tsv", sep='\t', quote=F, row.names=F)
+summary_df <- left_join(alt_df, date, by="article_id")
+
+write.table(summary_df, "data/asm_altmetric/altmetric_summary.tsv", sep='\t', quote=F, row.names=F)
+

### 2017-04-18 code/build_figure1.R
Regenerate figure 1 with updated data

@@ -39,7 +39,8 @@ counts <- biorxiv %>% filter(!is.na(date_first_deposited)) %>%
 				 																			sapply(date_first_deposited, get_quarter))) %>%
 									group_by(year_quarter) %>%
 									summarize(all_n_pp = n(),
-														micro_n_pp = sum(is_microbiology | category =="Microbiology", na.rm=T))
+														micro_n_pp = sum(is_microbiology | category =="Microbiology", na.rm=T)) %>%
+									filter(year_quarter != "2017 2")
 
 tidied <- gather(counts, key=dataset, value=n_pp, all_n_pp, micro_n_pp)
 
@@ -51,10 +52,11 @@ time_course <- ggplot(tidied,
 										) +
 			geom_rect(aes(xmin=-Inf, xmax=1.5, ymin=-Inf, ymax=Inf), fill="#CCCCCC", color="#CCCCCC") +
 			geom_rect(aes(xmin=5.5, xmax=9.5, ymin=-Inf, ymax=Inf), fill="#CCCCCC", color="#CCCCCC") +
+			geom_rect(aes(xmin=13.5, xmax=Inf, ymin=-Inf, ymax=Inf), fill="#CCCCCC", color="#CCCCCC") +
 			geom_line(lineend="round") +
 			labs(x="Year", y="Number of Preprints\nPosted per Quarter") +
 			scale_x_continuous(breaks=c(3.5,7.5,11.5), labels=c("2014", "2015", "2016")) +
-			scale_y_continuous(limits=c(0,1500)) +
+			scale_y_continuous(limits=c(0,2010)) +
 			scale_color_manual(breaks=c("all_n_pp", "micro_n_pp"),
 													labels=c("All preprints", "Microbiology-affiliated"),
 													values=c("#002c5a", "#ffcb0b"), name=NULL)+

### 2017-04-18 submission/rebuttal.md
Format reviewers' comments

**Editor comments:

Overall, the reviewers and I agree that the manuscript is novel, timely, and worth publishing. It is extremely well written, with excellent examples of current and potential applications and outcomes of the use of preprints. With one example, "Arsenic Life" (mentioned kindly), serving as the "poster child" in support of preprints. At the outset, I wondered if he had subjected this paper to the Preprint process (he did) so it includes a "real time" test of the concepts he develops and discusses. The author is to be commended for taking on this study, beyond the call of scientific research papers, and I am sure it will have an impact on thinking about, discussion of, and ultimately the use of preprints in microbial sciences.

Main issues with the manuscript by Reviewer 1 lie primarily with documenting references for many of his assertions. Reviewer 2 comments are very thoughtful, though a bit more philosophical. All points should be considered in a revision, including added citations, and brief additions to the 'history' of preprints. I think an extended discussion of the role of preprints in physics is beyond the scope of this paper. All comments - accepted or not - should be addressed both in a response to reviews with changes to the manuscript noted as well as arguments against changes.**

## Reviewer 1

**1. This is overall an excellent and very useful paper on preprints in one general area (microbiology)

2. I believe the overall analysis is sound and the claims are generally supported by the evidence.

3. There are a few areas of the manuscript that could use modification - mostly just additional detail. I provide line by line comments for any part of the manuscript that I believe could use some modification below.

4. It would be good if all references to web sites include a data when the web site was accessed and in many cases it would be good to include some information from the site as supplemental material. After all, web sites can change and referencing them is tricky. More detail in line by line comments below.

5. The posting of a reproducible version of the analysis in Github is great and I would recommend highlighting this in the text when the analysis is first mentioned.**

**Lines 18 and 19.

"Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues (5)"

I think it would be good to discuss a little bit more the history of preprints and of sharing manuscripts prior to publication. The text here makes it seem like preprint sharing started in the 1960s when I believe this is untrue. The reference cited here appears to focus on organized efforts to share preprints in the 60s (e.g. an attempt by NIH and efforts by the physics community). While important these were not the beginning of preprints and thus the text is a bit inaccurate

In addition, I think it is not quite accurate to say this was a means of "sharing interesting research among colleagues". The efforts in the 60s were attempts to make preprints more broadly available and with less of a bias where some people saw preprints but others did not.

Furthermore, I think there were probably many reasons why people did this including establishing priority and staking out territory (i.e., it was not just about sharing interesting research among colleagues).**

**Line 36

"preprints are typically publicly available in about 24 hours"

Is there data supporting this claim**

**Lines 42-45

"This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations"

Is there a reference for this claim?**

**Lines 48-49

"their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g. Proceedings of the National Academy of Sciences). "

Should this read "to a journal as SOME journals"**

**Lines 53-55.

"Compared to the bioRxiv site, the PeerJ Preprint site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints."

This should include a date of accessing the sites and I would recommend perhaps submit screenshots as supplemental material.**

**Lines 55-57

"With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on bioRxiv."

and

Lines 57-58.

"The only direct submission mechanism for manuscripts submitted at PeerJ Preprint is to the PeerJ journal"

A reference / web link would be useful here. Plus a date when these policies were examined would be helpful. I would recommend including the text of the policies as supplemental material if possible.**

**Lines 68-71.

"A relatively new example of what this might look like is PrePubMed (http://www.prepubmed.org/), which seeks to index preprints from numerous sources. A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org)."

It would be good to include the date of access of these sites and if possible some additional information in supplemental material such as text from the site or screen captures to support the text.**

**Lines 72-73

There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.

Please clarify. Hope from whom?**

**Lines 81-83.

"First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in terrorist activities"

DURC is not just about terrorist activities - it is about any possible misuse of research information.**

**Lines 83-85

"Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research."

I would suggest adding a line here about animal research too and how it is critical that appropriate reviews were done for such research.**

**Lines 89-90

"Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers"

Could you clarify or provide examples of what you mean by policies.**

**Lines 100-101.

"Each take a generally permissive stance towards posting of preprints prior to submission."

Given the following sentences about journal policies changing it would be good to mention how the journal policy was inferred and if possible include references and or web links with dates and such.**

**Line 145-146.

"Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second."

I personally agree with this statement but many in the community do not. This only works if people view preprints as valid publications. There are many examples where peer reviewed papers have been published claiming priority on some novel finding when preprints existed on the topic and where the authors of the peer reviewed paper and sometimes the editors of the journal have stated something akin to "we do not consider preprints valid papers".**

**Lines 160-162.

"Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts."

It would be helpful to reference examples of people expressing such fear if they are available online anywhere.**

**Lines 173-176

"In fact, several funding agencies including the Wellcome Trust and the UK Medical Research Council encouraging fellowship applicants to include preprints in their materials; meanwhile, the NIH is in the process of soliciting input from the scientific community on their role in grant applications."

References / links would be very useful here.**

**Lines 193-195

"Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus."

I think the wording here and in a few other places in the paper is a bit confusing or awkward. Preprints are published too. So I would suggest using some alternative wording to "published" for papers that have gone through peer review vs. preprints for those that have not.**

**Lines 207-214

Discussion of NY Subway metagenomics.

I think an important part of the story has been left out. On February 17, 2015 Chris Mason wrote a long blog post (at the request of this reviewer) for microBEnet about their paper and about some of the challenges in inferring the presence of anthrax in the subway. See
https://www.microbe.net/2015/02/17/the-long-road-from-data-to-wisdom-and-from-dna-to-pathogen/**

**Lines 265-267

"Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback."

Any information you could provide on the relative balance of commenting in other systems (e.g., Twitter, Facebook, Blogs) would be very helpful here. Or perhaps at least refer to the discussion later in the article**

**Lines 301-303

"Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community"

I would love for this to be true. But I am not sure I completely follow the logic of this claim here. Could it not be that the citations for preprints are mostly coming from the authors of those preprints? I know we in my lab cite our preprints quite a bit. Or could it be that a subset of the community cites preprints a lot but others do not?**

## Reviewer #2

**One of the first and most acute causes of culture shock in physicists who have fallen among biologists is the relative role played by preprint servers in the two sciences. The arxiv has been a standard part of physics for years; a place where preliminary results can be displayed, critiqued and refined. In contrast biology preprint servers like biorxiv have only recently begun to attract attention and widespread use. For those who don't yet know about preprints, this perspective is a good introduction.

The MS is very strong on educating the reader about preprints and their advantages for an individual researcher. But less so when it comes to the advantages to the field in general. I think this is important, because the value to the individual and the field are entwined with how preprints are viewed, and the respect in which they are held, and this article is an opportunity to push the dial in the direction of more respect.

Physics and biology are very different enterprises. The position of arxiv in the former is not (only) due to a more open-minded attitude among physicists, but the history of the science and the esteem in which preprints are held. So in a highly competitive field such as Fermi gas microscopy, researchers upload their work as soon as possible and their priority is recognized. Similarly, dense theoretical work can be trialed online in front of a tiny community of peers who can suggest alternatives. These may be extremes/caricatures, but it is true that the important factor is the status of preprints in the community. And while preprints have all the advantages stated in this article, unless their status changes they will remain underused.

In a high status preprint world, as the MS states, publishing on a preprint server does get your paper out and could be seen as 'scooping' competitors. But we are a very long way from that at present. Why cite a preprint that came out well over a year ago, and is accepted but still waiting to see the light of day, when there's an alternative in a glamor journal that came out a few months later? The preprint might get some nice comments on twitter, but nobody is going to see it as having priority.

Also in a high status preprint world, folks would be more likely to comment. At the moment, only a few preprints get many comments, which limits the value of the approach quite a lot. I know the MS says this, but it could say more about it as without this many of the advantages claimed for preprints fall away - so what if you can show your preliminary findings to the world if the world doesn't give you feedback? I suspect it is also true that the numbers of comments are not only down to the inherent interest of the content, but also the profile of the authors. If Nick Loman (for example) puts something on twitter about his preprint, it will get looked at more. Similarly a Very Eminent Scientist* has tried to convince me that the large amount of attention and comments their preprints receive is wholly down to their extraordinary high quality, and has nothing to do with the fact that they are member of the National Academy with a very high profile. Such distortions will never go away, but might be less likely if preprints were consumed with the same interest as 'proper' journals.

So I urge some rewriting to raise these issues -perhaps explicitly recommending that funders mandate that papers should be put up as preprints at the same time they are initially submitted for publication. I have the following specific points I noted as I was reading**

**Line 14 - these other things like blog posts seem interesting, but quite different from preprints. I'd suggest ditching them or making the focus clearer**

**64 repetitions of landscapes fractured etc**

This sentence has been edited to minimize the repetition.

**82 and beyond. Several issues are raised here that are never fully dealt with. The most important is DURC. I think you should say a bit more about how this can be handled responsibly, and the potential for preprints to be subject to minimal review to prevent some of these things.**

**186 Could preprints not attract adversarial comments as well? I am not sure scientists are fully free from the attributes of BTL commentators. What about the possibility of vexatious criticisms? This could be especially true for 'political' topics.**

**249 I wonder if preprints are more common in fields with a high proportion of physics types?**

**286 the public, or other scientists?**

**294 impact factors are 'more traditional' than altmetric, but more 'controversial'? I have to say this made me giggle. I also confess I have no idea how to interpret these scores so this bit was useful to me.**

**301 The comparisons with mBio are really neat, but there is a skew evident in the comparison of the means and median citations. It looks like the majority of preprints get very few citations, but a few get many more. The mBio citations look more normally distributed. Can you say more about this?**

**321 I think this is a bit misleading as review is still needed before publication. Sidestepping is not possible.**

**365 brining? :)**

This has been corrected to "bringing"

### 2017-04-19 submission/response_to_reviewers.md
First pass at responding to reviewers' comments

--- 2017-04-18 submission/rebuttal.md
@@
 All comments - accepted or not - should be addressed both in a response to reviews with changes to the manuscript noted as well as arguments against changes.**
+
+Thank you for the kind comments and useful feedback from the two reviewers.
+I am excited to learn that the manuscript received such a positive reaction.
+You will see my comments in a normal font interleaved with the reviewers' comments in a bold font.
+In addition to responding to the reviewer comments I have made several additional changes to the manuscript.
+First, the original version of the manuscript used preprints that were posted by December 31, 2016.
+The revised manuscript uses those preprints posted prior to April 17, 2017.
+Second, on March 24, 2017, NIH released a notice (NOT-OD-17-050) addressing preprints.
+The previous version of the manuscript intimated that there might be something in the works at NIH and this notice addresses many of those comments.
 
@@
 
+I appreciate the feed back and have done my best to incorporate your comments in the revised manuscript.
+I added a sentence to the end of the Acknowledgements section that citations of  information contained within any webpages was current as of April 19, 2017; I thought it was too clunky and redundant to repeat this accession date repeatedly.
+Regarding the last point, I have added a reference to the paper's GitHub repository to LXXX.
+
 **Lines 18 and 19.
@@
 
+I have modified the text here to make clear that it was the first formal structure (as opposed to people informally sending manuscripts to each other) with the goal of broadly disseminating paper-based preprints.
+I also added a reference to Till (2001), which has a nice overview of predecessors of electronic preprint servers.
+
 **Line 36
@@
 Is there data supporting this claim**
+
+This has been my experience based on posting 7 preprints and is the specific claim made by *bioRxiv*.
+I have added a clause to the beginning of this sentence indicating that these observations are taken from information provided by the *bioRxiv* and *PeerJ Preprints* websites.
 
@@
 
+I have added a link to the *mBio* Instructions to Authors which states the global ASM Policy:
+
+> **Preprint policy.** ASM Journals will consider for publication manuscripts that have been posted in a recognized not-for-profit preprint archive provided that upon acceptance of the manuscript for publication, the author is still able to grant ASM copyright or agree to the terms of an Open Access license and pay the associated fee.
+It is the responsibility of authors to inform the journal at the time of submission if and where their article has been previously posted, and if the manuscript is accepted for publication in an ASM journal, authors are required to update the preprint with a citation to the final published article that includes the DOI along with a link.
+
 **Lines 48-49
@@
 
+This has been clarified since *PNAS* is the only journal I have been able to find with this restriction.
+
 **Lines 53-55.
@@
 This should include a date of accessing the sites and I would recommend perhaps submit screenshots as supplemental material.**
+
+I have added Figures S1 and S2, which provide screenshots of two preprints at the different sites.
 
@@
 
+I have added a sentence to the end of the manuscript indicating that the policies were current as of April 19, 2017.
+I think it would be inappropriate to copy the text of policies as supplemental material since it is not my own work.
+
 **Lines 68-71.
@@
 
+I added a sentence to the end of the Acknowledgements section that citations of  information contained within any webpages was current as of April 19, 2017
+
 **Lines 72-73
@@
 Please clarify. Hope from whom?**
+
+This section has been rewritten in light of the NIH Notice on preprints (NOT-OD-17-050).
 
@@
 
+This has been corrected.
+
 **Lines 83-85
@@
 I would suggest adding a line here about animal research too and how it is critical that appropriate reviews were done for such research.**
+
+A comment about appropriate oversight for all vertebrate research has been added to this sentence.
 
@@
 
+I have clarified this sentence to indicate that I meant that most journals have screening procedures and oversight committees that look for problems relating to ethics, DURC, etc.
+
 **Lines 100-101.
@@
 Given the following sentences about journal policies changing it would be good to mention how the journal policy was inferred and if possible include references and or web links with dates and such.**
+
+Links to two sites that aggregate journal policies are provided at the end of the paragraph.
 
@@
 
+I have added a sentence in this section indicating that it remains to be determined whether the journals that claim to apply "scoop protection" will stand by these policies.
+
 **Lines 160-162.
@@
 
+I have added a citation to the FASEB letter in response to the NIH's RFI regarding the use of preprints.
+
 **Lines 173-176
@@
 References / links would be very useful here.**
+
+This section has been rewritten in light of the NIH Notice on preprints (NOT-OD-17-050).
 
@@
 
+I have edited the manuscript to make this clear.
+I am trying to use the NIH definition of preprints that these are documents that are not final.
+I would take "published" to be "final" and since preprints are interim research products that are "posted".
+I get that this is a nuance that is likely lost on many people.
+I have tried to take the suggested approach of differentiating between what is peer-reviewed and what is not.
+
 **Lines 207-214
@@
 
+The focus of this manuscript and the section in question is on how preprints have been used to help move the scientific record.
+I appreciate Chris Mason's comments on the microBEnet blog, but I have also pointed out his response and correction to the scientific record, which was at least partially motivated by Petit et al's preprint posted on Zenodo.
+
 **Lines 265-267
@@
 Or perhaps at least refer to the discussion later in the article**
+
+I have added a sentence to this section to indicate that although twitter, facebook, and blogs are a mechanism for providing feedback these comments are often lost since they are not directly connected to the preprint.
 
@@
 Or could it be that a subset of the community cites preprints a lot but others do not?**
+
+I have edited this sentence to make it more clear that the metrics I presented indicate that the science presented in preprints are accepted by microbiologists on a level comparable to more traditional publications.
 
@@
 
+This has been edited as suggested.
+
 **64 repetitions of landscapes fractured etc**
@@
 
+I have clarified this point in the second to last sentence of the paragraph (LXXX).
+
 **186 Could preprints not attract adversarial comments as well?
@@
 
+I agree that it may still be adversarial; however, given the public and free nature of preprints, it is far less likely for responses to preprints to be adversarial.
+
 **249 I wonder if preprints are more common in fields with a high proportion of physics types?**
 
+I suspect they are more common among groups of biologists where there is a culture of openness.
+For example, the widespread use of open source software among those in bioinformatics and genomics likely translates to openness in research.
+Unfortunately, I don't have direct data to test this and I think it is probably beyond the scope of the current manuscript.
+
 **286 the public, or other scientists?**
+
+Public. The metric incorporates inclusion in popular media and does not incorporate the peer reviewed literature. I have edited this sentence to make both points more clear.
 
@@
 I also confess I have no idea how to interpret these scores so this bit was useful to me.**
+
+I have edited this sentence to make my intention more clear: "A controversial, yet more traditional metric of impact has been the number of citations an article receives."
 
@@
 
+This is one of the big problems with Journal Impact Factors (JIFs), since they focus on the mean, rather than the median.
+Considering the mean is more sensitive to outliers, it is really an inappropriate metric for citation counts, which are typically zero-inflated and long tailed.
+I have included the means to provide a basis for comparison to JIFs.
+
 **321 I think this is a bit misleading as review is still needed before publication. Sidestepping is not possible.**
+
+I have edited this sentence to make my intent more clear, "we were able to publicize our results prior to lengthy review processes".
 

### 2017-04-19 submission/Schloss_PrePrints_mBio_2017.Rmd
First pass at responding to reviewers' comments

@@
 ---
+
+*published* vs. *peer-reviewed*
 
@@
 micro_aff_author_counts <- sort(table(biorxiv[micro_affiliated, "corr_author"]), decreasing=T)
-
-micro_aff_institutes <- levels(as.factor(biorxiv[micro_affiliated, "affiliation"]))
 
@@
 
-***Background.*** Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public.
-A preprint is an interim research product, such as an unpublished manuscript, made publicly available before going through an official peer-review process [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016].
+***Background.*** A preprint is an interim research product, such as a manuscript draft, that is made publicly available before going through an official peer-review process with the goals of soliciting feedback, accelerating dissemination of results, establishing priority, and publicizing negative results [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016; @NIH_NOTICE].
 Authors can post their manuscript to a preprint server for others to read, share, and comment.
-Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues [@Nature1966].
-While the biological community's commitment to preprints waned, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011].
+Information Exchange Groups were the first formal attempt to disseminate paper-based preprints among physicists and biologists in the 1960s as a formal mechanism of broadly sharing research [@Nature1966; @Till2001].
+While the biological community's commitment to preprints waned by 1967, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011].
 For some physicists and mathematicians, posting a preprint to *arXiv* optionally followed by submission to a peer-reviewed journal has become a standard publication pathway.
@@
 ***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013].
-Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built-in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
+According to information provided on the *bioRxiv* and *PeerJ Preprints* websites both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built-in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
 There are several important differences between the two options.
 First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory.
-This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations.
+This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by not-for-profit organizations (http://mbio.asm.org/site/misc/journal-ita_edi.xhtml#02).
 Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse.
-This can be relevant for authors hoping to submit their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g.
-*Proceedings of the National Academy of Sciences*).
+This can be relevant for authors hoping to submit their work to *Proceedings of the National Academy of Sciences* as they will not consider manuscripts posted as preprints under a CC-BY license.
+The NIH encourages authors to post preprints under the CC-BY or public domain licenses [@NIH_NOTICE].
 The flexibility of the *bioRxiv* licensing empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research results; however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option.
 A cosmetic, but still relevant difference between the two is the layout and feel of the two websites.
-Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints.
+Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints (Figures S1 and S2).
 With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*.
@@
 
-One solution to the fracturing of the preprint landscape would be indexing sites that allow a user to easily search for content across the preprint landscape.
+One solution to the fracturing of the preprint landscape would be indexing sites that allow a user to easily search for content across the various preprint servers.
 Several examples of these efforts already exist and it likely that these interfaces and their ability to span the landscape will improve.
@@
 A relatively new example of what this might look like is PrePubMed (http://www.prepubmed.org/), which seeks to index preprints from numerous sources.
-A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org).
-There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.
+A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org/category/central-service).
 As preprint servers and other content providers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted.
@@
 It is critical that assurances be given that policies are in place to address these issues.
-First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in terrorist activities.
-Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research.
+First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in inappropriate activities.
+Second, for researchers engaging in research that involves human subjects and other vertebrates it is critical that assurances be made that institutional oversight committees have been consulted and have approved of the research.
 Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results.
 Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism or misconduct.
-Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers.
+Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have screening procedures and oversight committees that address these issues that should be easy to implement by preprint servers.
 It is possible that if preprint usage continues to expand, many of these problems may also grow as has been experienced in the expansion of the traditional publishing industry.
@@
 The use of preprints uncouples the communication of the discovery from the relevance of the discovery, which will come later based on peer-review, comments from other scientists at meetings or online, and eventually citations.
-A growing number of scientific societies and journals, including ASM view preprints as citable and as having a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016].
+A growing number of scientific societies and journals, including ASM view preprints as citable and as having a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016]; however, it remains to be determined whether the journals will stand by these policies.
 Some scientists worry that with such protection a researcher can make a claim without valid data to support their claims [@Berg2016].
@@
 Given the length limitations placed on grant proposals by funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data.
-Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts.
+The National Institutes of Health (NIH) recently released a notice clarifying their position on the use of preprints and synthesizing feedback that they received as part of a request for information [@NIH_NOTICE].
+In this notice, the NIH indicated that preprints can be cited anywhere that other research is cited including research plans, bibliographies, biosketches, and progress reports.
+Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts [@FASEB_letter].
 One would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.
-This would be greatly facilitated if funding agencies would include preprints as evidence for research progress, but listed separately from peer-reviewed publications to help review panels in their decisions and to help author substantiate evidence they feel they need to provide.
+This would be greatly facilitated by following the NIH recommendation of using preprints as evidence for research progress, but providing an indication that the preprints are not peer-reviewed publications [@NIH_NOTICE].
+This would help review panels in rendering their decisions and help author substantiate evidence they feel they need to provide.
 
@@
 Regardless, given the propensity for researchers to list manuscripts as being "in preparation" or "in review" on an application or curriculum vitae, listing them instead as preprints that can be reviewed by a committee would significantly enhance an application and a reviewer's ability to judge the application.
-In fact, several funding agencies including the Wellcome Trust and the UK Medical Research Council encouraging fellowship applicants to include preprints in their materials; meanwhile, the NIH is in the process of soliciting input from the scientific community on their role in grant applications.
-Others are mandating that researchers post preprints for all of their work prior to submitting the work to a journal [@Dolgin2016].
+In fact, several funding agencies including the NIH, Wellcome Trust, UK Medical Research Council encouraging fellowship applicants to include preprints in their materials [@NIH_NOTICE].
+Other funding agencies have mandated that researchers post preprints for all of their work prior to submitting the work to a journal [@Dolgin2016].
 
@@
 ***Microbiology anecdotes.*** The peer-review editorial process can be lengthy and adversarial.
-In contrast, preprints represent a rapid and potentially collaborative method for disseminating research.
+Because preprints are public and freely available they represent a rapid and potentially collaborative method for disseminating research.
 Several anecdotes from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints.
@@
 During the recent outbreak, more than 130 Zika virus-related preprints have been posted at *bioRxiv*.
-Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus.
+Any manuscript that was formally published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus.
 In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly.
@@
 
-***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, I downloaded the *bioRxiv* on December 31, 2016.
-I chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,650 available at *PeerJ Preprint*.
+***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, I downloaded the *bioRxiv* on April 17, 2017.
+I chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,911 preprints that were available at *PeerJ Preprint* on the same date.
+The code used to analyze these preprints and the rest of this manuscript are available as a reproducible GitHub repository at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.
 Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category.
@@
 Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
-Although it is not in the tradition of the scientific community to comment publicly online about colleagues’ research results, I am optimistic that this will change given the possibilities of new media, and possibly incentives for open commenting and reviewing could shift the trend.
+In spite of the lack of tradition within the scientific community to comment publicly online about colleagues’ research results, I am optimistic that this will change given the possibilities of new media (e.g.
+Twitter, Facebook, blogs), and possibly incentives for open commenting and reviewing could shift the trend; the advantage of the centralized commenting is that it is easier for the authors and others to integrate the feedback with the preprint.
 Importantly, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints were revised at least once.
@@
 Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall.
-To obtain a measure of a preprint's ability to garner attention and engage the public, I obtained the Altmetric Attention Score for each preprint (**Figure 1B**).
-The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, traditional media, Wikipedia, policy documents, and other sources [@Altmetric].
+To obtain a measure of a preprint's ability to garner attention and engage the general public, I obtained the Altmetric Attention Score for each preprint (**Figure 1B**).
+The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, traditional media, Wikipedia, policy documents, and other sources; it does not include the number of citations [@Altmetric].
 A higher score indicates that a preprint received more attention.
@@
 Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *bioRxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`).
-A more traditional and controversial metric of impact has been the number of citations an article receives.
+A controversial, yet more traditional metric of impact has been the number of citations an article receives.
 I obtained the number of citations for the published versions of manuscripts that were initially posted as preprints.
@@
 For comparison, among the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`).
-Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community.
+Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that the science presented in preprints and the publications that result from them are accepted by the microbiology community at a level comparable to more traditionally presented research.
 
@@
 Since 2015, we have continued to post manuscripts as preprints at the same time as we have submitted manuscripts.
-Although the feedback to other manuscripts has not always been as helpful as our initial experience, in each case we were able to sidestep lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b].
+Although the feedback to other manuscripts has not always been as helpful as our initial experience, in each case we were able to publicize our results prior to lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b].
 As another example, I posted a preprint of the current manuscript to *bioRxiv* on February 22, 2017.
@@
 Preprints can also be viewed as a lost opportunity to journals.
-A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal.
+A preprint that garners significant attention may be ignored when it is finally published, bringing little additional attention to the journal.
 Going forward, there will likely be many innovative approaches that publishers develop to benefit from incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.
@@
 A reproducible version of this manuscript and analysis is available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.
+All journal policies and the information cited using webpage links was current on April 19, 2017.
 
@@
 
+**Supplemental Figure 1. Screen shot of the preprint for this manuscript at bioRxiv.**
+
+**Supplemental Figure 2. Screen shot of a preprint by the author hosted at PeerJ Preprints.**
+
 \newpage

### 2017-04-20 submission/response_to_reviewers.md
Final edits to manuscript

@@
-**Editor comments:
+---
+title: ""
+output:
+  pdf_document:
+    includes:
+      in_header: header.tex
+fontsize: 11pt
+geometry: margin=1.0in
+---
 
-Overall, the reviewers and I agree that the manuscript is novel, timely, and worth publishing.
+## Editor comments:
+
+**Overall, the reviewers and I agree that the manuscript is novel, timely, and worth publishing.
 It is extremely well written, with excellent examples of current and potential applications and outcomes of the use of preprints.
@@
 At the outset, I wondered if he had subjected this paper to the Preprint process (he did) so it includes a "real time" test of the concepts he develops and discusses.
-The author is to be commended for taking on this study, beyond the call of scientific research papers, and I am sure it will have an impact on thinking about, discussion of, and ultimately the use of preprints in microbial sciences.
+The author is to be commended for taking on this study, beyond the call of scientific research papers, and I am sure it will have an impact on thinking about, discussion of, and ultimately the use of preprints in microbial sciences.**
 
-Main issues with the manuscript by Reviewer 1 lie primarily with documenting references for many of his assertions.
+**Main issues with the manuscript by Reviewer 1 lie primarily with documenting references for many of his assertions.
 Reviewer 2 comments are very thoughtful, though a bit more philosophical.
@@
 
-**1. This is overall an excellent and very useful paper on preprints in one general area (microbiology)
+**1. This is overall an excellent and very useful paper on preprints in one general area (microbiology)**
 
-2. I believe the overall analysis is sound and the claims are generally supported by the evidence.
+**2. I believe the overall analysis is sound and the claims are generally supported by the evidence.**
 
-3.
+**3.
 There are a few areas of the manuscript that could use modification - mostly just additional detail.
-I provide line by line comments for any part of the manuscript that I believe could use some modification below.
+I provide line by line comments for any part of the manuscript that I believe could use some modification below.**
 
-4.
+**4.
 It would be good if all references to web sites include a data when the web site was accessed and in many cases it would be good to include some information from the site as supplemental material.
 After all, web sites can change and referencing them is tricky.
-More detail in line by line comments below.
+More detail in line by line comments below.**
 
-5. The posting of a reproducible version of the analysis in Github is great and I would recommend highlighting this in the text when the analysis is first mentioned.**
+**5. The posting of a reproducible version of the analysis in Github is great and I would recommend highlighting this in the text when the analysis is first mentioned.**
 
 I appreciate the feed back and have done my best to incorporate your comments in the revised manuscript.
-I added a sentence to the end of the Acknowledgements section that citations of  information contained within any webpages was current as of April 19, 2017; I thought it was too clunky and redundant to repeat this accession date repeatedly.
-Regarding the last point, I have added a reference to the paper's GitHub repository to LXXX.
+I added a sentence to the end of the Acknowledgements section that citations of  information contained within any webpages was current as of April 21, 2017; I thought it was too clunky and redundant to repeat this accession date repeatedly.
+Regarding the last point, I have added a reference to the paper's GitHub repository to L248.
 
-**Lines 18 and 19.
+**Lines 18 and 19.**
 
-"Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues (5)"
+**"Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues (5)"**
 
-I think it would be good to discuss a little bit more the history of preprints and of sharing manuscripts prior to publication.
+**I think it would be good to discuss a little bit more the history of preprints and of sharing manuscripts prior to publication.
 The text here makes it seem like preprint sharing started in the 1960s when I believe this is untrue.
@@
 an attempt by NIH and efforts by the physics community).
-While important these were not the beginning of preprints and thus the text is a bit inaccurate
+While important these were not the beginning of preprints and thus the text is a bit inaccurate**
 
-In addition, I think it is not quite accurate to say this was a means of "sharing interesting research among colleagues".
-The efforts in the 60s were attempts to make preprints more broadly available and with less of a bias where some people saw preprints but others did not.
+**In addition, I think it is not quite accurate to say this was a means of "sharing interesting research among colleagues".
+The efforts in the 60s were attempts to make preprints more broadly available and with less of a bias where some people saw preprints but others did not.**
 
-Furthermore, I think there were probably many reasons why people did this including establishing priority and staking out territory (i.e., it was not just about sharing interesting research among colleagues).**
+**Furthermore, I think there were probably many reasons why people did this including establishing priority and staking out territory (i.e., it was not just about sharing interesting research among colleagues).**
 
@@
 
-**Line 36
+**Line 36**
 
-"preprints are typically publicly available in about 24 hours"
+**"preprints are typically publicly available in about 24 hours"**
 
-Is there data supporting this claim**
+**Is there data supporting this claim**
 
@@
 
-**Lines 42-45
+**Lines 42-45**
 
-"This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations"
+**"This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations"**
 
-Is there a reference for this claim?**
+**Is there a reference for this claim?**
 
@@
 
-**Lines 48-49
+**Lines 48-49**
 
-"their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g. Proceedings of the National Academy of Sciences). "
+**"their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g. Proceedings of the National Academy of Sciences). "**
 
-Should this read "to a journal as SOME journals"**
+**Should this read "to a journal as SOME journals"**
 
@@
 
-**Lines 53-55.
+**Lines 53-55.**
 
-"Compared to the bioRxiv site, the PeerJ Preprint site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints."
+**"Compared to the bioRxiv site, the PeerJ Preprint site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints."**
 
-This should include a date of accessing the sites and I would recommend perhaps submit screenshots as supplemental material.**
+**This should include a date of accessing the sites and I would recommend perhaps submit screenshots as supplemental material.**
 
@@
 
-**Lines 55-57
+**Lines 55-57**
 
-"With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on bioRxiv."
+**"With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on bioRxiv."**
 
-and
+**and**
 
-Lines 57-58.
+**Lines 57-58.**
 
-"The only direct submission mechanism for manuscripts submitted at PeerJ Preprint is to the PeerJ journal"
+**"The only direct submission mechanism for manuscripts submitted at PeerJ Preprint is to the PeerJ journal"**
 
-A reference / web link would be useful here.
+**A reference / web link would be useful here.
 Plus a date when these policies were examined would be helpful.
@@
 
-I have added a sentence to the end of the manuscript indicating that the policies were current as of April 19, 2017.
+I have added a sentence to the end of the manuscript indicating that the policies were current as of April 21, 2017.
 I think it would be inappropriate to copy the text of policies as supplemental material since it is not my own work.
 
-**Lines 68-71.
+**Lines 68-71.**
 
-"A relatively new example of what this might look like is PrePubMed (http://www.prepubmed.org/), which seeks to index preprints from numerous sources.
-A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org)."
+**"A relatively new example of what this might look like is PrePubMed (http://www.prepubmed.org/), which seeks to index preprints from numerous sources.
+A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org)."**
 
-It would be good to include the date of access of these sites and if possible some additional information in supplemental material such as text from the site or screen captures to support the text.**
+**It would be good to include the date of access of these sites and if possible some additional information in supplemental material such as text from the site or screen captures to support the text.**
 
-I added a sentence to the end of the Acknowledgements section that citations of  information contained within any webpages was current as of April 19, 2017
+I added a sentence to the end of the Acknowledgements section that citations of  information contained within any webpages was current as of April 21, 2017
 
-**Lines 72-73
+**Lines 72-73**
 
-There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.
+**There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.**
 
-Please clarify. Hope from whom?**
+**Please clarify. Hope from whom?**
 
@@
 
-**Lines 81-83.
+**Lines 81-83.**
 
-"First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in terrorist activities"
+**"First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in terrorist activities"**
 
-DURC is not just about terrorist activities - it is about any possible misuse of research information.**
+**DURC is not just about terrorist activities - it is about any possible misuse of research information.**
 
@@
 
-**Lines 83-85
+**Lines 83-85**
 
-"Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research."
+**"Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research."**
 
-I would suggest adding a line here about animal research too and how it is critical that appropriate reviews were done for such research.**
+**I would suggest adding a line here about animal research too and how it is critical that appropriate reviews were done for such research.**
 
@@
 
-**Lines 89-90
+**Lines 89-90**
 
-"Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers"
+**"Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers"**
 
-Could you clarify or provide examples of what you mean by policies.**
+**Could you clarify or provide examples of what you mean by policies.**
 
@@
 
-**Lines 100-101.
+**Lines 100-101.**
 
-"Each take a generally permissive stance towards posting of preprints prior to submission."
+**"Each take a generally permissive stance towards posting of preprints prior to submission."**
 
-Given the following sentences about journal policies changing it would be good to mention how the journal policy was inferred and if possible include references and or web links with dates and such.**
+**Given the following sentences about journal policies changing it would be good to mention how the journal policy was inferred and if possible include references and or web links with dates and such.**
 
-Links to two sites that aggregate journal policies are provided at the end of the paragraph.
+Links to two sites that aggregate journal policies are provided in the sentence that follows this one.
 
-**Line 145-146.
+**Line 145-146.**
 
-"Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second."
+**"Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second."**
 
-I personally agree with this statement but many in the community do not.
+**I personally agree with this statement but many in the community do not.
 This only works if people view preprints as valid publications.
@@
 
-**Lines 160-162.
+**Lines 160-162.**
 
-"Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts."
+**"Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts."**
 
-It would be helpful to reference examples of people expressing such fear if they are available online anywhere.**
+**It would be helpful to reference examples of people expressing such fear if they are available online anywhere.**
 
@@
 
-**Lines 173-176
+**Lines 173-176**
 
-"In fact, several funding agencies including the Wellcome Trust and the UK Medical Research Council encouraging fellowship applicants to include preprints in their materials; meanwhile, the NIH is in the process of soliciting input from the scientific community on their role in grant applications."
+**"In fact, several funding agencies including the Wellcome Trust and the UK Medical Research Council encouraging fellowship applicants to include preprints in their materials; meanwhile, the NIH is in the process of soliciting input from the scientific community on their role in grant applications."**
 
-References / links would be very useful here.**
+**References / links would be very useful here.**
 
@@
 
-**Lines 193-195
+**Lines 193-195**
 
-"Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus."
+**"Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus."**
 
-I think the wording here and in a few other places in the paper is a bit confusing or awkward.
+**I think the wording here and in a few other places in the paper is a bit confusing or awkward.
 Preprints are published too.
@@
 
-**Lines 207-214
+**Lines 207-214**
 
-Discussion of NY Subway metagenomics.
+**Discussion of NY Subway metagenomics.**
 
-I think an important part of the story has been left out.
+**I think an important part of the story has been left out.
 On February 17, 2015 Chris Mason wrote a long blog post (at the request of this reviewer) for microBEnet about their paper and about some of the challenges in inferring the presence of anthrax in the subway.
@@
 
-**Lines 265-267
+**Lines 265-267**
 
-"Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback."
+**"Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback."**
 
-Any information you could provide on the relative balance of commenting in other systems (e.g., Twitter, Facebook, Blogs) would be very helpful here.
+**Any information you could provide on the relative balance of commenting in other systems (e.g., Twitter, Facebook, Blogs) would be very helpful here.
 Or perhaps at least refer to the discussion later in the article**
@@
 
-**Lines 301-303
+**Lines 301-303**
 
-"Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community"
+**"Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community"**
 
-I would love for this to be true.
+**I would love for this to be true.
 But I am not sure I completely follow the logic of this claim here.
@@
 In contrast biology preprint servers like biorxiv have only recently begun to attract attention and widespread use.
-For those who don't yet know about preprints, this perspective is a good introduction.
+For those who don't yet know about preprints, this perspective is a good introduction.**
 
-The MS is very strong on educating the reader about preprints and their advantages for an individual researcher.
+**The MS is very strong on educating the reader about preprints and their advantages for an individual researcher.
 But less so when it comes to the advantages to the field in general.
-I think this is important, because the value to the individual and the field are entwined with how preprints are viewed, and the respect in which they are held, and this article is an opportunity to push the dial in the direction of more respect.
+I think this is important, because the value to the individual and the field are entwined with how preprints are viewed, and the respect in which they are held, and this article is an opportunity to push the dial in the direction of more respect.**
 
-Physics and biology are very different enterprises.
+**Physics and biology are very different enterprises.
 The position of arxiv in the former is not (only) due to a more open-minded attitude among physicists, but the history of the science and the esteem in which preprints are held.
@@
 These may be extremes/caricatures, but it is true that the important factor is the status of preprints in the community.
-And while preprints have all the advantages stated in this article, unless their status changes they will remain underused.
+And while preprints have all the advantages stated in this article, unless their status changes they will remain underused.**
 
-In a high status preprint world, as the MS states, publishing on a preprint server does get your paper out and could be seen as 'scooping' competitors.
+**In a high status preprint world, as the MS states, publishing on a preprint server does get your paper out and could be seen as 'scooping' competitors.
 But we are a very long way from that at present.
 Why cite a preprint that came out well over a year ago, and is accepted but still waiting to see the light of day, when there's an alternative in a glamor journal that came out a few months later?
-The preprint might get some nice comments on twitter, but nobody is going to see it as having priority.
+The preprint might get some nice comments on twitter, but nobody is going to see it as having priority.**
 
-Also in a high status preprint world, folks would be more likely to comment.
+**Also in a high status preprint world, folks would be more likely to comment.
 At the moment, only a few preprints get many comments, which limits the value of the approach quite a lot.
@@
 Similarly a Very Eminent Scientist* has tried to convince me that the large amount of attention and comments their preprints receive is wholly down to their extraordinary high quality, and has nothing to do with the fact that they are member of the National Academy with a very high profile.
-Such distortions will never go away, but might be less likely if preprints were consumed with the same interest as 'proper' journals.
+Such distortions will never go away, but might be less likely if preprints were consumed with the same interest as 'proper' journals.**
 
-So I urge some rewriting to raise these issues -perhaps explicitly recommending that funders mandate that papers should be put up as preprints at the same time they are initially submitted for publication.
+**So I urge some rewriting to raise these issues -perhaps explicitly recommending that funders mandate that papers should be put up as preprints at the same time they are initially submitted for publication.
 I have the following specific points I noted as I was reading**

### 2017-04-20 submission/Schloss_PrePrints_mBio_2017.Rmd
Final edits to manuscript

@@
 ---
-
-*published* vs. *peer-reviewed*
 
@@
 
-\textbf{Number of words:} \textasciitilde5400 plus references, figures, and abstract
+\textbf{Counts:} \textasciitilde5600 words plus 50 references, 1 figure, and a 150 word abstract
 
@@
 Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck.
-Furthermore, posting preprints can help to transparently recruit a more diverse pool of reviewers prior to submitting to a traditional journal.
+Posting preprints can help to transparently recruit a more diverse pool of reviewers prior to submitting to a journal for formal peer-review.
 Although use of preprints is still limited in the biological sciences, early indications are that preprints are a robust tool that can complement and enhance peer-reviewed publications.
@@
 
-***Background.*** A preprint is an interim research product, such as a manuscript draft, that is made publicly available before going through an official peer-review process with the goals of soliciting feedback, accelerating dissemination of results, establishing priority, and publicizing negative results [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016; @NIH_NOTICE].
+***Background.*** A preprint is an interim research product that is made publicly available before going through an official peer-review process with the goals of soliciting feedback, accelerating dissemination of results, establishing priority, and publicizing negative results [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016; @NIH_NOTICE].
 Authors can post their manuscript to a preprint server for others to read, share, and comment.
-Information Exchange Groups were the first formal attempt to disseminate paper-based preprints among physicists and biologists in the 1960s as a formal mechanism of broadly sharing research [@Nature1966; @Till2001].
-While the biological community's commitment to preprints waned by 1967, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011].
+In the 1960s, Information Exchange Groups were the first formal attempt to broadly disseminate paper-based preprints among physicists and biologists [@Nature1966; @Till2001].
+Although the biological community's commitment to preprints waned by 1967, the physics community persisted and eventually adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011].
 For some physicists and mathematicians, posting a preprint to *arXiv* optionally followed by submission to a peer-reviewed journal has become a standard publication pathway.
-Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists.
-Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012].
+Although *arXiv* has hosted a number of computational biology preprints, the server has not drawn widespread attention from biologists.
+Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of science and helping authors reach a wider audience for critique and establishment of priority [@Shuai2012].
 Considering the broadening adoption of preprints among microbiologists, I sought to explore the specific uses of and concerns regarding preprints.
@@
 ***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013].
-According to information provided on the *bioRxiv* and *PeerJ Preprints* websites both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built-in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
+According to information provided on the *bioRxiv* and *PeerJ Preprints* websites and my personal experiences, both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built-in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded.
 There are several important differences between the two options.
 First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory.
-This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by not-for-profit organizations (http://mbio.asm.org/site/misc/journal-ita_edi.xhtml#02).
+This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by not-for-profit organizations [@mBio_ITA].
 Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse.
-This can be relevant for authors hoping to submit their work to *Proceedings of the National Academy of Sciences* as they will not consider manuscripts posted as preprints under a CC-BY license.
+This can be relevant for authors hoping to submit their work to *Proceedings of the National Academy of Sciences* as the journal will not consider manuscripts posted as preprints under a CC-BY license.
 The NIH encourages authors to post preprints under the CC-BY or public domain licenses [@NIH_NOTICE].
 The flexibility of the *bioRxiv* licensing empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research results; however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option.
-A cosmetic, but still relevant difference between the two is the layout and feel of the two websites.
-Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints (Figures S1 and S2).
+A cosmetic, but still relevant difference is the layout and feel of the two websites.
+Compared to the *bioRxiv* site (Figure S1), the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints (Figure S2).
 With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*.
@@
 
-One solution to the fracturing of the preprint landscape would be indexing sites that allow a user to easily search for content across the various preprint servers.
-Several examples of these efforts already exist and it likely that these interfaces and their ability to span the landscape will improve.
+One solution to the fracturing of the preprint landscape would be the creation of indexing sites that allow a user to easily search for content across multiple preprint servers.
+Several examples of these efforts already exist and it is likely that these interfaces and their ability to span the landscape will improve.
 For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not.
-A relatively new example of what this might look like is PrePubMed (http://www.prepubmed.org/), which seeks to index preprints from numerous sources.
-A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org/category/central-service).
-As preprint servers and other content providers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted.
-It is therefore essential to balance the requirements placed on authors for features associated with preprints with the current desirable efficiency of the preprint format.
+A relatively new example of what this might look like is PrePubMed [@PrePubMed], which seeks to index preprints from numerous sources.
+A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences [@ASAPbio].
+As preprint servers and other content providers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product that is nimble and quickly posted.
+It is therefore essential to balance the requirements placed on authors for features associated with preprints with the efficiency of the preprint format.
 
 ***Specific challenges for microbiology.*** Although preprints offer an efficient and novel venue for disseminating microbiology research, there are several considerations that the scientific community and those that oversee preprint servers must consider.
-It is critical that assurances be given that policies are in place to address these issues.
-First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in inappropriate activities.
-Second, for researchers engaging in research that involves human subjects and other vertebrates it is critical that assurances be made that institutional oversight committees have been consulted and have approved of the research.
-Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results.
+It is critical that assurances be given that policies are in place to address these issues and that these policies are made transparent.
+First, attention has to be given to dual use research of concern (DURC) since microbiology-related research could offer insights to individuals seeking to engage in inappropriate activities.
+Second, for researchers engaging in research that involves human subjects and other vertebrates, it is critical that assurances be made that institutional oversight committees have been consulted and have approved of the research.
+Third, there is significant concern regarding researchers disclosing potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results.
 Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism or misconduct.
-Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have screening procedures and oversight committees that address these issues that should be easy to implement by preprint servers.
-It is possible that if preprint usage continues to expand, many of these problems may also grow as has been experienced in the expansion of the traditional publishing industry.
+Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have screening procedures and oversight committees that address these issues.
+Similar efforts need to be implemented by preprint servers.
+As preprint usage continues to expand many of these problems may also grow similar to the experiences within the traditional publishing industry has expanded.
 
@@
 Each take a generally permissive stance towards posting of preprints prior to submission.
+Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated [@PreprintPolicy; @Sherpa].
 Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work.
-Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated [@PreprintPolicy; @Sherpa].
 
@@
 The public dissemination of one's research is a critical component of the scientific method.
-By describing their research, scientists subject their work to formal and informal peer review.
+By describing their research, scientists subject their work to formal and informal peer-review.
 Their research is scrutinized, praised, and probed to identify questions that help seed the next iteration of the scientific method.
@@
 This would be greatly facilitated by following the NIH recommendation of using preprints as evidence for research progress, but providing an indication that the preprints are not peer-reviewed publications [@NIH_NOTICE].
-This would help review panels in rendering their decisions and help author substantiate evidence they feel they need to provide.
+This would help review panels in rendering their decisions and help authors substantiate their preliminary data.
 
@@
 In fact, several funding agencies including the NIH, Wellcome Trust, UK Medical Research Council encouraging fellowship applicants to include preprints in their materials [@NIH_NOTICE].
-Other funding agencies have mandated that researchers post preprints for all of their work prior to submitting the work to a journal [@Dolgin2016].
 
@@
 First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies.
-Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of March 2017 the number of Zika virus-related publications was over 2,000.
-During the recent outbreak, more than 130 Zika virus-related preprints have been posted at *bioRxiv*.
+Prior to the recent Zika virus outbreak there were approximately 50 peer-reviewed publications that touched on the biology and epidemiology of the virus; as of April 2017 the number of Zika virus-related peer-reviewed publications was over 2,300.
+During the recent outbreak, more than 150 Zika virus-related preprints have been posted at *bioRxiv*.
 Any manuscript that was formally published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus.
@@
 Over the last several years there have also been rapid advances in DNA sequencing technologies that have fundamentally changed how microbial science is performed.
-One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 100 preprints describing new MinIon-based methods and results to preprint servers.
+One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 110 preprints describing new MinIon-based methods and results to preprint servers.
 For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.
@@
 Second, preprints have proven useful for rapidly correcting the scientific literature.
-On February 9, 2015, *Cell Systems* posted a study by Afshinnekoo et al.
-online [@Afshinnekoo2015a].
-The study collected and analyzed metagenomic sequence data from the New York City subway system and reported finding *Yersinia pestis* and *Bacillus anthracis*.
+On February 9, 2015, *Cell Systems* published a study that collected and analyzed metagenomic sequence data from the New York City subway system and reported finding *Yersinia pestis* and *Bacillus anthracis* [@Afshinnekoo2015a].
 Because of the focus on these two bioterrorism agents, this study generated a considerable amount of media attention.
@@
 On November 23, 2015 a study by Boothby et al.
-[@Boothby2015] was first published online.
+[@Boothby2015] was published online.
 The authors claimed that 17.5% of its genes came from bacteria, archaea, fungi, plants, and viruses.
 Another group had been analyzing sequence data from a parallel tardigrade genome sequencing project and did not observe the same result.
-A week later, on December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants [@Koutsovoulos2016a]; this analysis would eventually be published online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016 [@Boothby2016; @Koutsovoulos2016b].
-Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016 [@Bemm2016; @Arakawa2016; @Delmont2016].
-These anecdotes underscore the value of having a rapid posting cycle to correcting errors in the scientific literature and that results posted to preprint servers were able to correct the record within weeks of the initial publication while the traditional path took six months in both cases.
+A week later, on December 1, 2015, the second group posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants [@Koutsovoulos2016a]; this analysis would eventually be peer-reviewed and published online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016 [@Boothby2016; @Koutsovoulos2016b].
+Two other analyses of the original data were peer-reviewed and published in May 2016 and a third was posted as a preprint on February 2, 2016 [@Bemm2016; @Arakawa2016; @Delmont2016].
+Both of these anecdotes underscore the value of having a rapid posting cycle to correcting errors in the scientific literature and that results posted to preprint servers were able to correct the record within weeks of the initial publication while the traditional peer-review path took six months in both cases.
 A final notable case where preprints have accelerated the correction of the scientific record was a preprint posted by Bik et al.
-[@Bik2016a] reporting numerous cases of image manipulation in peer reviewed studies.
+[@Bik2016a] reporting numerous cases of image manipulation in peer-reviewed studies.
 This was a case where a journal may have been reluctant to publish the findings because it could have put the journal in a bad light.
-Posting the manuscript as a preprint removed potential conflicts of interests from journals that could have hindered its ability to be published.
-After the preprint was posted on April 20, 2016 it was published in *mBio* on June 7, 2016 [@Bik2016b].
-Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the infamous "Arsenic Life" paper [@WolfeSimon2010] would have been different had they initially been posted as preprints.
+Posting the manuscript as a preprint removed potential conflicts of interests from journals that could have hindered its ability to be formally published in a journal.
+After the preprint was posted on April 20, 2016 it was peer-reviewed and published in *mBio* on June 7, 2016 [@Bik2016b].
+Instead of using preprints to react to published papers that have been through peer-review, it would be interesting to consider how the editorial process for these examples and the infamous "Arsenic Life" paper [@WolfeSimon2010] would have been different had they initially been posted as preprints.
 
@@
 Among the microbiology-affiliated preprints, `r n_micro_aff_ever_commented` (`r 100*n_micro_aff_ever_commented/sum(micro_affiliated, na.rm=T)`%) had been commented on at least once and only `r n_micro_aff_thrice_commented` (`r 100*n_micro_aff_thrice_commented/sum(micro_affiliated, na.rm=T)`%) more than three times using the *bioRxiv*-hosted commenting feature.
-Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
+Although the hosted commenting is only one mechanism for peer-review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback.
 In spite of the lack of tradition within the scientific community to comment publicly online about colleagues’ research results, I am optimistic that this will change given the possibilities of new media (e.g.
-Twitter, Facebook, blogs), and possibly incentives for open commenting and reviewing could shift the trend; the advantage of the centralized commenting is that it is easier for the authors and others to integrate the feedback with the preprint.
-Importantly, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints were revised at least once.
+Twitter, Facebook, blogs); the advantage of the centralized commenting is that it is easier for the authors and others to integrate the feedback with the preprint.
+It is possible that incentives for open commenting and reviewing could shift the trend.
+Importantly, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) microbiology-affiliated preprints were revised at least once.
 Among the preprints posted prior to January 1, 2016, `r 100*n_micro_published/sum(biorxiv$category == "Microbiology", na.rm=T)`% of the Microbiology category preprints, `r 100*n_micro_aff_published/sum(micro_affiliated, na.rm=T)`% of the microbiology-affiliated preprints, and `r 100*n_all_published/nrow(biorxiv)`% of all preprints have been published.
@@
 Using several metrics I sought to quantify the effect that broadly defined microbiology-affiliated preprints have had on the work of others.
-Using the download statistics associated with each preprint, I found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively.
+Using the download statistics associated with each preprint, I found that the median number of times an abstract or PDF had been accessed was `r round(median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T))` (IQR: `r paste(round(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75))), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively.
 These values represent two aspects of posting a preprint.
@@
 Under the traditional peer-review model, an author may need to submit and revise their work multiple times to several journals over a long period before it is finally published.
-In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the editorial process.
+In contrast, an author can post the preprint at the start of the process for others to consume and comment on as it works its way through the peer-review process.
 A first example illustrates the utility of preprints for improving access to research and the quality of its reporting.
@@
 Since 2015, we have continued to post manuscripts as preprints at the same time as we have submitted manuscripts.
-Although the feedback to other manuscripts has not always been as helpful as our initial experience, in each case we were able to publicize our results prior to lengthy review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b].
+Although the feedback to other manuscripts has not always been as helpful as our initial experience, in each case we were able to publicize our results prior to lengthy peer-review processes by immediately making our results available; in one case our preprint was available 7 months ahead of the final published version [@Baxter2016a; @Baxter2016b].
 As another example, I posted a preprint of the current manuscript to *bioRxiv* on February 22, 2017.
@@
 This process engaged 3 commenters on *bioRxiv*, 61 people either tweeted or re-tweeted the preprint on Twitter, 2 people on the manuscript's GitHub repository, 1 person on a blog, and 2 via email.
-Compared to the two or three scientists that typically review a manuscript, this experience engaged a much larger and more diverse community than had I foregone the posting of a preprint.
-Furthermore, the preprint version of this manuscript had an Attention Score of 44, which placed it in the top 5% of all research scored by Altmetric.
+Compared to the two scientists that eventually reviewed the manuscript, the preliminary round of informal peer-review engaged a much larger and more diverse community than had I foregone the posting of a preprint.
+By the time that the final version of the manuscript was submitted on April 21, 2017, the preprint version of this manuscript had an Attention Score of 58, which placed it in the top 5% of all research scored by Altmetric and the abstract and PDF had been accessed 2,152 and 512 times, respectively.
 Although there are concerns regarding the quality of the science posted to a preprint server, I contend that responsible use of preprints as a part of the scientific process can significantly enhance the science.
@@
 
-***Conclusions.*** Since the first microbiology-affiliated preprint was posted on bioRxiv in November 2013 [@Hockett2013], an increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method for disseminating their research prior to peer review.
+***Conclusions.*** Since the first microbiology-affiliated preprint was posted on bioRxiv in November 2013 [@Hockett2013], an increasing number of microbiologists are posting their unpublished work to preprint severs as an efficient method for disseminating their research prior to peer-review.
 A number of critical concerns remain about how widespread their adoption will be, how they will be perceived by traditional journals and other scientists, and whether traditional peer-review will adapt to the new scientific trends and technologies.
@@
 rentrez (v.`r packageDescription("rentrez")$Version`), RJSONIO (v.`r packageDescription("RJSONIO")$Version`), rvest (v.`r packageDescription("rvest")$Version`), sportcolors (v.`r packageDescription("sportcolors")$Version`), and tidyr (v.`r packageDescription("tidyr")$Version`) packages.
-A reproducible version of this manuscript and analysis is available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.
-All journal policies and the information cited using webpage links was current on April 19, 2017.
+All journal policies and the information cited using webpage links was current on April 21, 2017.
 
@@
 **Figure 1.
-Summary of microbiology-affiliated preprints since the creation of** ***bioRxiv.*** The total number of preprints posted for each quarter ending December 31, 2016 has largely tracked the overall submission of preprints to *bioRxiv* (A).
+Summary of microbiology-affiliated preprints since the creation of** ***bioRxiv.*** The total number of preprints posted for each quarter ending March 31, 2017 has largely tracked the overall submission of preprints to *bioRxiv* (A).
 The Altmetric attention scores of preprints posted to *bioRxiv* are similar to those published in *mBio* since November 2013 indicating preprints engender a similar level of attention (B).

### 2017-04-20 submission/Schloss_PrePrints_mBio_2017.tex
Final edits to manuscript

--- 2017-03-14 submission/Schloss_PrePrints_mBio_2017.tex
@@
 
-\textbf{Number of words:} \textasciitilde4500 plus references, figures, and abstract
+\textbf{Counts:} \textasciitilde5600 words plus 50 references, 1 figure, and a 150 word abstract
 
@@
 transformative advances in technology and the influx of scientists
-driven by a curiosity to understand how microbes interact with each
-other and their environment to sustain myriad biochemical processes that
-are essential for maintaining the Earth. With this explosion in
+driven by a curiosity to understand how microbes sustain myriad
+biochemical processes that maintain the Earth. With this explosion in
 scientific output, a significant bottleneck has been the ability to
-disseminate this new knowledge to peers and the public in a timely
-manner. Preprints have emerged as a tool that a growing number of
-microbiologists are using to overcome this bottleneck. Furthermore,
-posting preprints can help to transparently recruit a more diverse pool
-of reviewers prior to submitting to a traditional journal. Although use
-of preprints is still limited in the biological sciences, early
-indications are that preprints are a robust tool that can complement and
-enhance peer-reviewed publications. As publishing moves to embrace
-advances in internet technology, there are many opportunities for
-preprints and peer-reviewed journals to coexist in the same ecosystem.
+rapidly disseminate new knowledge to peers and the public. Preprints
+have emerged as a tool that a growing number of microbiologists are
+using to overcome this bottleneck. Posting preprints can help to
+transparently recruit a more diverse pool of reviewers prior to
+submitting to a journal for formal peer-review. Although use of
+preprints is still limited in the biological sciences, early indications
+are that preprints are a robust tool that can complement and enhance
+peer-reviewed publications. As publishing moves to embrace advances in
+internet technology, there are many opportunities for preprints and
+peer-reviewed journals to coexist in the same ecosystem.
 
@@
 
-\textbf{\emph{Background.}} Many scientists, including microbiologists,
-have begun to use preprints and other online venues such as social
-media, blog posts, and videos as methods to garner attention for their
-research and to engage the public. A preprint is an interim research
-product, such as an unpublished manuscript, made publicly available
-before going through an official peer-review process (1--4). Authors can
-post their manuscript to a preprint server for others to read, share,
-and comment. Preprints were initially adopted among physicists and
-biologists in the 1960s as a method of sharing interesting research
-amongst colleagues (5). While the biological community's commitment to
-preprints waned, the physics community adopted what is now the
+\textbf{\emph{Background.}} A preprint is an interim research product
+that is made publicly available before going through an official
+peer-review process with the goals of soliciting feedback, accelerating
+dissemination of results, establishing priority, and publicizing
+negative results (1--5). Authors can post their manuscript to a preprint
+server for others to read, share, and comment. In the 1960s, Information
+Exchange Groups were the first formal attempt to broadly disseminate
+paper-based preprints among physicists and biologists (6, 7). Although
+the biological community's commitment to preprints waned by 1967, the
+physics community persisted and eventually adopted what is now the
 \emph{arXiv} (pronounced ``archive'') preprint server that was hosted at
 the Los Alamos National Laboratories from 1991 to 1999 and then at
-Cornell University (6). For some physicists and mathematicians, posting
+Cornell University (8). For some physicists and mathematicians, posting
 a preprint to \emph{arXiv} optionally followed by submission to a
@@
 Although \emph{arXiv} has hosted a number of computational biology
-papers, the server has not drawn widespread attention from biologists.
-Among proponents of \emph{arXiv}, preprints have aided in the
-development of research communication by accelerating the release of the
-science and helping it to achieve a wider audience for critique and
-reception (7). Considering the broadening adoption of preprints among
-microbiologists, I sought to explore the specific uses of and concerns
-regarding preprints.
+preprints, the server has not drawn widespread attention from
+biologists. Among proponents of \emph{arXiv}, preprints have aided in
+the development of research communication by accelerating the release of
+science and helping authors reach a wider audience for critique and
+establishment of priority (9). Considering the broadening adoption of
+preprints among microbiologists, I sought to explore the specific uses
+of and concerns regarding preprints.
 
@@
 Preprints}, were launched as preprint servers for biologists that would
-parallel \emph{arXiv} (8). Both platforms offer similar features:
-preprint posting is free; each preprint receives a digital object
-identifier (DOI) that facilitates the ability to cite preprints in other
-scholarly work; if the preprint is ever published, the preprint is
-linked to the published version; the submission process for both options
-is relatively simple allowing authors to upload a PDF version of their
-preprint and supplemental materials; preprints are typically publicly
-available in about 24 hours; they have built-in venues for authors to
-discuss their research with people who leave comments on the manuscript;
-preprints undergo a basic screening process to remove submissions with
-offensive or non-scientific content; and the sites provide article-level
-metrics indicating the number of times an abstract has been accessed or
-the preprint has been downloaded. There are several important
-differences between the two options. First, \emph{PeerJ Prints} is a
-for-profit organization and \emph{bioRxiv} is a non-profit organization
-sponsored by Cold Spring Harbor Laboratory. This difference can be
-meaningful to authors since some journals, including the American
-Society for Microbiology (ASM) Journals, will only accept submissions
-that have been posted on preprint servers hosted by non-profit
-organizations. Second, preprints at \emph{PeerJ Preprints} are posted
-under the Creative Commons Attribution License (CC-BY) and
-\emph{bioRxiv} preprints can be posted under one of four CC-BY licenses
-or with no permission for reuse. This can be relevant for authors hoping
-to submit their work to a journal as journals will not consider
-manuscripts posted as preprints under a CC-BY license (e.g.
-\emph{Proceedings of the National Academy of Sciences}). The flexibility
-of the \emph{bioRxiv} licensing empowers authors to choose the model
-that best suits them, while ensuring the rapid posting of their research
-results; however, it is important to provide clear information to
-authors on the legal and practical tradeoffs of each option. A cosmetic,
-but still relevant difference between the two is the layout and feel of
-the two websites. Compared to the \emph{bioRxiv} site, the \emph{PeerJ
-Preprint} site is more fluid, gives readers the ability to ``follow'' a
-preprint, and provides better access to article keywords and the ability
-to search preprints. With broader acceptance of preprints by traditional
-journals, many journals, including all of the ASM journals, have
-established mechanisms to directly submit manuscripts that are posted as
-preprints on \emph{bioRxiv}. The only direct submission mechanism for
-manuscripts submitted at \emph{PeerJ Preprint} is to the \emph{PeerJ}
-journal. In many ways, preprint servers have taken on the feel of a
-journal. As adoption of this approach expands, it is likely that the
-features of these sites will continue to improve. It is also worth
-noting that numerous other opportunities exist for other forms of
+parallel \emph{arXiv} (10). According to information provided on the
+\emph{bioRxiv} and \emph{PeerJ Preprints} websites and my personal
+experiences, both platforms offer similar features: preprint posting is
+free; each preprint receives a digital object identifier (DOI) that
+facilitates the ability to cite preprints in other scholarly work; if
+the preprint is ever published, the preprint is linked to the published
+version; the submission process for both options is relatively simple
+allowing authors to upload a PDF version of their preprint and
+supplemental materials; preprints are typically publicly available in
+about 24 hours; they have built-in venues for authors to discuss their
+research with people who leave comments on the manuscript; preprints
+undergo a basic screening process to remove submissions with offensive
+or non-scientific content; and the sites provide article-level metrics
+indicating the number of times an abstract has been accessed or the
+preprint has been downloaded. There are several important differences
+between the two options. First, \emph{PeerJ Prints} is a for-profit
+organization and \emph{bioRxiv} is a non-profit organization sponsored
+by Cold Spring Harbor Laboratory. This difference can be meaningful to
+authors since some journals, including the American Society for
+Microbiology (ASM) Journals, will only accept submissions that have been
+posted on preprint servers hosted by not-for-profit organizations (11).
+Second, preprints at \emph{PeerJ Preprints} are posted under the
+Creative Commons Attribution License (CC-BY) and \emph{bioRxiv}
+preprints can be posted under one of four CC-BY licenses or with no
+permission for reuse. This can be relevant for authors hoping to submit
+their work to \emph{Proceedings of the National Academy of Sciences} as
+the journal will not consider manuscripts posted as preprints under a
+CC-BY license. The NIH encourages authors to post preprints under the
+CC-BY or public domain licenses (5). The flexibility of the
+\emph{bioRxiv} licensing empowers authors to choose the model that best
+suits them, while ensuring the rapid posting of their research results;
+however, it is important to provide clear information to authors on the
+legal and practical tradeoffs of each option. A cosmetic, but still
+relevant difference is the layout and feel of the two websites. Compared
+to the \emph{bioRxiv} site (Figure S1), the \emph{PeerJ Preprint} site
+is more fluid, gives readers the ability to ``follow'' a preprint, and
+provides better access to article keywords and the ability to search
+preprints (Figure S2). With broader acceptance of preprints by
+traditional journals, many journals, including all of the ASM journals,
+have established mechanisms to directly submit manuscripts that are
+posted as preprints on \emph{bioRxiv}. The only direct submission
+mechanism for manuscripts submitted at \emph{PeerJ Preprint} is to the
+\emph{PeerJ} journal. In many ways, preprint servers have taken on the
+feel of a journal. As adoption of this approach expands, it is likely
+that the features of these sites will continue to improve. It is also
+worth noting that numerous other opportunities exist for other forms of
 interim research products (e.g.~blog posts, videos, protocols, etc.) to
@@
 
-One solution to the fracturing of the preprint landscape would be
-indexing sites that allow a user to easily search for content across the
-preprint landscape. Several examples of these efforts already exist and
-it likely that these interfaces and their ability to span the landscape
-will improve. For example, although Google Scholar includes preprints
-hosted at \emph{bioRxiv} and \emph{PeerJ Preprints} in their search
-results, PubMed and Web of Science do not. A relatively new example of
-what this might look like is PrePubMed
-(\url{http://www.prepubmed.org/}), which seeks to index preprints from
-numerous sources. A more organized effort is being initiated with
-funding through ASAPbio to create a ``Central Service'' that would
-aggregate preprints in the life sciences (\url{http://asapbio.org}).
-There is also hope that the National Institutes of Health (NIH) will
-renew their interest in indexing preprints as separate research products
-than peer-reviewed publications. As preprint servers and other content
-providers begin to look and act like traditional journals by
-incorporating features and interfaces, it is important to value the
-strength of the preprint - that of an interim research product, nimble
-and quickly posted. It is therefore essential to balance the
-requirements placed on authors for features associated with preprints
-with the current desirable efficiency of the preprint format.
+One solution to the fracturing of the preprint landscape would be the
+creation of indexing sites that allow a user to easily search for
+content across multiple preprint servers. Several examples of these
+efforts already exist and it is likely that these interfaces and their
+ability to span the landscape will improve. For example, although Google
+Scholar includes preprints hosted at \emph{bioRxiv} and \emph{PeerJ
+Preprints} in their search results, PubMed and Web of Science do not. A
+relatively new example of what this might look like is PrePubMed (12),
+which seeks to index preprints from numerous sources. A more organized
+effort is being initiated with funding through ASAPbio to create a
+``Central Service'' that would aggregate preprints in the life sciences
+(13). As preprint servers and other content providers begin to look and
+act like traditional journals by incorporating features and interfaces,
+it is important to value the strength of the preprint - that of an
+interim research product that is nimble and quickly posted. It is
+therefore essential to balance the requirements placed on authors for
+features associated with preprints with the efficiency of the preprint
+format.
 
@@
 that assurances be given that policies are in place to address these
-issues. First, a significant amount of attention has to be given to the
-potential dual use research of concern (DURC) since posted results in
-microbiology research could offer insights to individuals seeking to
-engage in terrorist activities. Second, for researchers engaging in
-research that involves human subjects it is critical that assurances be
-made that institutional review boards have been consulted and have
-approved of the research. Third, there is significant concern regarding
-researchers hiding potential conflicts of interest that could affect a
-project's experimental design, analysis, and interpretation of results.
-Finally, recent expansions in scientific publishing have revealed
-numerous cases of plagiarism or misconduct. Again, while hoping to
-maintain the efficiency of the preprint format, traditional microbiology
-journals have policies for these issues in place that should be easy to
-implement by preprint servers. It is possible that if preprint usage
-continues to expand, many of these problems may also grow as has been
-experienced in the expansion of the traditional publishing industry.
+issues and that these policies are made transparent. First, attention
+has to be given to dual use research of concern (DURC) since
+microbiology-related research could offer insights to individuals
+seeking to engage in inappropriate activities. Second, for researchers
+engaging in research that involves human subjects and other vertebrates,
+it is critical that assurances be made that institutional oversight
+committees have been consulted and have approved of the research. Third,
+there is significant concern regarding researchers disclosing potential
+conflicts of interest that could affect a project's experimental design,
+analysis, and interpretation of results. Finally, recent expansions in
+scientific publishing have revealed numerous cases of plagiarism or
+misconduct. Again, while hoping to maintain the efficiency of the
+preprint format, traditional microbiology journals have screening
+procedures and oversight committees that address these issues. Similar
+efforts need to be implemented by preprint servers. As preprint usage
+continues to expand many of these problems may also grow similar to the
+experiences within the traditional publishing industry has expanded.
 
@@
 as preprints as a stage in disseminating their research was whether it
-constituted prior publication (9). The broad consensus of the
+constituted prior publication (14). The broad consensus of the
 International Committee of Medical Journal Editors and numerous journals
-is that preprints do not constitute prior publication (10). This
+is that preprints do not constitute prior publication (15). This
 consensus is reflected in the current policies of journals that commonly
@@
 and Cell press. Each take a generally permissive stance towards posting
-of preprints prior to submission. Considering the relatively fluid
-nature of many of these policies and the journals' specific policies,
-prospective authors should be aware of the positions taken by the
-journals where they may eventually submit their work. Comprehensive
-lists of journals' attitudes towards preprints are available online and
-are regularly updated (11, 12).
+of preprints prior to submission. Comprehensive lists of journals'
+attitudes towards preprints are available online and are regularly
+updated (16, 17). Considering the relatively fluid nature of many of
+these policies and the journals' specific policies, prospective authors
+should be aware of the positions taken by the journals where they may
+eventually submit their work.
 
@@
 citations in other scientific reports and grant proposals has recently
-been called into question (13). It is important to note that the
+been called into question (18). It is important to note that the
 peer-review process was adapted to the technologies and trends that have
@@
 journals currently use was not developed until the end of the 1800s with
-the advent of typewriters and carbon paper (14). Editorial decisions
+the advent of typewriters and carbon paper (19). Editorial decisions
 were typically made by a single person or a committee (i.e.~the
@@
 specialization and to deal with the large number of manuscript
-submissions (15). Peer-review did not achieve widespread use at many
+submissions (20). Peer-review did not achieve widespread use at many
 journals, including the \emph{Journal of Bacteriology}, until the 1940s
@@
 component of the scientific method. By describing their research,
-scientists subject their work to formal and informal peer review. Their
+scientists subject their work to formal and informal peer-review. Their
 research is scrutinized, praised, and probed to identify questions that
@@
 including ASM view preprints as citable and as having a legitimate claim
-to primacy (1, 16--18). Some scientists worry that with such protection
-a researcher can make a claim without valid data to support their claims
-(3). This is possible; however, it is also the responsibility of the
-scientific community to utilize the peer-review mechanisms that are
-available to comment on those preprints pointing out methodological
-problems or to indicate that they are speaking beyond the data. As
-preprints gain broader adoption, the tension between establishing
-primacy and the completeness of the preprint may test the policies of
-preprint-friendly journals.
+to primacy (1, 21--23); however, it remains to be determined whether the
+journals will stand by these policies. Some scientists worry that with
+such protection a researcher can make a claim without valid data to
+support their claims (3). This is possible; however, it is also the
+responsibility of the scientific community to utilize the peer-review
+mechanisms that are available to comment on those preprints pointing out
+methodological problems or to indicate that they are speaking beyond the
+data. As preprints gain broader adoption, the tension between
+establishing primacy and the completeness of the preprint may test the
+policies of preprint-friendly journals.
 
@@
 research team's competence in an area or to provide preliminary data.
-Some fear that the use of preprints will allow scientists to circumvent
-page limits by posting preliminary manuscripts. One would hope that both
-consumers of preprints and grant proposal reviewers would be able to
-differentiate between someone trying to game the system and someone that
-is using preprints as a mechanism to improve their science. This would
-be greatly facilitated if funding agencies would include preprints as
-evidence for research progress, but listed separately from peer-reviewed
-publications to help review panels in their decisions and to help author
-substantiate evidence they feel they need to provide.
+The National Institutes of Health (NIH) recently released a notice
+clarifying their position on the use of preprints and synthesizing
+feedback that they received as part of a request for information (5). In
+this notice, the NIH indicated that preprints can be cited anywhere that
+other research is cited including research plans, bibliographies,
+biosketches, and progress reports. Some fear that the use of preprints
+will allow scientists to circumvent page limits by posting preliminary
+manuscripts (24). One would hope that both consumers of preprints and
+grant proposal reviewers would be able to differentiate between someone
+trying to game the system and someone that is using preprints as a
+mechanism to improve their science. This would be greatly facilitated by
+following the NIH recommendation of using preprints as evidence for
+research progress, but providing an indication that the preprints are
+not peer-reviewed publications (5). This would help review panels in
+rendering their decisions and help authors substantiate their
+preliminary data.
 
@@
 judge the application. In fact, several funding agencies including the
-Wellcome Trust and the UK Medical Research Council encouraging
-fellowship applicants to include preprints in their materials;
-meanwhile, the NIH is in the process of soliciting input from the
-scientific community on their role in grant applications. Others are
-mandating that researchers post preprints for all of their work prior to
-submitting the work to a journal (19).
+NIH, Wellcome Trust, UK Medical Research Council encouraging fellowship
+applicants to include preprints in their materials (5).
 
@@
 publication goals. Some authors are explicitly stating that a preprint
-will not be submitted to a journal (20). Although these authors may be a
+will not be submitted to a journal (25). Although these authors may be a
 minority of those who post preprints, such an approach may be attractive
@@
 \textbf{\emph{Microbiology anecdotes.}} The peer-review editorial
-process can be lengthy and adversarial. In contrast, preprints represent
-a rapid and potentially collaborative method for disseminating research.
-Several anecdotes from the microbiology literature are emblematic of
-benefits of the rapid release cycle that is inherent in the use of
-preprints.
+process can be lengthy and adversarial. Because preprints are public and
+freely available they represent a rapid and potentially collaborative
+method for disseminating research. Several anecdotes from the
+microbiology literature are emblematic of benefits of the rapid release
+cycle that is inherent in the use of preprints.
 
@@
 for disease outbreaks and new technologies. Prior to the recent Zika
-virus outbreak there were approximately 50 publications that touched on
-the biology and epidemiology of the virus; as of March 2017 the number
-of Zika virus-related publications was over 2,000. During the recent
-outbreak, more than 130 Zika virus-related preprints have been posted at
-\emph{bioRxiv}. Any manuscript that was published went through several
-month delays in releasing information to health care workers, the
-public, and scientists needing to learn new methods to study a
-previously obscure virus. In contrast, those that posted their work as a
-preprint were able to disseminate their methods and results instantly.
-Another interesting use of preprints to disseminate new information
-about Zika virus has been the posting of a preprint describing the Zika
-virus outbreak in the US Virgin Islands that will be continually updated
-as new data and analyses are performed (21). Over the last several years
-there have also been rapid advances in DNA sequencing technologies that
-have fundamentally changed how microbial science is performed. One
-notable technology, the MinIon sequencing platform from Oxford Nanopore,
-has received considerable attention from researchers who have posted
-more than 100 preprints describing new MinIon-based methods and results
-to preprint servers. For such a rapidly developing technology, the
-ability to share and consume methods from other scientists has created a
-feed forward effect where the technology has likely advanced at a faster
-rate than it otherwise would have.
+virus outbreak there were approximately 50 peer-reviewed publications
+that touched on the biology and epidemiology of the virus; as of April
+2017 the number of Zika virus-related peer-reviewed publications was
+over 2,300. During the recent outbreak, more than 150 Zika virus-related
+preprints have been posted at \emph{bioRxiv}. Any manuscript that was
+formally published went through several month delays in releasing
+information to health care workers, the public, and scientists needing
+to learn new methods to study a previously obscure virus. In contrast,
+those that posted their work as a preprint were able to disseminate
+their methods and results instantly. Another interesting use of
+preprints to disseminate new information about Zika virus has been the
+posting of a preprint describing the Zika virus outbreak in the US
+Virgin Islands that will be continually updated as new data and analyses
+are performed (26). Over the last several years there have also been
+rapid advances in DNA sequencing technologies that have fundamentally
+changed how microbial science is performed. One notable technology, the
+MinIon sequencing platform from Oxford Nanopore, has received
+considerable attention from researchers who have posted more than 110
+preprints describing new MinIon-based methods and results to preprint
+servers. For such a rapidly developing technology, the ability to share
+and consume methods from other scientists has created a feed forward
+effect where the technology has likely advanced at a faster rate than it
+otherwise would have.
 
 Second, preprints have proven useful for rapidly correcting the
-scientific literature. On February 9, 2015, \emph{Cell Systems} posted a
-study by Afshinnekoo et al. online (22). The study collected and
-analyzed metagenomic sequence data from the New York City subway system
-and reported finding \emph{Yersinia pestis} and \emph{Bacillus
-anthracis}. Because of the focus on these two bioterrorism agents, this
-study generated a considerable amount of media attention. On April 25,
-2015, Petit et al. (23) posted a preprint to Zenodo demonstrating that
-there was no evidence for \emph{B. anthracis} in the dataset. On July
-29, 2015, a critique was published by \emph{Cell Systems} along with a
-response from the original authors offering a correction to their
-manuscript (24, 25). A second anecdote of using preprints to aid in
-post-publication peer-review surrounds the publishing of a draft
-tardigrade genome in \emph{The Proceedings of the National Academy of
-Sciences}. On November 23, 2015 a study by Boothby et al. (26) was first
-published online. The authors claimed that 17.5\% of its genes came from
-bacteria, archaea, fungi, plants, and viruses. Another group had been
-analyzing sequence data from a parallel tardigrade genome sequencing
-project and did not observe the same result. A week later, on December
-1, 2015, the second group had posted a preprint comparing the two genome
-sequences and demonstrating that the exciting claims of horizontal gene
-transfer were really the product of contaminants (27); this analysis
-would eventually be published online by the original journal on March
-24, 2016 followed by a rebuttal by the original authors on May 31, 2016
-(28, 29). Two other analyses of the original data were published in May
-2016 and a third was posted as a preprint on February 2, 2016 (30--32).
-These anecdotes underscore the value of having a rapid posting cycle to
+scientific literature. On February 9, 2015, \emph{Cell Systems}
+published a study that collected and analyzed metagenomic sequence data
+from the New York City subway system and reported finding \emph{Yersinia
+pestis} and \emph{Bacillus anthracis} (27). Because of the focus on
+these two bioterrorism agents, this study generated a considerable
+amount of media attention. On April 25, 2015, Petit et al. (28) posted a
+preprint to Zenodo demonstrating that there was no evidence for \emph{B.
+anthracis} in the dataset. On July 29, 2015, a critique was published by
+\emph{Cell Systems} along with a response from the original authors
+offering a correction to their manuscript (29, 30). A second anecdote of
+using preprints to aid in post-publication peer-review surrounds the
+publishing of a draft tardigrade genome in \emph{The Proceedings of the
+National Academy of Sciences}. On November 23, 2015 a study by Boothby
+et al. (31) was published online. The authors claimed that 17.5\% of its
+genes came from bacteria, archaea, fungi, plants, and viruses. Another
+group had been analyzing sequence data from a parallel tardigrade genome
+sequencing project and did not observe the same result. A week later, on
+December 1, 2015, the second group posted a preprint comparing the two
+genome sequences and demonstrating that the exciting claims of
+horizontal gene transfer were really the product of contaminants (32);
+this analysis would eventually be peer-reviewed and published online by
+the original journal on March 24, 2016 followed by a rebuttal by the
+original authors on May 31, 2016 (33, 34). Two other analyses of the
+original data were peer-reviewed and published in May 2016 and a third
+was posted as a preprint on February 2, 2016 (35--37). Both of these
+anecdotes underscore the value of having a rapid posting cycle to
 correcting errors in the scientific literature and that results posted
 to preprint servers were able to correct the record within weeks of the
-initial publication while the traditional path took six months in both
-cases. A final notable case where preprints have accelerated the
-correction of the scientific record was a preprint posted by Bik et al.
-(33) reporting numerous cases of image manipulation in peer reviewed
-studies. This was a case where a journal may have been reluctant to
-publish the findings because it could have put the journal in a bad
-light. Posting the manuscript as a preprint removed potential conflicts
-of interests from journals that could have hindered its ability to be
-published. After the preprint was posted on April 20, 2016 it was
-published in \emph{mBio} on June 7, 2016 (34). Instead of using
-preprints to react to published papers that have been through peer
-review, it would be interesting to consider how the editorial process
-for these examples and the infamous ``Arsenic Life'' paper (35) would
-have been different had they initially been posted as preprints.
+initial publication while the traditional peer-review path took six
+months in both cases. A final notable case where preprints have
+accelerated the correction of the scientific record was a preprint
+posted by Bik et al. (38) reporting numerous cases of image manipulation
+in peer-reviewed studies. This was a case where a journal may have been
+reluctant to publish the findings because it could have put the journal
+in a bad light. Posting the manuscript as a preprint removed potential
+conflicts of interests from journals that could have hindered its
+ability to be formally published in a journal. After the preprint was
+posted on April 20, 2016 it was peer-reviewed and published in
+\emph{mBio} on June 7, 2016 (39). Instead of using preprints to react to
+published papers that have been through peer-review, it would be
+interesting to consider how the editorial process for these examples and
+the infamous ``Arsenic Life'' paper (40) would have been different had
+they initially been posted as preprints.
 
 \textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
-analyze the use of preprints, I downloaded the \emph{bioRxiv} on
-December 31, 2016. I chose to analyze \emph{bioRxiv} preprints because
-these preprints are amenable for submission to ASM journals and there
-were 7,434 \emph{bioRxiv} preprints compared to the 2,650 available at
-\emph{PeerJ Preprint}. Among the 7,434 preprints on bioRxiv, 329 were
-assigned by the authors into the Microbiology category. One limitation
-of the \emph{bioRxiv} interface is the inability to assign manuscripts
-to multiple categories or to tag the content of the preprint. For
-example, this manuscript could be assigned to either the Microbiology or
-the Scientific Communication and Education categories. To counter this
-limitation, I developed a more permissive approach that classified
-preprints as being microbiology-affiliated if their title or abstract
-had words containing \emph{yeast}, \emph{fung}, \emph{viral},
-\emph{virus}, \emph{archaea}, \emph{bacteri}, \emph{microb},
-\emph{microorganism}, or \emph{pathogen}. I identified 1,228 additional
-manuscripts that I considered microbiology-affiliated. These
-microbiology-affiliated preprints were primarily assigned to the
-Evolutionary Biology (N=221), Genomics (N=184), or Bioinformatics
-(N=182) categories.
+analyze the use of preprints, I downloaded the \emph{bioRxiv} on April
+17, 2017. I chose to analyze \emph{bioRxiv} preprints because these
+preprints are amenable for submission to ASM journals and there were
+9,780 \emph{bioRxiv} preprints compared to the 2,911 preprints that were
+available at \emph{PeerJ Preprint} on the same date. The code used to
+analyze these preprints and the rest of this manuscript are available as
+a reproducible GitHub repository at
+\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.
+Among the 9,780 preprints on bioRxiv, 483 were assigned by the authors
+into the Microbiology category. One limitation of the \emph{bioRxiv}
+interface is the inability to assign manuscripts to multiple categories
+or to tag the content of the preprint. For example, this manuscript
+could be assigned to either the Microbiology or the Scientific
+Communication and Education categories. To counter this limitation, I
+developed a more permissive approach that classified preprints as being
+microbiology-affiliated if their title or abstract had words containing
+\emph{yeast}, \emph{fung}, \emph{viral}, \emph{virus}, \emph{archaea},
+\emph{bacteri}, \emph{microb}, \emph{microorganism}, \emph{pathogen}, or
+\emph{protist}. I identified 1,617 additional manuscripts that I
+considered microbiology-affiliated. These microbiology-affiliated
+preprints were primarily assigned to the Evolutionary Biology (N=283),
+Bioinformatics (N=237), or Genomics (N=231) categories.
 
@@
 with the format and considerable geographic diversity. Reflecting the
-relative novelty of preprints, 1,132 (86.1\%) corresponding authors who
-submitted a microbiology-affiliated preprint (N=1,314 total) have posted
-a single preprint and 3.6\% have posted 3 or more preprints.
+relative novelty of preprints, 1,484 (85.5\%) corresponding authors who
+submitted a microbiology-affiliated preprint (N=1,735 total) have posted
+a single preprint and 4.6\% have posted 3 or more preprints.
 Corresponding authors that have posted microbiology-affiliated preprints
-are from 60 countries and are primarily affiliated with institutions in
-the United States (50.8\% of microbiology-affiliated preprints), United
-Kingdom (11.9\%), and Germany (4.2\%). As the preprint format matures,
+are from 67 countries and are primarily affiliated with institutions in
+the United States (46.2\% of microbiology-affiliated preprints), United
+Kingdom (12.9\%), and Germany (4.6\%). As the preprint format matures,
 it will be interesting to see whether the fraction of authors that post
@@
 the quality of their work by adding a more formal and public step to the
-scientific process. Among the microbiology-affiliated preprints, 146
-(9.3\%) had been commented on at least once and only 35 (2.2\%) more
+scientific process. Among the microbiology-affiliated preprints, 197
+(9.3\%) had been commented on at least once and only 48 (2.3\%) more
 than three times using the \emph{bioRxiv}-hosted commenting feature.
-Although the hosted commenting is only one mechanism for peer review,
+Although the hosted commenting is only one mechanism for peer-review,
 this result was somewhat disturbing since the preprint model implicitly
-depends on people's willingness to offer others feedback. Although it is
-not in the tradition of the scientific community to comment publicly
-online about colleagues' research results, I am optimistic that this
-will change given the possibilities of new media, and possibly
-incentives for open commenting and reviewing could shift the trend.
-Importantly, authors do appear to be incorporating feedback from
-colleagues or editorial insights from journals as 404 (25.8\%) of
-preprints were revised at least once. Among the preprints posted prior
-to January 1, 2016, 31.6\% of the Microbiology category preprints,
-35.1\% of the microbiology-affiliated preprints, and 33.8\% of all
-preprints have been published. As noted above, not all authors submit
-their preprints to journals. This would indicate that the ``acceptance
-rates'' are actually higher. Regardless, considering that these
-acceptance rates are higher than many peer-reviewed journals
-(e.g.~approximately 20\% at ASM Journals), these results dispel the
-critique that preprints represent overly preliminary research.
+depends on people's willingness to offer others feedback. In spite of
+the lack of tradition within the scientific community to comment
+publicly online about colleagues' research results, I am optimistic that
+this will change given the possibilities of new media (e.g.~Twitter,
+Facebook, blogs); the advantage of the centralized commenting is that it
+is easier for the authors and others to integrate the feedback with the
+preprint. It is possible that incentives for open commenting and
+reviewing could shift the trend. Importantly, authors do appear to be
+incorporating feedback from colleagues or editorial insights from
+journals as 545 (25.9\%) microbiology-affiliated preprints were revised
+at least once. Among the preprints posted prior to January 1, 2016,
+31.3\% of the Microbiology category preprints, 35.6\% of the
+microbiology-affiliated preprints, and 33.6\% of all preprints have been
+published. As noted above, not all authors submit their preprints to
+journals. This would indicate that the ``acceptance rates'' are actually
+higher. Regardless, considering that these acceptance rates are higher
+than many peer-reviewed journals (e.g.~approximately 20\% at ASM
+Journals), these results dispel the critique that preprints represent
+overly preliminary research.
 
@@
 each preprint, I found that the median number of times an abstract or
-PDF had been accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to
-568), respectively. These values represent two aspects of posting a
+PDF had been accessed was 922 (IQR: 601 to 1446) and 301 (IQR: 155 to
+549), respectively. These values represent two aspects of posting a
 preprint. First, they reflect the number of times people were able to
@@
 published behind a paywall. To obtain a measure of a preprint's ability
-to garner attention and engage the public, I obtained the Altmetric
-Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
-Attention Score measures the number of times a preprint or paper is
-mentioned in social media, traditional media, Wikipedia, policy
-documents, and other sources (36). A higher score indicates that a
-preprint received more attention. Microbiology-affiliated preprints have
-had a median Altmetric Attention Score of 7.3 (IQR: 3.2 to 16.3) and
-those of all preprints hosted at \emph{bioRxiv} have had a median score
-of 7.0 (IQR: 3 to 15.6). For comparison, the median Altmetric Attention
-Score for articles published in \emph{mBio} published since 2013 was 4.5
-(IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
-Altmetric Attention Score for preprints posted at \emph{bioRxiv} ranks
-at the 86 percentile (IQR: 66 to 94). A more traditional and
-controversial metric of impact has been the number of citations an
-article receives. I obtained the number of citations for the published
-versions of manuscripts that were initially posted as preprints. To
-allow for a comparison to traditional journals, I considered the
-citations for preprints published in 2014 and 2015 as aggregated by Web
-of Science (\textbf{Figure 1C}). Among the preprints that were published
-and could be found in the Web of Science database, the median number of
-citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, among the
-papers published in \emph{mBio} in 2014 and 2015, the median number of
-citations was 5 (IQR: 2-9; mean: 6.7). Although it is impossible to
+to garner attention and engage the general public, I obtained the
+Altmetric Attention Score for each preprint (\textbf{Figure 1B}). The
+Altmetric Attention Score measures the number of times a preprint or
+paper is mentioned in social media, traditional media, Wikipedia, policy
+documents, and other sources; it does not include the number of
+citations (41). A higher score indicates that a preprint received more
+attention. Microbiology-affiliated preprints have had a median Altmetric
+Attention Score of 7.6 (IQR: 3.2 to 16.6) and those of all preprints
+hosted at \emph{bioRxiv} have had a median score of 7.7 (IQR: 3.1 to
+16.2). For comparison, the median Altmetric Attention Score for articles
+published in \emph{mBio} published since 2013 was 5.0 (IQR: 1.5 to
+14.5). Of all scholarship tracked by Altmetric, the median Altmetric
+Attention Score for preprints posted at \emph{bioRxiv} ranks at the 87
+percentile (IQR: 75 to 94). A controversial, yet more traditional metric
+of impact has been the number of citations an article receives. I
+obtained the number of citations for the published versions of
+manuscripts that were initially posted as preprints. To allow for a
+comparison to traditional journals, I considered the citations for
+preprints published in 2014 and 2015 as aggregated by Web of Science
+(\textbf{Figure 1C}). Among the preprints that were published and could
+be found in the Web of Science database, the median number of citations
+was 9 (IQR: 3-19; mean: 17.1). For comparison, among the papers
+published in \emph{mBio} in 2014 and 2015, the median number of
+citations was 6 (IQR: 3-11; mean: 8.5). Although it is impossible to
 quantify the quality or impact of research with individual metrics, it
-is clear that preprints and the publications that result from them are
-broadly accepted by the microbiology community.
+is clear that the science presented in preprints and the publications
+that result from them are accepted by the microbiology community at a
+level comparable to more traditionally presented research.
 
@@
 post the preprint at the start of the process for others to consume and
-comment on as it works its way through the editorial process. A first
+comment on as it works its way through the peer-review process. A first
 example illustrates the utility of preprints for improving access to
@@
 sequencing 16S rRNA gene sequences using the Pacific Biosciences
-sequencing platform (37). At the same time, we submitted the manuscript
+sequencing platform (42). At the same time, we submitted the manuscript
 for review at \emph{PeerJ}. While the manuscript was under review, we
@@
 academic scientist and Pacific Biosciences. It was eventually published
-by \emph{PeerJ} (38, 39). Since 2015, we have continued to post
+by \emph{PeerJ} (43, 44). Since 2015, we have continued to post
 manuscripts as preprints at the same time as we have submitted
@@
 been as helpful as our initial experience, in each case we were able to
-sidestep lengthy review processes by immediately making our results
-available; in one case our preprint was available 7 months ahead of the
-final published version (40, 41). As another example, I posted a
-preprint of the current manuscript to \emph{bioRxiv} on February 22,
-2017. I then solicited feedback on the manuscript using social media. On
-March 14, 2017 I incorporated the comments and posted a revised preprint
-and submitted the manuscript to \emph{mBio}. During that time, the
-abstract was accessed 189 times and the PDF was accessed 107 times. This
-process engaged 3 commenters on \emph{bioRxiv}, 61 people either tweeted
-or re-tweeted the preprint on Twitter, 2 people on the manuscript's
-GitHub repository, 1 person on a blog, and 2 via email. Compared to the
-two or three scientists that typically review a manuscript, this
-experience engaged a much larger and more diverse community than had I
-foregone the posting of a preprint. Furthermore, the preprint version of
-this manuscript had an Attention Score of 44, which placed it in the top
-5\% of all research scored by Altmetric. Although there are concerns
+publicize our results prior to lengthy peer-review processes by
+immediately making our results available; in one case our preprint was
+available 7 months ahead of the final published version (45, 46). As
+another example, I posted a preprint of the current manuscript to
+\emph{bioRxiv} on February 22, 2017. I then solicited feedback on the
+manuscript using social media. On March 14, 2017 I incorporated the
+comments and posted a revised preprint and submitted the manuscript to
+\emph{mBio}. During that time, the abstract was accessed 189 times and
+the PDF was accessed 107 times. This process engaged 3 commenters on
+\emph{bioRxiv}, 61 people either tweeted or re-tweeted the preprint on
+Twitter, 2 people on the manuscript's GitHub repository, 1 person on a
+blog, and 2 via email. Compared to the two scientists that eventually
+reviewed the manuscript, the preliminary round of informal peer-review
+engaged a much larger and more diverse community than had I foregone the
+posting of a preprint. By the time that the final version of the
+manuscript was submitted on April 21, 2017, the preprint version of this
+manuscript had an Attention Score of 58, which placed it in the top 5\%
+of all research scored by Altmetric and the abstract and PDF had been
+accessed 2,152 and 512 times, respectively. Although there are concerns
 regarding the quality of the science posted to a preprint server, I
@@
 process where an editorial decision is rendered within five days and
-publication in \emph{mSphere} within a month (42). As the mSphereDirect
+publication in \emph{mSphere} within a month (47). As the mSphereDirect
 mechanism evolves and is perhaps adopted by other journals, it will be
@@
 citation of preprints in their other publications and recognize the
-priority of preprints in the literature (16--18). These are policies
+priority of preprints in the literature (21--23). These are policies
 that empower authors and make specific journals more attractive. Other
@@
 \emph{Genome Biology} have publicly stated that they scout preprints for
-this purpose (43, 44). Preprints can also be viewed as a lost
+this purpose (48, 49). Preprints can also be viewed as a lost
 opportunity to journals. A preprint that garners significant attention
-may be ignored when it is finally published, brining little additional
+may be ignored when it is finally published, bringing little additional
 attention to the journal. Going forward, there will likely be many
@@
 \textbf{\emph{Conclusions.}} Since the first microbiology-affiliated
-preprint was posted on bioRxiv in November 2013 (45), an increasing
+preprint was posted on bioRxiv in November 2013 (50), an increasing
 number of microbiologists are posting their unpublished work to preprint
 severs as an efficient method for disseminating their research prior to
-peer review. A number of critical concerns remain about how widespread
+peer-review. A number of critical concerns remain about how widespread
 their adoption will be, how they will be perceived by traditional
@@
 (v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
-rjson (v.0.2.15), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and tidyr
-(v.0.6.0) packages. A reproducible version of this manuscript and
-analysis is available at
-\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.
+RJSONIO (v.1.3-0), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and
+tidyr (v.0.6.0) packages. All journal policies and the information cited
+using webpage links was current on April 21, 2017.
 
 \newpage
-
-\includegraphics[width=3.5in]{../figures/figure1.png}
 
@@
 creation of} \textbf{\emph{bioRxiv.}} The total number of preprints
-posted for each quarter ending December 31, 2016 has largely tracked the
+posted for each quarter ending March 31, 2017 has largely tracked the
 overall submission of preprints to \emph{bioRxiv} (A). The Altmetric
@@
 median number of citations.
+
+\textbf{Supplemental Figure 1. Screen shot of the preprint for this
+manuscript at bioRxiv.}
+
+\textbf{Supplemental Figure 2. Screen shot of a preprint by the author
+hosted at PeerJ Preprints.}
 
@@
 
+\hypertarget{ref-NIH_NOTICE}{}
+5. Reporting preprints and other interim research products.
+\url{https://grants.nih.gov/grants/guide/notice-files/NOT-OD-17-050.html}.
+
 \hypertarget{ref-Nature1966}{}
-5. 1966. Preprints galore. Nature \textbf{211}:897--898.
+6. 1966. Preprints galore. Nature \textbf{211}:897--898.
 doi:\href{https://doi.org/10.1038/211897a0}{10.1038/211897a0}.
 
+\hypertarget{ref-Till2001}{}
+7. \textbf{Till JE}. 2001. Predecessors of preprint servers. Learned
+Publishing \textbf{14}:7--13.
+doi:\href{https://doi.org/10.1087/09531510125100214}{10.1087/09531510125100214}.
+
 \hypertarget{ref-Ginsparg2011}{}
-6. \textbf{Ginsparg P}. 2011. ArXiv at 20. Nature \textbf{476}:145--147.
+8. \textbf{Ginsparg P}. 2011. ArXiv at 20. Nature \textbf{476}:145--147.
 doi:\href{https://doi.org/10.1038/476145a}{10.1038/476145a}.
@@
 \hypertarget{ref-Shuai2012}{}
-7. \textbf{Shuai X}, \textbf{Pepe A}, \textbf{Bollen J}. 2012. How the
+9. \textbf{Shuai X}, \textbf{Pepe A}, \textbf{Bollen J}. 2012. How the
 scientific community reacts to newly submitted preprints: Article
@@
 \hypertarget{ref-Callaway2013}{}
-8. \textbf{Callaway E}. 2013. Biomedical journal and publisher hope to
+10. \textbf{Callaway E}. 2013. Biomedical journal and publisher hope to
 bring preprints to life. Nature Medicine \textbf{19}:512--512.
@@
 
+\hypertarget{ref-mBio_ITA}{}
+11. mBio instructions to authors.
+\url{http://mbio.asm.org/site/misc/journal-ita_edi.xhtml}.
+
+\hypertarget{ref-PrePubMed}{}
+12. PrePubMed. \url{http://www.prepubmed.org}.
+
+\hypertarget{ref-ASAPbio}{}
+13.. \url{http://asapbio.org/feb23}.
+
 \hypertarget{ref-Angell1991}{}
-9. \textbf{Angell M}, \textbf{Kassirer JP}. 1991. The ingelfinger rule
+14. \textbf{Angell M}, \textbf{Kassirer JP}. 1991. The ingelfinger rule
 revisited. New England Journal of Medicine \textbf{325}:1371--1373.
@@
 \hypertarget{ref-ICMJE}{}
-10. Recommendations for the conduct, reporting, editing, and publication
+15. Recommendations for the conduct, reporting, editing, and publication
 of scholarly work in medical journals.
@@
 \hypertarget{ref-PreprintPolicy}{}
-11. List of academic journals by preprint policy.
+16. List of academic journals by preprint policy.
 \url{https://en.wikipedia.org/wiki/List_of_academic_journals_by_preprint_policy}.
@@
 \hypertarget{ref-Sherpa}{}
-12. Publisher copyright policies \& self-archiving.
+17. Publisher copyright policies \& self-archiving.
 \url{http://www.sherpa.ac.uk/romeo/index.php}.
@@
 \hypertarget{ref-Drubin2016}{}
-13. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
+18. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
 articles and why MBoC quickly embraced preprints. Molecular Biology of
@@
 \hypertarget{ref-Spier2002}{}
-14. \textbf{Spier R}. 2002. The history of the peer-review process.
+19. \textbf{Spier R}. 2002. The history of the peer-review process.
 Trends in Biotechnology \textbf{20}:357--358.
@@
 \hypertarget{ref-Burnham1990}{}
-15. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
+20. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
 JAMA: The Journal of the American Medical Association \textbf{263}:1323.
@@
 \hypertarget{ref-Pulverer2016}{}
-16. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
+21. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
 \textbf{35}:2617--2619.
@@
 \hypertarget{ref-Loew2016}{}
-17. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
+22. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
 \textbf{111}:E01--E02.
@@
 \hypertarget{ref-Vale2016}{}
-18. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
+23. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
 the life sciences. eLife \textbf{5}.
@@
 
-\hypertarget{ref-Dolgin2016}{}
-19. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
-Nature.
-doi:\href{https://doi.org/10.1038/nature.2016.21074}{10.1038/nature.2016.21074}.
+\hypertarget{ref-FASEB_letter}{}
+24. Interim research product rfi response from faseb.
+\url{http://www.faseb.org/Portals/2/PDFs/opa/2016/Interim\%20Research\%20Product\%20RFI.pdf}.
 
 \hypertarget{ref-SinghChawla2017}{}
-20. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
+25. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
 Nature.
@@
 \hypertarget{ref-Black2017}{}
-21. \textbf{Black A}, \textbf{Potter B}, \textbf{Dudas G},
+26. \textbf{Black A}, \textbf{Potter B}, \textbf{Dudas G},
 \textbf{Feldstein L}, \textbf{Grubaugh ND}, \textbf{Andersen KG},
@@
 \hypertarget{ref-Afshinnekoo2015a}{}
-22. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
+27. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
 \textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
@@
 \hypertarget{ref-Petit2015}{}
-23. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
+28. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
 \textbf{Read TD}. 2015. Searching for anthrax in the New York City
@@
 \hypertarget{ref-Ackelsberg2015}{}
-24. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
+29. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
 \textbf{Petersen J}, \textbf{Mead P}, \textbf{Schriefer M},
@@
 \hypertarget{ref-Afshinnekoo2015b}{}
-25. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
+30. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
 \textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
@@
 \hypertarget{ref-Boothby2015}{}
-26. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
+31. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
 \textbf{Wang JR}, \textbf{Patanella KA}, \textbf{Nishimura EO},
@@
 \hypertarget{ref-Koutsovoulos2016a}{}
-27. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
+32. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
 \textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
@@
 \hypertarget{ref-Boothby2016}{}
-28. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
+33. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
 al. and arakawa: Identifying foreign genes in independentHypsibius
@@
 \hypertarget{ref-Koutsovoulos2016b}{}
-29. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
+34. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
 \textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
@@
 \hypertarget{ref-Bemm2016}{}
-30. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
+35. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
 \textbf{Förster F}. 2016. Genome of a tardigrade: Horizontal gene
@@
 \hypertarget{ref-Arakawa2016}{}
-31. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
+36. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
 transfer from the draft genome of a tardigrade. Proceedings of the
@@
 \hypertarget{ref-Delmont2016}{}
-32. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
+37. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
 contamination with advanced visualization and analysis practices:
@@
 \hypertarget{ref-Bik2016a}{}
-33. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
+38. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
 prevalence of inappropriate image duplication in biomedical research
@@
 \hypertarget{ref-Bik2016b}{}
-34. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
+39. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
 prevalence of inappropriate image duplication in biomedical research
@@
 \hypertarget{ref-WolfeSimon2010}{}
-35. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
+40. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
 \textbf{Gordon GW}, \textbf{Hoeft SE}, \textbf{Pett-Ridge J},
@@
 \hypertarget{ref-Altmetric}{}
-36. How is the Altmetric Attention Score calculated?
+41. How is the Altmetric Attention Score calculated?
 \url{https://help.altmetric.com/support/solutions/articles/6000060969-how-is-the-altmetric-attention-score-calculated-}.
@@
 \hypertarget{ref-Schloss2015}{}
-37. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
+42. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
 \textbf{Highlander SK}. 2015. Sequencing 16S rRNA gene fragments using
@@
 \hypertarget{ref-Schloss2016a}{}
-38. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
+43. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
 \textbf{Westcott SL}, \textbf{Highlander SK}. 2016. Sequencing 16S rRNA
@@
 \hypertarget{ref-Schloss2016b}{}
-39. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
+44. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
 \textbf{Westcott SL}, \textbf{Highlander SK}. 2016. Sequencing 16S rRNA
@@
 \hypertarget{ref-Baxter2016a}{}
-40. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
+45. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
 \textbf{Ruffin MT}, \textbf{Schloss P}. 2016. DNA from fecal
@@
 \hypertarget{ref-Baxter2016b}{}
-41. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
+46. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
 \textbf{Ruffin MT}, \textbf{Schloss PD}. 2016. DNA from fecal
@@
 \hypertarget{ref-Imperiale2016}{}
-42. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
+47. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
 mSphereDirect: Author-initiated peer review of manuscripts. mSphere
@@
 \hypertarget{ref-Vence2017}{}
-43. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.
+48. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.
 
 \hypertarget{ref-Barsh2016}{}
-44. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
+49. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
 \textbf{Singh ND}, \textbf{Copenhaver GP}. 2016. Bringing PLOS genetics
@@
 \hypertarget{ref-Hockett2013}{}
-45. \textbf{Hockett KL}, \textbf{Nishimura MT}, \textbf{Karlsrud E},
+50. \textbf{Hockett KL}, \textbf{Nishimura MT}, \textbf{Karlsrud E},
 \textbf{Dougherty K}, \textbf{Baltrus DA}. 2013. Interactions between

### 2017-04-21 submission/Schloss_PrePrints_mBio_2017.tex
Render on flux

@@
-\documentclass[11pt,]{article}
+\documentclass[11,]{article}
 \usepackage{lmodern}
@@
 \usepackage[margin=1.0in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdftitle={Preprinting Microbiology},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
+            pdftitle={Preprinting Microbiology},
+            colorlinks=true,
+            citecolor=blue,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
 \setlength{\parindent}{0pt}
 \setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 \setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
 
@@
 \begin{document}
+
 \maketitle
@@
 \newpage
-
 \linenumbers
@@
 interface (API) access to their databases. The workflow utilized
-commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
-Within R I utilized the cowplot (v.0.6.3), dplyr (v.0.5.0), ggplot2
-(v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
-RJSONIO (v.1.3-0), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and
-tidyr (v.0.6.0) packages. All journal policies and the information cited
-using webpage links was current on April 21, 2017.
+commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.3).
+Within R I utilized the cowplot (v.0.7.0), dplyr (v.0.5.0), ggplot2
+(v.2.2.1), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
+RJSONIO (v.1.3-0), rvest (v.0.3.2), sportcolors (v.0.0.1), and tidyr
+(v.0.6.1) packages. All journal policies and the information cited using
+webpage links was current on April 21, 2017.
 
@@
 
-\subsection*{References}\label{references}
-\addcontentsline{toc}{subsection}{References}
-
-\hypertarget{refs}{}
-\hypertarget{ref-Vale2015}{}
+\subsection{References}\label{references}
+
 1. \textbf{Vale RD}. 2015. Accelerating scientific publication in
@@
 \textbf{112}:13439--13446.
-doi:\href{https://doi.org/10.1073/pnas.1511912112}{10.1073/pnas.1511912112}.
-
-\hypertarget{ref-DesjardinsProulx2013}{}
+doi:\href{http://dx.doi.org/10.1073/pnas.1511912112}{10.1073/pnas.1511912112}.
+
 2. \textbf{Desjardins-Proulx P}, \textbf{White EP}, \textbf{Adamson JJ},
@@
 open preprints in biology. PLoS Biology \textbf{11}:e1001563.
-doi:\href{https://doi.org/10.1371/journal.pbio.1001563}{10.1371/journal.pbio.1001563}.
-
-\hypertarget{ref-Berg2016}{}
+doi:\href{http://dx.doi.org/10.1371/journal.pbio.1001563}{10.1371/journal.pbio.1001563}.
+
 3. \textbf{Berg JM}, \textbf{Bhalla N}, \textbf{Bourne PE},
@@
 \textbf{352}:899--901.
-doi:\href{https://doi.org/10.1126/science.aaf9133}{10.1126/science.aaf9133}.
-
-\hypertarget{ref-Bhalla2016}{}
+doi:\href{http://dx.doi.org/10.1126/science.aaf9133}{10.1126/science.aaf9133}.
+
 4. \textbf{Bhalla N}. 2016. Has the time come for preprints in biology?
 Molecular Biology of the Cell \textbf{27}:1185--1187.
-doi:\href{https://doi.org/10.1091/mbc.e16-02-0123}{10.1091/mbc.e16-02-0123}.
-
-\hypertarget{ref-NIH_NOTICE}{}
+doi:\href{http://dx.doi.org/10.1091/mbc.e16-02-0123}{10.1091/mbc.e16-02-0123}.
+
 5. Reporting preprints and other interim research products.
@@
 
-\hypertarget{ref-Nature1966}{}
 6. 1966. Preprints galore. Nature \textbf{211}:897--898.
-doi:\href{https://doi.org/10.1038/211897a0}{10.1038/211897a0}.
-
-\hypertarget{ref-Till2001}{}
+doi:\href{http://dx.doi.org/10.1038/211897a0}{10.1038/211897a0}.
+
 7. \textbf{Till JE}. 2001. Predecessors of preprint servers. Learned
 Publishing \textbf{14}:7--13.
-doi:\href{https://doi.org/10.1087/09531510125100214}{10.1087/09531510125100214}.
-
-\hypertarget{ref-Ginsparg2011}{}
+doi:\href{http://dx.doi.org/10.1087/09531510125100214}{10.1087/09531510125100214}.
+
 8. \textbf{Ginsparg P}. 2011. ArXiv at 20. Nature \textbf{476}:145--147.
-doi:\href{https://doi.org/10.1038/476145a}{10.1038/476145a}.
-
-\hypertarget{ref-Shuai2012}{}
+doi:\href{http://dx.doi.org/10.1038/476145a}{10.1038/476145a}.
+
 9. \textbf{Shuai X}, \textbf{Pepe A}, \textbf{Bollen J}. 2012. How the
@@
 downloads, twitter mentions, and citations. PLoS ONE \textbf{7}:e47523.
-doi:\href{https://doi.org/10.1371/journal.pone.0047523}{10.1371/journal.pone.0047523}.
-
-\hypertarget{ref-Callaway2013}{}
+doi:\href{http://dx.doi.org/10.1371/journal.pone.0047523}{10.1371/journal.pone.0047523}.
+
 10. \textbf{Callaway E}. 2013. Biomedical journal and publisher hope to
 bring preprints to life. Nature Medicine \textbf{19}:512--512.
-doi:\href{https://doi.org/10.1038/nm0513-512}{10.1038/nm0513-512}.
-
-\hypertarget{ref-mBio_ITA}{}
+doi:\href{http://dx.doi.org/10.1038/nm0513-512}{10.1038/nm0513-512}.
+
 11. mBio instructions to authors.
@@
 
-\hypertarget{ref-PrePubMed}{}
 12. PrePubMed. \url{http://www.prepubmed.org}.
 
-\hypertarget{ref-ASAPbio}{}
-13.. \url{http://asapbio.org/feb23}.
-
-\hypertarget{ref-Angell1991}{}
+13. ASAPbio awarded \$1 million from Helmsley Charitable Trust for
+next-generation life sciences preprint infrastructure.
+\url{http://asapbio.org/feb23}.
+
 14. \textbf{Angell M}, \textbf{Kassirer JP}. 1991. The ingelfinger rule
 revisited. New England Journal of Medicine \textbf{325}:1371--1373.
-doi:\href{https://doi.org/10.1056/nejm199111073251910}{10.1056/nejm199111073251910}.
-
-\hypertarget{ref-ICMJE}{}
+doi:\href{http://dx.doi.org/10.1056/nejm199111073251910}{10.1056/nejm199111073251910}.
+
 15. Recommendations for the conduct, reporting, editing, and publication
@@
 
-\hypertarget{ref-PreprintPolicy}{}
 16. List of academic journals by preprint policy.
@@
 
-\hypertarget{ref-Sherpa}{}
 17. Publisher copyright policies \& self-archiving.
@@
 
-\hypertarget{ref-Drubin2016}{}
 18. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
@@
 the Cell \textbf{27}:3181--3182.
-doi:\href{https://doi.org/10.1091/mbc.e16-09-0651}{10.1091/mbc.e16-09-0651}.
-
-\hypertarget{ref-Spier2002}{}
+doi:\href{http://dx.doi.org/10.1091/mbc.e16-09-0651}{10.1091/mbc.e16-09-0651}.
+
 19. \textbf{Spier R}. 2002. The history of the peer-review process.
 Trends in Biotechnology \textbf{20}:357--358.
-doi:\href{https://doi.org/10.1016/s0167-7799(02)01985-6}{10.1016/s0167-7799(02)01985-6}.
-
-\hypertarget{ref-Burnham1990}{}
+doi:\href{http://dx.doi.org/10.1016/s0167-7799(02)01985-6}{10.1016/s0167-7799(02)01985-6}.
+
 20. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
 JAMA: The Journal of the American Medical Association \textbf{263}:1323.
-doi:\href{https://doi.org/10.1001/jama.1990.03440100023003}{10.1001/jama.1990.03440100023003}.
-
-\hypertarget{ref-Pulverer2016}{}
+doi:\href{http://dx.doi.org/10.1001/jama.1990.03440100023003}{10.1001/jama.1990.03440100023003}.
+
 21. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
 \textbf{35}:2617--2619.
-doi:\href{https://doi.org/10.15252/embj.201670030}{10.15252/embj.201670030}.
-
-\hypertarget{ref-Loew2016}{}
+doi:\href{http://dx.doi.org/10.15252/embj.201670030}{10.15252/embj.201670030}.
+
 22. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
 \textbf{111}:E01--E02.
-doi:\href{https://doi.org/10.1016/j.bpj.2016.06.035}{10.1016/j.bpj.2016.06.035}.
-
-\hypertarget{ref-Vale2016}{}
+doi:\href{http://dx.doi.org/10.1016/j.bpj.2016.06.035}{10.1016/j.bpj.2016.06.035}.
+
 23. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
 the life sciences. eLife \textbf{5}.
-doi:\href{https://doi.org/10.7554/elife.16931}{10.7554/elife.16931}.
-
-\hypertarget{ref-FASEB_letter}{}
-24. Interim research product rfi response from faseb.
+doi:\href{http://dx.doi.org/10.7554/elife.16931}{10.7554/elife.16931}.
+
+24. Interim research product rFI response from fASEB.
 \url{http://www.faseb.org/Portals/2/PDFs/opa/2016/Interim\%20Research\%20Product\%20RFI.pdf}.
 
-\hypertarget{ref-SinghChawla2017}{}
 25. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
 Nature.
-doi:\href{https://doi.org/10.1038/nature.2017.21333}{10.1038/nature.2017.21333}.
-
-\hypertarget{ref-Black2017}{}
+doi:\href{http://dx.doi.org/10.1038/nature.2017.21333}{10.1038/nature.2017.21333}.
+
 26. \textbf{Black A}, \textbf{Potter B}, \textbf{Dudas G},
@@
 \textbf{Ellis BR}, \textbf{Ellis EM}, \textbf{Bedford T}. 2017. Genetic
-characterization of the zika virus epidemic in the us virgin islands.
+characterization of the zika virus epidemic in the uS virgin islands.
 bioRxiv 113100.
 
-\hypertarget{ref-Afshinnekoo2015a}{}
 27. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
@@
 \textbf{Nawrin T}, \textbf{Saletore Y}, \textbf{Alexander N},
-\textbf{Vijay P}, \textbf{Hénaff EM}, \textbf{Zumbo P}, \textbf{Walsh
+\textbf{Vijay P}, \textbf{H{é}naff EM}, \textbf{Zumbo P}, \textbf{Walsh
 M}, \textbf{O'Mullan GD}, \textbf{Tighe S}, \textbf{Dudley JT},
@@
 \textbf{1}:72--87.
-doi:\href{https://doi.org/10.1016/j.cels.2015.01.001}{10.1016/j.cels.2015.01.001}.
-
-\hypertarget{ref-Petit2015}{}
+doi:\href{http://dx.doi.org/10.1016/j.cels.2015.01.001}{10.1016/j.cels.2015.01.001}.
+
 28. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
@@
 subway metagenome.
-doi:\href{https://doi.org/10.5281/zenodo.17158}{10.5281/zenodo.17158}.
-
-\hypertarget{ref-Ackelsberg2015}{}
+doi:\href{http://dx.doi.org/10.5281/zenodo.17158}{10.5281/zenodo.17158}.
+
 29. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
@@
 \textbf{1}:4--5.
-doi:\href{https://doi.org/10.1016/j.cels.2015.07.008}{10.1016/j.cels.2015.07.008}.
-
-\hypertarget{ref-Afshinnekoo2015b}{}
+doi:\href{http://dx.doi.org/10.1016/j.cels.2015.07.008}{10.1016/j.cels.2015.07.008}.
+
 30. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
@@
 metagenomic complexity. Cell Systems \textbf{1}:6--7.
-doi:\href{https://doi.org/10.1016/j.cels.2015.07.007}{10.1016/j.cels.2015.07.007}.
-
-\hypertarget{ref-Boothby2015}{}
+doi:\href{http://dx.doi.org/10.1016/j.cels.2015.07.007}{10.1016/j.cels.2015.07.007}.
+
 31. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
@@
 \textbf{112}:15976--15981.
-doi:\href{https://doi.org/10.1073/pnas.1510461112}{10.1073/pnas.1510461112}.
-
-\hypertarget{ref-Koutsovoulos2016a}{}
+doi:\href{http://dx.doi.org/10.1073/pnas.1510461112}{10.1073/pnas.1510461112}.
+
 32. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
@@
 tardigrade hypsibius dujardini. bioRxiv 033464.
-doi:\href{https://doi.org/10.1101/033464}{10.1101/033464}.
-
-\hypertarget{ref-Boothby2016}{}
+doi:\href{http://dx.doi.org/10.1101/033464}{10.1101/033464}.
+
 33. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
@@
 Sciences \textbf{113}:E3058--E3061.
-doi:\href{https://doi.org/10.1073/pnas.1601149113}{10.1073/pnas.1601149113}.
-
-\hypertarget{ref-Koutsovoulos2016b}{}
+doi:\href{http://dx.doi.org/10.1073/pnas.1601149113}{10.1073/pnas.1601149113}.
+
 34. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
@@
 Sciences \textbf{113}:5053--5058.
-doi:\href{https://doi.org/10.1073/pnas.1600338113}{10.1073/pnas.1600338113}.
-
-\hypertarget{ref-Bemm2016}{}
-35. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
+doi:\href{http://dx.doi.org/10.1073/pnas.1600338113}{10.1073/pnas.1600338113}.
+
+35. \textbf{Bemm F}, \textbf{Wei{ß} CL}, \textbf{Schultz J},
 \textbf{Förster F}. 2016. Genome of a tardigrade: Horizontal gene
@@
 of Sciences \textbf{113}:E3054--E3056.
-doi:\href{https://doi.org/10.1073/pnas.1525116113}{10.1073/pnas.1525116113}.
-
-\hypertarget{ref-Arakawa2016}{}
+doi:\href{http://dx.doi.org/10.1073/pnas.1525116113}{10.1073/pnas.1525116113}.
+
 36. \textbf{Arakawa K}. 2016. No evidence for extensive horizontal gene
@@
 National Academy of Sciences \textbf{113}:E3057--E3057.
-doi:\href{https://doi.org/10.1073/pnas.1602711113}{10.1073/pnas.1602711113}.
-
-\hypertarget{ref-Delmont2016}{}
+doi:\href{http://dx.doi.org/10.1073/pnas.1602711113}{10.1073/pnas.1602711113}.
+
 37. \textbf{Delmont TO}, \textbf{Eren AM}. 2016. Identifying
 contamination with advanced visualization and analysis practices:
-Metagenomic approaches for eukaryotic genome assemblies.
-doi:\href{https://doi.org/10.7287/peerj.preprints.1695v1}{10.7287/peerj.preprints.1695v1}.
-
-\hypertarget{ref-Bik2016a}{}
+metagenomic approaches for eukaryotic genome assemblies.
+doi:\href{http://dx.doi.org/10.7287/peerj.preprints.1695v1}{10.7287/peerj.preprints.1695v1}.
+
 38. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
@@
 publications. bioRxiv 049452.
-doi:\href{https://doi.org/10.1101/049452}{10.1101/049452}.
-
-\hypertarget{ref-Bik2016b}{}
+doi:\href{http://dx.doi.org/10.1101/049452}{10.1101/049452}.
+
 39. \textbf{Bik EM}, \textbf{Casadevall A}, \textbf{Fang FC}. 2016. The
@@
 publications. mBio \textbf{7}:e00809--16.
-doi:\href{https://doi.org/10.1128/mbio.00809-16}{10.1128/mbio.00809-16}.
-
-\hypertarget{ref-WolfeSimon2010}{}
+doi:\href{http://dx.doi.org/10.1128/mbio.00809-16}{10.1128/mbio.00809-16}.
+
 40. \textbf{Wolfe-Simon F}, \textbf{Blum JS}, \textbf{Kulp TR},
@@
 \textbf{332}:1163--1166.
-doi:\href{https://doi.org/10.1126/science.1197258}{10.1126/science.1197258}.
-
-\hypertarget{ref-Altmetric}{}
+doi:\href{http://dx.doi.org/10.1126/science.1197258}{10.1126/science.1197258}.
+
 41. How is the Altmetric Attention Score calculated?
@@
 
-\hypertarget{ref-Schloss2015}{}
 42. \textbf{Schloss PD}, \textbf{Westcott SL}, \textbf{Jenior ML},
@@
 the PacBio SMRT DNA sequencing system.
-doi:\href{https://doi.org/10.7287/peerj.preprints.778v1}{10.7287/peerj.preprints.778v1}.
-
-\hypertarget{ref-Schloss2016a}{}
+doi:\href{http://dx.doi.org/10.7287/peerj.preprints.778v1}{10.7287/peerj.preprints.778v1}.
+
 43. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
@@
 gene fragments using the PacBio SMRT DNA sequencing system.
-doi:\href{https://doi.org/10.7287/peerj.preprints.778v2}{10.7287/peerj.preprints.778v2}.
-
-\hypertarget{ref-Schloss2016b}{}
+doi:\href{http://dx.doi.org/10.7287/peerj.preprints.778v2}{10.7287/peerj.preprints.778v2}.
+
 44. \textbf{Schloss PD}, \textbf{Jenior ML}, \textbf{Koumpouras CC},
@@
 \textbf{4}:e1869.
-doi:\href{https://doi.org/10.7717/peerj.1869}{10.7717/peerj.1869}.
-
-\hypertarget{ref-Baxter2016a}{}
+doi:\href{http://dx.doi.org/10.7717/peerj.1869}{10.7717/peerj.1869}.
+
 45. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MA},
@@
 cancer screening. bioRxiv 048389.
-doi:\href{https://doi.org/10.1101/048389}{10.1101/048389}.
-
-\hypertarget{ref-Baxter2016b}{}
+doi:\href{http://dx.doi.org/10.1101/048389}{10.1101/048389}.
+
 46. \textbf{Baxter NT}, \textbf{Koumpouras CC}, \textbf{Rogers MAM},
@@
 using a microbiota-based model. Microbiome \textbf{4}.
-doi:\href{https://doi.org/10.1186/s40168-016-0205-y}{10.1186/s40168-016-0205-y}.
-
-\hypertarget{ref-Imperiale2016}{}
+doi:\href{http://dx.doi.org/10.1186/s40168-016-0205-y}{10.1186/s40168-016-0205-y}.
+
 47. \textbf{Imperiale MJ}, \textbf{Shenk T}, \textbf{Bertuzzi S}. 2016.
@@
 \textbf{1}:e00307--16.
-doi:\href{https://doi.org/10.1128/msphere.00307-16}{10.1128/msphere.00307-16}.
-
-\hypertarget{ref-Vence2017}{}
+doi:\href{http://dx.doi.org/10.1128/msphere.00307-16}{10.1128/msphere.00307-16}.
+
 48. \textbf{Vence T}. 2017. Journals seek out preprints. TheScientist.
 
-\hypertarget{ref-Barsh2016}{}
 49. \textbf{Barsh GS}, \textbf{Bergman CM}, \textbf{Brown CD},
@@
 editors to preprint servers. PLOS Genetics \textbf{12}:e1006448.
-doi:\href{https://doi.org/10.1371/journal.pgen.1006448}{10.1371/journal.pgen.1006448}.
-
-\hypertarget{ref-Hockett2013}{}
+doi:\href{http://dx.doi.org/10.1371/journal.pgen.1006448}{10.1371/journal.pgen.1006448}.
+
 50. \textbf{Hockett KL}, \textbf{Nishimura MT}, \textbf{Karlsrud E},

### 2017-11-20 code/get_biorxiv_doi_numbers.R
Update for November

@@ -12,13 +12,13 @@ counter <- n_articles
 while(counter == n_articles){
 	search <- paste0("http://api.crossref.org/prefixes/10.1101/works?rows=", n_articles, "&filter=from-pub-date:2013-11&cursor=")
 
-	search_cursor <- paste0(search, cursor)
+	search_cursor <- paste0(search, URLencode(cursor, reserved=TRUE))
 
 	page <- getURL(search_cursor)
 	json <- fromJSON(page, unexpected.escape="keep")
 
 	if(json$status == "ok"){
-		cursor <- json$message["next-cursor"]
+		cursor <- json$message[["next-cursor"]]
 
 		articles <- json$message[["items"]]
 		counter <- length(articles)
@@ -26,12 +26,13 @@ while(counter == n_articles){
 		urls <- c(urls, unlist(sapply(articles, '[[', 'URL')))
 
 		print(length(urls))
-
+#		print(search_cursor)
 	} else {
 		counter <- 0;
 	}
-	Sys.sleep(0.5)
+	Sys.sleep(1.0)
 }
 
 biorxiv_urls <- urls[grepl("10.1101\\/\\d{6}", urls)]
 write(biorxiv_urls, "data/biorxiv_doi_urls.tsv")
+

### 2017-11-20 code/wos-amr/lookup_ids.py

@@ -110,16 +110,14 @@ def main():
     # Write the results to a csv file.
     with open(outfile, 'wb') as of:
         writer = csv.writer(of)
-        writer.writerow(('batch', 'id', 'ut', 'doi', 'pmid', 'times cited', 'source'))
-        batch = 0
+        writer.writerow(('id', 'ut', 'doi', 'pmid', 'times cited', 'source'))
         for grp in found:
             for k, item in grp.items():
                 ut = item.get('ut')
                 if ut is not None:
                     ut = "WOS:" + ut
-                writer.writerow([batch, k, ut, item.get('doi', ""), item.get('pmid', ""), item.get('timesCited', '0'),
+                writer.writerow([k, ut, item.get('doi', ""), item.get('pmid', ""), item.get('timesCited', '0'),
                                  item.get('sourceURL', 'N/A')])
-            batch = batch + 1
 
 if __name__ == "__main__":
     main()

### 2017-11-20 code/build_figure1.R
Properly generate Fig 1A

@@ -6,6 +6,9 @@ library(sportcolors)
 
 get_quarter <- function(date){
 
+	date <- gsub("older version \\(", "", date)
+	date <- gsub(" -.*", "", date)
+
 	month <- gsub("(.*) \\d{1,2}, \\d{4}", "\\1", date)
 
 	quarter <- NA
@@ -22,6 +25,15 @@ get_quarter <- function(date){
 	return(quarter)
 }
 
+get_year <- function(date){
+	date <- gsub("older version \\(", "", date)
+	date <- gsub(" -.*", "", date)
+	year <- gsub(".* \\d{1,2}, (\\d{4})", "\\1", date)
+
+	return(year)
+}
+
+
 my_theme <- theme_classic() +
 							theme(legend.title = element_blank(),
 										legend.background = element_blank(),
@@ -34,13 +46,14 @@ my_theme <- theme_classic() +
 biorxiv <- read.table(file="data/processed/biorxiv_data_summary.tsv", header=T, stringsAsFactors=F)
 biorxiv$journal_published_doi <- tolower(gsub("http://dx.doi.org/", "", biorxiv$journal_published_doi))
 
-counts <- biorxiv %>% filter(!is.na(date_first_deposited)) %>%
-									mutate(year_quarter = paste(gsub(".*, ", "", date_first_deposited),
+counts <- biorxiv %>%
+									filter(!is.na(date_first_deposited)) %>%
+									mutate(year_quarter = paste(sapply(date_first_deposited, get_year),
 				 																			sapply(date_first_deposited, get_quarter))) %>%
 									group_by(year_quarter) %>%
 									summarize(all_n_pp = n(),
 														micro_n_pp = sum(is_microbiology | category =="Microbiology", na.rm=T)) %>%
-									filter(year_quarter != "2017 2")
+									filter(year_quarter != "2017 4")
 
 tidied <- gather(counts, key=dataset, value=n_pp, all_n_pp, micro_n_pp)
 
@@ -55,8 +68,8 @@ time_course <- ggplot(tidied,
 			geom_rect(aes(xmin=13.5, xmax=Inf, ymin=-Inf, ymax=Inf), fill="#CCCCCC", color="#CCCCCC") +
 			geom_line(lineend="round") +
 			labs(x="Year", y="Number of Preprints\nPosted per Quarter") +
[…]

### 2017-11-21 submission/Schloss_PrePrints_mBio_2017.tex
Update ASM data

--- 2017-04-20 submission/Schloss_PrePrints_mBio_2017.tex
@@
 preprints are amenable for submission to ASM journals and there were
-9,780 \emph{bioRxiv} preprints compared to the 2,911 preprints that were
-available at \emph{PeerJ Preprint} on the same date. The code used to
-analyze these preprints and the rest of this manuscript are available as
-a reproducible GitHub repository at
+16,740 \emph{bioRxiv} preprints compared to the 2,911 preprints that
+were available at \emph{PeerJ Preprint} on the same date. The code used
+to analyze these preprints and the rest of this manuscript are available
+as a reproducible GitHub repository at
 \url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.
-Among the 9,780 preprints on bioRxiv, 483 were assigned by the authors
+Among the 16,740 preprints on bioRxiv, 936 were assigned by the authors
 into the Microbiology category. One limitation of the \emph{bioRxiv}
@@
 \emph{bacteri}, \emph{microb}, \emph{microorganism}, \emph{pathogen}, or
-\emph{protist}. I identified 1,617 additional manuscripts that I
+\emph{protist}. I identified 2,699 additional manuscripts that I
 considered microbiology-affiliated. These microbiology-affiliated
-preprints were primarily assigned to the Evolutionary Biology (N=283),
-Bioinformatics (N=237), or Genomics (N=231) categories.
+preprints were primarily assigned to the Evolutionary Biology (N=400),
+Bioinformatics (N=353), or Genomics (N=339) categories.
 
@@
 with the format and considerable geographic diversity. Reflecting the
-relative novelty of preprints, 1,484 (85.5\%) corresponding authors who
-submitted a microbiology-affiliated preprint (N=1,735 total) have posted
-a single preprint and 4.6\% have posted 3 or more preprints.
+relative novelty of preprints, 2,445 (84\%) corresponding authors who
+submitted a microbiology-affiliated preprint (N=2,910 total) have posted
+a single preprint and 5.5\% have posted 3 or more preprints.
 Corresponding authors that have posted microbiology-affiliated preprints
-are from 67 countries and are primarily affiliated with institutions in
-the United States (46.2\% of microbiology-affiliated preprints), United
-Kingdom (12.9\%), and Germany (4.6\%). As the preprint format matures,
-it will be interesting to see whether the fraction of authors that post
+are from 66 countries and are primarily affiliated with institutions in
+the United States (49.4\% of microbiology-affiliated preprints), United
+Kingdom (13.7\%), and Germany (4\%). As the preprint format matures, it
+will be interesting to see whether the fraction of authors that post
 multiple preprints increases and whether the geographic diversity
@@
 the quality of their work by adding a more formal and public step to the
-scientific process. Among the microbiology-affiliated preprints, 197
-(9.3\%) had been commented on at least once and only 48 (2.3\%) more
+scientific process. Among the microbiology-affiliated preprints, 313
+(8.6\%) had been commented on at least once and only 58 (1.6\%) more
 than three times using the \emph{bioRxiv}-hosted commenting feature.
@@
 incorporating feedback from colleagues or editorial insights from
-journals as 545 (25.9\%) microbiology-affiliated preprints were revised
+journals as 951 (26.2\%) microbiology-affiliated preprints were revised
 at least once. Among the preprints posted prior to January 1, 2016,
-31.3\% of the Microbiology category preprints, 35.6\% of the
-microbiology-affiliated preprints, and 33.6\% of all preprints have been
+36.0\% of the Microbiology category preprints, 36.7\% of the
+microbiology-affiliated preprints, and 33.9\% of all preprints have been
 published. As noted above, not all authors submit their preprints to
@@
 each preprint, I found that the median number of times an abstract or
-PDF had been accessed was 922 (IQR: 601 to 1446) and 301 (IQR: 155 to
-549), respectively. These values represent two aspects of posting a
-preprint. First, they reflect the number of times people were able to
-access science before it was published. Second, they reflect the number
-of times people were able to access a version of a manuscript that is
+PDF had been accessed was 898 (IQR: 585 to 1428) and 0 (IQR: 0 to 0),
+respectively. These values represent two aspects of posting a preprint.
+First, they reflect the number of times people were able to access
+science before it was published. Second, they reflect the number of
+times people were able to access a version of a manuscript that is
 published behind a paywall. To obtain a measure of a preprint's ability
@@
 attention. Microbiology-affiliated preprints have had a median Altmetric
-Attention Score of 7.6 (IQR: 3.2 to 16.6) and those of all preprints
-hosted at \emph{bioRxiv} have had a median score of 7.7 (IQR: 3.1 to
-16.2). For comparison, the median Altmetric Attention Score for articles
-published in \emph{mBio} published since 2013 was 5.0 (IQR: 1.5 to
-14.5). Of all scholarship tracked by Altmetric, the median Altmetric
-Attention Score for preprints posted at \emph{bioRxiv} ranks at the 87
-percentile (IQR: 75 to 94). A controversial, yet more traditional metric
+Attention Score of 7.7 (IQR: 3.1 to 16.6) and those of all preprints
+hosted at \emph{bioRxiv} have had a median score of 8.1 (IQR: 3.1 to
+16.5). For comparison, the median Altmetric Attention Score for articles
+published in \emph{mBio} published since 2013 was 5.8 (IQR: 1.8 to
+15.5). Of all scholarship tracked by Altmetric, the median Altmetric
+Attention Score for preprints posted at \emph{bioRxiv} ranks at the 86
+percentile (IQR: 74 to 93). A controversial, yet more traditional metric
 of impact has been the number of citations an article receives. I
@@
 be found in the Web of Science database, the median number of citations
-was 9 (IQR: 3-19; mean: 17.1). For comparison, among the papers
+was 14 (IQR: 6-26; mean: 26.7). For comparison, among the papers
 published in \emph{mBio} in 2014 and 2015, the median number of
-citations was 6 (IQR: 3-11; mean: 8.5). Although it is impossible to
+citations was 9 (IQR: 4-16; mean: 12.7). Although it is impossible to
 quantify the quality or impact of research with individual metrics, it
@@
 interface (API) access to their databases. The workflow utilized
-commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
-Within R I utilized the cowplot (v.0.6.3), dplyr (v.0.5.0), ggplot2
-(v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
-RJSONIO (v.1.3-0), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and
-tidyr (v.0.6.0) packages. All journal policies and the information cited
-using webpage links was current on April 21, 2017.
+commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.4.1).
+Within R I utilized the cowplot (v.0.9.1), dplyr (v.0.7.0), ggplot2
+(v.2.2.1), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.1.0),
+RJSONIO (v.1.3-0), rvest (v.0.3.2), sportcolors (v.0.0.1), and tidyr
+(v.0.7.1) packages. All journal policies and the information cited using
+webpage links was current on April 21, 2017.
 
@@
 \hypertarget{ref-ASAPbio}{}
-13.. \url{http://asapbio.org/feb23}.
+13. ASAPbio awarded \$1 million from Helmsley Charitable Trust for
+next-generation life sciences preprint infrastructure.
+\url{http://asapbio.org/feb23}.
 

### 2017-11-21 code/get_asm_doi_numbers.R

@@ -11,13 +11,13 @@ n_articles <- 1000
 while(n_articles == 1000){
 	search <- "http://api.crossref.org/prefixes/10.1128/works?rows=1000&filter=from-pub-date:2010-01&cursor="
 
-	search_cursor <- paste0(search, cursor)
+	search_cursor <- paste0(search, URLencode(cursor, reserved=TRUE))
 
 
 	page <- fromJSON(getURL(search_cursor), unexpected.escape="keep")
 
 	if(page$status == "ok"){
-		cursor <- page$message["next-cursor"]
+		cursor <- page$message[["next-cursor"]]
 
 		articles <- page$message[["items"]]
 		n_articles <- length(articles)
